### 2019-05-20 paper/ref_approach.tex
first version

\documentclass[american,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Reference model in feature selection problems},
            pdfauthor={Federico Pavone, Juho Piironen, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table,dvipsnames]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{soul}
\usepackage{mathtools}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx,pdflscape}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{supertabular}
%\usepackage{booktabs,caption,fixltx2e}
\usepackage{booktabs,fixltx2e}
\usepackage[font={small,it}]{caption}
\usepackage{tcolorbox}
\usepackage{paralist}
\usepackage{multicol}
\setcitestyle{round}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\theoremstyle{definition}
\newtheorem{example}{Example}

\title{Reference model in feature selection problems 
	\vspace{.1in}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner and Aki Vehtari}

    \author{
    Federico Pavone, 
  Juho Piironen,
  Paul-Christian B\"{u}rkner
  and Aki Vehtari\footnote{Helsinki Institute for Information Technology HIIT,
  Department of Computer Science, Aalto University, Finland.}
  }

    \preauthor{\centering\large\emph}
  \postauthor{\par}
    \date{\today}
    \date{\today}
%    \predate{}\postdate{}

\begin{document}
\maketitle
\begin{abstract}
We carry out a comparison of different methods of feature selection using or not what we call a reference model on top of the procedure, that is a model that describes well our data. We measure the performance and the stability of each method using both the standard approach, that simply relies on data, and the reference model one. We include different procedures in the comparison as a selection through high probability density posterior credibility intervals, a selection made by controlling the Q-value and the local false discovery rate. Finally, we include in the comparison also a real world data example. Results show an increased stability and a better performance of the selection in favour of the reference model approach.
\end{abstract}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection. From a full Bayesian perspective, when the goal of the analysis is to do prediction, no selection should be carried out and integration over all parameters uncertainties, i.e. posterior distributions, is the recommended procedure. However, a high dimensional parameter space brings different difficulties as computation burden and overfitting. For such reason different feature selection procedures have been proposed both in the frequentist and Bayesian setting (e.g. see \cite{paper:feature_selection}, \cite{paper:vehtari_ojanen} and \cite{paper:model_selection}). Sometimes the task of the analysis is not prediction, but rather inference on which variables are significantly related to the phenomenon of interest. A common case is microarray data in medicine or biology, where for example for a very large number of genes, expression levels are measured for two sets of patients labeled as \textit{positive} or \textit{negative} to some disease (typically a \textit{small n large p} scenario).  The main goal of the analysis is to spot which subset of these genes is significantly related to the disease in order to perform further experiments. A possible way to proceed is to perform hypothesis testing to assess the significance of each gene, based on some modelling assumptions. \cite{book:efron} refers to this as multiple hypothesis testing problem. Such example could be still considered as feature selection, intended this time as the problem of ``identifying \textit{all} features that are predictive about (that is, statistically related to) the target variable'' \citep{paper:projpred}.

Regardless which kind of selection problem we are trying to solve, we consider examples of the reference model approach all those methods that make use of a full-encompassing model, i.e. the reference one, to carry out the selection. The idea of using a reference model is already present in some works from the 60s as \cite{paper:reference_lindley}. It is also the basis for the projection predictive approach \citep{paper:original_proj, paper:projpred}, from which we have taken the hint of using the reference model as a filter (see Section \ref{reference-model-approach}).

\begin{itemize}
\item add original contribution that are:
\item motivation and example on how the use of a reference model improves the selection (projpred example)
\item a comparison between using a reference model or not in the normal means problem  both with simulated data and the bodyfat data
\end{itemize}

The paper is structured as follows. In Section \ref{reference-model-approach} we introduce the idea of the reference model, its benefits with examples and how we used it as a filter on our data in a very simple way. In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem. Finally, in Section \ref{conclusions} we present our conclusions.

\hypertarget{reference-model-approach}{%
\section{Reference model approach to feature selection}\label{reference-model-approach}}

The reference model approach has his roots in  the $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen} and started to be used in the feature selection context already starting from the 60s with \cite{paper:reference_lindley}. There is not a specific definition of what a reference model is; ideally any full-encompassing model which has a good predictive performance is a candidate reference model. General guidelines on how to devise it are the same about any model in a data analysis context, expect for the fact that no selection is carried out for the reference model. \cite{paper:projpred} showed that through the projection predictive approach the reference model can helps in terms of stability and model size in the selection process. In this Section we aim to give some hints on why this happens and on how we can generally rely on a reference model approach to feature selection with a simple example.

Consider the following data generation mechanism for each statistical unit, already used in \cite{paper:projpred}:
\
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber
\end{alignat}
$f$ is the latent variable of interest of which $Y$ is a noisy observation. The first $k$ covariates are significantly related to the target variable $Y$ and correlated among themselves. Precisely $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$. Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distribution, we observe that using a reference model the two group of features, i.e. relevant and non-relevant, have a minor overlap with respect to when the correlation is computed using directly the observed data. Therefore the significance of each covariate is more clearly described when those are compared to a less noisy representation of the true phenomenon of interest, that is the prediction done by a reference model.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
  \caption{Sample correlation plot of each feature (relevant in red, non-relevant in blue) with the target variable $y$ and the latent variable $f$ respectively on the x and y axis. Simulation parameters: $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
  \label{fig:correlation}
\end{figure}

What is shown in Figure \ref{fig:correlation} is related also to the projection predictive approach. In case of a submodel belonging to the generalised linear model family, it happens that the draw-by-draw projection coincide with the maximum likelihood estimator with observed data substituted with reference model's predictions \citep{paper:projpred}. It is possible to see the idea of the reference model as a filter on our data also from the projection of the predictive distribution itself. Let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions. The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
\
\begin{equation} 
\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
\end{equation}
Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
\
\begin{equation} 
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
\end{equation}
where $p_{t}$ is the distribution of a new observation under the true data generation mechanism. Maximising the elpd of a model is equivalent to minimising the KL-divergence of its predictive distribution from the true data generation mechanism. Therefore the projection corresponds to maximising the elpd using as distribution of the true data generation mechanism the posterior predictive distribution of the reference model, i.e.:
\
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y} 
\end{equation}
Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e. the reference model posterior predictive distribution.

A simple, but effective, reference model approach that can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g. posterior predictive mean. Afterwards any method for feature selection can be used. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

\hypertarget{projection}{%
\subsection{Benefits of the reference model: an example with the projection predictive approach}\label{projection}}
\begin{itemize}
\item correct bootstrap results for projpred --> 1000 bootstrap samples 
\item thus correct the comment on the table and on the barplot!!!!
\end{itemize}

The projection predictive approach uses the reference model to project the posterior samples in the submodels. The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and additionally provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model. When the goal is prediction, the choice is usually on the smallest submodel that is sufficiently close to the reference model prediction utility score. Further details on the projection predictive approach can be found in \cite{paper:projpred}.

We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{paper:bodyfat_johnson}. The analysis is mainly taken from Vehtari's R-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, adjusting only the number of bootstrap repetitions to 1000 to have a consistent comparison with results from \cite{paper:bodyfat}. The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure, and the original covariates are 13 anthropometric measurements (e.g. height, weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection, for a total of 251 observations. The goal is to find the simplest model which is able to describe, that is to predict, sufficiently well the amount of fat.

\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection fixing abdomen and height to be always included in the model. We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search, the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. In order to automatise the procedure, we select the submodel size as the smallest which has an elpd score higher than the reference model with probability 0.05. Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection. The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), while the stepwise regression has seven features, of which abdomen and height are fixed. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of 74\% with projpred, whereas with the stepwise regression only of 11.5\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/inc_prob.pdf}
  \caption{Bootstrap inclusion frequencies after 1000 bootstrap samples.}
  \label{fig:inclusion_frequencies}
\end{figure}

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l||l|r||l|r}
  \hline
M & projpred & Freq & steplm & Freq  \\ 
  \hline
1 & abdomen, weight & 37 & abdomen, height, wrist, age, chest, biceps & 32 \\
2 & abdomen, wrist & 10 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 29 \\
3 & abdomen, height & 10 & abdomen, height, wrist, age, forearm, chest & 19 \\
4 & abdomen, height, wrist & 9 & abdomen, height, wrist, age, neck, forearm, chest & 19 \\
5 & abdomen, weight, wrist & 8 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 19 \\
6 & abdomen, chest, height, wrist & 3 & abdomen, height, wrist, age, neck, chest, biceps & 18 \\
7 & abdomen, height, neck, wrist & 2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 16 \\
8 & abdomen, age, wrist & 2 & abdomen, height, wrist, age, neck, forearm & 15 \\
9 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, height, wrist, age, neck, biceps & 15 \\
10 & abdomen, chest & 1 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 14 \\
   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination. We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features. While with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|r|r|r|r}
  \hline
 & rmse.full & rmse.sel & size.sel & noisy.sel \\ 
  \hline
projpred & 4.4 & 4.5 & 2 & -  \\
steplm & 4.4 & 4.5 & 7 & - \\
\hline
\hline
projpred & $^{*}$4.4 & $^{*}$4.5 & 2 & 0  \\
steplm & 5.3 & 5.5 & 38 & 32 \\
   \hline
\end{tabular}
\caption{Model predictive performances with original data (top table) and adding noisy features (bottom table). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
\label{tab:model_performances}
\end{table}

\hypertarget{comparison}{%
\section{A comparison in the normal means problem framework}\label{comparison}}

In this Section we show the benefits of the use of a reference model. We consider as reference problem the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations. Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations, the normal means problem can be written as follows:
\
\begin{equation}\label{eq:normal_means_problem}
Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}) \quad j=1,..,p
\end{equation}
Note that it is equivalent to a linear regression where the design matrix is the identity one. This formulation can be retrieved in different ways, a common example is given by microarray data, where a large set of genes are usually tested in two groups of patient labelled as positive or negative to some disease. The objective of the analysis is to spot the whole subset of statistically relevant genes to the disease and one possible way to proceed is to compute the two-samples $t$-statistics for each gene and after combining it with the cumulative density function of the standard distribution, the resulting data can be used in the problem formulation \eqref{eq:normal_means_problem}. For further details see the examples in \cite{paper:efron, book:efron}. 
\\
In our examples we retrieve the normal means problem from the sample correlation using the Fisher $z$-transformation approximation \citep{paper:hawkins}. Suppose to have a continuous target random variable $Y$ and a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$ and let us call $\rho_{j}=Cor(Y,X_{j})$. Suppose to observe $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the j-th covariate $\{x_{ij}\}_{i=1}^{n}$. Let finally refer to the function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$. It holds the following modelling approximation (assuming each pair $(Y,X_{j})$ normally distributed):
\
\begin{equation}
T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p
\end{equation}
Therefore rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we find again formulation \eqref{eq:normal_means_problem} with unit variance:
\
\begin{equation} \label{eq:normal_means_problem2}
Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p
\end{equation}
Note that now the quantity of interest $\theta_{j}$ stands for $\sqrt{n-3}\,T_{F}(\rho_{j})$. There are different ways to proceed with the selection from the normal means problem, we consider in our comparison both frequentist and Bayesian state-of-the-art methods. From a full-Bayesian perspective, a Bayesian regression model is fitted to the normal means problem typically using a sparsifying prior as in \cite{paper:dirichlet_laplace}, \cite{paper:horseshoe+} and \cite{paper:EBmed}. In case of continuous priors, as the Dirichlet-Laplace (DL) and the horseshoe+ priors, there is not a canonical way to complete the selection; in their experiments \cite{paper:dirichlet_laplace} use k-means clustering over the posterior samples using the DL prior, whereas \cite{paper:horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior. We include in our experiments the DL and the regularised horseshoe prior \citep{paper:rhs}, which has shown in our opinion better scalability with respect to the horseshoe+, comparing the shrinkage and the correct estimation of the sparse signals using or not the reference model approach. The quantity of interests that we consider are the average SSE (sum of square errors) and the average SESE (sum of expected square errors), defined as follows:
\
\begin{align}
\text{SSE}&=\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
\text{SESE}&=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|\mathbf{z}] \label{eq:SESE}
\end{align}
where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. \cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior. We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for the HDP posterior credible intervals using the regularised horseshoe prior. All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e. ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e. ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.

\hypertarget{simulated-data}{%
\subsection{Simulated data}\label{simulated-data}}
\begin{itemize}
\item details about hyperparameters of the methods used
\end{itemize}

First we use simulated data in order to vary the difficulty of the selection problem. We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation ($\rho$) and number observation ($n$), precisely $p$ and $k$ are fixed respectively at $1000$ and $100$, whereas $n\in\{50,70,100\}$ and $\rho\in\{0.3,0.5\}$. Lower the correlation level and the number of observation are, more challenging the selection is. As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions. It consists in a linear regression using the first five supervised principal components (SPCs) \citep{paper:original_spc, paper:spc} as follows:
\
\begin{equation}
\label{eq:ref_mod}
\begin{aligned}
    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,..,n \\
    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} N(0,\tau^{2})\\
    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
    \end{aligned} &j=1,..,5 \\ 
    &\sigma \sim t_{3}^{+}(0,10) \\
\end{aligned}
\end{equation}
where $\boldsymbol{u}_{i}$ stays for the $i$-th SPC and $s_{max}$ denotes the sample standard deviation of the largest SPC. All model are implemented in Stan \citep{paper:stan}. The normal means problem formulation is obtained as explained in Section \ref{comparison} by Fisher-transformation. We label as ``ref'' the reference approach, which consists in using the reference model on top of the computation of the z-values, and ``data'' the standard approach based on the observed data only. In Section \ref{shrinkage-signal} we analyse in the context of full-Bayes methods the different shrinkage and signal estimation provided by the use of a reference model or not. Section \ref{complete-selection} shows results for the complete selection procedures.

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection. 
As already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}). In the case of the regularised horseshoe prior, we also take into account the posterior mean for the shrinkage factor for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as:
\
\begin{equation}
\kappa_{j}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}
\end{equation}
with $\tau$ and $\lambda_{j}$ respectively global and local shrinkage parameters, for further details see \cite{paper:rhs}.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
  \caption{Posterior intervals for the parameters of the normal means problem ($n=50$, $\rho=0.3$) using the regularised horseshoe prior. Posterior means and one standard deviation intervals depicted. Respectively in red and in blue relevant and non-relevant features. Horizontal dashed line corresponds to the true value of the mean for the relevant features.\\}
  \label{fig:posterior_intervals}
\end{figure}

Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior. Respectively on the right and on the left the results using or not the reference model approach. It is evident how the reference model helps in tearing apart the signals from the noise, resulting in less biased estimates. This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations. We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE. As $n$ and $\rho$ grow, the amount of error diminish, as expected, when using the reference model, whereas it unexpectedly increases when it is not used \hl{(WHY??)}. We also note that the two priors seem to achieve very similar results, regardless of the approach used.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
  \caption{Average SESE and SSE after 100 simulations.\\}
  \label{fig:SESE_SSE}
\end{figure}

Figure \ref{fig:k} shows the posterior medians for the shrinkage factors of each parameter, averaged after 100 data simulations. Relevant and non-relevant features are respectively highlighted in red and blue. The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise. In almost every simulated scenario, the reference model approach achieves a better shrinkage, resulting in a lower posterior median value for $\kappa$ for the relevant features (in red) and a higher one for the non-relevant ones. The only exception is the case $n=50$ and $\rho=0.3$, where we observe that on average the reference model approach slightly underestimate the shrinkage factor for the non-relevant variables with the respect to the approach without a reference model. However, the shrinkage factor for the relevant features is much better estimated using a reference model with a difference in the order of 0.2 units, whereas for the non-relevant features the relative underestimation is only about 0.05.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/k.pdf}
  \caption{Average posterior median values for the shrinkage factors after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
  \label{fig:k}
\end{figure}

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, book:efron}, the empirical Bayes median \citep{paper:EBmed} and the selection by posterior credible intervals. The control of the local false discovery rate is applied through the R-package \textit{locfdr} using splines with 7 degrees of freedom to fit the marginal density and selecting features with local false discovery rate under the value 0.2. Such a value is the common suggested one just for the fact that it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison. The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose highest probability density posterior credible interval does not include zero at the level 0.9.
\\
Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$. For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach. The best selection performance is on the top left corner, which means lowest false discovery rate and highest sensitivity. It is possible to note that regardless of the method used for the selection, the use of a reference model improves the quality diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting). In accordance with what we would expect, higher the number of observation and the correlation are, easier the selection is and thus the benefit of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr.pdf}
  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
  \label{fig:sensitivity_vs_fdr}
\end{figure}

Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals after 100 simulations. Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample) modelling the selection of each variable as a Bernoulli process. Further details are available in their paper as asymptotic normal distribution, based on which confidence intervals are computed. The reference model helps improving the stability of the selection: again such benefit is notable when the problem is more difficult (small $n$ and $\rho$). We observe also less uncertainty in the stability estimates for the reference approach (i.e. the width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
  \label{fig:stability}
\end{figure}

\hypertarget{real-world-data}{%
\subsection{Real world data}\label{real-world-data}}

\begin{itemize}
\item Bodyfat data
\item Results for local false discovery rate
\end{itemize}

\hypertarget{conclusions}{%
\section{Conclusions and discussion}\label{conclusions}}

\bibliography{ref_approach}

\end{document}

### 2019-05-20 code/bodyfat_bootstrap.R

@@ -1,0 +1,59 @@
+library(here)
+library(rstanarm)
+options(mc.cores = parallel::detectCores())
+library(loo)
+library(projpred)
+library(dplyr)
+
+#' Bootstrap iterations for projpred for bodyfat
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip", 
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+
+p0 <- 2 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+rhs_prior <- hs(global_scale=tau0)
+
+bootnum <- 1000
+boot_est <-  boot_se <- matrix(0, ncol = length(pred) + 1, nrow = bootnum,
+                               dimnames = list(NULL, c("(Intercept)", pred)))
+boot_nvs <- matrix(0, ncol=1, nrow=bootnum)
+bbn <- matrix(0, ncol=1, nrow=bootnum)
+for (i in 1:bootnum) {
+  print(i)
+  set.seed(5437854+i)
+  data_id <- sample(1:dim(df)[1], replace = T)
+  bbn[i,] <- length(unique(data_id))
+  fitb <- stan_glm(formula, data = df[data_id, ], 
+                   prior=rhs_prior, QR=TRUE, seed=i, refresh=0)
+  bcvvs <- cv_varsel(fitb, method='forward', cv_method='LOO', nloo=n,
+                     verbose = FALSE)
+  print(nv <- suggest_size(bcvvs,alpha=0.1))
+  boot_nvs[i,] <- nv
+  # print(bcvvs$vind[1:nv])
+  projb <- project(bcvvs, nv = nv, ns = 4000)
+  boot_est[i, colnames(as.matrix(projb)[,-(nv+2)])] <- colMeans(as.matrix(projb)[,-(nv+2)])
+}
+boot_01 <- (boot_est != 0) * 1
[…]

### 2019-05-20 code/dlprior.R

@@ -1,0 +1,162 @@
+### Dirichlet-Laplace prior for variable selection by ###
+###  Bhattacharya, Pati, Pillai and Dunson (2015)     ###
+### "Dirichlet–Laplace Priors for Optimal Shrinkage"  ###
+
+# R-code by Maryclare Griffin  https://github.com/maryclare/dlprior
+# Code for paper is given at https://github.com/debdeeptamu/Dirichlet_Laplace/blob/master/DL.m
+
+library(GIGrvg)
+library(statmod)
+
+sym.sq.root <- function(A) {
+  A.eig <- eigen((A + t(A))/2)
+  crossprod(t(A.eig$vectors), tcrossprod(diag(sqrt(ifelse(A.eig$values > 0, A.eig$values, 0)),
+                                              nrow = nrow(A), ncol = ncol(A)), A.eig$vectors))
+}
+
+ei.inv <- function(A) {
+  A.eig <- eigen(A)
+  crossprod(t(A.eig$vectors), tcrossprod(diag(ifelse(A.eig$values > 0, 1/A.eig$values, 0)), A.eig$vectors))
+}
+
+dl.beta <- function(XtX, Xty, sig.sq, psi, lambda) {
+  
+  if (is.matrix(XtX)) {
+    
+    p <- nrow(XtX)
+    diagonals <- exp(log(lambda) + log(psi)/2)
+    phiphit <- tcrossprod(diagonals)
+    A <- (XtX/sig.sq)*(phiphit) + diag(p)
+    A.inv <- ei.inv(A)
+    mean <- crossprod(A.inv*phiphit, Xty/sig.sq)
+    # cat("Diagonals\n")
+    # print(summary(psi)) # sqrt(psi)
+    # cat("A.inv\n")
+    # print(summary(c(abs(A.inv))))
+    return(crossprod(t(tcrossprod(diagonals, rep(1, p))*sym.sq.root(A.inv)), rnorm(p)) + mean)
+  } else if (is.vector(XtX)) {
+    p <- length(XtX)
+    
+    A <- XtX/sig.sq + 1/(exp(2*log(lambda) + log(psi)))
+    A.inv <- 1/(A)
+    mean <- A.inv*Xty/sig.sq
+    var <- A.inv
+    
+    return(sqrt(var)*rnorm(p) + mean)
+  }
+}
+
+dl.psi <- function(beta, lambda) {
+  p <- length(beta)
+  
[…]

### 2019-05-20 code/full_bayes.R

@@ -1,0 +1,231 @@
+library(dplyr)
+library(purrr)
+library(tibble)
+library(dimreduce)
+library(locfdr)
+library(EbayesThresh)
+library(rstan)
+library(rstanarm)
+options(mc.cores = parallel::detectCores())
+set.seed(453876)
+
+args = commandArgs(trailingOnly=TRUE) # n rho nc
+
+## Simulation parameters
+n <- as.numeric(args[1])  # number of observations
+rho <- as.numeric(args[2])  # correlation level
+p <- 1000   # total number of features
+k <- 100    # number of relevant features
+
+times <- 100
+
+## Data simulation mechanism
+simulate_data <- function(){ # n, rho, p and k from global environment
+  f <- rnorm(n) # the true underlying function
+  
+  data <- tibble(y = f + rnorm(n)) %>%   # observed targe variable y
+    bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
+    bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
+    set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
+  
+  return(data)
+}
+
+results <- tibble(error = numeric(),
+                  error_type = character(),
+                  prior = character(),
+                  approach = character(),
+                  n = numeric(),
+                  rho = numeric())
+
+## Stan models
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+rhs_model <- stan_model("mht_rhs.stan", model_name = "rhs_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+dl_model <- stan_model("dl_shrinkage.stan", model_name = "dl_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+k_RHS_ref <- numeric(p)
+k_RHS_data <- numeric(p)
+
+for(i in 1:times){
+  data <- simulate_data()
+  y <- dplyr::pull(data, var="y")
[…]

### 2019-05-20 code/getStability.R

@@ -1,0 +1,34 @@
+# https://github.com/nogueirs/JMLR2018/blob/master/R/getStability.R
+
+getStability <- function(X,alpha=0.05) {
+  ## the input X is a binary matrix of size M*d where:
+  ## M is the number of bootstrap replicates
+  ## d is the total number of features
+  ## alpha is the level of significance (e.g. if alpha=0.05, we will get 95% confidence intervals)
+  ## it's an optional argument and is set to 5% by default
+  ### first we compute the stability
+  
+  M<-nrow(X)
+  d<-ncol(X)
+  hatPF<-colMeans(X)
+  kbar<-sum(hatPF)
+  v_rand=(kbar/d)*(1-kbar/d)
+  stability<-1-(M/(M-1))*mean(hatPF*(1-hatPF))/v_rand ## this is the stability estimate
+  
+  ## then we compute the variance of the estimate
+  ki<-rowSums(X)
+  phi_i<-rep(0,M)
+  for(i in 1:M){ 
+    phi_i[i]<-(1/v_rand)*((1/d)*sum(X[i,]*hatPF)-(ki[i]*kbar)/d^2-(stability/2)*((2*kbar*ki[i])/d^2-ki[i]/d-kbar/d+1))
+  }
+  phi_bar=mean(phi_i)
+  var_stab=(4/M^2)*sum((phi_i-phi_bar)^2) ## this is the variance of the stability estimate
+  
+  ## then we calculate lower and upper limits of the confidence intervals
+  z<-qnorm(1-alpha/2) # this is the standard normal cumulative inverse at a level 1-alpha/2
+  upper<-stability+z*sqrt(var_stab) ## the upper bound of the (1-alpha) confidence interval
+  lower<-stability-z*sqrt(var_stab) ## the lower bound of the (1-alpha) confidence interval
+  
+  return(list("stability"=stability,"variance"=var_stab,"lower"=lower,"upper"=upper))
+  
+}

### 2019-05-20 code/plots.R

@@ -1,0 +1,293 @@
+##########################################
+### Script for the plots of the paper ####
+##########################################
+library(tidyverse)
+library(ggplot2)
+library(latex2exp)
+source("getStability.R")
+
+p <- 1000
+k <- 100
+
+avg.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+avg.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+data.plot <- tibble(n = numeric(),
+                    rho = numeric(),
+                    method = character(),
+                    approach = character(),
+                    recall = numeric(),
+                    fdr = numeric(),
+                    stab.low = numeric(),
+                    stab.mean = numeric(),
+                    stab.up = numeric())
+
+for(nn in c(50,70,100)){
+  for(rr in c(0.3,0.5)){
+    load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
+    
+    data.plot <- data.plot %>% 
+      # Credibility intervals inclusion probabilities with regularized horseshoe prior
+      bind_rows(tibble(n = rep(n,2),      
+              rho = rep(rho,2),
+              method = rep("ci.90",2),
+              approach = c("ref","data"),
+              sensitivity = c(avg.sensitivity(ci90_X_ref),avg.sensitivity(ci90_X_data)),
+              fdr = c(avg.fdr(ci90_X_ref),avg.fdr(ci90_X_data)),
+              stab.low = c(getStability(ci90_X_ref)$lower,getStability(ci90_X_data)$lower),
+              stab.mean = c(getStability(ci90_X_ref)$stability,getStability(ci90_X_data)$stability),
+              stab.up = c(getStability(ci90_X_ref)$upper,getStability(ci90_X_data)$upper))) %>%
+      # Control of the local false discovery rate
+      bind_rows(tibble(n = rep(n,2),      
+              rho = rep(rho,2),
+              method = rep("loc.fdr",2),
+              approach = c("ref","data"),
[…]

### 2019-05-20 code/ref_approach.R

@@ -1,0 +1,205 @@
+library(dplyr)
+library(purrr)
+library(loo)
+library(dimreduce)
+library(locfdr)
+library(EbayesThresh)
+library(rstan)
+library(rstanarm)
+options(mc.cores = parallel::detectCores())
+set.seed(453876)
+
+args = commandArgs(trailingOnly=TRUE) # n rho nc
+
+## Simulation parameters
+n <- as.numeric(args[1])  # number of observations
+rho <- as.numeric(args[2])  # correlation level
+p <- 1000   # total number of features
+k <- 100    # number of relevant features
+
+times <- 100
+
+## Data simulation mechanism
+simulate_data <- function(){ # n, rho, p and k from global environment
+  f <- rnorm(n) # the true underlying function
+  
+  data <- as_tibble(f + rnorm(n)) %>%   # observed targe variable y
+    bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
+    bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
+    set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
+  
+  return(data)
+}
+
+
+## Control of the local false discovery rate
+lfdr_X_ref <- matrix(0,nrow=times,ncol=p)
+lfdr_X_data <- matrix(0,nrow=times,ncol=p)
+
+lfdr_mean_ref <- numeric(p)
+lfdr_mean_data <- numeric(p)
+
+## Empirical Bayes median thresholding
+ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
+ebmt_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Confidence intervals inclusion probabilities 
+ci80_X_ref <- matrix(0,nrow=times,ncol=p)
+ci90_X_ref <- matrix(0,nrow=times,ncol=p)
+ci95_X_ref <- matrix(0,nrow=times,ncol=p)
+ci80_X_data <- matrix(0,nrow=times,ncol=p)
+ci90_X_data <- matrix(0,nrow=times,ncol=p)
+ci95_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Control of the Q-value 
[…]

### 2019-05-20 code/shrinkage.R

@@ -1,0 +1,173 @@
+# library(dplyr)
+# library(purrr)
+# library(tibble)
+library(tidyverse)
+library(dimreduce)
+library(locfdr)
+library(EbayesThresh)
+library(rstan)
+library(rstanarm)
+library(latex2exp)
+options(mc.cores = parallel::detectCores())
+set.seed(453876)
+
+## Simulation parameters
+n <- 50  # number of observations
+rho <- 0.3  # correlation level
+p <- 1000   # total number of features
+k <- 100    # number of relevant features
+
+## Data simulation mechanism
+simulate_data <- function(){ # n, rho, p and k from global environment
+  f <- rnorm(n) # the true underlying function
+  
+  data <- tibble(y = f + rnorm(n)) %>%   # observed targe variable y
+    bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
+    bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
+    set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
+  
+  return(data)
+}
+
+## Stan models
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+rhs_model <- stan_model("mht_rhs.stan", model_name = "rhs_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+k_RHS_ref <- numeric(p)
+k_RHS_data <- numeric(p)
+
+for(i in 1:10){
+data <- simulate_data()
+y <- dplyr::pull(data, var="y")
+x <- dplyr::select(data, -contains("y"))
+
+
+## Fitting the reference model
+nc <- 5
+dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p, sup.only = T, verbose = F)
+z <- predict(dr, x)
+
+model_data <- list(y = y,
+                   X = z,
+                   p = nc,
+                   n = n,
+                   s_max = dr$sdev[1])
+fit <- sampling(fit_model, data = model_data, 
[…]

### 2019-05-20 code/plots.R
fixed posterior intervals plot

@@ -164,9 +164,10 @@ ggsave("../paper/graphics/k.pdf",plot_k,width=10,height=3)
 
 
 ## Posterior intervals: done with the last iteration
+load(paste("fullBayes_n50rho0.3.Rdata",sep=""))
 
-theta_ref <- extract(rhs_ref,pars=paste("theta[",1:p,"]",sep=""))
-theta_data <- extract(rhs_data,pars=paste("theta[",1:p,"]",sep=""))
+theta_ref <- rstan::extract(rhs_ref,pars=paste("theta[",1:p,"]",sep=""))
+theta_data <- rstan::extract(rhs_data,pars=paste("theta[",1:p,"]",sep=""))
 
 int_ref <- theta_ref %>% 
   map(~c(mean=mean(.),sd=sd(.))) %>%

### 2019-05-21 paper/ref_approach.tex
more in the introduction and added hyperparameter info DL RHS

@@
 It is also the basis for the projection predictive approach \citep{paper:original_proj, paper:projpred}, from which we have taken the hint of using the reference model as a filter (see Section \ref{reference-model-approach}).
+The reference model, if properly designed, is a less noisy representation of the true data generation mechanism with respect to the observed data distribution.
+Therefore in a variable selection context it improves the selection process in terms of quality and stability of the selected subset of features, whether the goal is the smallest model with high enough predictive performance or the whole subset of relevant features.
+
+In this paper we try to show such benefits with:
 
 \begin{itemize}
-\item add original contribution that are:
-\item motivation and example on how the use of a reference model improves the selection (projpred example)
-\item a comparison between using a reference model or not in the normal means problem  both with simulated data and the bodyfat data
+\item a real-world data example comparing the projection predictive approach with the stepwise backward regression selection,
+\item a structured comparison in the framework of the normal means estimation problem using different state-of-the-art methods with or not a reference model on top of the procedure, with simulated data and a real-world data example.
 \end{itemize}
@@
 \subsection{Simulated data}\label{simulated-data}}
-\begin{itemize}
-\item details about hyperparameters of the methods used
-\end{itemize}
 
@@
 Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
+We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs} setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
+
 As already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}).

### 2019-05-23 code/bodyfat_bootstrap.R
saving data after the loop

@@ -42,16 +42,28 @@ for (i in 1:bootnum) {
   projb <- project(bcvvs, nv = nv, ns = 4000)
   boot_est[i, colnames(as.matrix(projb)[,-(nv+2)])] <- colMeans(as.matrix(projb)[,-(nv+2)])
 }
+
+save.image("body_bootstrap.RData")
+
 boot_01 <- (boot_est != 0) * 1
 boot_inclusion <- data.frame(projpred_incp=(apply(boot_01, 2, function(x) sum(x) / length(x) * 100)))
 boot_01 <- data.frame(boot_01)
 
-bn <- data.frame(boot_nvs) %>% group_by_all() %>% count(sort=TRUE)
-bd <- boot_01 %>% group_by_at(vars(-X.Intercept.)) %>% count(sort=TRUE)
-boot_inclusion <- boot_inclusion %>% tibble::rownames_to_column(var="variable") %>% filter(variable != "X.Intercept.") %>% arrange(-projpred_incp)
+bn <- data.frame(boot_nvs) %>% 
+  group_by_all() %>% 
+  count(sort=TRUE)
+bd <- boot_01 %>% 
+  group_by_at(vars(-X.Intercept.)) %>% 
+  count(sort=TRUE)
+boot_inclusion <- boot_inclusion %>% 
+  tibble::rownames_to_column(var="variable") %>% 
+  filter(variable != "X.Intercept.") %>% 
+  arrange(-projpred_incp)
 boot_inclusion$steplm_incp <- c(100, 28, 98, 100, 85, 63, 51, 48, 34, 43, 54, 41, 18)
-boot_inclusion <- boot_inclusion %>% rename(projpred=projpred_incp, steplm=steplm_incp)
+boot_inclusion <- boot_inclusion %>% 
+  rename(projpred=projpred_incp, steplm=steplm_incp)
 cumsum(bd$n)
+
 for (i in 1:20) {
   print(paste(paste0(colnames(bd)[c(as.logical(bd[i,1:13]),FALSE)], collapse=", "),bd$n[i],sep=", "))
 }

### 2019-05-23 paper/ref_approach.tex
expanded introduction with references to reference model approach + motivation of interest in the paper

--- 2019-05-20 paper/ref_approach.tex
@@
 
-In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection.
+In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, that can be seen as a special case of model reduction.
 From a full Bayesian perspective, when the goal of the analysis is to do prediction, no selection should be carried out and integration over all parameters uncertainties, i.e.
@@
 Regardless which kind of selection problem we are trying to solve, we consider examples of the reference model approach all those methods that make use of a full-encompassing model, i.e.
-the reference one, to carry out the selection.
-The idea of using a reference model is already present in some works from the 60s as \cite{paper:reference_lindley}.
-It is also the basis for the projection predictive approach \citep{paper:original_proj, paper:projpred}, from which we have taken the hint of using the reference model as a filter (see Section \ref{reference-model-approach}).
+the reference one.
+Such an idea is not new to the model reduction literature, it has been used for many years using different type of names.
+\cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
+He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximate the best model and the inheritance of the shrinkage when it is applied to the full model.
+\cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data.
+Neural networks typically perform very well in terms of prediction, but it is not very clear how to interpret the significance of each covariate.
+\cite{paper:faraggi_nn} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
+\cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso \citep{paper:tibshirani_lasso} or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
+\cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
+\\
+The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
+In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction.
+The best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
+The resulting problem is convex and thus many efficient optimisation algorithm are available.
+Following \cite{paper:goutis_projection}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
+In the special case of candidate models in the family of the GLMs, the optimisation problem correspond to the maximum likelihood estimation problem having the expected model point prediction by the reference model instead of the observed target values.
+Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model.
+\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance with the reference model one.
 
-\begin{itemize}
-\item add original contribution that are:
-\item motivation and example on how the use of a reference model improves the selection (projpred example)
-\item a comparison between using a reference model or not in the normal means problem  both with simulated data and the bodyfat data
-\end{itemize}
+\cite{paper:projpred} show in their experiments the benefits of the projection predictive approach in terms of predictive ability of the selected model and smaller size compared to other methods.
+It could be of interest to know how often a certain method includes non-relevant features.
+One could argue that such question can not have a general answer, because it depends both on the data and on the choice of the reference model.
+Moreover in real settings it is hard to define what relevant means, in most of the cases all the features have some level of relevance in term of prediction ability and thus the question looses of meaning.
+However, it is still possible to simulate certain artificial scenarios and control which features are included.
+\cite{paper:model_selection} report results about the proportion of relevant and non-relevant features selected with different variable selection methods, showing overall better results in favour of the projection predictive approach.
+The explored submodels using the projection show also a higher performance and stability with respect to the compared methods, given the same submodel size.
+
+In this paper we try to give further examples and intuitions on why the reference model helps.
+Using a real world dataset, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression.
+Wherever it has been used, the reference model can be always seen acting as a filter on the observed data.
+Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
+Our goal is to show the reference model benefits, regardless of what specific procedure is applied.
+We take as reference problem the normal means estimation problem.
+We apply different state-of-the-art methods comparing in each case the results using the data or using a reference model.
+In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
+We believe that these results should motivate the use of a reference model when doing model reduction, regardless of the specific method used and thus we hope this work can be of interest to a large number of people.
 
@@
 \hypertarget{reference-model-approach}{%
-\section{Reference model approach to feature selection}\label{reference-model-approach}}
+\section{Why the reference model helps}\label{reference-model-approach}}
 
-The reference model approach has his roots in  the $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen} and started to be used in the feature selection context already starting from the 60s with \cite{paper:reference_lindley}.
-There is not a specific definition of what a reference model is; ideally any full-encompassing model which has a good predictive performance is a candidate reference model.
+The main assumption under any reference model approach is to operate in  the $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, thus to be able to have a model, that is the reference model, which is the best available description of a future observation.
+There is not a specific definition of how a reference model should be; in practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
 General guidelines on how to devise it are the same about any model in a data analysis context, expect for the fact that no selection is carried out for the reference model.
-\cite{paper:projpred} showed that through the projection predictive approach the reference model can helps in terms of stability and model size in the selection process.
-In this Section we aim to give some hints on why this happens and on how we can generally rely on a reference model approach to feature selection with a simple example.
 
@@
 What is shown in Figure \ref{fig:correlation} is related also to the projection predictive approach.
-In case of a submodel belonging to the generalised linear model family, it happens that the draw-by-draw projection coincide with the maximum likelihood estimator with observed data substituted with reference model's predictions \citep{paper:projpred}.
+In case of a submodel belonging to the generalised linear model family, it happens that the draw-by-draw projection coincide with the maximum likelihood estimator with observed data substituted with reference model's predictions \citep{paper:original_proj}.
 It is possible to see the idea of the reference model as a filter on our data also from the projection of the predictive distribution itself.

### 2019-05-23 paper/ref_approach.tex
more corrections on the introduction

@@
 the reference one.
-Such an idea is not new to the model reduction literature, it has been used for many years using different type of names.
+Such an idea is not new to the model reduction literature, it has been used for long time using different names.
 \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
-He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximate the best model and the inheritance of the shrinkage when it is applied to the full model.
+He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
 \cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data.
@@
 It could be of interest to know how often a certain method includes non-relevant features.
-One could argue that such question can not have a general answer, because it depends both on the data and on the choice of the reference model.
+One could argue that such question can not have a general answer, because it depends both on the data and, when it is used, on the choice of the reference model.
 Moreover in real settings it is hard to define what relevant means, in most of the cases all the features have some level of relevance in term of prediction ability and thus the question looses of meaning.
@@
 Using a real world dataset, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression.
-Wherever it has been used, the reference model can be always seen acting as a filter on the observed data.
+However it has been used, the reference model can be always seen acting as a filter on the observed data.
 Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
@@
 We apply different state-of-the-art methods comparing in each case the results using the data or using a reference model.
-In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
-We believe that these results should motivate the use of a reference model when doing model reduction, regardless of the specific method used and thus we hope this work can be of interest to a large number of people.
+In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
+We believe that these results should motivate the use of a reference model when doing model reduction, regardless of the specific method used and, thus, we hope this work can be of interest to a large number of practitioners.
 
 The paper is structured as follows.
-In Section \ref{reference-model-approach} we introduce the idea of the reference model, its benefits with examples and how we used it as a filter on our data in a very simple way.
+In Section \ref{reference-model-approach} we introduce the idea of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
 In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem.

### 2019-05-24 paper/ref_approach.tex
fixed bootstrap results with 1000 simulations for projpred

@@
 \subsection{Benefits of the reference model: an example with the projection predictive approach}\label{projection}}
-\begin{itemize}
-\item correct bootstrap results for projpred --> 1000 bootstrap samples 
-\item thus correct the comment on the table and on the barplot!!!!
-\end{itemize}
 
@@
 Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection.
-The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), while the stepwise regression has seven features, of which abdomen and height are fixed.
+The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), the third most included is `wrist' at 49.5 and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50, of which abdomen and height are fixed.
 Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
-The first five selected models have a cumulative frequency of 74\% with projpred, whereas with the stepwise regression only of 11.5\%.
+The first five selected models have a cumulative frequency of almost 70\% with projpred, whereas with the stepwise regression only of 11.8\%.
 In addition to that we note that the size of the selected model is much smaller when using projpred.
@@
   \hline
-M & projpred & Freq & steplm & Freq  \\ 
+M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
   \hline
-1 & abdomen, weight & 37 & abdomen, height, wrist, age, chest, biceps & 32 \\
-2 & abdomen, wrist & 10 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 29 \\
-3 & abdomen, height & 10 & abdomen, height, wrist, age, forearm, chest & 19 \\
-4 & abdomen, height, wrist & 9 & abdomen, height, wrist, age, neck, forearm, chest & 19 \\
-5 & abdomen, weight, wrist & 8 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 19 \\
-6 & abdomen, chest, height, wrist & 3 & abdomen, height, wrist, age, neck, chest, biceps & 18 \\
-7 & abdomen, height, neck, wrist & 2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 16 \\
-8 & abdomen, age, wrist & 2 & abdomen, height, wrist, age, neck, forearm & 15 \\
-9 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, height, wrist, age, neck, biceps & 15 \\
-10 & abdomen, chest & 1 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 14 \\
+1 & abdomen, weight & 34.2 & abdomen, height, wrist, age, chest, biceps & 3.2 \\
+2 & abdomen, wrist & 13.3 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 2.9 \\
+3 & abdomen, weight, wrist & 7.6 & abdomen, height, wrist, age, forearm, chest & 1.9 \\
+4 & abdomen, height & 7.4 & abdomen, height, wrist, age, neck, forearm, chest & 1.9 \\
+5 & abdomen, height, wrist & 6.7 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 1.9 \\
+6 & abdomen, age, wrist & 2.9 & abdomen, height, wrist, age, neck, chest, biceps & 1.8 \\
+7 & abdomen, height, neck & 2.2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 1.6 \\
+8 & abdomen, age, height, wrist & 1.2 & abdomen, height, wrist, age, neck, forearm & 1.5 \\
+9 & abdomen, weight, thigh & 1.1 & abdomen, height, wrist, age, neck, biceps & 1.5 \\
+10 & abdomen, weight, neck & 1.0 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 1.4 \\
    \hline

### 2019-05-24 code/bodyfat_bootstrap.R

@@ -43,7 +43,7 @@ for (i in 1:bootnum) {
   boot_est[i, colnames(as.matrix(projb)[,-(nv+2)])] <- colMeans(as.matrix(projb)[,-(nv+2)])
 }
 
-save.image("body_bootstrap.RData")
+#save.image("body_bootstrap.RData")
 
 boot_01 <- (boot_est != 0) * 1
 boot_inclusion <- data.frame(projpred_incp=(apply(boot_01, 2, function(x) sum(x) / length(x) * 100)))
@@ -57,7 +57,7 @@ bd <- boot_01 %>%
   count(sort=TRUE)
 boot_inclusion <- boot_inclusion %>% 
   tibble::rownames_to_column(var="variable") %>% 
-  filter(variable != "X.Intercept.") %>% 
+  filter(variable != "(Intercept)") %>% 
   arrange(-projpred_incp)
 boot_inclusion$steplm_incp <- c(100, 28, 98, 100, 85, 63, 51, 48, 34, 43, 54, 41, 18)
 boot_inclusion <- boot_inclusion %>% 
@@ -68,4 +68,4 @@ for (i in 1:20) {
   print(paste(paste0(colnames(bd)[c(as.logical(bd[i,1:13]),FALSE)], collapse=", "),bd$n[i],sep=", "))
 }
 
-save(boot_01, boot_inclusion, boot_nvs, bbn, file = "bodyfat_bootstrap.RData")
+save.image("bodyfat_bootstrap.RData")

### 2019-05-24 code/plots.R

@@ -203,24 +203,25 @@ ggsave("../paper/graphics/post_int.pdf",post_int,width=10,height=3)
 #####################################################
 ###### BOOTSTRAP INCLUSION PROBABILITES PLOT ########
 
-data_plot <- tibble(variable = c("abdomen","weight","wrist","height",
-                                 "age", "neck", "biceps", "chest", "thigh",
-                                 "ankle", "forearm", "hip", "knee"),
-                    projpred = c(100,58,46,35,9,9,6,5,4,4,3,0,0),
-                    steplm = c(100,28,98,100,85,63,51,48,34,43,54,41,18))
+load("bodyfat_bootstrap.RData")
 
-inc_prob <- data_plot %>%
+inc_prob <- boot_inclusion %>%
   gather(key="method", value="freq", projpred,steplm) %>%
   ggplot(aes(x=variable,y=freq,fill=method)) + 
   geom_bar(stat="identity",position=position_dodge()) +
   labs(x="",y="",fill="") +
   #guides(fill=FALSE) +
-  scale_x_discrete(limits=data_plot$variable) +
+  scale_x_discrete(limits=boot_inclusion$variable) +
   scale_fill_manual(values=c('steplm'="#819FF7",'projpred'="#FAAC58")) +
   theme_light()
 
 ggsave("../paper/graphics/inc_prob.pdf",inc_prob,width=10,height=3)
 
+
+# Model selection frequencies
+for (i in 1:20) {
+  print(paste(paste0(colnames(bd)[c(as.logical(bd[i,1:13]),FALSE)], collapse=", "),bd$n[i],sep=", "))
+}
 
 
 #####################################################

### 2019-05-24 code/bodyfat_comparison.R
changed locfdr fit to type = 1 (from spline to polynomial

@@ -1,0 +1,173 @@
+## BODYFAT COMPARISON ##
+rm(list=ls())
+args = commandArgs(trailingOnly=TRUE) 
+library(rstan)
+library(rstanarm)
+library(locfdr)
+library(dimreduce)
+library(EbayesThresh)
+set.seed(3428954)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n_full <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip", 
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p <- 1000
+n <- as.numeric(args[1])
+times <- 100
+
+## Control of the local false discovery rate
+lfdr_X_ref <- matrix(0,nrow=times,ncol=p)
+lfdr_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Empirical Bayes median thresholding
+ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
+ebmt_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Confidence intervals inclusion probabilities 
+ci80_X_ref <- matrix(0,nrow=times,ncol=p)
+ci90_X_ref <- matrix(0,nrow=times,ncol=p)
+ci95_X_ref <- matrix(0,nrow=times,ncol=p)
+ci80_X_data <- matrix(0,nrow=times,ncol=p)
+ci90_X_data <- matrix(0,nrow=times,ncol=p)
+ci95_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Stan models
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+rhs_model <- stan_model("mht_rhs.stan", model_name = "rhs_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+for(i in 1:times){
+  noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
[…]

### 2019-05-27 paper/ref_approach.tex
improved introduction

@@
 \hypersetup{unicode=true,
-            pdftitle={Reference model in feature selection problems},
-            pdfauthor={Federico Pavone, Juho Piironen, Aki Vehtari},
+            pdftitle={The reference model approach in feature selection problems},
+            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
             pdfkeywords={keywords},
@@
 
-\title{Reference model in feature selection problems 
+\title{The reference model approach in feature selection problems 
 	\vspace{.1in}}
@@
 
-In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, that can be seen as a special case of model reduction.
+In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
 From a full Bayesian perspective, when the goal of the analysis is to do prediction, no selection should be carried out and integration over all parameters uncertainties, i.e.
 posterior distributions, is the recommended procedure.
-However, a high dimensional parameter space brings different difficulties as computation burden and overfitting.
-For such reason different feature selection procedures have been proposed both in the frequentist and Bayesian setting (e.g.
-see \cite{paper:feature_selection}, \cite{paper:vehtari_ojanen} and \cite{paper:model_selection}).
-Sometimes the task of the analysis is not prediction, but rather inference on which variables are significantly related to the phenomenon of interest.
-A common case is microarray data in medicine or biology, where for example for a very large number of genes, expression levels are measured for two sets of patients labeled as \textit{positive} or \textit{negative} to some disease (typically a \textit{small n large p} scenario).
-The main goal of the analysis is to spot which subset of these genes is significantly related to the disease in order to perform further experiments.
-A possible way to proceed is to perform hypothesis testing to assess the significance of each gene, based on some modelling assumptions.
-\cite{book:efron} refers to this as multiple hypothesis testing problem.
-Such example could be still considered as feature selection, intended this time as the problem of ``identifying \textit{all} features that are predictive about (that is, statistically related to) the target variable'' \citep{paper:projpred}.
+In a high dimensional parameter space the choice of the prior plays an even more key role due to different difficulties that can rise, as computation burden and overfitting.
+In addition to that, sometimes collecting all the features for a future observation is not possible or too expensive.
+In order to solve or, at least, simplify these problems, different feature selection procedures have been proposed both in the frequentist and the Bayesian setting \cite[e.g.
+see][]{paper:feature_selection,paper:vehtari_ojanen,paper:model_selection}.
+Sometimes the task of the analysis is not prediction, but rather inference on which variables are substantially related to the phenomenon of interest.
+This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
+A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease.
+The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
 
-Regardless which kind of selection problem we are trying to solve, we consider examples of the reference model approach all those methods that make use of a full-encompassing model, i.e.
-the reference one.
-Such an idea is not new to the model reduction literature, it has been used for long time using different names.
-\cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
+Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism.
+Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones.
+The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{paper:tibshirani_lasso} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data.
+The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e.
+the reference model, as an approximation of the data generation mechanism.
+Such an idea is widely present in the literature with different names.
+For example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
@@
 
-\cite{paper:projpred} show in their experiments the benefits of the projection predictive approach in terms of predictive ability of the selected model and smaller size compared to other methods.
+%\cite{paper:projpred} show in their experiments the benefits of the projection predictive approach in terms of predictive ability of the selected model and smaller size compared to other methods.
 It could be of interest to know how often a certain method includes non-relevant features.
@@
 
-In this paper we try to give further examples and intuitions on why the reference model helps.
-Using a real world dataset, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression.
-However it has been used, the reference model can be always seen acting as a filter on the observed data.
+In this paper we try to bring motivations for the use of a reference model.
+A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process.
+As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression with a real world dataset.
+We argue that however the reference model has been used, it can be always seen acting as a filter on the observed data.
 Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
-Our goal is to show the reference model benefits, regardless of what specific procedure is applied.
-We take as reference problem the normal means estimation problem.
-We apply different state-of-the-art methods comparing in each case the results using the data or using a reference model.
+We thus show the reference model benefits, regardless of what specific procedure is applied, using as a benchmark the normal means estimation problem.
+We apply different state-of-the-art methods comparing in each case the results basing the selection on the data or on the reference model.
 In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
-We believe that these results should motivate the use of a reference model when doing model reduction, regardless of the specific method used and, thus, we hope this work can be of interest to a large number of practitioners.
+We believe that these results show how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it.
+Of course we recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
+Therefore we hope that this work can increase the interest on this family of methods and it can be of interest to a large number of practitioners.
 
@@
 \text{SSE}&=\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-\text{SESE}&=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|\mathbf{z}] \label{eq:SESE}
+\text{SESE}&=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
 \end{align}

### 2019-05-28 code/bodyfat_comparison.R
corrected for not fixed sigma in all methods

@@ -43,7 +43,7 @@ ci95_X_data <- matrix(0,nrow=times,ncol=p)
 ## Stan models
 fit_model <- stan_model("model.stan", model_name = "reference_model",
                         auto_write = rstan_options("auto_write"=TRUE))
-rhs_model <- stan_model("mht_rhs.stan", model_name = "rhs_model",
+rhs_model <- stan_model("mht_rhs_sigmaprior.stan", model_name = "rhs_model",
                         auto_write = rstan_options("auto_write"=TRUE))
 
 for(i in 1:times){
@@ -90,20 +90,20 @@ for(i in 1:times){
   z_data <- sqrt(n-3) * 0.5*log((1+r_data)/(1-r_data)) # Fisher transformation * (n-3)
   
   ## Control of of the local false discovery rate
-  lfdr_ref <- locfdr(z_ref, nulltype = 0, plot = 0, bre = 120, type = 1)
-  lfdr_data <- locfdr(z_data, nulltype = 0, plot = 0, bre = 120, type = 1)
+  lfdr_ref <- locfdr(z_ref, nulltype = 1, plot = 0, bre = 120, type = 1)
+  lfdr_data <- locfdr(z_data, nulltype = 1, plot = 0, bre = 120, type = 1)
   
-  lfdr_sel_ref <- which(lfdr_ref$fdr<0.2)
-  lfdr_sel_data <- which(lfdr_data$fdr<0.2)
+  lfdr_sel_ref <- which(lfdr_ref$fdr<=0.2)
+  lfdr_sel_data <- which(lfdr_data$fdr<=0.2)
   
   lfdr_X_ref[i,lfdr_sel_ref] <- 1
   lfdr_X_data[i,lfdr_sel_data] <- 1
   
   ## Empirical Bayes median thresholding
   z.est_ref <- ebayesthresh(z_ref, prior = "laplace", a = NA,
-                            sdev = 1, verbose = TRUE, threshrule = "median") 
+                            sdev = NA, verbose = TRUE, threshrule = "median") 
   z.est_data <- ebayesthresh(z_data, prior = "laplace", a = NA,
-                             sdev = 1, verbose = TRUE, threshrule = "median") 
+                             sdev = NA, verbose = TRUE, threshrule = "median") 
   
   ebmt_sel_ref <- which(z.est_ref$muhat!=0)
   ebmt_sel_data <- which(z.est_data$muhat!=0)
@@ -123,7 +123,7 @@ for(i in 1:times){
[…]

### 2019-05-29 code/plots.R
added bodyfat comparison plots

@@ -292,4 +292,94 @@ cor_plot_final <- ggExtra::ggMarginal(cor_plot,
                                       xparams = list(size=0.5), 
                                       yparams = list(size=0.5))
 ggsave("../paper/graphics/correlation.pdf",cor_plot_final, width=4, height=4)
+
+
+##################################################
+########## BODYFAT VARIABLE SELECTION ############
+
+k <- 13
+
+avg.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+avg.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+data.plot <- tibble(n = numeric(),
+                    rho = numeric(),
+                    method = character(),
+                    approach = character(),
+                    recall = numeric(),
+                    fdr = numeric(),
+                    stab.low = numeric(),
+                    stab.mean = numeric(),
+                    stab.up = numeric())
+
+for(nn in c(50,70,100,251)){
+  load(paste("bodyfat_type1_n",nn,".Rdata",sep=""))
+  
+  data.plot <- data.plot %>% 
+    # Credibility intervals inclusion probabilities with regularized horseshoe prior
+    bind_rows(tibble(n = rep(n,2),      
+                     method = rep("ci.90",2),
+                     approach = c("ref","data"),
+                     sensitivity = c(avg.sensitivity(ci90_X_ref),avg.sensitivity(ci90_X_data)),
+                     fdr = c(avg.fdr(ci90_X_ref),avg.fdr(ci90_X_data)),
+                     stab.low = c(getStability(ci90_X_ref)$lower,getStability(ci90_X_data)$lower),
+                     stab.mean = c(getStability(ci90_X_ref)$stability,getStability(ci90_X_data)$stability),
+                     stab.up = c(getStability(ci90_X_ref)$upper,getStability(ci90_X_data)$upper))) %>%
+    # Control of the local false discovery rate
+    bind_rows(tibble(n = rep(n,2),      
+                     method = rep("loc.fdr",2),
+                     approach = c("ref","data"),
[…]

### 2019-05-29 paper/ref_approach.tex
added bodyfat comparison results and comments

@@
 Therefore we hope that this work can increase the interest on this family of methods and it can be of interest to a large number of practitioners.
+\\
+We would like also the reader to note that beside the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.
 
@@
 
-The main assumption under any reference model approach is to operate in  the $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, thus to be able to have a model, that is the reference model, which is the best available description of a future observation.
+The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, i.e.
+to be able to have a model, that is the reference model, which is the best available description of a future observation.
 There is not a specific definition of how a reference model should be; in practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
@@
 
-Consider the following data generation mechanism for each statistical unit, already used in \cite{paper:projpred}:
+A good predictive model is able to clean part of the noise present in the data.
+The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
+Indeed, consider the following data generation mechanism for each statistical unit, already used in \cite{paper:projpred}:
 \
@@
 Precisely $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$.
-Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
+If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.
+When using a reference model, we are trying to model $f$ through the covariates $\{X_{j}\}_{j=1}^{p}$ taking in account that what we observe (i.e.
+$Y$) is corrupted by noise.
+Thus, if our model is good, we are able to describe $f$ better than the simply observed variable $Y$ and to use such information to assess the relevance of the features.
+Indeed, Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
 Looking at the marginal distribution, we observe that using a reference model the two group of features, i.e.
-relevant and non-relevant, have a minor overlap with respect to when the correlation is computed using directly the observed data.
-Therefore the significance of each covariate is more clearly described when those are compared to a less noisy representation of the true phenomenon of interest, that is the prediction done by a reference model.
+relevant and non-relevant, have a minor overlap, and thus can be better distinguished, with respect to when the correlation is computed using directly the observed data.
+We can think about the correlation as a general indicator of the relevance of a feature.
 
@@
 
-What is shown in Figure \ref{fig:correlation} is related also to the projection predictive approach.
-In case of a submodel belonging to the generalised linear model family, it happens that the draw-by-draw projection coincide with the maximum likelihood estimator with observed data substituted with reference model's predictions \citep{paper:original_proj}.
-It is possible to see the idea of the reference model as a filter on our data also from the projection of the predictive distribution itself.
-Let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions.
+What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
+This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
+As an another example, let us consider a candidate submodel in a feature selection process and let us refer with $\pi$ to the parameter distribution of the submodel and with $q_{\pi}(\tilde{y})$ to the induced predictive distribution.
+We would like to choose $\pi$ in order that the latter maximises some predictive performance utility, as the expected log-predictive density (elpd) defined as:
+\
+\begin{equation}\label{eq:elpd}
+\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
+\end{equation}
+If we refer to the posterior predictive distribution of a reference model with $p_{\text{ref}}(\tilde{y}|D)$, where $D$ stands for the data on which we condition on, we can approximate \eqref{eq:elpd} using $p_{\text{ref}}(\tilde{y}|D)$ instead of the true, unknown, data generation mechanism $p_{t}(\tilde{y})$.
+The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model predictive distribution and the submodel one:
+\
+\begin{equation} \label{proj_as_filter}
+\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})]
+\end{equation}
+The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred as the projection of the predictive distribution, which is the general idea behind the projection predictive approach.
+Again the reference model is acting as a filter, or substitute, on data.
+
+--- OR ---
+
+What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
+This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.
+Also the general idea of the projection of the predictive can be seen under this perspective.
+Indeed, let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions.
 The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
@@
 
-A simple, but effective, reference model approach that can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g.
+------------------
+
+Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach that can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g.
 posterior predictive mean.
@@
 \
-\begin{equation}
+\begin{equation} \label{eq:fisher_transformation}
 T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p
@@
 \text{SSE}&=\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-\text{SESE}&=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
+\text{SESE}&=\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j}=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
 \end{align}
@@
 The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise.
-In almost every simulated scenario, the reference model approach achieves a better shrinkage, resulting in a lower posterior median value for $\kappa$ for the relevant features (in red) and a higher one for the non-relevant ones.
-The only exception is the case $n=50$ and $\rho=0.3$, where we observe that on average the reference model approach slightly underestimate the shrinkage factor for the non-relevant variables with the respect to the approach without a reference model.
-However, the shrinkage factor for the relevant features is much better estimated using a reference model with a difference in the order of 0.2 units, whereas for the non-relevant features the relative underestimation is only about 0.05.
+Respectively on the y-axis and on the x-axis are depicted the shrinkage factors using the reference model approach or not.
+If the reference model did not make any difference, we would expect the points to lie on the diagonal.
+Non-relevant features happen to lie on average on the diagonal for all the simulated scenario, meaning not evident benefits coming from the reference model.
+Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals.
+Such benefit is proportional to the difficulty of the problem, that is it increase with lower correlation and number of observations.
+Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distribution of the shrinkage factors is due to the averaging over the 100 data simulations.
+In a single data realisation there would be more noise and the cluster would be closer and more overlapping.
 
@@
 \hypertarget{real-world-data}{%
-\subsection{Real world data}\label{real-world-data}}
+\subsection{Real world data: the body fat dataset}\label{real-world-data}}
 
-\begin{itemize}
-\item Bodyfat data
-\item Results for local false discovery rate
-\end{itemize}
+We conclude our experiments using the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
+Consistently with the previous comparisons, we design the variable selection by normal means problem.
+We add to the original data noisy uncorrelated covariates up to a total of 1000 features.
+These covariates are normally distributed and scaled as the original ones.
+We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher transformation.
+The original assumption in order that \eqref{eq:fisher_transformation} holds is that the variables are jointly normally distributed.
+In our experience the normal approximation is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one.
+The methods we compare are those used in Section \ref{complete-selection}, which are the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90).
+The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
+6]{book:efron}, whereas the median absolute deviation from zero for the empirical Bayes median method.
+The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance.
+In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$, $70$, $100$ up to $n=251$.
+Each time we average results over 100 bootstrap subsamples.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
+  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+  \label{fig:bodyfat_sensitivity_vs_fdr}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
+  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+  \label{fig:bodyfat_stability}
+\end{figure}
+
+Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate.
+Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
+We thus consider as non-relevant all the artificially added ones.
+When $n=70$ we observe an increment in terms of sensitivity, also the false discovery rate slightly increase, but in a lower amount.
+In all other bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate.
+We observe again that the benefits are more evident as the selection is more challenging (i.e.
+less number of observations).
+\\
+Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
+The benefit of the reference model are here marginal, small improvements can be observed, but overall not very significant.
 

### 2019-05-29 paper/ref_approach.tex
added computational burden subsection; other minor changes

@@
 
-\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection fixing abdomen and height to be always included in the model.
-We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search, the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
-In order to automatise the procedure, we select the submodel size as the smallest which has an elpd score higher than the reference model with probability 0.05.
+\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
+We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+In order to automatise the procedure, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05.
 Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection.
-The projection predictive approach has only two variables with inclusion frequencies above 50 (abdomen is the only included always), the third most included is `wrist' at 49.5 and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50, of which abdomen and height are fixed.
+The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed.
 Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
@@
 \end{tabular}
-\caption{Model predictive performances with original data (top table) and adding noisy features (bottom table). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
+\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
 \label{tab:model_performances}
 \end{table}
+
+\hypertarget{computational-burden}{%
+\subsection{Computational burden} \label{computational-burden}}
+
+\begin{itemize}
+\item add more quantitative results: e.g. times for projpred and steplm
+\end{itemize}
+
+We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique.
+It is possible to identify a common and inevitable overhead though, that is the cost of fitting the reference model.
+In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost.
+In general, a full Bayesian model is advisable to have the best predictive performance, however including all the available features can be often quite computationally demanding.
+In such a case a first possible speed-up could be to use screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}.
+However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and thus many of them have to be included in the reference model anyway.
+Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use frequentist approach, if predictions are good enough.
+
+The comparison example between projpred and steplm shows that such additional computational burden can be worth it.
+In the case of the projection predictive approach it results in sparser submodels, which can result in saving time and general costs using the selected model for future predictions.
+\ref{tab:model_performances} shows that there could be even an improvement in the prediction ability, thus justifying more additional computational costs in the selection.
+More benefits obtainable through the reference model are provided in the experiments of Section \ref{comparison}.
 
@@
 As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions.
-It consists in a linear regression using the first five supervised principal components (SPCs) \citep{paper:original_spc, paper:spc} as follows:
+It consists in a linear regression using the first five supervised principal components (SPCs) \citep{paper:original_spc, paper:piironen_spc} as follows:
 \
@@
 The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance.
-In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$, $70$, $100$ up to $n=251$.
-Each time we average results over 100 bootstrap subsamples.
+In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$.
+Each time results are averaged over 100 bootstrap subsamples.
 

### 2019-05-29 paper/ref_approach.tex
minor fix

@@
 Of course we recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
-Therefore we hope that this work can increase the interest on this family of methods and it can be of interest to a large number of practitioners.
+We hope that this work can increase the attractiveness on this family of methods and, thus, it can be of interest to a large number of practitioners.
 \\
-We would like also the reader to note that beside the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.
+We would like also the reader to note that besides the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.
 

### 2019-05-31 code/full_bayes.R
minor change

@@ -1,6 +1,4 @@
-library(dplyr)
-library(purrr)
-library(tibble)
+library(tidyverse)
 library(dimreduce)
 library(locfdr)
 library(EbayesThresh)
@@ -50,7 +48,7 @@ k_RHS_ref <- numeric(p)
 k_RHS_data <- numeric(p)
 
 for(i in 1:times){
-  data <- simulate_data()
+  data <- simulate_data() 
   y <- dplyr::pull(data, var="y")
   x <- dplyr::select(data, -contains("y"))
   

### 2019-05-31 paper/ref_approach.tex
SESE/SSE independent of n

@@
 \begin{align}
-\text{SSE}&=\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-\text{SESE}&=\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j}=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
+\text{SSE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
+\text{SESE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
+&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
 \end{align}
 where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations.
+We divide the errors by $\sqrt{n-3}$ to have quantities independent of the number of statistical units.
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
@@
 Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
-We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs} setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
+We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
+Yet we have not observed any sensibility of the results due to such a choice.
 
@@
 We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE.
-As $n$ and $\rho$ grow, the amount of error diminish, as expected, when using the reference model, whereas it unexpectedly increases when it is not used \hl{(WHY??)}.
+As $n$ and $\rho$ grow, the amount of error diminish, as expected, due to a larger amount of information of the relevance of each variable provided by the data.
 We also note that the two priors seem to achieve very similar results, regardless of the approach used.

### 2019-05-31 code/plots.R

@@ -116,6 +116,9 @@ for(nn in c(50,70,100)){
   for(rr in c(0.3,0.5)){
     load(paste("fullBayes_n",nn,"rho",rr,".Rdata",sep=""))
     
+    # Correcting SSE and SESE to be independent of n
+    results$error <- results$error/sqrt(n-3)
+    
     table_results <- table_results %>%
       bind_rows(results)
     

### 2019-05-31 code/plots.R
fixed SSE and SESE dividing by n-3

@@ -117,7 +117,7 @@ for(nn in c(50,70,100)){
     load(paste("fullBayes_n",nn,"rho",rr,".Rdata",sep=""))
     
     # Correcting SSE and SESE to be independent of n
-    results$error <- results$error/sqrt(n-3)
+    results$error <- results$error/(n-3)
     
     table_results <- table_results %>%
       bind_rows(results)

### 2019-06-03 paper/ref_approach.tex
improved introduction + started conclusions

@@
 
-In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
+%In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
 From a full Bayesian perspective, when the goal of the analysis is to do prediction, no selection should be carried out and integration over all parameters uncertainties, i.e.
@@
 Sometimes the task of the analysis is not prediction, but rather inference on which variables are substantially related to the phenomenon of interest.
+This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
+A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease.
+The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
+
+In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
+The necessity of carrying out the selection arises from different problematics.
+Sometimes the main objective of the analysis is doing prediction for future observations, thus the main focus in building the model is on the predictive performance.
+Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens, e.g.
+when we are operating on limited resources, and thus a sparser representation of the same model would be preferred.
+In addition to that, simpler models bring also advantages in terms of interpretability.
+The variable selection can also be seen as an inferential tool: some other times the interest is on knowing which are the variables that are meaningful, or relevant, in relation to the target variable of interest.
 This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
@@
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
-\cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data.
-Neural networks typically perform very well in terms of prediction, but it is not very clear how to interpret the significance of each covariate.
+\cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance.
 \cite{paper:faraggi_nn} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
-\cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso \citep{paper:tibshirani_lasso} or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
+\cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
 \cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
@@
 Following \cite{paper:goutis_projection}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
-In the special case of candidate models in the family of the GLMs, the optimisation problem correspond to the maximum likelihood estimation problem having the expected model point prediction by the reference model instead of the observed target values.
+In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values.
 Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model.
@@
 
-In this paper we try to bring motivations for the use of a reference model.
+In this paper we bring motivations for the use of a reference model.
 A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process.
@@
 In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
-We believe that these results show how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it.
-Of course we recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
+The results indicate how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it.
+We do recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
 We hope that this work can increase the attractiveness on this family of methods and, thus, it can be of interest to a large number of practitioners.
@@
 In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem.
-Finally, in Section \ref{conclusions} we present our conclusions.
+Finally, in Section \ref{discussion} we present our conclusions.
 
@@
 The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, i.e.
-to be able to have a model, that is the reference model, which is the best available description of a future observation.
-There is not a specific definition of how a reference model should be; in practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
-General guidelines on how to devise it are the same about any model in a data analysis context, expect for the fact that no selection is carried out for the reference model.
+to be able to construct a model, that is the reference model, whose description of a future observation distribution is comparable to the ``true'' data generation mechanism.
+In practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
+General modelling guidelines apply also for the reference model, expect for the fact that no variable selection is carried out at this stage.
 
@@
 The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
-Indeed, consider the following data generation mechanism for each statistical unit, already used in \cite{paper:projpred}:
+Indeed, consider the following data generation mechanism for each statistical unit, suggested in \cite{paper:projpred}:
 \
@@
 
-What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
+In Figure \ref{fig:correlation} the reference model acts as a noise-filter on the observed data through its predictions.
 This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
@@
 In the case of the projection predictive approach it results in sparser submodels, which can result in saving time and general costs using the selected model for future predictions.
-\ref{tab:model_performances} shows that there could be even an improvement in the prediction ability, thus justifying more additional computational costs in the selection.
+Table \ref{tab:model_performances} shows that there could be even an improvement in the prediction ability, thus justifying more additional computational costs in the selection.
 More benefits obtainable through the reference model are provided in the experiments of Section \ref{comparison}.
@@
 \begin{align}
-\text{SSE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-\text{SESE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
-&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
+\text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
+\text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
+&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
 \end{align}
 where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations.
-We divide the errors by $\sqrt{n-3}$ to have quantities independent of the number of statistical units.
+We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units.
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
@@
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefit of the reference model are here marginal, small improvements can be observed, but overall not very significant.
+The benefit of the reference model are here marginal, small improvements can be observed, but overall not very noticeable.
 
-\hypertarget{conclusions}{%
-\section{Conclusions and discussion}\label{conclusions}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction.
+The reference model acts as an approximation of the data generation mechanism through its predictive distribution.
+Such approximation is generally less noisy than sample estimation available from the observed data, leading to the main benefits of the reference model approach.
+In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used.
+The overall benefits, consisting in stability and goodness of the selection, observed when using point predictions of the reference model instead of the observed data, independently of the specific method applied, motivate what we refer to as the reference model approach for the model reduction framework.
+Such approach translates into a family of different methods, some of which have been present in the literature for several years.
+\\
+In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}.
+The selection via projection resulted to be more stable and led to a sparser representation.
+After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
+
+\begin{itemize}
+\item add future research
+\item extend conclusions further
+\end{itemize}
 

### 2019-06-04 paper/ref_approach.tex
first complete version

@@
   Paul-Christian B\"{u}rkner
-  and Aki Vehtari\footnote{Helsinki Institute for Information Technology HIIT,
+  and Aki Vehtari \footnote{Helsinki Institute for Information Technology HIIT,
   Department of Computer Science, Aalto University, Finland.}
@@
 \begin{abstract}
-We carry out a comparison of different methods of feature selection using or not what we call a reference model on top of the procedure, that is a model that describes well our data.
-We measure the performance and the stability of each method using both the standard approach, that simply relies on data, and the reference model one.
-We include different procedures in the comparison as a selection through high probability density posterior credibility intervals, a selection made by controlling the Q-value and the local false discovery rate.
-Finally, we include in the comparison also a real world data example.
-Results show an increased stability and a better performance of the selection in favour of the reference model approach.
+When a reference model is used to guide the variable selection problem, it acts as a noise-filter.
+We show how this translate into higher stability and goodness of the selection.
+We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods using or not the reference model.
+We include in our comparisons state-of-the-art complete selection procedures showing improved stability, false discovery rate and sensitivity of the selection, and also Bayesian methods controlling the amount of posterior shrinkage and bias.
+In addition to that we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
 \end{abstract}
@@
 Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens, e.g.
-when we are operating on limited resources, and thus a sparser representation of the same model would be preferred.
+when we are operating on limited resources, and thus a sparser representation of the model would be preferred.
 In addition to that, simpler models bring also advantages in terms of interpretability.
-The variable selection can also be seen as an inferential tool: some other times the interest is on knowing which are the variables that are meaningful, or relevant, in relation to the target variable of interest.
+Some other times, variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest.
 This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
@@
 the reference model, as an approximation of the data generation mechanism.
-Such an idea is widely present in the literature with different names.
-For example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
+Such an idea is widely present in the literature with different names; for example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
@@
 \cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
-\cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
+%\cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
 \\
 The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
-In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction.
-The best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
+In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
 The resulting problem is convex and thus many efficient optimisation algorithm are available.
@@
 Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model.
-\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance with the reference model one.
+\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
 
@@
 As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression with a real world dataset.
-We argue that however the reference model has been used, it can be always seen acting as a filter on the observed data.
+We argue that however the reference model is used, it can be always seen acting as a filter on the observed data.
 Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
@@
 We do recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
-We hope that this work can increase the attractiveness on this family of methods and, thus, it can be of interest to a large number of practitioners.
+We hope that this work can increase the attractiveness on this family of methods and, therefore, it can be of interest to a large number of practitioners.
 \\
@@
 In practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
-General modelling guidelines apply also for the reference model, expect for the fact that no variable selection is carried out at this stage.
+General modelling guidelines apply also for the reference model, except no variable selection is carried out at this stage.
 
@@
 
---- OR ---
+%--- OR ---
 
-What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
+%What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
 This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.
@@
 The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
-\
-\begin{equation} 
-\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
-\end{equation}
-Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
-\
-\begin{equation} 
-\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
-\end{equation}
-where $p_{t}$ is the distribution of a new observation under the true data generation mechanism.
+%\
+%\begin{equation} 
+%\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
+%\end{equation}
+%Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
+%\
+%\begin{equation} 
+%\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
+%\end{equation}
+%where $p_{t}$ is the distribution of a new observation under the true data generation mechanism.
 Maximising the elpd of a model is equivalent to minimising the KL-divergence of its predictive distribution from the true data generation mechanism.
 Therefore the projection corresponds to maximising the elpd using as distribution of the true data generation mechanism the posterior predictive distribution of the reference model, i.e.:
-\
-\begin{equation} \label{proj_as_filter}
-\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y}
-\end{equation}
-Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e.
+%\
+%\begin{equation} \label{proj_as_filter}
+%\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y}
+%\end{equation}
+%Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e.
 the reference model posterior predictive distribution.
 
-------------------
+%------------------
 
-Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach that can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g.
+Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach which can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g.
 posterior predictive mean.
@@
 We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features.
-While with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.
+Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.
 
@@
 In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost.
-In general, a full Bayesian model is advisable to have the best predictive performance, however including all the available features can be often quite computationally demanding.
-In such a case a first possible speed-up could be to use screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}.
+In general, a full Bayesian model is advisable in order to have the best predictive performance, however including all the available features can be often quite computationally demanding.
+In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}.
 However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and thus many of them have to be included in the reference model anyway.
@@
 
-In this Section we show the benefits of the use of a reference model.
-We consider as reference problem the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations.
-Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations, the normal means problem can be written as follows:
+In this Section we show the benefits of the use of a reference model using as a benchmark the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations.
+Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$, the normal means problem consists in estimating the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:
 \
@@
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
+
 \cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior.
-We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for the HDP posterior credible intervals using the regularised horseshoe prior.
+We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior.
 All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e.
@@
 Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals.
-Such benefit is proportional to the difficulty of the problem, that is it increase with lower correlation and number of observations.
-Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distribution of the shrinkage factors is due to the averaging over the 100 data simulations.
+Such benefit is proportional to the difficulty of the problem, that is it increases with lower correlation and number of observations.
+Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
 In a single data realisation there would be more noise and the cluster would be closer and more overlapping.
@@
 The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood.
-The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose highest probability density posterior credible interval does not include zero at the level 0.9.
+The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.
 \\
@@
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefit of the reference model are here marginal, small improvements can be observed, but overall not very noticeable.
+The benefit of the reference model are here marginal, small improvements can be observed, but overall not very notable.
 
@@
 This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction.
+We want to highlight that the goal of this paper is not to provide a specific algorithm or procedure to carry out the selection, but rather to bring motivations and attentions to the general use of a reference model.
+\\
 The reference model acts as an approximation of the data generation mechanism through its predictive distribution.
-Such approximation is generally less noisy than sample estimation available from the observed data, leading to the main benefits of the reference model approach.
+Such approximation is generally less noisy than the sample estimation available from the observed data, leading to the main benefits of the reference model approach.
 In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used.
-The overall benefits, consisting in stability and goodness of the selection, observed when using point predictions of the reference model instead of the observed data, independently of the specific method applied, motivate what we refer to as the reference model approach for the model reduction framework.
+The overall benefits we have showed independently of the specific method applied, consisting in stability and goodness of the selection, motivate what we refer to as the reference model approach for the model reduction framework.
 Such approach translates into a family of different methods, some of which have been present in the literature for several years.
@@
 After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
-
-\begin{itemize}
-\item add future research
-\item extend conclusions further
-\end{itemize}
+\\
+Whenever it is possible to come up with a reasonable reference model, our suggestion is to employ it when selecting models, because of its nature as baseline of the comparisons and its ability to improve the selection.
+Note that the main challenge in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
+\\
+All Bayesian models have been implemented using Stan \citep{paper:stan}, which uses HMC-NUTS sampler \citep{paper:NUTS} and allows full posterior Bayesian inference.
+The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.
 

### 2019-06-05 code/plots.R
changed axis scale

@@ -363,8 +363,8 @@ facet.labels <- labeller(n = function(x){paste("n=",x,sep="")})
 plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) + 
   facet_grid(~n, labeller=facet.labels) + 
   #geom_abline(intercept=0, slope=1, linetype='dashed') +
-  scale_x_continuous(limits=c(0,0.9)) +
-  scale_y_continuous(limits=c(0,0.9)) +
+  scale_x_continuous(limits=c(0,0.5)) +
+  scale_y_continuous(limits=c(0.25,0.9)) +
   geom_point(aes(shape=approach),size=2.5) +
   scale_shape_manual(values = c(16,15)) +
   geom_line(aes(col=method)) +

### 2019-06-05 paper/ref_approach.tex
minor fix

@@
 The necessity of carrying out the selection arises from different problematics.
-Sometimes the main objective of the analysis is doing prediction for future observations, thus the main focus in building the model is on the predictive performance.
-Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens, e.g.
-when we are operating on limited resources, and thus a sparser representation of the model would be preferred.
+Sometimes the leading objective of the analysis is to predict future observations, thus the main focus in building the model is on the predictive performance.
+Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens (e.g.
+when we are operating on limited resources), and thus a sparser representation of the model would be preferred.
 In addition to that, simpler models bring also advantages in terms of interpretability.
@@
 This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
-A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease.
-The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
+A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
 
@@
 A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process.
-As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression with a real world dataset.
-We argue that however the reference model is used, it can be always seen acting as a filter on the observed data.
+As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression, with a real world dataset.
+We argue that, however the reference model is used, it can be always seen acting as a filter on the observed data.
 Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
@@
 posterior predictive mean.
-Afterwards any method for feature selection can be used.
+Afterwards, any method for feature selection can be used.
 In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.
@@
 
-\begin{itemize}
-\item add more quantitative results: e.g. times for projpred and steplm
-\end{itemize}
-
 We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique.
@@
 In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}.
-However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and thus many of them have to be included in the reference model anyway.
-Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use frequentist approach, if predictions are good enough.
+However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and, thus, many of them have to be included in the reference model anyway.
+Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use a frequentist approach, if predictions are good enough.
 
@@
 
-First we use simulated data in order to vary the difficulty of the selection problem.
+Here we use simulated data in order to control the difficulty of the selection problem.
 We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation ($\rho$) and number observation ($n$), precisely $p$ and $k$ are fixed respectively at $1000$ and $100$, whereas $n\in\{50,70,100\}$ and $\rho\in\{0.3,0.5\}$.
@@
 \end{equation}
-where $\boldsymbol{u}_{i}$ stays for the $i$-th SPC and $s_{max}$ denotes the sample standard deviation of the largest SPC.
+where $u_{ij}$ stays for the $j$-th SPC of observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
 All model are implemented in Stan \citep{paper:stan}.

### 2019-06-05 paper/ref_approach.tex
language edits

@@
 We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation ($\rho$) and number observation ($n$), precisely $p$ and $k$ are fixed respectively at $1000$ and $100$, whereas $n\in\{50,70,100\}$ and $\rho\in\{0.3,0.5\}$.
-Lower the correlation level and the number of observation are, more challenging the selection is.
+Lower the correlation level and the number of observations are, more challenging the selection is.
 As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions.
@@
 Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
-We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
+We used an uniform prior on the interval $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
 Yet we have not observed any sensibility of the results due to such a choice.
 
-As already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}).
+Since, as already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}).
 In the case of the regularised horseshoe prior, we also take into account the posterior mean for the shrinkage factor for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as:
@@
 Such benefit is proportional to the difficulty of the problem, that is it increases with lower correlation and number of observations.
-Note that the perfect distinction of the two cluster of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
-In a single data realisation there would be more noise and the cluster would be closer and more overlapping.
+Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
+In a single data realisation there would be more noise and the clusters would be closer and more overlapping.
 
@@
 The control of the local false discovery rate is applied through the R-package \textit{locfdr} using splines with 7 degrees of freedom to fit the marginal density and selecting features with local false discovery rate under the value 0.2.
-Such a value is the common suggested one just for the fact that it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison.
+Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison.
 The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
@@
 For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach.
-The best selection performance is on the top left corner, which means lowest false discovery rate and highest sensitivity.
-It is possible to note that regardless of the method used for the selection, the use of a reference model improves the quality diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting).
-In accordance with what we would expect, higher the number of observation and the correlation are, easier the selection is and thus the benefit of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.
+The best selection performance is on the top-left corner of each plot, meaning lowest false discovery rate and highest sensitivity.
+It is possible to note that regardless of the method used, the use of a reference model improves the goodness of the selection diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting).
+In accordance with what expected, higher the number of observations and the correlation are, easier the selection is and, thus, the benefits of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.
 
@@
 Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals after 100 simulations.
-Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample) modelling the selection of each variable as a Bernoulli process.
+Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process.
 Further details are available in their paper as asymptotic normal distribution, based on which confidence intervals are computed.
-The reference model helps improving the stability of the selection: again such benefit is notable when the problem is more difficult (small $n$ and $\rho$).
+The reference model helps improving the stability of the selection: again, such benefit is notable when the problem is more difficult (small $n$ and $\rho$).
 We observe also less uncertainty in the stability estimates for the reference approach (i.e.
@@
 We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher transformation.
-The original assumption in order that \eqref{eq:fisher_transformation} holds is that the variables are jointly normally distributed.
-In our experience the normal approximation is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one.
-The methods we compare are those used in Section \ref{complete-selection}, which are the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90).
+The original assumption, in order that \eqref{eq:fisher_transformation} holds, is that the variables are jointly normally distributed.
+In our experience the normal approximation is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, but we estimate it from the data.
+The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90).
 The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
@@
 We thus consider as non-relevant all the artificially added ones.
-When $n=70$ we observe an increment in terms of sensitivity, also the false discovery rate slightly increase, but in a lower amount.
-In all other bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate.
+In almost all the bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate.
+When $n=50$, we observe a worsening in terms of false discovery rate, yet in a lower amount compared to the gain in sensitivity.
 We observe again that the benefits are more evident as the selection is more challenging (i.e.
@@
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefit of the reference model are here marginal, small improvements can be observed, but overall not very notable.
+The benefits of the reference model are here marginal: small improvements can be observed, but overall not very notable.
 

### 2019-06-07 paper/ref_approach.tex
minor edits

@@
 
-In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
+In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which is a special case of model reduction.
 The necessity of carrying out the selection arises from different problematics.
@@
 where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations.
-We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units.
+We divide the errors by $(n-3)$ to have quantities independent from the number of statistical units.
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.

### 2019-06-13 code/full_bayes.R
improved code structure

@@ -47,6 +47,9 @@ dl_model <- stan_model("dl_shrinkage.stan", model_name = "dl_model",
 k_RHS_ref <- numeric(p)
 k_RHS_data <- numeric(p)
 
+k_DL_ref <- numeric(p)
+k_DL_data <- numeric(p)
+
 for(i in 1:times){
   data <- simulate_data() 
   y <- dplyr::pull(data, var="y")
@@ -122,23 +125,23 @@ for(i in 1:times){
   SESE_RHS_ref <- theta_RHS_ref %>% 
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
     map(~.^2) %>%
-    map(~mean(.)) %>%
+    map(~mean(.)/(n-3)) %>%
     reduce(sum)
   SESE_RHS_data <- theta_RHS_data %>% 
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
     map(~.^2) %>%
-    map(~mean(.)) %>%
+    map(~mean(.)/(n-3)) %>%
     reduce(sum)
   
   SSE_RHS_ref <- theta_RHS_ref %>%
     map(~median(.)) %>%
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
-    map(~.^2) %>%
+    map(~(.^2)/(n-3)) %>%
     reduce(sum)
   SSE_RHS_data <- theta_RHS_data %>%
     map(~median(.)) %>%
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
-    map(~.^2) %>%
+    map(~(.^2)/(n-3)) %>%
     reduce(sum)
   
   lambda_RHS_ref <- extract(rhs_ref,pars=paste("lambda[",1:p,"]",sep=""))
@@ -177,24 +180,50 @@ for(i in 1:times){
   SESE_DL_ref <- theta_DL_ref %>% 
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
     map(~.^2) %>%
-    map(~mean(.)) %>%
+    map(~mean(.)/(n-3)) %>%
     reduce(sum)
   SESE_DL_data <- theta_DL_data %>% 
     map2(as.list(c(rep(true,k),rep(0,p-k))), ~ ..1 - ..2) %>%
[…]

### 2019-06-13 code/plots.R
improved plots

@@ -99,6 +99,10 @@ ggsave("../paper/graphics/stability.pdf",plot2,width=10,height=3)
 ###########################################
 ########### FULL BAYES PLOTS ##############
 
+#### NOTE CLEAN CODE AFTER NEW fullBayes result!!!
+# 1) no more 1/(n-3) in this script
+# 2) results_RHS and results_DL objects
+
 table_results <- tibble(error = numeric(),
                         error_type = character(),
                         prior = character(),
@@ -106,26 +110,35 @@ table_results <- tibble(error = numeric(),
                         n = numeric(),
                         rho = numeric())
 
-k_plot <- tibble(k.value = numeric(),
+k_plot_RHS <- tibble(k.value = numeric(),
                  n = numeric(),
                  rho = numeric(),
                  label = character(),
                  approach = character())
+
+k_plot_DL <- tibble(k.value = numeric(),
+                     n = numeric(),
+                     rho = numeric(),
+                     label = character(),
+                     approach = character())
 
 for(nn in c(50,70,100)){
   for(rr in c(0.3,0.5)){
     load(paste("fullBayes_n",nn,"rho",rr,".Rdata",sep=""))
     
     # Correcting SSE and SESE to be independent of n
-    results$error <- results$error/(n-3)
-    
+    #results$error <- results$error/(n-3)
+
     table_results <- table_results %>%
       bind_rows(results)
-    
-    k_plot <- k_plot %>%
-      bind_rows((k_result %>% 
-                  add_column(label = rep(c(rep('r',k),rep('s',p-k)),2)) %>%
+
+    k_plot_RHS <- k_plot_RHS %>%
+      bind_rows((k_result_RHS %>%
                   add_column(id = rep(1:p,2))))
+    
+    k_plot_DL <- k_plot_DL %>%
+      bind_rows((k_result_DL %>%
+                   add_column(id = rep(1:p,2))))
   }
 }
 
@@ -134,9 +147,10 @@ facet.labels <- labeller(error_type = function(x){x},
 
 plot_SESE_SSE <- table_results %>%
   group_by(error_type,prior,approach,n,rho) %>%
[…]

### 2019-06-13 paper/ref_approach.tex
updated version

@@
 In order to solve or, at least, simplify these problems, different feature selection procedures have been proposed both in the frequentist and the Bayesian setting \cite[e.g.
-see][]{paper:feature_selection,paper:vehtari_ojanen,paper:model_selection}.
+see][]{paper:feature_selection,vehtari2012survey,paper:model_selection}.
 Sometimes the task of the analysis is not prediction, but rather inference on which variables are substantially related to the phenomenon of interest.
@@
 A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease.
-The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
+The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
 
@@
 This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
-A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{book:efron}.
+A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
 
@@
 Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones.
-The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{paper:tibshirani_lasso} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data.
+The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{tibshirani1996regression} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data.
 The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e.
 the reference model, as an approximation of the data generation mechanism.
-Such an idea is widely present in the literature with different names; for example, \cite{book:harrell} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
+Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
-\cite{paper:faraggi_nn} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance.
-\cite{paper:faraggi_nn} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
-\cite{paper:paul_preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
-%\cite{book:harrell} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
+\cite{faraggi2001understanding} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance.
+\cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
+\cite{paul2008preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
+%\cite{harrell2015regression} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
 \\
 The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
-In the case of generalised linear models (GLMs), \cite{paper:tran_predictivelasso} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
+In the case of generalised linear models (GLMs), \cite{tran2012predictive} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
 The resulting problem is convex and thus many efficient optimisation algorithm are available.
-Following \cite{paper:goutis_projection}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
+Following \cite{goutis1998model}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
 In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values.
-Different extensions have followed \cite{paper:original_proj}, as \cite{paper:nott_projection} that add an $l_{1}$ penalty to select the best approximating model.
-\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
+Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model.
+A recent review of these methods together with some methodological improvements is given by \cite{paper:projpred}.
+%\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
 
@@
 In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem.
-Finally, in Section \ref{discussion} we present our conclusions.
+Finally, in Section \ref{conclusion} we present our conclusions.
 
@@
 
-The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,paper:vehtari_ojanen}, i.e.
+The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,vehtari2012survey}, i.e.
 to be able to construct a model, that is the reference model, whose description of a future observation distribution is comparable to the ``true'' data generation mechanism.
@@
 The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
-Indeed, consider the following data generation mechanism for each statistical unit, suggested in \cite{paper:projpred}:
+Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}.
+The data generation mechanism for each statistical unit is the following:
 \
@@
 The first $k$ covariates are significantly related to the target variable $Y$ and correlated among themselves.
-Precisely $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$.
+Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$.
 If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.
@@
   \caption{Sample correlation plot of each feature (relevant in red, non-relevant in blue) with the target variable $y$ and the latent variable $f$ respectively on the x and y axis.
-Simulation parameters: $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
+Data are generated according to procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
   \label{fig:correlation}
@@
 In Figure \ref{fig:correlation} the reference model acts as a noise-filter on the observed data through its predictions.
-This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
+This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
 As an another example, let us consider a candidate submodel in a feature selection process and let us refer with $\pi$ to the parameter distribution of the submodel and with $q_{\pi}(\tilde{y})$ to the induced predictive distribution.
@@
 %What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
-This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paper:paul_preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.
+This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.
 Also the general idea of the projection of the predictive can be seen under this perspective.
@@
 
-The projection predictive approach uses the reference model to project the posterior samples in the submodels.
-The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and additionally provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
-When the goal is prediction, the choice is usually on the smallest submodel that is sufficiently close to the reference model prediction utility score.
-Further details on the projection predictive approach can be found in \cite{paper:projpred}.
+As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels.
+The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
+\\
+We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}.
+Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main step are the followings:
+\begin{enumerate}
+\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
+\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature. The submodel are naturally identify by their model size.
+\item For each submodel, project the reference model samples as follows:
+\begin{equation}\label{eq:draw_by_draw}
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
+\end{equation}
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
+\item For each submodel (size), test the predictive performance.
+\item Choose the smallest submodel (size) that is sufficiently close to the reference model prediction utility score.
+\end{enumerate}
 
-We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{paper:bodyfat_johnson}.
+Expression \eqref{eq:draw_by_draw} is not a easy an easy optimisation problem, indeed \textit{projpred} implements the projection in the special case of submodels in the GLMs family, where \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem.
+For further details on \textit{projpred} workflow and implementation see \cite{paper:projpred}.
+
+We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}.
 The analysis is mainly taken from Vehtari's R-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, adjusting only the number of bootstrap repetitions to 1000 to have a consistent comparison with results from \cite{paper:bodyfat}.
@@
 In general, a full Bayesian model is advisable in order to have the best predictive performance, however including all the available features can be often quite computationally demanding.
-In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{paper:original_spc,paper:piironen_spc}.
+In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}.
 However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and, thus, many of them have to be included in the reference model anyway.
@@
 The objective of the analysis is to spot the whole subset of statistically relevant genes to the disease and one possible way to proceed is to compute the two-samples $t$-statistics for each gene and after combining it with the cumulative density function of the standard distribution, the resulting data can be used in the problem formulation \eqref{eq:normal_means_problem}.
-For further details see the examples in \cite{paper:efron, book:efron}.
+For further details see the examples in \cite{paper:efron, efron2012large}.
 \\
-In our examples we retrieve the normal means problem from the sample correlation using the Fisher $z$-transformation approximation \citep{paper:hawkins}.
+In our examples we retrieve the normal means problem from the sample correlation using the Fisher $z$-transformation approximation \citep{hawkins1989using}.
 Suppose to have a continuous target random variable $Y$ and a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$ and let us call $\rho_{j}=Cor(Y,X_{j})$.
@@
 There are different ways to proceed with the selection from the normal means problem, we consider in our comparison both frequentist and Bayesian state-of-the-art methods.
-From a full-Bayesian perspective, a Bayesian regression model is fitted to the normal means problem typically using a sparsifying prior as in \cite{paper:dirichlet_laplace}, \cite{paper:horseshoe+} and \cite{paper:EBmed}.
-In case of continuous priors, as the Dirichlet-Laplace (DL) and the horseshoe+ priors, there is not a canonical way to complete the selection; in their experiments \cite{paper:dirichlet_laplace} use k-means clustering over the posterior samples using the DL prior, whereas \cite{paper:horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior.
+From a full-Bayesian perspective, a Bayesian regression model is fitted to the normal means problem typically using a sparsifying prior as in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
+In case of continuous priors, as the Dirichlet-Laplace (DL) and the horseshoe+ priors, there is not a canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero; in their experiments \cite{paper:dirichlet_laplace} use k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior.
 We include in our experiments the DL and the regularised horseshoe prior \citep{paper:rhs}, which has shown in our opinion better scalability with respect to the horseshoe+, comparing the shrinkage and the correct estimation of the sparse signals using or not the reference model approach.
@@
 \end{align}
-where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations.
+where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expectations.
 We divide the errors by $(n-3)$ to have quantities independent from the number of statistical units.
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
+Note that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median.
+The results that we show later in Section \ref{shrinkage-signal} are not sensible to such a choice.
+We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as follows:
+\
+\begin{equation}
+\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}
+\end{equation}
+respectively for the regularised horseshoe and the Dirichlet-Laplace priors.
+In the left hand-side expression, $\tau$ and $\lambda_{j}$ stand for the global and local shrinkage parameters of the regularised horseshoe prior \cite[notation and further details in][]{paper:rhs}, whereas on the right hand-side $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$, following the same notation as \cite{paper:dirichlet_laplace}.
 
-\cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior.
-We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior.
+\cite{johnstone2004needles} use a prior of spike-and-slab type \citep{paper:spike_slab_mitchell} given by a mixture of a delta distribution in zero and a heavy-tailed distribution; when the latter is a Laplace distribution they show an interesting thresholding property of the median estimator and, thus, present a complete selection procedure using their prior.
+We include in our comparison such method together with the control of the local false discovery rate \citep{efron2012large, paper:efron} and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior (ci.90).
 All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e.
@@
 We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.
+Table \ref{tab:comparison} summarises the methods used in the comparison.
+
+\begin{table}[tp]
+\scriptsize
+\centering
+\begin{tabular}{l|l|l|l}
+  \hline
+ Method & Alias & Type & Quantities of interest \\ 
+  \hline
+ Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
+ Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
+ Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
+ Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
+ Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
+ \hline
+\end{tabular}
+\caption{Summary of the methods used in the comparison.}
+\label{tab:comparison}
+\end{table}
 
@@
 As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions.
-It consists in a linear regression using the first five supervised principal components (SPCs) \citep{paper:original_spc, paper:piironen_spc} as follows:
+It consists in a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as follows:
 \
@@
 where $u_{ij}$ stays for the $j$-th SPC of observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
-All model are implemented in Stan \citep{paper:stan}.
+We use as screening threshold for the SPCs the value $0.6s_{max}$, which has shown satisfying predictive performance.
+In our experiments the results are not very sensible to the chosen value, yet a more principled approach would be to use cross-validation to select the threshold as in \cite{paper:projpred}.
+\\
 The normal means problem formulation is obtained as explained in Section \ref{comparison} by Fisher-transformation.
@@
 In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}.
-Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
+Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
 We used an uniform prior on the interval $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
 Yet we have not observed any sensibility of the results due to such a choice.
-
-Since, as already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}).
-In the case of the regularised horseshoe prior, we also take into account the posterior mean for the shrinkage factor for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as:
 \
-\begin{equation}
-\kappa_{j}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}
-\end{equation}
-with $\tau$ and $\lambda_{j}$ respectively global and local shrinkage parameters, for further details see \cite{paper:rhs}.
+Since, as already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrink factors.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
-  \caption{Average SESE and SSE after 100 simulations.\\}
+  \caption{Average SESE and SSE with one standard deviation error bars after 100 simulations.\\}
   \label{fig:SESE_SSE}
@@
 
-Figure \ref{fig:k} shows the posterior medians for the shrinkage factors of each parameter, averaged after 100 data simulations.
+Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged after 100 data simulations.
 Relevant and non-relevant features are respectively highlighted in red and blue.
@@
 In a single data realisation there would be more noise and the clusters would be closer and more overlapping.
+The results for the Dirichlet-Laplace prior are very similar and they are reported in the Appendix \ref{ap:shrinkage_signal}.
 
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/k.pdf}
-  \caption{Average posterior median values for the shrinkage factors after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
+  \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
+  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
   \label{fig:k}
@@
 \subsubsection{Complete selection analysis}\label{complete-selection}}
-As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, book:efron}, the empirical Bayes median \citep{paper:EBmed} and the selection by posterior credible intervals.
-The control of the local false discovery rate is applied through the R-package \textit{locfdr} using splines with 7 degrees of freedom to fit the marginal density and selecting features with local false discovery rate under the value 0.2.
-Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36, other values can be considered and in our experience do not affect the results of the comparison.
+As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals.
+\\
+The control of the local false discovery rate is applied through the R-package \textit{locfdr}.
+It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
+In our case $f_{0}$ correspond to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}).
+The quantity of interest is the local false discovery rate (loc.fdr) defined as:
+\
+\begin{equation}
+loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
+\end{equation}
+where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values.
+The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2.
+Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $p_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison.
+We use the default setting to estimate $p_{0}$ from the data provided by the package.
+\\
 The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
@@
 The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood.
+\\
 The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.
-\\
+
 Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$.
@@
 The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
-6]{book:efron}, whereas the median absolute deviation from zero for the empirical Bayes median method.
+6]{efron2012large}, whereas the median absolute deviation from zero for the empirical Bayes median method.
 The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance.
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 \\
-All Bayesian models have been implemented using Stan \citep{paper:stan}, which uses HMC-NUTS sampler \citep{paper:NUTS} and allows full posterior Bayesian inference.
+All Bayesian models have been implemented using Stan \citep{paper:stan}, which uses HMC-NUTS sampler \citep{hoffman2014no} and allows full posterior Bayesian inference.
 The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.
@@
 
+\appendix
+
+\hypertarget{ap:shrinkage_signal}{%
+\section*{Appendix A: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
+Figure \ref{fig:k_DL} shows the posterior mean shrinkage factors using the Dirichlet-Laplace prior for the normal means problem in the simulated data study of Section \ref{comparison}.
+The result is qualitatively equal to the regularised horseshoe prior's one (see Figure \ref{fig:k}).
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/k_DL.pdf}
+  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
+  \label{fig:k_DL}
+\end{figure}
+
 \end{document}

### 2019-06-14 paper/ref_approach.tex
minor fix

@@
 The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
-In the case of generalised linear models (GLMs), \cite{tran2012predictive} provide a procedure to estimate and do variable selection with the goal of prediction: the best approximating model is recovered by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
-The resulting problem is convex and thus many efficient optimisation algorithm are available.
-Following \cite{goutis1998model}, \cite{paper:original_proj}  instead project the posterior distribution of the reference model in each candidate model and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
+Following \cite{goutis1998model}, \cite{paper:original_proj} project the posterior distribution of the reference model in each candidate model by minimisation of the Kullback-Liebler divergence, and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
 In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values.
-Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model.
-A recent review of these methods together with some methodological improvements is given by \cite{paper:projpred}.
+Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model and \cite{tran2012predictive}, who select the best approximating model by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
+A recent review of these methods together with some methodological improvements, as clustered projection and selection by comparison of a predictive performance utility, is given by \cite{paper:projpred}.
 %\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
@@
 
-Expression \eqref{eq:draw_by_draw} is not a easy an easy optimisation problem, indeed \textit{projpred} implements the projection in the special case of submodels in the GLMs family, where \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem.
+Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem, but in the special case of submodels in the GLMs family, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (e.g.
+using iteratively reweighted least squares alogirthm, IRLS).
 For further details on \textit{projpred} workflow and implementation see \cite{paper:projpred}.
@@
 Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
-Note that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median.
+Note also that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median.
 The results that we show later in Section \ref{shrinkage-signal} are not sensible to such a choice.
-We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} is defined as follows:
+We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type:
+\begin{align}
+Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
+&\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
+\end{align}
+is defined as:
+\begin{equation}
+\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}
+\end{equation}
 \
+and, thus, in our case it becomes:
 \begin{equation}
@@
 The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2.
-Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $p_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison.
-We use the default setting to estimate $p_{0}$ from the data provided by the package.
+Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison.
+We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
 \\

### 2019-06-14 code/plots.R

@@ -14,17 +14,29 @@ avg.sensitivity <- function(X){
   return(mean(tmp, na.rm = TRUE))
 }
 
+sd.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(sd(tmp, na.rm = TRUE))
+}
+
 avg.fdr <- function(X){
   tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
   return(mean(tmp, na.rm = TRUE))
+}
+
+sd.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(sd(tmp, na.rm = TRUE))
 }
 
 data.plot <- tibble(n = numeric(),
                     rho = numeric(),
                     method = character(),
                     approach = character(),
-                    recall = numeric(),
+                    sensitivity = numeric(),
+                    sensitivity.sd = numeric(),
                     fdr = numeric(),
+                    fdr.sd = numeric(),
                     stab.low = numeric(),
                     stab.mean = numeric(),
                     stab.up = numeric())
@@ -40,7 +52,9 @@ for(nn in c(50,70,100)){
               method = rep("ci.90",2),
               approach = c("ref","data"),
               sensitivity = c(avg.sensitivity(ci90_X_ref),avg.sensitivity(ci90_X_data)),
+              sensitivity.sd = c(sd.sensitivity(ci90_X_ref),sd.sensitivity(ci90_X_data)),
               fdr = c(avg.fdr(ci90_X_ref),avg.fdr(ci90_X_data)),
+              fdr.sd = c(sd.fdr(ci90_X_ref),sd.fdr(ci90_X_data)),
               stab.low = c(getStability(ci90_X_ref)$lower,getStability(ci90_X_data)$lower),
               stab.mean = c(getStability(ci90_X_ref)$stability,getStability(ci90_X_data)$stability),
               stab.up = c(getStability(ci90_X_ref)$upper,getStability(ci90_X_data)$upper))) %>%
@@ -50,7 +64,9 @@ for(nn in c(50,70,100)){
               method = rep("loc.fdr",2),
               approach = c("ref","data"),
[…]

### 2019-06-28 code/dexter/dexter.R
dexter data

@@ -1,21 +1,85 @@
 library(tidyverse)
+library(rstan)
+library(dimreduce)
+library(rstanarm)
 
 load('dexter.RData')
 
-n <- nrow(x)
-p <- ncol(x)
+## Original dataset:
+## - 9947 features (of which 2562 always zero) that represent frequencies of
+##   occurences of word stems in text
+## - target: binary variable indexing which article (statistical unit) is about
+##   corporate acquisitions
+##
+## The frequency of appearance of words in text is known to follow Zipf's law.
+## Such law has been used to input 10053 features drawn at random.
 
-xx <- as.matrix(x)
 
-constant <- numeric()
-for(i in 1:p){
-  if(sum(xx[,i])==0 | sum(xx[,i])==n) constant <- c(constant,i)
+dexter <- x
+target <- y
+
+n <- nrow(dexter)
+p <- ncol(dexter)
+
+hist(cor(as.matrix(x),y))
+
+true <- cor(as.matrix(x),y)
+
+sub <- sample(1:n,n/20)
+
+sample <- cor(as.matrix(x[sub,]),y[sub])
+
+qplot(y=true,x=sample) +
+    geom_abline(intercept=0,slope=1,linetype='dashed')
+
+## Define reference model
+
+x.sample <- as.matrix(x[sub,])
+y.sample <- y[sub]
+
+## Stan models
+nc <- 50
+dr <- spca(x.sample,y.sample, nctot=nc, screenthresh = NULL, window=p, sup.only = F, verbose = F)
+z <- predict(dr, x.sample)
+
+## fit the model
+fit <- stan_glm('y~.',data=data.frame(y=y.sample,z=z), family=binomial(link=logit),
+                prior = normal(), prior_intercept=normal(),
+                chains=2)
+
+
+bayesplot::mcmc_intervals(as.matrix(fit))
+## In-sample predictions
+
+yfit <- apply(posterior_predict(fit),2,mean)
+
+ref <- cor(x.sample,yfit)
+
+qplot(x=sample,y=true) +
+    geom_point(data=data.frame(ref=ref,true=true),aes(x=ref,y=true),color='red') +
+    geom_abline(intercept=0,slope=1,linetype='dashed')
+
+## Out-of-sample predictions
+
+yfit <- numeric(n/20)
+for(i in 1:(n/20)){
+  nc <- 10
[…]

### 2019-06-28 code/dexter/dexter.R
deleted dexter data

@@ -1,85 +1,0 @@
-library(tidyverse)
-library(rstan)
-library(dimreduce)
-library(rstanarm)
-
-load('dexter.RData')
-
-## Original dataset:
-## - 9947 features (of which 2562 always zero) that represent frequencies of
-##   occurences of word stems in text
-## - target: binary variable indexing which article (statistical unit) is about
-##   corporate acquisitions
-##
-## The frequency of appearance of words in text is known to follow Zipf's law.
-## Such law has been used to input 10053 features drawn at random.
-
-
-dexter <- x
-target <- y
-
-n <- nrow(dexter)
-p <- ncol(dexter)
-
-hist(cor(as.matrix(x),y))
-
-true <- cor(as.matrix(x),y)
-
-sub <- sample(1:n,n/20)
-
-sample <- cor(as.matrix(x[sub,]),y[sub])
-
-qplot(y=true,x=sample) +
-    geom_abline(intercept=0,slope=1,linetype='dashed')
-
-## Define reference model
-
-x.sample <- as.matrix(x[sub,])
-y.sample <- y[sub]
-
-## Stan models
-nc <- 50
-dr <- spca(x.sample,y.sample, nctot=nc, screenthresh = NULL, window=p, sup.only = F, verbose = F)
-z <- predict(dr, x.sample)
-
-## fit the model
-fit <- stan_glm('y~.',data=data.frame(y=y.sample,z=z), family=binomial(link=logit),
-                prior = normal(), prior_intercept=normal(),
-                chains=2)
-
-
-bayesplot::mcmc_intervals(as.matrix(fit))
-## In-sample predictions
-
-yfit <- apply(posterior_predict(fit),2,mean)
-
-ref <- cor(x.sample,yfit)
-
-qplot(x=sample,y=true) +
-    geom_point(data=data.frame(ref=ref,true=true),aes(x=ref,y=true),color='red') +
-    geom_abline(intercept=0,slope=1,linetype='dashed')
-
-## Out-of-sample predictions
-
-yfit <- numeric(n/20)
-for(i in 1:(n/20)){
-  nc <- 10
-  dr <- spca(x.sample[-i,],y.sample[-i], nctot=nc, screenthresh = NULL, window = p, sup.only = F, verbose = F)
-  z <- predict(dr, x.sample[-i,])
[…]

### 2019-06-28 code/plots.R
updated plots script

@@ -43,10 +43,10 @@ data.plot <- tibble(n = numeric(),
 for(nn in c(50,70,100)){
   for(rr in c(0.3,0.5)){
     load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
-    
-    data.plot <- data.plot %>% 
+
+    data.plot <- data.plot %>%
       # Credibility intervals inclusion probabilities with regularized horseshoe prior
-      bind_rows(tibble(n = rep(n,2),      
+      bind_rows(tibble(n = rep(n,2),
               rho = rep(rho,2),
               method = rep("ci.90",2),
               approach = c("ref","data"),
@@ -58,7 +58,7 @@ for(nn in c(50,70,100)){
               stab.mean = c(getStability(ci90_X_ref)$stability,getStability(ci90_X_data)$stability),
               stab.up = c(getStability(ci90_X_ref)$upper,getStability(ci90_X_data)$upper))) %>%
       # Control of the local false discovery rate
-      bind_rows(tibble(n = rep(n,2),      
+      bind_rows(tibble(n = rep(n,2),
               rho = rep(rho,2),
               method = rep("loc.fdr",2),
               approach = c("ref","data"),
@@ -70,7 +70,7 @@ for(nn in c(50,70,100)){
               stab.mean = c(getStability(lfdr_X_ref)$stability,getStability(lfdr_X_data)$stability),
               stab.up = c(getStability(lfdr_X_ref)$upper,getStability(lfdr_X_data)$upper))) %>%
       # Empirical Bayes median thresholding
-      bind_rows(tibble(n = rep(n,2),      
+      bind_rows(tibble(n = rep(n,2),
               rho = rep(rho,2),
               method = rep("EB.med",2),
               approach = c("ref","data"),
@@ -81,7 +81,7 @@ for(nn in c(50,70,100)){
               stab.low = c(getStability(ebmt_X_ref)$lower,getStability(ebmt_X_data)$lower),
               stab.mean = c(getStability(ebmt_X_ref)$stability,getStability(ebmt_X_data)$stability),
               stab.up = c(getStability(ebmt_X_ref)$upper,getStability(ebmt_X_data)$upper)))
-    
+
   }
 }
 
[…]

### 2019-06-28 code/prostate_cancer.R
prostate cancer data and script

@@ -1,0 +1,119 @@
+library(tidyverse)
+library(corrplot)
+library(bayesplot)
+theme_set(bayesplot::theme_default(base_family = "sans"))
+library(rstanarm)
+options(mc.cores = parallel::detectCores())
+library(loo)
+library(dimreduce)
+library(locfdr)
+SEED=14124869
+
+# file preview shows a header row
+diabetes <- read.csv("prostmat.csv", header = TRUE)
+
+data <- diabetes %>% 
+  rownames_to_column() %>%
+  gather(target,value,-rowname) %>%
+  spread(rowname,value) %>%
+  mutate_at('target',~as.numeric(grepl('cancer',.)))
+
+order <- as.numeric(colnames(data)[-1])
+  
+n <- nrow(data)
+p <- ncol(data)-1
+
+x <- data[,-1]
+y <- data$target
+
+nc <- 10
+
+dr1 <- spca(as.matrix(data[,-1]),data$target, nctot=1, screenthresh = NULL, window = p, sup.only = F, verbose = F)
+aa <- prcomp(as.matrix(data[,-1]))
+ggplot(data.frame(spc1=aa$x[,1],spc2=aa$x[,2],label=as.factor(y)),aes(x=spc1,y=spc2,color=label)) + geom_point()
+
+
+dr <- spca(as.matrix(data[,-1]),data$target, nctot=nc, screenthresh = NULL, window = p, sup.only = T, verbose = F)
+z <- predict(dr, x)
+
+# fit the model
+fit <- stan_glm('y~.', family = binomial(link="logit"), data = data.frame(y=y,X=z),
+                prior = normal(), prior_intercept = normal(), chains=4)
+
+folds <- sample(1:5,n,replace=TRUE)
+acc <- numeric(5)
+for(k in 1:5){
+  sel <- which(folds==k)
+  x_k <- x[sel,]
+  y_k <- y[sel]
+  
+  nc <- 10
+  dr_k <- spca(as.matrix(x_k),y_k, nctot=nc, screenthresh = NULL, window = p, sup.only = T, verbose = F)
+  z_k <- predict(dr_k, x_k)
+  
+  fit_k <- stan_glm('y~.', family = binomial(link="logit"), data = data.frame(y=y_k,X=z_k),
[…]

### 2019-06-28 code/bodyfat_steplm.R
bodyfat steplm analysis with and without ref model

@@ -1,0 +1,92 @@
+library(tidyverse)
+library(rstan)
+library(dimreduce)
+set.seed(5345334)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p <- 100
+
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+noisy_ref <- numeric(100)
+noisy_data <- numeric(100)
+
+rmse_ref <- numeric(100)
+rmse_data <- numeric(100)
+
+for(boot in 1:100){
+    noise <- array(rnorm((p-13)*n), c(n,(p-13)))
+    dfr<-cbind(df,noise=noise)
+    formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+    pred2 <- c(pred,colnames(dfr[,15:(p+1)]))
+
+    sel <- sample(1:n,n,replace=TRUE)
+    dfr.train <- dfr[sel,]
+    dfr.test  <- dfr[-unique(sel),]
+
+    step_data <- step(lm(formula2,data=dfr.train),direction='backward')
+
+    nc <- 5
+    x <- dfr.train[,-1]
+    y <- dfr.train$siri
+    dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p, sup.only = T, verbose = F)
+    z <- predict(dr, x)
+
+    ## fit the model
+
+    model_data <- list(y=y,X=z,p=ncol(z),n=n,s_max=dr$sdev[1])
+    fit <- sampling(fit_model, data = model_data,
+                    chains = 1, iter = 2000, seed = 45342)
+    predfun <- function(zt){
+        colMns <- colMeans(x)
+        colSds <- apply(x,2,sd)
+        zt <- t(apply(zt,1,function(x){(x-colMns)/colSds}))%*%dr$w
[…]

### 2019-06-28 code/fit_reference_model.R
function to estimate spca threshold by cv

@@ -1,0 +1,49 @@
+# Function to fit the reference model properly, choosing the
+# SPCA threhsold by cross-validation maximazing the lpd
+
+cv_threshold <- function(x,y,nc = 5, K = 5, sup.only.flag = FALSE){
+  n <- nrow(x)
+  p <- ncol(x)
+  
+  folds <- sample(1:K,n,replace=TRUE)
+  
+  thresholds <- seq(0.2,0.9,by=0.05)
+  logdens_fit <- numeric(length(thresholds))
+  i <- 0
+  for(thresh in thresholds){
+    i <- i + 1
+    for(k in 1:K){
+      sel <- which(folds==k)
+      x_k <- x[sel,]
+      y_k <- y[sel]
+      
+      dr_k <- spca(as.matrix(x_k),y_k, nctot=nc, screenthresh = thresh, 
+                   window = p, sup.only = sup.only.flag, verbose = F)
+      z_k <- predict(dr_k, x_k)
+      
+      model_data_k <- list(y=y_k,X=z_k,p=ncol(z_k),n=length(y_k),s_max=dr_k$sdev[1])
+      fit_k <- sampling(fit_model, data = model_data_k, 
+                      chains = 2, iter = 2000, seed = 45342)  
+      
+      draws <- as.matrix(fit_k) # posterior draws
+      sigma <- draws[,'sigma'] # noise std
+      beta <- draws[,2:(ncol(z_k)+1)] # regression coefficients
+      alpha <- draws[,'intercept'] # intercept
+      
+      predfun <- function(zt){
+        colMns <- colMeans(x_k)
+        colSds <- apply(x_k,2,sd)
+        zt <- t(apply(zt,1,function(x){(x-colMns)/colSds}))%*%dr_k$w
+        return(t( beta %*% t(zt) + alpha ))   # n x s
+      }
+     
+      mufit <- predfun(x[-sel,]) 
+      logdens_fit[i] <- logdens_fit[i] + sum(dnorm(y[-sel],mean=mufit,sd=sigma))/length(y[-sel])
+    }
+  }
+  
+  return(list(optimal=thresholds[which.max(logdens_fit)],all=logdens_fit))
+}
+
+
+res <- cv_threshold(x,y)

### 2019-06-28 code/bodyfat_comparison_outofsample.R
out of sample reference model prediction for bodyfat normal means problem

@@ -1,0 +1,174 @@
+## BODYFAT COMPARISON ##
+rm(list=ls())
+args = commandArgs(trailingOnly=TRUE) 
+library(rstan)
+library(rstanarm)
+library(locfdr)
+library(dimreduce)
+library(EbayesThresh)
+set.seed(3428954)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n_full <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip", 
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p <- 1000
+n <- as.numeric(args[1])
+times <- 100
+
+## Control of the local false discovery rate
+lfdr_X_ref <- matrix(0,nrow=times,ncol=p)
+lfdr_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Empirical Bayes median thresholding
+ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
+ebmt_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Confidence intervals inclusion probabilities 
+ci80_X_ref <- matrix(0,nrow=times,ncol=p)
+ci90_X_ref <- matrix(0,nrow=times,ncol=p)
+ci95_X_ref <- matrix(0,nrow=times,ncol=p)
+ci80_X_data <- matrix(0,nrow=times,ncol=p)
+ci90_X_data <- matrix(0,nrow=times,ncol=p)
+ci95_X_data <- matrix(0,nrow=times,ncol=p)
+
+## Stan models
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+rhs_model <- stan_model("mht_rhs_sigmaprior.stan", model_name = "rhs_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
+dfr<-cbind(df,noise=noise)
[…]

### 2019-06-28 paper/ref_approach.tex
updated paper: projpred description, bodyfat steplm analysis, explanation of fdr and EBmed, minor edits

@@
 Sometimes the leading objective of the analysis is to predict future observations, thus the main focus in building the model is on the predictive performance.
-Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens (e.g.
+Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features for future observations or computational and memory burdens (e.g.
 when we are operating on limited resources), and thus a sparser representation of the model would be preferred.
@@
 the reference model, as an approximation of the data generation mechanism.
-Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation.
+Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to seek a sparser approximation.
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
@@
 Indeed, Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
-Looking at the marginal distribution, we observe that using a reference model the two group of features, i.e.
+Looking at the marginal distribution, we observe that using a reference model the two groups of features, i.e.
 relevant and non-relevant, have a minor overlap, and thus can be better distinguished, with respect to when the correlation is computed using directly the observed data.
@@
 
-Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach which can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g.
+Relying on the idea of the reference model as a noise-filter, a simple reference model approach, which can be used on top of any feature selection procedure, consists in substituting the target observations with a point prediction of the reference model, e.g.
 posterior predictive mean.
 Afterwards, any method for feature selection can be used.
+Note that we do not argue that such reference model approach should be used as a feature selection tool in real applications; there are many other and more sophisticated ones available in the literature.
+The reason of this simple approach is to have a fair comparison between using a reference model or not with exactly the same selection procedure.
+Other kinds of comparison, as the one in Section \ref{projection}, work well as motivational examples, but fail in terms of generality, resulting in a not principled comparison since the presence of the reference model is not the only thing differentiating the two procedures.
 In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.
@@
 We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}.
-Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main step are the followings:
+Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main steps are the following:
 \begin{enumerate}
@@
 where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
+The projected samples correspond to the submodel parameter distribution.
 \item For each submodel (size), test the predictive performance.
@@
 In order to automatise the procedure, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05.
-Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection.
-The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed.
+Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusion frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection.
+The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8\%, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed.
 Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
@@
 It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
-In our case $f_{0}$ correspond to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}).
+In our case $f_{0}$ correspond to the standard normal distribution, see expression \eqref{eq:normal_means_problem2}.
 The quantity of interest is the local false discovery rate (loc.fdr) defined as:
@@
 \\
-The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.
+The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 0.05-th and the 0.95-th quantiles.
 
@@
 The original assumption, in order that \eqref{eq:fisher_transformation} holds, is that the variables are jointly normally distributed.
-In our experience the normal approximation is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, but we estimate it from the data.
+In our experience the normal approximation in \eqref{eq:fisher_transformation} is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, instead we estimate it from the data.
 The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90).
@@
 less number of observations).
-\\
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
 The benefits of the reference model are here marginal: small improvements can be observed, but overall not very notable.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
+  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
+  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+  \label{fig:bodyfat_varyingP_stability}
+\end{figure}
+
+As an additional experiment, we run the selection bootstrapping from the whole dataset, but varying the overall number of covariates from $p=100$ up to $p=5000$.
+Figures \ref{fig:bodyfat_varyingP_sensitivity_vs_fdr} and \ref{fig:bodyfat_varyingP_stability} respectively show the sensitivity against the false discovery rate and the stability results.
+As in the previous experiment, we note that the reference model has a larger impact as the complexity of the problem increases: previously as $n$ decreases, now as $p$ increases.
+Note the different scale of the sensitivity and the false discovery rate axes.
+We observe an odd behaviour of the selection via credible intervals (ci.90): when $p=100$ and $p=5000$ the results are strongly different from the other methods, both in terms of sensitivity/false discovery rate and stability.
+%Such behaviour can be in part explained by the connection between low stability and high uncertainty in the estimates.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
+  \caption{Stepwise backward selection using or not the reference model: number of noisy feature included in the model and RMSE after 100 bootstrap samples.\\}
+  \label{fig:bodyfat_step_refvsdata}
+\end{figure}
+
+Finally, we repeate the selection of Section \ref{projection} implementing the stepwise backward selection by AIC as implemented in the \textit{step} function in R.
+We have not fixed any variable to be always included in the model and the overall number of covariates (original plus noisy) is 100.
+We compare results using or not the reference model on top of the procedure; here we have used again the reference model given by the first five supervised principal components.
+Figure \ref{fig:bodyfat_step_refvsdata} shows the number of noisy features included in the final model and the out-of-sample root mean square error (RMSE).
+Results are after 100 bootstrap simulations and the predictive performance is tested on the observations excluded at each bootstrap sample.
+We observe that the reference model reduces the number of noisy features included in the final model.
+This leads to less overfit to the data and, thus, improved out-of-sample predictive performance in terms of RMSE.
+Also in this case, we see that there is not a notable difference in terms of the stability of the two approaches, which in this case is qualitatively assessed through the variability of the histogram.
+We can not use the stability measure provided by \cite{paper:stability}, since it does not take in account possibly swaps in the set of selected features due to high correlation between the covariates, which in this case can occur.
+Our reference model approach applied to the stepwise backward selection achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, as projpred (see results of Section \ref{projection}).
+
+We would like the reader to note that in this example we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and speed to fit.
+We do not argue that this is always a good choice, more sophisticated and well-thought models can lead to even better results.
+Since in our case the sake of the analysis was only explanatory in terms of the comparison we have been carrying out through the paper and needed to average results over many (100) simulations, we preferred to stick to such model.
 

### 2019-07-01 paper/ref_approach.tex
updated bodyfat real world example structure

@@
 Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features for future observations or computational and memory burdens (e.g.
-when we are operating on limited resources), and thus a sparser representation of the model would be preferred.
+when operating on limited resources), and thus a sparser representation of the model would be preferred.
 In addition to that, simpler models bring also advantages in terms of interpretability.
@@
 Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
-In a single data realisation there would be more noise and the clusters would be closer and more overlapping.
+In a single data realisation there would be more noise and the clusters would be closer and overlapping.
 The results for the Dirichlet-Laplace prior are very similar and they are reported in the Appendix \ref{ap:shrinkage_signal}.
@@
 We conclude our experiments using the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
-Consistently with the previous comparisons, we design the variable selection by normal means problem.
-We add to the original data noisy uncorrelated covariates up to a total of 1000 features.
+We carry out two different analyses: one using the normal means problem framework and the other one using the stepwise backward regression.
+In the former, we add to the original data noisy uncorrelated covariates up to a total of 1000 features.
 These covariates are normally distributed and scaled as the original ones.
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+  \caption{Sensitivity against false discovery rate after 100 bootstrap samples.\\}
   \label{fig:bodyfat_sensitivity_vs_fdr}
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
-  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+  \caption{Stability estimates with 0.95 confidence intervals after 100 bootstrap samples.\\}
   \label{fig:bodyfat_stability}
@@
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
-  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
-\end{figure}
+%\begin{figure}[tp]
+%  \centering
+%  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
+%  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+%  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
+%\end{figure}
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
-  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
-  \label{fig:bodyfat_varyingP_stability}
-\end{figure}
+%\begin{figure}[tp]
+%  \centering
+%  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
+%  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+%  \label{fig:bodyfat_varyingP_stability}
+%\end{figure}
 
-As an additional experiment, we run the selection bootstrapping from the whole dataset, but varying the overall number of covariates from $p=100$ up to $p=5000$.
+% As an additional experiment, we run the selection bootstrapping from the whole dataset, but varying the overall number of covariates from $p=100$ up to $p=5000$.
 Figures \ref{fig:bodyfat_varyingP_sensitivity_vs_fdr} and \ref{fig:bodyfat_varyingP_stability} respectively show the sensitivity against the false discovery rate and the stability results.
@@
 
-Finally, we repeate the selection of Section \ref{projection} implementing the stepwise backward selection by AIC as implemented in the \textit{step} function in R.
-We have not fixed any variable to be always included in the model and the overall number of covariates (original plus noisy) is 100.
+In the second analysis, we repeat the selection of Section \ref{projection} implementing the stepwise backward regression by AIC as implemented in the \textit{step} function in R.
+We have not fixed any variable to be always included in the model and the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
 We compare results using or not the reference model on top of the procedure; here we have used again the reference model given by the first five supervised principal components.
 Figure \ref{fig:bodyfat_step_refvsdata} shows the number of noisy features included in the final model and the out-of-sample root mean square error (RMSE).
-Results are after 100 bootstrap simulations and the predictive performance is tested on the observations excluded at each bootstrap sample.
+Results are after 100 bootstrap samples on the whole dataset, and the predictive performance is tested on the observations excluded at each bootstrap sample.
 We observe that the reference model reduces the number of noisy features included in the final model.
@@
 We can not use the stability measure provided by \cite{paper:stability}, since it does not take in account possibly swaps in the set of selected features due to high correlation between the covariates, which in this case can occur.
-Our reference model approach applied to the stepwise backward selection achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, as projpred (see results of Section \ref{projection}).
+Our reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, as projpred (see results of Section \ref{projection}).
 
@@
 After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
+Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching projection predictive approach results.
 \\
 Whenever it is possible to come up with a reasonable reference model, our suggestion is to employ it when selecting models, because of its nature as baseline of the comparisons and its ability to improve the selection.
-Note that the main challenge in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
+Note that one of the main challenges in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
 \\
@@
 \hypertarget{ap:shrinkage_signal}{%
-\section*{Appendix A: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
+\section{Appendix: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
 Figure \ref{fig:k_DL} shows the posterior mean shrinkage factors using the Dirichlet-Laplace prior for the normal means problem in the simulated data study of Section \ref{comparison}.

### 2019-07-01 code/plots.R
updated plot style

@@ -2,6 +2,10 @@
 ### Script for the plots of the paper ####
 ##########################################
 library(tidyverse)
+theme_set(theme_light() +
+          theme(strip.background = element_rect(color='black',fill='white'),
+                strip.text.x = element_text(color='black'),
+                strip.text.y = element_text(color='black')))
 library(latex2exp)
 source("getStability.R")
 
@@ -97,8 +101,8 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
  # geom_errorbarh(aes(xmin=fdr-fdr.sd, xmax=fdr+fdr.sd)) +
   scale_shape_manual(values = c(16,15)) +
   geom_line(aes(col=method)) +
-  labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method") +
-  theme_light()
+  labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
+#  theme_light()
 
 ggsave("../paper/graphics/sensitivity_vs_fdr.pdf",plot1,width=10,height=3)
 
@@ -109,8 +113,8 @@ plot2 <- ggplot(data.plot,aes(y=stab.mean,x=method,col=approach)) +
   geom_linerange(aes(ymin=stab.low,ymax=stab.up)) +
   coord_flip() +
   labs(x="",y="Stability", col="Approach") +
-  scale_color_manual(values=c("#819FF7","#FAAC58")) +
-  theme_light()
+  scale_color_manual(values=c("#819FF7","#FAAC58"))
+#  theme_light()
 
 ggsave("../paper/graphics/stability.pdf",plot2,width=10,height=3)
 
@@ -171,8 +175,8 @@ plot_SESE_SSE <- table_results %>%
   scale_x_continuous(breaks=c(50,70,100)) +
   facet_grid(error_type~rho, labeller=facet.labels) +
   labs(x="Number of observations", y="", linetype="Prior", color="Approach") +
-  scale_color_manual(values=c("#819FF7","#FAAC58")) +
-  theme_light()
+  scale_color_manual(values=c("#819FF7","#FAAC58"))
+ # theme_light()
 
 ggsave("../paper/graphics/SESE_SSE.pdf",plot_SESE_SSE,width=10,height=3)
 
[…]

### 2019-07-04 code/bodyfat_notebook.R
bodyfat steplm analysis + steplm vs projpred

@@ -1,0 +1,69 @@
+library(tidyverse)
+library(rstanarm)
+library(projpred)
+set.seed(5345334)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p0 <- 2 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+rhs_prior <- hs(global_scale=tau0)
+
+## Analysis with original covariates
+bootnum <- 100
+boot_proj <- boot_step <- matrix(0, ncol = length(pred), nrow = bootnum,
+                                 dimnames = list(NULL, pred))
+for (i in 1:bootnum) {
+  print(i)
+  set.seed(5437854+i)
+  data_id <- sample(1:dim(df)[1], replace = T)
+  fitb <- stan_glm(formula, data = df[data_id, ],
+                   prior=rhs_prior, QR=TRUE, seed=i, refresh=0)
+  bcvvs <- cv_varsel(fitb, method='forward', cv_method='LOO', nloo=n,
+                     verbose = FALSE)
+  nv <- suggest_size(bcvvs,alpha=0.1)
+  boot_proj[i, bcvvs$vind[1:nv]] <- 1
+
+  steplm <- step(lm(formula, data = df[data_id, ]), direction = 'backward')
+  boot_step[i, names(steplm$coefficients)[-1]] <- 1
+}
+
+boot_inclusion <- tibble(variable = pred,
+                         projpred = colMeans(boot_proj)*100,
+                         steplm = colMeans(boot_step)*100)
+
+## Save.image('bodyfat_notebook.Rdata')
+
+
+# Model selection frequencies
+models_step <- as_tibble(boot_step) %>%
+    group_by_at(pred) %>%
+    count() %>%
+    ungroup() %>%
+    arrange(desc(n))
+
+for(i in 1:min(10,nrow(models_step))){
[…]

### 2019-07-04 code/bodyfat_notebook_RMSE.R

@@ -1,0 +1,160 @@
+library(tidyverse)
+library(rstanarm)
+library(projpred)
+set.seed(453872238)
+
+## 10-fold cross-validation RMSE for projpred vs step.lm with and without noisy covariates
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+K <- 10
+
+## Original covariates
+sel <- step(lm(formula, data = df,  x=T,y=T),
+                direction = "backward",
+                trace = 0)
+
+p0 <- 2 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+rhs_prior <- hs(global_scale=tau0)
+fitrhs <- stan_glm(formula, data = df, prior=rhs_prior, QR=TRUE,
+                   seed=1513306866, refresh=0)
+fitrhs_cvvs <- cv_varsel(fitrhs, method = 'forward', cv_method = 'LOO',
+                          nloo=n, verbose = FALSE)
+nv <- suggest_size(fitrhs_cvvs, alpha=0.1)
+print(fitrhs_cvvs$vind[1:nv])
+
+
+perm <- sample.int(n)
+idx <- ceiling(seq(from = 1, to = n, length.out = K + 1))
+bin <- .bincode(perm, breaks = idx, right = FALSE, include.lowest = TRUE)
+lmmuss <- list()
+lmvsnlmuss <- list()
+lmvsnlnvss <- list()
+muss <- list()
+vsmuss <- list()
+vsnvss <- list()
+for (k in 1:K) {
+    message("Fitting model ", k, " out of ", K)
+    omitted <- which(bin == k)
+    ## Stepwise regression
+    lmfit_k <- lm(formula, data = df[-omitted,, drop=FALSE],  x=T,y=T)
[…]

### 2019-07-04 code/plots.R
updated plots

@@ -191,7 +191,7 @@ plot_k_RHS <- k_plot_RHS %>%
   geom_abline(slope=1,intercept=0,linetype="dashed",size=0.5) +
   geom_point(size=0.5) +
   facet_grid(rho~n, labeller=facet.labels) +
-  labs(x="k.data",y="k.ref") +
+  labs(x="kappa.data",y="kappa.ref") +
   guides(color=FALSE)
 #  theme_light()
 
@@ -203,7 +203,7 @@ plot_k_DL <- k_plot_DL %>%
   geom_abline(slope=1,intercept=0,linetype="dashed",size=0.5) +
   geom_point(size=0.5) +
   facet_grid(rho~n, labeller=facet.labels) +
-  labs(x="k.data",y="k.ref") +
+  labs(x="kappa.data",y="kappa.ref") +
   guides(color=FALSE)
 #  theme_light()
 
@@ -253,15 +253,16 @@ ggsave("../paper/graphics/post_int.pdf",post_int,width=10,height=3)
 #####################################################
 ###### BOOTSTRAP INCLUSION PROBABILITES PLOT ########
 
-load("bodyfat_bootstrap.RData")
-
+load("bodyfat_notebook.RData") # originally bodyfat_bootstrap.Rdata
+ordered <- boot_inclusion %>%
+    arrange(desc(projpred))
 inc_prob <- boot_inclusion %>%
   gather(key="method", value="freq", projpred,steplm) %>%
   ggplot(aes(x=variable,y=freq,fill=method)) +
   geom_bar(stat="identity",position=position_dodge()) +
   labs(x="",y="",fill="") +
   #guides(fill=FALSE) +
-  scale_x_discrete(limits=boot_inclusion$variable) +
+  scale_x_discrete(limits=ordered$variable) +
   scale_y_continuous(labels = scales::number_format(suffix="%")) +
   scale_fill_manual(values=c('steplm'="#819FF7",'projpred'="#FAAC58"))
 #  theme_light()
@@ -270,8 +271,26 @@ ggsave("../paper/graphics/inc_prob.pdf",inc_prob,width=10,height=3)
 
 
 # Model selection frequencies
-for (i in 1:20) {
-  print(paste(paste0(colnames(bd)[c(as.logical(bd[i,1:13]),FALSE)], collapse=", "),bd$n[i],sep=", "))
+models_step <- as_tibble(boot_step) %>%
+    group_by_at(pred) %>%
+    count() %>%
[…]

### 2019-07-04 paper/ref_approach.tex
some edits + bodyfat vs projpred analysis new without fixing variables

@@
 \begin{abstract}
-When a reference model is used to guide the variable selection problem, it acts as a noise-filter.
+When a reference model is used to guide the variable selection problem, it acts as a noise-filter modelling the data generation mechanism.
 We show how this translate into higher stability and goodness of the selection.
@@
 As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels.
-The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
+The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
 \\
@@
 using iteratively reweighted least squares alogirthm, IRLS).
-For further details on \textit{projpred} workflow and implementation see \cite{paper:projpred}.
+For further details on \texttt{projpred} workflow and implementation see \cite{paper:projpred}.
 
 We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}.
-The analysis is mainly taken from Vehtari's R-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, adjusting only the number of bootstrap repetitions to 1000 to have a consistent comparison with results from \cite{paper:bodyfat}.
+The analysis is based on from Vehtari's R-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}.
 The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure, and the original covariates are 13 anthropometric measurements (e.g.
@@
 The goal is to find the simplest model which is able to describe, that is to predict, sufficiently well the amount of fat.
+We use the same data again later in Section \ref{real-world-data}.
 
-\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
-We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
-In order to automatise the procedure, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05.
-Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusion frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection.
-The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8\%, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed.
+\cite{paper:bodyfat} report results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
+We implement the stepwise backward elimination via AIC without fixing any variable, and the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+The experiments are implemented in \texttt{R}: the stepwise elimination is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projection using the \texttt{projpred} package.
+In order to automatise the latter, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05.
+The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}: the projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 44\% and the fourth is `height' at 35\%, while the stepwise regression has seven features above 50\%.
 Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
-The first five selected models have a cumulative frequency of almost 70\% with projpred, whereas with the stepwise regression only of 11.8\%.
+The first five selected models have a cumulative frequency of 76\% with projpred, whereas with the stepwise regression only of 14\%.
 In addition to that we note that the size of the selected model is much smaller when using projpred.
@@
   \includegraphics[width=0.98\textwidth]{graphics/inc_prob.pdf}
-  \caption{Bootstrap inclusion frequencies after 1000 bootstrap samples.}
+  \caption{Bootstrap inclusion frequencies after 100 bootstrap samples.}
   \label{fig:inclusion_frequencies}
@@
   \hline
-1 & abdomen, weight & 34.2 & abdomen, height, wrist, age, chest, biceps & 3.2 \\
-2 & abdomen, wrist & 13.3 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 2.9 \\
-3 & abdomen, weight, wrist & 7.6 & abdomen, height, wrist, age, forearm, chest & 1.9 \\
-4 & abdomen, height & 7.4 & abdomen, height, wrist, age, neck, forearm, chest & 1.9 \\
-5 & abdomen, height, wrist & 6.7 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 1.9 \\
-6 & abdomen, age, wrist & 2.9 & abdomen, height, wrist, age, neck, chest, biceps & 1.8 \\
-7 & abdomen, height, neck & 2.2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 1.6 \\
-8 & abdomen, age, height, wrist & 1.2 & abdomen, height, wrist, age, neck, forearm & 1.5 \\
-9 & abdomen, weight, thigh & 1.1 & abdomen, height, wrist, age, neck, biceps & 1.5 \\
-10 & abdomen, weight, neck & 1.0 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 1.4 \\
+1 & abdomen, weight & 39 & abdomen, age, forearm, height, hip, neck, thigh, wrist & 4 \\
+2 & abdomen, wrist & 10 & abdomen, age, chest, forearm, height, neck, thigh, wrist & 4 \\
+3 & abdomen, height & 10 & abdomen, forearm, height, neck, wrist & 2 \\
+4 & abdomen, height, wrist & 9 & abdomen, forearm, neck, weight, wrist & 2 \\
+5 & abdomen, weight, wrist & 8 & abdomen, age, height, hip, thigh, wrist & 2 \\
+6 & abdomen, chest, height, wrist & 2 & abdomen, age, height, hip, neck, thigh, wrist & 2 \\
+7 & abdomen, biceps, weight, wrist & 2 & abdomen, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
+8 & abdomen, height, weight, wrist & 2 & abdomen, age, biceps, chest, height, neck, wrist & 2 \\
+9 & abdomen, age, wrist & 2 & abdomen, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
+10 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, age, ankle, biceps, weight, wrist & 2 \\
    \hline
 \end{tabular}
-\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
+\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
 \label{tab:model_frequencies}
@@
 
+%\begin{table}[tp]
+%\scriptsize
+%\centering
+%\begin{tabular}{l||l|r||l|r}
+%  \hline
+%M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
+%  \hline
+%1 & abdomen, weight & 34.2 & abdomen, height, wrist, age, chest, biceps & 3.2 \\
+%2 & abdomen, wrist & 13.3 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 2.9 \\
+%3 & abdomen, weight, wrist & 7.6 & abdomen, height, wrist, age, forearm, chest & 1.9 \\
+%4 & abdomen, height & 7.4 & abdomen, height, wrist, age, neck, forearm, chest & 1.9 \\
+%5 & abdomen, height, wrist & 6.7 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 1.9 \\
+%6 & abdomen, age, wrist & 2.9 & abdomen, height, wrist, age, neck, chest, biceps & 1.8 \\
+%7 & abdomen, height, neck & 2.2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 1.6 \\
+%8 & abdomen, age, height, wrist & 1.2 & abdomen, height, wrist, age, neck, forearm & 1.5 \\
+%9 & abdomen, weight, thigh & 1.1 & abdomen, height, wrist, age, neck, biceps & 1.5 \\
+%10 & abdomen, weight, neck & 1.0 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 1.4 \\
+%   \hline
+%\end{tabular}
+%\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
+%\label{tab:model_frequencies}
+%\end{table}
+
 Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination.
 We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features.
-Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (32 over 38) of noisy features.
+Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (13 over 19) of noisy features.
 
@@
   \hline
-projpred & 4.4 & 4.5 & 2 & -  \\
-steplm & 4.4 & 4.5 & 7 & - \\
+projpred & 4.35 & 4.47 & 2 & -  \\
+steplm & 4.38 & 4.47 & 7 & - \\
 \hline
 \hline
-projpred & $^{*}$4.4 & $^{*}$4.5 & 2 & 0  \\
-steplm & 5.3 & 5.5 & 38 & 32 \\
+projpred & 4.58 & 4.54 & 2 & 0  \\
+steplm & 5.89 & 5.43 & 19 & 13 \\
    \hline
 \end{tabular}
-\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
+\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation.}
 \label{tab:model_performances}
 \end{table}
+
+%\begin{table}[tp]
+%\scriptsize
+%\centering
+%\begin{tabular}{l|r|r|r|r}
+%  \hline
+% & rmse.full & rmse.sel & size.sel & noisy.sel \\ 
+%  \hline
+%projpred & 4.4 & 4.5 & 2 & -  \\
+%steplm & 4.4 & 4.5 & 7 & - \\
+%\hline
+%\hline
+%projpred & $^{*}$4.4 & $^{*}$4.5 & 2 & 0  \\
+%steplm & 5.3 & 5.5 & 38 & 32 \\
+%   \hline
+%\end{tabular}
+%\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
+%\label{tab:model_performances}
+%\end{table}
 
@@
 In a single data realisation there would be more noise and the clusters would be closer and overlapping.
-The results for the Dirichlet-Laplace prior are very similar and they are reported in the Appendix \ref{ap:shrinkage_signal}.
+The results for the Dirichlet-Laplace prior are very similar and we do not include them in the paper.
 
@@
 \\
-The control of the local false discovery rate is applied through the R-package \textit{locfdr}.
+The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}.
 It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
@@
 \\
-The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
+The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
 We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e.
@@
 
-We conclude our experiments using the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
+We conclude our experiments using one more time the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
 We carry out two different analyses: one using the normal means problem framework and the other one using the stepwise backward regression.
@@
 
-In the second analysis, we repeat the selection of Section \ref{projection} implementing the stepwise backward regression by AIC as implemented in the \textit{step} function in R.
-We have not fixed any variable to be always included in the model and the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
-We compare results using or not the reference model on top of the procedure; here we have used again the reference model given by the first five supervised principal components.
+In the second analysis, we repeat the selection of Section \ref{projection} via stepwise backward regression by AIC.
+In this case the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
+We compare results using or not the reference model on top of the procedure according to our simple reference model approach; here the reference model is again given by the first five supervised principal components.
 Figure \ref{fig:bodyfat_step_refvsdata} shows the number of noisy features included in the final model and the out-of-sample root mean square error (RMSE).
@@
 After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
-Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching projection predictive approach results.
+Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching the projection predictive approach results.
 \\
@@
 \\
-All Bayesian models have been implemented using Stan \citep{paper:stan}, which uses HMC-NUTS sampler \citep{hoffman2014no} and allows full posterior Bayesian inference.
+All Bayesian models have been implemented using \texttt{Stan} \citep{paper:stan}, which uses HMC-NUTS sampler \citep{hoffman2014no} and allows full posterior Bayesian inference.
 The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.
@@
 
-\appendix
+%\appendix
 
-\hypertarget{ap:shrinkage_signal}{%
-\section{Appendix: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
-Figure \ref{fig:k_DL} shows the posterior mean shrinkage factors using the Dirichlet-Laplace prior for the normal means problem in the simulated data study of Section \ref{comparison}.
+%\hypertarget{ap:shrinkage_signal}{%
+%\section{Appendix: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
+%Figure \ref{fig:k_DL} shows the posterior mean shrinkage factors using the Dirichlet-Laplace prior for the normal means problem in the simulated data study of Section \ref{comparison}.
 The result is qualitatively equal to the regularised horseshoe prior's one (see Figure \ref{fig:k}).
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/k_DL.pdf}
-  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
-  \label{fig:k_DL}
-\end{figure}
+%\begin{figure}[tp]
+%  \centering
+%  \includegraphics[width=0.98\textwidth]{graphics/k_DL.pdf}
+%  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
+%  \label{fig:k_DL}
+%\end{figure}
 

### 2019-07-08 paper/ref_approach.tex
edited abstract, intro and beginning of sec 2

@@
 When a reference model is used to guide the variable selection problem, it acts as a noise-filter modelling the data generation mechanism.
-We show how this translate into higher stability and goodness of the selection.
-We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods using or not the reference model.
+We show how this translate into higher stability and better selection of variables.
+We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods with or without a reference model.
 We include in our comparisons state-of-the-art complete selection procedures showing improved stability, false discovery rate and sensitivity of the selection, and also Bayesian methods controlling the amount of posterior shrinkage and bias.
-In addition to that we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
+Furthermore we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
 \end{abstract}
@@
 
-In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which is a special case of model reduction.
-The necessity of carrying out the selection arises from different problematics.
-Sometimes the leading objective of the analysis is to predict future observations, thus the main focus in building the model is on the predictive performance.
+In statistical applications, one of the main steps of the modelling
+workflow is covariate or feature selection, which is a special case of
+model reduction.  Simpler models bring advantages in reduced
+measurement costs and improved interpretability. Variable selection
+can be also used as an inferential tool: the interest is on knowing
+which variables contain predictive information about the target
+variable of interest.  The variable selection is most challenging in a
+\textit{small n large p} scenario, which is common case, for example,
+in microarray data analysis in medicine and biology.
+
+% The necessity of carrying out the selection arises from different problematics.
+Sometimes the leading objective of the analysis is to predict future observationgs, thus the main focus in building the model is on the predictive performance.
 Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features for future observations or computational and memory burdens (e.g.
@@
 In addition to that, simpler models bring also advantages in terms of interpretability.
-Some other times, variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest.
-This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
-A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
+Some other times,
+% variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest.
+% This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
 
-Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism.
-Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones.
-The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{tibshirani1996regression} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data.
-The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e.
-the reference model, as an approximation of the data generation mechanism.
-Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to seek a sparser approximation.
-He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
-\cite{faraggi2001understanding} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance.
-\cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
-\cite{paul2008preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$.
-%\cite{harrell2015regression} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
-\\
-The reference model approach has been used for long time also in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
+% A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
+
+The goal of the variable selection can be the minimal subset of which
+provides good predictive performance (or balance sparsity with
+predictive performance), or the all variables which have some
+predictive information about the target variable.  In the predictive
+performance based variable selection, the future data generation
+mechanism can be modelled either using the observed data or a
+reference model.
+% process is going to be based on assumptions regarding the ``true''
+% data generation mechanism.  Making assumptions means making models,
+% thus we identify two families of feature selection, or more in general
+% model reduction, approaches depending on how the data generation
+% mechanism is modelled: the data based and the reference model based
+% ones.
+The data based approaches, such as the Lasso selection
+\cite{tibshirani1996regression} and the stepwise backward/forward
+regression the observed empirical data distribution is used as a
+proxy of the future data usually in combination with cross-validation
+or information criteria to take into account the double use of the
+data.
+%
+The reference model based methods approximate the future data
+mechanism using the predictive distribution of a reference model,
+which can be, for example, the full-encompassing model. The reference
+model approach has been used for long time in the Bayesian framework
+since seminal work by \citet{paper:reference_lindley}. For more
+historical references see review by \citet{vehtari2012survey} and for
+most recent methodological development see paper by
+\citet{paper:projpred}.
+
+% The reference model approach has been used for long time in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
 Following \cite{goutis1998model}, \cite{paper:original_proj} project the posterior distribution of the reference model in each candidate model by minimisation of the Kullback-Liebler divergence, and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
@@
 A recent review of these methods together with some methodological improvements, as clustered projection and selection by comparison of a predictive performance utility, is given by \cite{paper:projpred}.
+
+The reference models have been used also in non-Bayesian context. For example,
+\cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard''.
+% and shows some examples of how it can be used to seek a sparser approximation.
+He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
+\cite{faraggi2001understanding} deal with the necessity of identifying
+interpretable risk groups in the context of survival data using neural
+networks, which typically perform very well in terms of prediction,
+but whose covariates are difficult to be understood in terms of
+relevance.
+% \cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
+\cite{paul2008preconditioning}, using the term preconditioning,
+explore approximating models fitting Lasso or stepwise regression
+against consistent estimates $\hat{y}$ of a reference model instead of
+the observed response quantities $y$.
+%\cite{harrell2015regression} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
+\\
 %\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
@@
 
-In this paper we bring motivations for the use of a reference model.
-A properly designed model is able to clean part of the noise present in the data, thus to provide an improved and more stable selection process.
-As an example, we show the improvements in the selection when using the projection predictive approach versus the stepwise regression, with a real world dataset.
+In this paper we examine in detail the benefits of using a reference
+model.  A properly designed reference model is able to filter part of
+the noise present in the data, thus to provide an improved and more
+stable selection process even if the reference model would not be the
+true data generating process. The substantial reduction of the variance is more important than small bias due the potential model misspecification.
+
 We argue that, however the reference model is used, it can be always seen acting as a filter on the observed data.
@@
 In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
-The results indicate how the core reason why the reference model based methods perform well is the reference model itself, rather than the specific way of using it.
-We do recognise that all these methods diversify how the subset of variables is actually chosen and which properties it has, thus it remains fundamental to investigate and develop such different procedures.
-We hope that this work can increase the attractiveness on this family of methods and, therefore, it can be of interest to a large number of practitioners.
+We also demonstrate the improvements in applied case when using the reference model based projection predictive approach versus the stepwise regression.
+
+The results indicate the core reason why the reference model based
+methods perform well is the reference model itself, rather than the
+specific way of using it. We do recognize that all these methods
+diversify how the subset of variables is actually chosen and which
+properties it has, thus it remains fundamental to investigate and
+develop such different procedures.
+% We hope that this work can increase
+% the attractiveness on this family of methods and, therefore, it can be
+% of interest to a large number of practitioners.
 \\
-We would like also the reader to note that besides the fact that we consider a Bayesian framework in our discussion, the reference model can and is built also in frequentist settings, as it is done in some of the references previously provided.
+We would like also the reader to note that although we focus on
+Bayesian approach, the benefits of the reference model approach can be
+obtained also in frequentist settings.
 
 The paper is structured as follows.
-In Section \ref{reference-model-approach} we introduce the idea of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
+In Section \ref{reference-model-approach} we review the concept of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
 In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem.
@@
 
-The main assumption under any reference model approach is to be operating in a $\mathcal{M}$-\textit{complete} framework \citep{book:bernardo_smith,vehtari2012survey}, i.e.
-to be able to construct a model, that is the reference model, whose description of a future observation distribution is comparable to the ``true'' data generation mechanism.
-In practice, any full-encompassing model which has a good predictive performance is a candidate reference model.
-General modelling guidelines apply also for the reference model, except no variable selection is carried out at this stage.
+The main assumption under any reference model approach is that we
+operate in a $\mathcal{M}$-\textit{complete} framework
+\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
+model which reflects in the best way our beliefs about the future
+data. In practice, this would often be the full-encompassing model
+(including as submodels all models we consider having non-zero prior
+probability) which has passed model checking and criticism \citep[see,
+e.g.][]{BDA3}.
 
-A good predictive model is able to clean part of the noise present in the data.
+A good predictive model is able to filter part of the noise present in the data.
 The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
 Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}.
-The data generation mechanism for each statistical unit is the following:
-\
+The data generation mechanism is
 \begin{alignat}{2} \label{eq:simulated_data}
@@
      X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
-     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber
+     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
 \end{alignat}
-$f$ is the latent variable of interest of which $Y$ is a noisy observation.
-The first $k$ covariates are significantly related to the target variable $Y$ and correlated among themselves.
-Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$.
+where $f$ is the latent variable of interest of which $Y$ is a noisy observation.
+The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves.
+Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any relevant covariate and respectively $f$ and $Y$.
 If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.
-When using a reference model, we are trying to model $f$ through the covariates $\{X_{j}\}_{j=1}^{p}$ taking in account that what we observe (i.e.
-$Y$) is corrupted by noise.
-Thus, if our model is good, we are able to describe $f$ better than the simply observed variable $Y$ and to use such information to assess the relevance of the features.
-Indeed, Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
-Looking at the marginal distribution, we observe that using a reference model the two groups of features, i.e.
-relevant and non-relevant, have a minor overlap, and thus can be better distinguished, with respect to when the correlation is computed using directly the observed data.
-We can think about the correlation as a general indicator of the relevance of a feature.
+
+When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$.
+If our model is good, we are able to describe $f$ better than the noisy $Y$, which imporves the accuracy in the estimation of the relevance of the covariates.
+Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
+Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly using only the observed noisy data.
 
@@
 
-In Figure \ref{fig:correlation} the reference model acts as a noise-filter on the observed data through its predictions.
-This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
+% In Figure \ref{fig:correlation} the reference model filters the noise.
+% This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
+% Above the correlation was used to estimate the relevance of a covariate.  
 As an another example, let us consider a candidate submodel in a feature selection process and let us refer with $\pi$ to the parameter distribution of the submodel and with $q_{\pi}(\tilde{y})$ to the induced predictive distribution.

### 2019-07-12 paper/ref_approach.tex
minor edits + BDA3 bibref

@@
 probability) which has passed model checking and criticism \citep[see,
-e.g.][]{BDA3}.
+e.g.][]{gelman2013bayesian}.
 
@@
 Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
-Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly using only the observed noisy data.
+Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly the observed noisy data.
 

### 2019-07-12 paper/ref_approach.tex
language improvements and minor edits

@@
 We show how this translate into higher stability and better selection of variables.
-We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods with or without a reference model.
+We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods using or not a reference model.
 We include in our comparisons state-of-the-art complete selection procedures showing improved stability, false discovery rate and sensitivity of the selection, and also Bayesian methods controlling the amount of posterior shrinkage and bias.
@@
 
-The goal of the variable selection can be the minimal subset of which
+The goal of the variable selection can be the minimal subset which
 provides good predictive performance (or balance sparsity with
-predictive performance), or the all variables which have some
+predictive performance), or the entire collection of variables which have some
 predictive information about the target variable.  In the predictive
@@
 % ones.
-The data based approaches, such as the Lasso selection
-\cite{tibshirani1996regression} and the stepwise backward/forward
-regression the observed empirical data distribution is used as a
+In the data based approaches, such as the Lasso selection
+\citep{tibshirani1996regression} and the stepwise backward/forward
+regression, the observed empirical data distribution is used as a
 proxy of the future data usually in combination with cross-validation
@@
 %
-The reference model based methods approximate the future data
+The reference model based methods approximate the future data generation
 mechanism using the predictive distribution of a reference model,
@@
 since seminal work by \citet{paper:reference_lindley}. For more
-historical references see review by \citet{vehtari2012survey} and for
-most recent methodological development see paper by
+historical references see the review by \citet{vehtari2012survey}, and for
+most recent methodological development see 
 \citet{paper:projpred}.
@@
 model.  A properly designed reference model is able to filter part of
-the noise present in the data, thus to provide an improved and more
+the noise present in the data, hence to provide an improved and more
 stable selection process even if the reference model would not be the
@@
 methods perform well is the reference model itself, rather than the
-specific way of using it. We do recognize that all these methods
+specific way of using it. We do recognise that all these methods
 diversify how the subset of variables is actually chosen and which
@@
 Relying on the idea of the reference model as a noise-filter, a simple reference model approach, which can be used on top of any feature selection procedure, consists in substituting the target observations with a point prediction of the reference model, e.g.
-posterior predictive mean.
+the posterior predictive mean.
 Afterwards, any method for feature selection can be used.
@@
 \item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
-\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature. The submodel are naturally identify by their model size.
+\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature.
+The submodel are naturally identified by their model size.
 \item For each submodel, project the reference model samples as follows:
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
 \end{equation}
@@
 We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}.
-The analysis is based on from Vehtari's R-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}.
+The analysis is based on Vehtari's \texttt{R}-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}.
 The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure, and the original covariates are 13 anthropometric measurements (e.g.
@@
 In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}.
-However, in some cases this does not always result in an appreciable speed-up, as when there are many predictive and not correlated features and, thus, many of them have to be included in the reference model anyway.
-Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or even use a frequentist approach, if predictions are good enough.
+However, in some cases this does not always result in an appreciable speed-up, as when there are several predictive and not correlated features and, thus, many of them have to be included in the reference model anyway.
+Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or use a frequentist approach, if predictions are good enough.
 
@@
 In case of continuous priors, as the Dirichlet-Laplace (DL) and the horseshoe+ priors, there is not a canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero; in their experiments \cite{paper:dirichlet_laplace} use k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior.
-We include in our experiments the DL and the regularised horseshoe prior \citep{paper:rhs}, which has shown in our opinion better scalability with respect to the horseshoe+, comparing the shrinkage and the correct estimation of the sparse signals using or not the reference model approach.
+We include in our experiments the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which has shown in our opinion better scalability with respect to the horseshoe+, comparing the shrinkage and the correct estimation of the sparse signals using or not the reference model approach.
 The quantity of interests that we consider are the average SSE (sum of square errors) and the average SESE (sum of expected square errors), defined as follows:
@@
 \cite{johnstone2004needles} use a prior of spike-and-slab type \citep{paper:spike_slab_mitchell} given by a mixture of a delta distribution in zero and a heavy-tailed distribution; when the latter is a Laplace distribution they show an interesting thresholding property of the median estimator and, thus, present a complete selection procedure using their prior.
-We include in our comparison such method together with the control of the local false discovery rate \citep{efron2012large, paper:efron} and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior (ci.90).
+We include in our comparison such method (EB.med) together with the control of the local false discovery rate \cite[loc.fdr; see][]{efron2012large, paper:efron} and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior (ci.90).
 All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e.
@@
 In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}.
-Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
+% Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
 We used an uniform prior on the interval $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.

### 2019-07-15 paper/ref_approach.tex
unifed notation equations sec 2 and 2.1

@@
 The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves.
-Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any relevant covariate and respectively $f$ and $Y$.
+Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and respectively $f$ and $Y$.
 If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.
@@
 When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$.
-If our model is good, we are able to describe $f$ better than the noisy $Y$, which imporves the accuracy in the estimation of the relevance of the covariates.
-Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
+If our model is good, we are able to describe $f$ better than the noisy $Y$, which improves the accuracy in the estimation of the relevance of the covariates.
+Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point predictions $\{\hat{y}\}_{i=1}^{n}$ of a reference model, in this case posterior predictive means of model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
 Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly the observed noisy data.
@@
 \end{equation}
-If we refer to the posterior predictive distribution of a reference model with $p_{\text{ref}}(\tilde{y}|D)$, where $D$ stands for the data on which we condition on, we can approximate \eqref{eq:elpd} using $p_{\text{ref}}(\tilde{y}|D)$ instead of the true, unknown, data generation mechanism $p_{t}(\tilde{y})$.
+If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we condition on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true, unknown, data generation mechanism $p_{t}(\tilde{y})$.
 The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model predictive distribution and the submodel one:
@@
 \begin{equation} \label{proj_as_filter}
-\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})]
+\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
 \end{equation}
@@
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
 \end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
 The projected samples correspond to the submodel parameter distribution.

### 2019-07-16 paper/ref_approach.tex
Update ref_approach.tex
rewrite the introduction

@@
 
+In statistical applications, one of the main steps in the modeling
+workflow is covariate or feature selection, which is a special case of
+model reduction. Variable selection may have multiple goals. 
+First, if the covariates themselves are of interest,
+we can use variable selection as an inferential tool to find the entire 
+collection of variables which have some predictive information about the target variable.
+Second, as simpler models come with the advantages of reduced
+measurement costs and improved interpretability, we may be interested in
+finding the minimal subset of covariates which
+provides good predictive performance (or good balance between simplicity and
+predictive performance). 
+In the latter case, where the focus is on prediction, the true data generation
+mechanism of future data can be approximated either by using the observed data directly or
+alternatively by using predictions from a \emph{reference model}.
+
+In data based approaches, such as Lasso selection
+\citep{tibshirani1996regression} or stepwise backward/forward
+regression, the observed empirical data distribution is utilized as a
+proxy of future data usually in combination with cross-validation
+or information criteria to provide estimates for out-of-sample
+predictive performance.
+In contrast, reference model based methods approximate the future data generation
+mechanism using the predictive distribution of a reference model,
+which can be, for example, a full-encompassing model including all
+covariates. The reference
+model approach has been used for long time in Bayesian statistics
+since the seminal work of \citet{paper:reference_lindley}. For more
+historical references, see the review by \citet{vehtari2012survey}, and for
+most recent methodological development see 
+\citet{paper:projpred}.
+Reference models have been also used in non-Bayesian contexts,
+where \cite{harrell2015regression} describes them as full models that
+can be thought of as a ``gold standard'' (for a given application).
+For example,
+\cite{faraggi2001understanding} deal with the necessity of identifying
+interpretable risk groups in the context of survival data using neural
+networks, which typically perform very well in terms of prediction,
+but whose covariates are difficult to be understood in terms of
+relevance. 
+\cite{paul2008preconditioning}, using the term preconditioning,
+explore approximating models fitting Lasso or stepwise regression
+against consistent estimates $\hat{y}$ of a reference model instead of
+the observed responses $y$.
+
+In this paper, we examine the benefits of using reference
+models in detail. We illustrate how a properly designed reference model is able 
+to filter parts of the noise present in the data, and hence provides an improved and more
+stable selection process. This holds even if the reference model does not actually resemble the
+true data generating process. Moreover, our analyses indicate that the substantial reduction of
+variance attributable to noise is usually
+more important than small potential bias due model misspecification.
+We argue that, regardless of how the reference model is set up and used in the
+inference prodecure, it can be always seen as acting as a filter on the observed 
+data. Following this idea, we devise a simple reference model approach that can
+be applied on top of any variable selection procedure.
+
+In our simulations and analysis of real data, we apply several state-of-the-art methods for variable selection and compare,
+for each of these methods, the results obtained by using a data based and a
+reference model based approach. When a full 
+variable selection is carried out, we report and compare quantities such as 
+the false discovery rate, sensitivity and stability of the selection. For fully Bayesian methods, we additionally report results in terms of shrinkage and accuracy of the posterior estimates.
+We show the benefits
+of a reference model approach, regardless of what specific procedure is applied, using 
+the normal means estimation problem as a benchmark. 
+Variable selection is typically most challenging in 
+\textit{small n large p} scenarios, that is, scenarios with small number of
+observations but a lot of unknown model parameters. These occur frequently, for example, in microarray data analysis in medicine or biology.
+In general, the less data we have and the more complex 
+the estimated models, the higher the benefit of using a reference
+models as the basis for variable selection.
+Our results indicate that the core reason why the reference model based
+methods perform well is the reference model itself, rather than the
+specific way of using it. We do recognise that all these methods
+diversify how the subset of variables is actually chosen and which
+properties it has, thus it remains fundamental to investigate and
+develop such different procedures. We want to note that, although we focus on
+Bayesian approach in this paper, the benefits of the reference model 
+approach can also be obtained in non-Bayesian settings.
+
+The remainder of the paper is structured as follows.
+In Section \ref{reference-model-approach}, we review the concept of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
+In Section \ref{comparison}, we use different methods for feature selection comparing the selection results with and without using a reference model in the framework of the normal means problem.
+Finally, we end with a conclusion in Section \ref{conclusion}.
+
 %In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
@@
 
-In statistical applications, one of the main steps of the modelling
-workflow is covariate or feature selection, which is a special case of
-model reduction.  Simpler models bring advantages in reduced
-measurement costs and improved interpretability. Variable selection
-can be also used as an inferential tool: the interest is on knowing
-which variables contain predictive information about the target
-variable of interest.  The variable selection is most challenging in a
-\textit{small n large p} scenario, which is common case, for example,
-in microarray data analysis in medicine and biology.
-
 % The necessity of carrying out the selection arises from different problematics.
@@
 
-The goal of the variable selection can be the minimal subset which
-provides good predictive performance (or balance sparsity with
-predictive performance), or the entire collection of variables which have some
-predictive information about the target variable.  In the predictive
-performance based variable selection, the future data generation
-mechanism can be modelled either using the observed data or a
-reference model.
 % process is going to be based on assumptions regarding the ``true''
@@
 % ones.
-In the data based approaches, such as the Lasso selection
-\citep{tibshirani1996regression} and the stepwise backward/forward
-regression, the observed empirical data distribution is used as a
-proxy of the future data usually in combination with cross-validation
-or information criteria to take into account the double use of the
-data.
-%
-The reference model based methods approximate the future data generation
-mechanism using the predictive distribution of a reference model,
-which can be, for example, the full-encompassing model. The reference
-model approach has been used for long time in the Bayesian framework
-since seminal work by \citet{paper:reference_lindley}. For more
-historical references see the review by \citet{vehtari2012survey}, and for
-most recent methodological development see 
-\citet{paper:projpred}.
 
@@
 
-The reference models have been used also in non-Bayesian context. For example,
-\cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard''.
 % and shows some examples of how it can be used to seek a sparser approximation.
 He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
-\cite{faraggi2001understanding} deal with the necessity of identifying
-interpretable risk groups in the context of survival data using neural
-networks, which typically perform very well in terms of prediction,
-but whose covariates are difficult to be understood in terms of
-relevance.
+
 % \cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
-\cite{paul2008preconditioning}, using the term preconditioning,
-explore approximating models fitting Lasso or stepwise regression
-against consistent estimates $\hat{y}$ of a reference model instead of
-the observed response quantities $y$.
+
 %\cite{harrell2015regression} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
-\\
 %\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
-
 %\cite{paper:projpred} show in their experiments the benefits of the projection predictive approach in terms of predictive ability of the selected model and smaller size compared to other methods.
@@
 
-In this paper we examine in detail the benefits of using a reference
-model.  A properly designed reference model is able to filter part of
-the noise present in the data, hence to provide an improved and more
-stable selection process even if the reference model would not be the
-true data generating process. The substantial reduction of the variance is more important than small bias due the potential model misspecification.
-
-We argue that, however the reference model is used, it can be always seen acting as a filter on the observed data.
-Following this idea, we devise a simple reference model approach that can be applied on top of any selection procedure.
-We thus show the reference model benefits, regardless of what specific procedure is applied, using as a benchmark the normal means estimation problem.
-We apply different state-of-the-art methods comparing in each case the results basing the selection on the data or on the reference model.
-In case of full Bayesian methods, we report results in terms of shrinkage and accuracy of the posterior estimates, whereas when a full selection is carried out, we compute quantities as false discovery rate, sensitivity and a measure of the stability of the selection.
-We also demonstrate the improvements in applied case when using the reference model based projection predictive approach versus the stepwise regression.
-
-The results indicate the core reason why the reference model based
-methods perform well is the reference model itself, rather than the
-specific way of using it. We do recognise that all these methods
-diversify how the subset of variables is actually chosen and which
-properties it has, thus it remains fundamental to investigate and
-develop such different procedures.
 % We hope that this work can increase
@@
 % of interest to a large number of practitioners.
-\\
-We would like also the reader to note that although we focus on
-Bayesian approach, the benefits of the reference model approach can be
-obtained also in frequentist settings.
-
-The paper is structured as follows.
-In Section \ref{reference-model-approach} we review the concept of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
-In Section \ref{comparison} we use different methods for feature selection comparing the selection results using or not the reference model in the framework of the normal means problem.
-Finally, in Section \ref{conclusion} we present our conclusions.
 

### 2019-07-16 paper/ref_approach.tex
minor edits + added references

@@
 predictive performance). 
-In the latter case, where the focus is on prediction, the true data generation
+Whenever the predictive capability is guiding the selection, the true data generation
 mechanism of future data can be approximated either by using the observed data directly or
@@
 \citep{tibshirani1996regression} or stepwise backward/forward 
-regression, the observed empirical data distribution is utilized as a
+regression \citep{venables2013modern,harrell2015regression}, the observed empirical data distribution is utilized as a
 proxy of future data usually in combination with cross-validation
@@
 We argue that, regardless of how the reference model is set up and used in the
-inference prodecure, it can be always seen as acting as a filter on the observed 
+inference procedure, it can be always seen as acting as a filter on the observed 
 data. Following this idea, we devise a simple reference model approach that can
@@
 variable selection is carried out, we report and compare quantities such as 
-the false discovery rate, sensitivity and stability of the selection. For fully Bayesian methods, we additionally report results in terms of shrinkage and accuracy of the posterior estimates.
+the false discovery rate \citep{paper:fdr_BH}, sensitivity and stability of the selection \citep{paper:stability}.
+For fully Bayesian methods, we additionally report results in terms of shrinkage and accuracy of the posterior estimates.
 We show the benefits
@@
 \textit{small n large p} scenarios, that is, scenarios with small number of
-observations but a lot of unknown model parameters. These occur frequently, for example, in microarray data analysis in medicine or biology.
+observations but a lot of unknown model parameters. 
+These occur frequently, for example, 
+in microarray data analysis in medicine or biology \citep{dudoit2003multiple,liao2007logistic,paper:efron}.
 In general, the less data we have and the more complex 

### 2019-07-16 paper/ref_approach.tex
edit section 2

--- 2019-07-16 paper/ref_approach.tex
@@
 The main assumption under any reference model approach is that we
-operate in a $\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
-model which reflects in the best way our beliefs about the future
-data. In practice, this would often be the full-encompassing model
-(including as submodels all models we consider having non-zero prior
-probability) which has passed model checking and criticism \citep[see,
+operate in an $\mathcal{M}$-\textit{complete} framework
+\citep{book:bernardo_smith,vehtari2012survey}.
+That is, we assume to be able to construct a model whose predictions reflect the best available description of the uncertainty of future data.
+In practice, this will often be the full-encompassing model
+(including all models we consider having non-zero prior
+probability as submodels) which has passed model checking and criticism \citep[see,
 e.g.][]{gelman2013bayesian}.
 
-A good predictive model is able to filter part of the noise present in the data.
+A good predictive model is able to filter parts of the noise present in the data.
 The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
@@
 The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves.
-Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and respectively $f$ and $Y$.
-If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.
+Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and, respectively, $f$ and $Y$.
+If we had an infinite amount of observations, the sample correlation would be equal to the true correlation between $X_j$ and $Y$.
+However, even in this ideal asymptotic regime, this  correlation would still remain a biased indicator of the true relevance of each covariate (represented by the correlation between $X_j$ and $f$) due to the intrinsic noisy nature of $Y$.
 
-When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$.
-If our model is good, we are able to describe $f$ better than the noisy $Y$, which improves the accuracy in the estimation of the relevance of the covariates.
-Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point predictions $\{\hat{y}\}_{i=1}^{n}$ of a reference model, in this case posterior predictive means of model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$.
-Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly the observed noisy data.
+When using a reference model, we first obtain predictions for $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we have only observed the noisy representation $Y$ of $f$.
+If our model is good, we are able to describe $f$ better than $Y$ itself can, which improves the accuracy in the estimation of the relevance of the covariates.
+Figure \ref{fig:correlation} illustrates this process in the form of a scatter plot of (absolute) correlations of the covariates with $Y$ against the corresponding correlations with the predictions of a reference model (in this case the posterior predictive means of model \eqref{eq:ref_mod}; see Section \ref{simulated-data}).
+Looking at the marginal distributions, we see that using a reference model to filter out noise in the data, the two groups of features (relevant and non-relevant) can be distinguished much better than when the correlation is computed using the observed noisy data directly.
 
@@
 % Above the correlation was used to estimate the relevance of a covariate.  
-As an another example, let us consider a candidate submodel in a feature selection process and let us refer with $\pi$ to the parameter distribution of the submodel and with $q_{\pi}(\tilde{y})$ to the induced predictive distribution.
-We would like to choose $\pi$ in order that the latter maximises some predictive performance utility, as the expected log-predictive density (elpd) defined as:
+As an another example, let us consider a candidate submodel in a feature selection process and let us refer to the parameter distribution of the submodel by $\pi$ and to the induced predictive distribution by $q_{\pi}(\tilde{y})$.
+We would like to choose $\pi$ so that $q_{\pi}(\tilde{y})$ maximises some predictive performance utility, for example, the expected log-predictive density (elpd) defined as:
 \
 \begin{equation}\label{eq:elpd}
-\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
+\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
 \end{equation}
-If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we condition on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true, unknown, data generation mechanism $p_{t}(\tilde{y})$.
-The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model predictive distribution and the submodel one:
+where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating mechanism of future data $\tilde{y}$.
+If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we conditioned on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true data generation mechanism $p_{t}(\tilde{y})$.
+The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model's and the submodel's predictive distributions:
 \
@@
 \end{equation}
-The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred as the projection of the predictive distribution, which is the general idea behind the projection predictive approach.
+The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred to as the projection of the predictive distribution, which is the general idea behind the projection predictive approach (cite).
 Again the reference model is acting as a filter, or substitute, on data.
@@
 
-Relying on the idea of the reference model as a noise-filter, a simple reference model approach, which can be used on top of any feature selection procedure, consists in substituting the target observations with a point prediction of the reference model, e.g.
-the posterior predictive mean.
+Relying on the idea of the reference model as a noise-filter, a generic reference model approach, which can be used on top of any feature selection procedure, consists of simply substituting the target observations with corresponding point predictions of the reference model, for instance, the posterior predictive means.
 Afterwards, any method for feature selection can be used.
-Note that we do not argue that such reference model approach should be used as a feature selection tool in real applications; there are many other and more sophisticated ones available in the literature.
-The reason of this simple approach is to have a fair comparison between using a reference model or not with exactly the same selection procedure.
-Other kinds of comparison, as the one in Section \ref{projection}, work well as motivational examples, but fail in terms of generality, resulting in a not principled comparison since the presence of the reference model is not the only thing differentiating the two procedures.
-In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.
+Note that we do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications.
+There are several more sophisticated reference model approaches available in the literature (cite), which are likely to yield even better results.
+Rather, the reason for focussing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures.
+Other kinds of comparisons, as the one presented in Section \ref{projection}, work well as motivational examples but fail in terms of generality since the presence or absence of a reference model is not the only aspect differentiating the two procedures.
+We will come back to the more general comparison in Section \ref{comparison}.
+
+%we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.
 
@@
 
-As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels.
+As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples to the submodels (cite).
 The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
@@
 We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}.
-Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main steps are the following:
+Suppose we have observed $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates for which we want to obtain a minimally relevant subset.
+Than, the main steps are the following:
 \begin{enumerate}
-\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
-\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature.
-The submodel are naturally identified by their model size.
-\item For each submodel, project the reference model samples as follows:
+\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ posterior samples of the reference model's parameters.
+\item Rank the covariates according to their relevance using some heuristics and consider as candidate submodels only those which preserve this order,  starting from including only the highest ranked covariate (the submodels are then naturally identified by their model size).
+This is not strictly necessary but reduces the number of submodels to consider in the following steps.
+\item For each submodel, project the reference model's samples as follows:
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right) \quad s=1,..,S
 \end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
-The projected samples correspond to the submodel parameter distribution.
-\item For each submodel (size), test the predictive performance.
-\item Choose the smallest submodel (size) that is sufficiently close to the reference model prediction utility score.
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the predictive distribution of the reference model with parameters fixed at the posterior sample $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate values related to the statistical unit (identified by the subscript $i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the predictive distribution of the submodel.
+The projected samples $\boldsymbol{\theta}_{\perp}^{s}$ then correspond to the submodel's parameter distribution.
+\item For each submodel (size), test the predictive performance for instance via cross-valdiation.
+\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
 \end{enumerate}
 
-Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem, but in the special case of submodels in the GLMs family, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (e.g.
-using iteratively reweighted least squares alogirthm, IRLS).
-For further details on \texttt{projpred} workflow and implementation see \cite{paper:projpred}.
+Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem in general, but in the special case of submodels for the family of generalize lineder models, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (cite).
+For further details on the projective prediction workflow and implementation see \cite{paper:projpred}.
 
@@
 The analysis is based on Vehtari's \texttt{R}-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}.
-The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure, and the original covariates are 13 anthropometric measurements (e.g.
-height, weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection, for a total of 251 observations.
-The goal is to find the simplest model which is able to describe, that is to predict, sufficiently well the amount of fat.
-We use the same data again later in Section \ref{real-world-data}.
+The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure.
+Additionally, we have information about 13 covariates which are anthropometric measurements (e.g., height and weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection.
+In total, we have 251 observations.
+The goal is to find the simplest model which is able to predict the amount of fat sufficiently well.
+We use the same data again later on in Section \ref{real-world-data}.
 
-\cite{paper:bodyfat} report results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
-We implement the stepwise backward elimination via AIC without fixing any variable, and the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
-The experiments are implemented in \texttt{R}: the stepwise elimination is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projection using the \texttt{projpred} package.
-In order to automatise the latter, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05.
-The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}: the projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 44\% and the fourth is `height' at 35\%, while the stepwise regression has seven features above 50\%.
-Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
-The first five selected models have a cumulative frequency of 76\% with projpred, whereas with the stepwise regression only of 14\%.
-In addition to that we note that the size of the selected model is much smaller when using projpred.
+\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
+Here, we implement steplm via AIC without fixing any variable.
+For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients (cite), submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+The experiments are implemented in \texttt{R} (cite).
+The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package.
+In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher than the reference model score with probability 0.05.
+The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}.
+The projpred approach has only two variables, 'abdomen' and 'weight', with inclusion frequencies above 50\% ('abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
+Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
+For exaple, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm.
+In addition, we note that the size of the selected model is much smaller when using projpred.
 
@@
 
-Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination.
-We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features.
-Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (13 over 19) of noisy features.
+Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the corresponding selected submodel using both projpred and steplm.
+We also repeat the selection after adding truely uncorrelated (i.e., irrelevant) features up to a total of 100 covariates.
+For this experiment, we report both the size of the selected submodel and the number of selected irrelevant features.
+Whilst, with the original data, we do not observe any gain using projpred in terms of predictive performance, what we do observe is a smaller size for the selected submodel, at the cost of a higher computation time compared to steplm.
+However, when additional irrelevant features are added, projpred is able to notably improve the predictive performance keeping the same submodel size, whereas steplm selects a much larger submodel also including a large number of irrelvant features (13 irrelevant out of a total of 19 selected features).
 
@@
   \hline
- & rmse.full & rmse.sel & size.sel & noisy.sel \\ 
+ & RMSE(Full) & RMSE(Sel) & Size(Sel) & SizeIr(Sel) \\ 
   \hline
@@
 \end{tabular}
-\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation.}
+\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation.
+Abbreviations: Full = full model; Sel = selected submodel; Size = total number of included covariates; SizeIr = number of included irrelevant covariates.}
 \label{tab:model_performances}
@@
 
-We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique.
-It is possible to identify a common and inevitable overhead though, that is the cost of fitting the reference model.
-In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost.
-In general, a full Bayesian model is advisable in order to have the best predictive performance, however including all the available features can be often quite computationally demanding.
-In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}.
-However, in some cases this does not always result in an appreciable speed-up, as when there are several predictive and not correlated features and, thus, many of them have to be included in the reference model anyway.
-Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or use a frequentist approach, if predictions are good enough.
+We consider the reference model approach as a family of methods, thus providing a general answer to the question of computational burden is not possible because not unique.
+It is possible to identify a common and inevitable overhead, though, which is the cost of fitting the reference model.
+In the simple ''bare-bones'' reference model approach we have described above, it is actually the only added cost.
+In general, a full Bayesian model is advisable in order to have the best predictive performance.
+However, including all the available features can often be quite computationally demanding.
+In such a case, a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}.
+However, in some cases, this does not always result in an appreciable speed-up.
+For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model anyway.
+Other alternatives could be fixing some parameters to their maximum marginal likelihood value (typically referred as empirical Bayes; cite) or use a completely frequentist approach, if predictions are good enough.
 
 The comparison example between projpred and steplm shows that such additional computational burden can be worth it.
-In the case of the projection predictive approach it results in sparser submodels, which can result in saving time and general costs using the selected model for future predictions.
-Table \ref{tab:model_performances} shows that there could be even an improvement in the prediction ability, thus justifying more additional computational costs in the selection.
-More benefits obtainable through the reference model are provided in the experiments of Section \ref{comparison}.
+We found that the reference model approach (projpred) selected much sparser submodels, which can result in saving time and general costs using the selected model for future predictions.
+Table \ref{tab:model_performances} displays that there could even be an improvement in the predictive ability compared to the full model, thus justifying more additional computational costs in the selection procedure.
+More benefits obtainable through a reference model approach are provided in the experiments discussed in the upcoming section.
 

### 2019-07-16 paper/ref_approach.tex
one more edit to section 2

@@
 The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package.
-In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher than the reference model score with probability 0.05.
+In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher (i.e., better) than the reference model score with probability of at least 5\%.
 The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}.

### 2019-07-16 paper/ref_approach.tex
start editing Section 3

@@
 
-In this Section we show the benefits of the use of a reference model using as a benchmark the normal means estimation problem, which consists in estimating the vector of means, usually sparse, of a normal vector of observations.
-Let us call $p$ the dimensionality of the vector of means and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$, the normal means problem consists in estimating the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:
+In this section, we demonstrate the benefits of reference model approaches using the normal means problem as a benchmark.
+The normal means problem consists of estimating the (usually sparse) vector of means of a vector of normally distributed observations.
+Let us denote the dimensionality of the vector of means by $p$ and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$.
+In the normal means problem, the task is to estimate the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:
 \
@@
 \end{equation}
-Note that it is equivalent to a linear regression where the design matrix is the identity one.
-This formulation can be retrieved in different ways, a common example is given by microarray data, where a large set of genes are usually tested in two groups of patient labelled as positive or negative to some disease.
-The objective of the analysis is to spot the whole subset of statistically relevant genes to the disease and one possible way to proceed is to compute the two-samples $t$-statistics for each gene and after combining it with the cumulative density function of the standard distribution, the resulting data can be used in the problem formulation \eqref{eq:normal_means_problem}.
+Note that it is equivalent to a linear regression where the design matrix is the identity matrix with the number of features being equal to the number of observations.
+This formulation can be found in practice at various places,
+for example, in the analysis of microarray data, where a large set of genes are tested in two groups of patients labeled as positive or negative to some disease (cite).
+The objective of the analysis is to select the subset of genes statistically relevant to the disease.
+One common way to proceed is to compute the two-samples $t$-statistic for every gene separately.
+After normalizing these statistics, they then become the data, $Z$, in the normal means problem \eqref{eq:normal_means_problem}.
 For further details see the examples in \cite{paper:efron, efron2012large}.
-\\
-In our examples we retrieve the normal means problem from the sample correlation using the Fisher $z$-transformation approximation \citep{hawkins1989using}.
-Suppose to have a continuous target random variable $Y$ and a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$ and let us call $\rho_{j}=Cor(Y,X_{j})$.
-Suppose to observe $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the j-th covariate $\{x_{ij}\}_{i=1}^{n}$.
-Let finally refer to the function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$.
-It holds the following modelling approximation (assuming each pair $(Y,X_{j})$ normally distributed):
+
+In our examples, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}.
+Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and let us denote $\rho_{j}=Cor(Y,X_{j})$.
+Further, suppose we have observed $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the $j$-th covariate $\{x_{ij}\}_{i=1}^{n}$.
+Finally, we refer to the Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$.
+Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed as well with known variance:
 \
@@
 \end{equation}
-Therefore rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we find again formulation \eqref{eq:normal_means_problem} with unit variance:
+Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we again find the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
 \
@@
 \end{equation}
-Note that now the quantity of interest $\theta_{j}$ stands for $\sqrt{n-3}\,T_{F}(\rho_{j})$.
-There are different ways to proceed with the selection from the normal means problem, we consider in our comparison both frequentist and Bayesian state-of-the-art methods.
-From a full-Bayesian perspective, a Bayesian regression model is fitted to the normal means problem typically using a sparsifying prior as in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
-In case of continuous priors, as the Dirichlet-Laplace (DL) and the horseshoe+ priors, there is not a canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero; in their experiments \cite{paper:dirichlet_laplace} use k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior.
-We include in our experiments the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which has shown in our opinion better scalability with respect to the horseshoe+, comparing the shrinkage and the correct estimation of the sparse signals using or not the reference model approach.
-The quantity of interests that we consider are the average SSE (sum of square errors) and the average SESE (sum of expected square errors), defined as follows:
+Note that in thise cse the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
+There are different ways to proceed with the selection in the normal means problem.
+Here, we consider several state-of-the-art approaches from both Bayesian and frequentist statistics (TODO: do we actually consider frequentist approaches here?)
+
+We begin by explaining some Bayesian estimation methods to solving the normal means problem.
+They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
+If these priors have continuous support, as is the case for the Dirichlet-Laplace (DL; cite) or horseshoe-like priors (cite), there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero.
+\cite{paper:dirichlet_laplace} suggest k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior (TODO: is this related to the former sentence?).
+In our experiments, we include the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better to higher number of covariates as compared to other horseshoe-like priors.
+For the Bayesian regression models with these priors, we compare the posterior shrinkage and the correct estimation of the sparse signals with and without using a reference model as a noise filter.
+For this purpose, we consider the   average SSE (sum of square errors) and the average SESE (sum of expected square errors) as quantities measuring estimation accuracy.
+They are defined as
 \
@@
 \end{align}
-where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expectations.
-We divide the errors by $(n-3)$ to have quantities independent from the number of statistical units.
-Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates.
-Note also that any kind of point estimate could be used to compute the SSE, here we follow \cite{paper:dirichlet_laplace} using the posterior median.
-The results that we show later in Section \ref{shrinkage-signal} are not sensible to such a choice.
-We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type:
+where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$.
+We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units.
+Note that the SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates.
+Note that actually any kind of point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median.
+The results that we show later on in Section \ref{shrinkage-signal} are not sensible to such a choice.
+
+We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type (TODO: please motivate why looking at shrinkage factors is relevant)
 \begin{align}
@@
 \end{align}
-is defined as:
+is defined as
 \begin{equation}
-\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}
+\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
 \end{equation}
 \
-and, thus, in our case it becomes:
+In our case, $\kappa_{j}$ can be computed as
 \begin{equation}
@@
 respectively for the regularised horseshoe and the Dirichlet-Laplace priors.
-In the left hand-side expression, $\tau$ and $\lambda_{j}$ stand for the global and local shrinkage parameters of the regularised horseshoe prior \cite[notation and further details in][]{paper:rhs}, whereas on the right hand-side $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$, following the same notation as \cite{paper:dirichlet_laplace}.
+In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}.
 
-\cite{johnstone2004needles} use a prior of spike-and-slab type \citep{paper:spike_slab_mitchell} given by a mixture of a delta distribution in zero and a heavy-tailed distribution; when the latter is a Laplace distribution they show an interesting thresholding property of the median estimator and, thus, present a complete selection procedure using their prior.
-We include in our comparison such method (EB.med) together with the control of the local false discovery rate \cite[loc.fdr; see][]{efron2012large, paper:efron} and a simple selection procedure using inclusion probability at 0.9 for posterior credible intervals using the regularised horseshoe prior (ci.90).
-All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e.
-ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e.
-ratio of the number of relevant selected features over the total number of relevant features).
-We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.
-Table \ref{tab:comparison} summarises the methods used in the comparison.
+Within the set of complete selection procedures, we consider three 
+Bayesian methods which are described in the following.
+\cite{johnstone2004needles} use a spike-and-slab type prior given by a mixture of a delta distribution in zero and a heavy-tailed distribution \cite[see also][]{paper:spike_slab_mitchell}.
+When the latter is a Laplace distribution, they show an interesting thresholding property of the median estimator and, based on this observation, present a complete selection procedure using their prior.
+We refer to this method as EB.med.
+In our experiments, we not only include the EB.med on its own but also in combination with an additional control of the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}.
+Further, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90).
+All of these methods provide a complete selection procedure and we compare their performance with and without using a reference model on top of them.
+As criteria of selection performance, we evaluate the average false discovery rate (i.e., the ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e., the ratio of the number of relevant selected features over the total number of relevant features).
+We also provide a comparison of the stability of the selection by means of a stability measure proposed by \cite{paper:stability}.
+Table \ref{tab:comparison} summarises the methods used in out numerical experiments.
 
@@
 \end{tabular}
-\caption{Summary of the methods used in the comparison.}
+\caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
 \label{tab:comparison}

### 2019-07-17 paper/ref_approach.tex
more edits to section 3

@@
 There are different ways to proceed with the selection in the normal means problem.
-Here, we consider several state-of-the-art approaches from both Bayesian and frequentist statistics (TODO: do we actually consider frequentist approaches here?)
+Here, we consider several state-of-the-art approaches primarily from Bayesian statistics.
 
@@
 If these priors have continuous support, as is the case for the Dirichlet-Laplace (DL; cite) or horseshoe-like priors (cite), there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero.
-\cite{paper:dirichlet_laplace} suggest k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior (TODO: is this related to the former sentence?).
+Whereas \cite{paper:dirichlet_laplace} used k-means clustering over the posterior samples to perform the actual selection, \cite{bhadra2017horseshoe+} just focused their analysis on the obtained shrinkage and the correct estimation of the sparse signals without any actual selection.
 In our experiments, we include the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better to higher number of covariates as compared to other horseshoe-like priors.
@@
 
-We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type (TODO: please motivate why looking at shrinkage factors is relevant)
+For shrinkage priors, one centeral aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features.
+Ideally, the irrelevant features should be completely shrunken to zero while the relevant features should not be shrunken at all.
+The amount of shrinkage can be quantitified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage).
+For model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type
 \begin{align}
@@
 \end{align}
-is defined as
+the shrinkage factor $\kappa_{j}$ is defined as
 \begin{equation}
@@
 \end{equation}
-respectively for the regularised horseshoe and the Dirichlet-Laplace priors.
+for the regularised horseshoe and the Dirichlet-Laplace prior respectively.
 In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}.
+We will use the posterior mean of $\kappa_{j}$ as a point estimate.
 
@@
 We refer to this method as EB.med.
-In our experiments, we not only include the EB.med on its own but also in combination with an additional control of the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}.
+Further, we use a method to control for the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}.
 Further, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90).
@@
 Here we use simulated data in order to control the difficulty of the selection problem.
-We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation ($\rho$) and number observation ($n$), precisely $p$ and $k$ are fixed respectively at $1000$ and $100$, whereas $n\in\{50,70,100\}$ and $\rho\in\{0.3,0.5\}$.
-Lower the correlation level and the number of observations are, more challenging the selection is.
-As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions.
-It consists in a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as follows:
+We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation $\rho\in\{0.3,0.5\}$ and number observation $n\in\{50,70,100\}$.
+The total number of covariates $p$ and the number of relevant covariates $k$ are fixed to $p = 1000$ and $k = 100$, respectively.
+In general, the lower $\rho$ and $n$, the more challenging the selection.
+As mentioned, this data generation mechanism was originally proposed by \cite{paper:projpred} who also devise a reference model performing sufficiently well in this situation.
+It consists of a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as covariates and imposing an
+hierarchical prior on their coefficients:
 \
@@
 \end{equation}
-where $u_{ij}$ stays for the $j$-th SPC of observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
-We use as screening threshold for the SPCs the value $0.6s_{max}$, which has shown satisfying predictive performance.
-In our experiments the results are not very sensible to the chosen value, yet a more principled approach would be to use cross-validation to select the threshold as in \cite{paper:projpred}.
-\\
-The normal means problem formulation is obtained as explained in Section \ref{comparison} by Fisher-transformation.
-We label as ``ref'' the reference approach, which consists in using the reference model on top of the computation of the z-values, and ``data'' the standard approach based on the observed data only.
-In Section \ref{shrinkage-signal} we analyse in the context of full-Bayes methods the different shrinkage and signal estimation provided by the use of a reference model or not.
-Section \ref{complete-selection} shows results for the complete selection procedures.
+In the above, $u_{ij}$ represents the $j$-th SPC evaluated at observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
+As screening threshold for the SPCs, we use the value $0.6s_{max}$, which has shown satisfying predictive performance (TODO: clarify this sentence).
+In our experiments the results are not very sensible to this choice, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
+
+The normal means problem formulation is obtained as explained in Section \ref{comparison} by applying the Fisher-z-transformation to the empirical correlations.
+We label the reference approach as ``ref'', which consists of using the reference model on top of the computation of the z-values, and the standard approach based on the observed data simply as ``data''.
+In Section \ref{shrinkage-signal}, we analyse the different shrinkage and signal estimates in the context of the full Bayes estimation methods by comparing the ref and data approach.
+In Section \ref{complete-selection}, we present results for the complete selection procedures.
 
@@
 \subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
-In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}.
+In the framework of fully Bayesian estimation methods, we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}.
 % Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
-We used an uniform prior on the interval $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.
-Yet we have not observed any sensibility of the results due to such a choice.
+For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we use an uniform prior on the interval $(1/p,1/2)$.
+For the reguelarised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage.
+We have not observed any sensibility of the results due to such a choice.
 \
-Since, as already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrink factors.
+Since, as explained at the start of Section \ref{comparison}, continuous priors usually do not provide an automatic selection procedure, we study the amount of shrinkage and the bias of the posterior medians looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrinkarge factors.
 
@@
   \caption{Posterior intervals for the parameters of the normal means problem ($n=50$, $\rho=0.3$) using the regularised horseshoe prior.
-Posterior means and one standard deviation intervals depicted.
-Respectively in red and in blue relevant and non-relevant features.
-Horizontal dashed line corresponds to the true value of the mean for the relevant features.\\}
+Posterior means and one standard deviation intervals are depicted.
+Relevant and non-relevant features are displayed in red and in blue respectively.
+Horizontal dashed lines corresponds to the true value of the mean for the relevant features.\\}
   \label{fig:posterior_intervals}
@@
 
-Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior.
-Respectively on the right and on the left the results using or not the reference model approach.
-It is evident how the reference model helps in tearing apart the signals from the noise, resulting in less biased estimates.
+Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior with the data approach on the left and the ref approach on the right-hand side.
+It is evident how the reference model helps in tearing apart the signal from the noise, resulting in less biased estimates and clearer separation between relevant and irrelevant features.
 This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations.
-We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE.
-As $n$ and $\rho$ grow, the amount of error diminish, as expected, due to a larger amount of information of the relevance of each variable provided by the data.
-We also note that the two priors seem to achieve very similar results, regardless of the approach used.
+We observe that the reference approach (in orange) has a clearly lower estimate for both the SESE and the SSE.
+As $n$ and $\rho$ increase, the amount of error diminishes, as expected, due to a larger amount of information of the relevance of each variable provided by the data.
+We also note that the two priors seem to achieve very similar results under all conditions.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
-  \caption{Average SESE and SSE with one standard deviation error bars after 100 simulations.\\}
+  \caption{Average SESE and SSE with one standard deviation intervals after 100 simulations.\\}
   \label{fig:SESE_SSE}
@@
 Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged after 100 data simulations.
-Relevant and non-relevant features are respectively highlighted in red and blue.
-The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise.
-Respectively on the y-axis and on the x-axis are depicted the shrinkage factors using the reference model approach or not.
+Relevant and non-relevant features are highlighted in red and blue respectively.
+The ideal shrinkage would be $\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is noise.
+The shrinkage factors using the data and reference approach are depicted on the y-axis and on the x-axis respectively.
 If the reference model did not make any difference, we would expect the points to lie on the diagonal.
-Non-relevant features happen to lie on average on the diagonal for all the simulated scenario, meaning not evident benefits coming from the reference model.
-Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals.
-Such benefit is proportional to the difficulty of the problem, that is it increases with lower correlation and number of observations.
+In our simulations, non-relevant features were indeed on the diagonal on average for all the simulated scenarios, which implies that their shrinkage was not improved by the reference approach.
+However, when considering the amount of shrinkage for the relevant feature, the points are always located under the diagonal, which means that the reference model helped in shrinking true signals less.
+Such benefit is roughly proportional to the difficulty of the problem, that is it increases with lower correlations and lower number of observations.
 Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
-In a single data realisation there would be more noise and the clusters would be closer and overlapping.
-The results for the Dirichlet-Laplace prior are very similar and we do not include them in the paper.
+In a single data realisation, there would be more noise and the clusters would be closer and overlapping.
+The results for the Dirichlet-Laplace prior are very similar and we do not display them in the paper.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
-  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
+  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations.
+Relevant and non-relevant variables are displayed in red and blue respectively.\\}
   \label{fig:k}
@@
 As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals.
-\\
+\
 The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}.
-It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
-In our case $f_{0}$ correspond to the standard normal distribution, see expression \eqref{eq:normal_means_problem2}.
+It consists of testing the z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$ meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
+In our case $f_{0}$ corresponds to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}).
 The quantity of interest is the local false discovery rate (loc.fdr) defined as:
@@
 \begin{equation}
-loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
+\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
 \end{equation}
-where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values.
-The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2.
-Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison.
+where $\pi_{0}$ is the prior probability of $H_0$ and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values.
+The latter is estimated using splines with 7 degrees of freedom.
+We select features with local false discovery rate below $0.2$.
+Such a value is commonly suggested only because it corresponds to a Bayes factor larger than 36 (assuming $\pi_{0}\geq0.9$).
+Other values can be considered and, in our experience, do not affect the results of the comparison.
 We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
-\\
-The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
-We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e.
-there exists a threshold value such that all the data under that threshold have posterior median equal to zero.
-Therefore the selection is done including those parameters whose posterior median is different from zero.
+The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists of fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
+As suggested by (cite), we use a Laplace distribution resulting in a thresholding property, that is, there exists a threshold value such that all the data under that threshold have posterior median equal to zero.
+Therefore the selection is done by selecting only those parameters whose posterior median is different from zero.
 The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood.
-\\
-The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 0.05-th and the 0.95-th quantiles.
+The selection by 90\% posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 5\% and the 95\% quantiles.
 
-Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$.
-For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach.
-The best selection performance is on the top-left corner of each plot, meaning lowest false discovery rate and highest sensitivity.
-It is possible to note that regardless of the method used, the use of a reference model improves the goodness of the selection diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting).
-In accordance with what expected, higher the number of observations and the correlation are, easier the selection is and, thus, the benefits of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.
+Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on the y-axis) versus the average false discovery rate on the x-axis after 100 data simulations for the different combinations of $n$ and $\rho$.
+For each method (different colours) the squares and the circles correspond to using the reference and approach respectively.
+The best selection performance is on the top-left corner of each plot, as it implies the lowest false discovery rate and the highest sensitivity.
+We see that regardless of the applied selection method, the use of a reference model improves the goodness of the selection as it reduces the false discovery rate (shifting to the left) and/or increasing the sensitivity (shifting upwards).
+In accordance with what can be expected, the higher number of observations and the higher the true correlations, the easier the selection is.
+Thus, for easier selection scenarios, the benefits of the reference model are less notable since the unprocessed data already provide enough information to identify the relevant covariates.
 
@@
 Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process.
-Further details are available in their paper as asymptotic normal distribution, based on which confidence intervals are computed.
-The reference model helps improving the stability of the selection: again, such benefit is notable when the problem is more difficult (small $n$ and $\rho$).
-We observe also less uncertainty in the stability estimates for the reference approach (i.e.
-the width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.
+Further details are available in (cite).
+The reference model helps in improving the stability of the selection: Again, such benefit is more notable when the problem is more difficult (small $n$ and $\rho$).
+In addition, we observe less uncertainty in the stability estimates for the reference approach (i.e., smaller width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
-  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+  \caption{Stability estimates with 95\% confidence intervals after 100 data simulations.\\}
   \label{fig:stability}
@@
 \hypertarget{real-world-data}{%
-\subsection{Real world data: the body fat dataset}\label{real-world-data}}
+\subsection{The body fat data: A real world example}\label{real-world-data}}
 
-We conclude our experiments using one more time the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
-We carry out two different analyses: one using the normal means problem framework and the other one using the stepwise backward regression.
-In the former, we add to the original data noisy uncorrelated covariates up to a total of 1000 features.
-These covariates are normally distributed and scaled as the original ones.
-We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher transformation.
-The original assumption, in order that \eqref{eq:fisher_transformation} holds, is that the variables are jointly normally distributed.
-In our experience the normal approximation in \eqref{eq:fisher_transformation} is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, instead we estimate it from the data.
-The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90).
-The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
+We conclude our experiments using the real world 'body fat' dataset one more time, which was already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
+We carry out two different analyses: One using the normal means problem framework and another one using selection via stepwise backward regression.
+In the former, we add noisy uncorrelated covariates to the original data up to a total of 1000 features.
+These covariates are normally distributed and scaled as the original covariates.
+We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher-Z-transformation.
+The original assumption in order for \eqref{eq:fisher_transformation} to hold is that the variables are jointly normally distributed.
+In our experience the normal approximation in \eqref{eq:fisher_transformation} is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and instead estimate it from the data.
+The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 90\% (ci.90).
+In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$ (i.e., the full size of the data).
+For each condition, results are averaged over 100 bootstrap samples of the respective size.
+
+%The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
 6]{efron2012large}, whereas the median absolute deviation from zero for the empirical Bayes median method.
-The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance.
-In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$.
-Each time results are averaged over 100 bootstrap subsamples.
+The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance
 
@@
 Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate.
-Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
-We thus consider as non-relevant all the artificially added ones.
-In almost all the bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate.
-When $n=50$, we observe a worsening in terms of false discovery rate, yet in a lower amount compared to the gain in sensitivity.
-We observe again that the benefits are more evident as the selection is more challenging (i.e.
-less number of observations).
+Since we do not have a ground truth available with regard the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
+The artificially added featues as of course irrelvant by construction.
+In almost all the bootstrapped subsamples, the reference model improves the seleciton both in terms of sensitivity and false discovery rate.
+When $n=50$, we observe a worsening in terms of false discovery rate, yet by a lower amount compared to the gain in sensitivity.
+Again, we observe that the benefits are more evident as the selection becomes more challenging (i.e., lower number of observations).
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefits of the reference model are here marginal: small improvements can be observed, but overall not very notable.
+The benefits of the reference model are here marginal: small improvements can be observed, but overall not very noteworthy.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
-  \caption{Stepwise backward selection using or not the reference model: number of noisy feature included in the model and RMSE after 100 bootstrap samples.\\}
+  \caption{Stepwise backward selection with and without using a reference model.
+The x-axis denotes the number of selected irrelvant features on the left and the out-of-sample RMSE on the right-hand side after 100 bootstrap samples.\\}
   \label{fig:bodyfat_step_refvsdata}
@@
 
-In the second analysis, we repeat the selection of Section \ref{projection} via stepwise backward regression by AIC.
-In this case the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
-We compare results using or not the reference model on top of the procedure according to our simple reference model approach; here the reference model is again given by the first five supervised principal components.
-Figure \ref{fig:bodyfat_step_refvsdata} shows the number of noisy features included in the final model and the out-of-sample root mean square error (RMSE).
+In the second analysis, we repeat the selection of Section \ref{projection} via stepwise backward regression.
+In this case, the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
+We compare results with and without using a reference model on top of the procedure following our simple reference model approach outlined in \eqref{eq:ref_mod}.
+Figure \ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant features included in the final model and the out-of-sample root mean square error (RMSE).
 Results are after 100 bootstrap samples on the whole dataset, and the predictive performance is tested on the observations excluded at each bootstrap sample.
-We observe that the reference model reduces the number of noisy features included in the final model.
-This leads to less overfit to the data and, thus, improved out-of-sample predictive performance in terms of RMSE.
-Also in this case, we see that there is not a notable difference in terms of the stability of the two approaches, which in this case is qualitatively assessed through the variability of the histogram.
+We observe that the reference model reduces the number of irrelevant features included in the final model.
+This leads to less overfitting and thus to improved out-of-sample predictive performance in terms of RMSE.
+Our reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, for instance, the projective prediction approach (see results of Section \ref{projection}).
+
+%Also, in this case, we see that there is no notable difference in terms of the stability of the two approaches, which in this case is qualitatively assessed through the variability of the histogram.
 We can not use the stability measure provided by \cite{paper:stability}, since it does not take in account possibly swaps in the set of selected features due to high correlation between the covariates, which in this case can occur.
-Our reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, as projpred (see results of Section \ref{projection}).
 
-We would like the reader to note that in this example we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and speed to fit.
-We do not argue that this is always a good choice, more sophisticated and well-thought models can lead to even better results.
-Since in our case the sake of the analysis was only explanatory in terms of the comparison we have been carrying out through the paper and needed to average results over many (100) simulations, we preferred to stick to such model.
+We would like the reader to note that, in this example, we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and efficient estimation.
+We do not argue that this is always a good choice and more sophisticated models can lead to even better results.
+Since, in our case, the sake of the analysis was only to motivate the use of reference models in general, and since we needed to average results over a lot of repetitions per simulation condition, we preferred to stick to such a comparably simple reference model.
 

### 2019-07-17 paper/ref_approach.tex
section 2: included more references

--- 2019-07-16 paper/ref_approach.tex
@@
 \end{equation}
-The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred to as the projection of the predictive distribution, which is the general idea behind the projection predictive approach (cite).
+The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred to as the projection of the predictive distribution, which is the general idea behind the projection predictive approach \cite[see][]{paper:projpred}.
 Again the reference model is acting as a filter, or substitute, on data.
@@
 Note that we do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications.
-There are several more sophisticated reference model approaches available in the literature (cite), which are likely to yield even better results.
+There are several more sophisticated reference model approaches available in the literature \cite[see, e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning}, which are likely to yield even better results.
 Rather, the reason for focussing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures.
@@
 
-As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples to the submodels (cite).
+As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples to the submodels \citep{paper:original_proj}.
 The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
@@
 
-Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem in general, but in the special case of submodels for the family of generalize lineder models, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (cite).
+Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem in general, but in the special case of submodels for the family of generalised linear models, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised \citep{paper:original_proj}.
 For further details on the projective prediction workflow and implementation see \cite{paper:projpred}.
@@
 
-\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model.
+\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection \citep{akaike1974new}, fixing abdomen and height to be always included in the model.
 Here, we implement steplm via AIC without fixing any variable.
-For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients (cite), submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
-The experiments are implemented in \texttt{R} (cite).
+For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+The experiments are implemented in \texttt{R} \citep{Rcore2018}.
 The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package.
@@
 Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the corresponding selected submodel using both projpred and steplm.
-We also repeat the selection after adding truely uncorrelated (i.e., irrelevant) features up to a total of 100 covariates.
+We also repeat the selection after adding truly uncorrelated (i.e., irrelevant) features up to a total of 100 covariates.
 For this experiment, we report both the size of the selected submodel and the number of selected irrelevant features.
@@
 For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model anyway.
-Other alternatives could be fixing some parameters to their maximum marginal likelihood value (typically referred as empirical Bayes; cite) or use a completely frequentist approach, if predictions are good enough.
+Other alternatives could be fixing some parameters to their maximum marginal likelihood value \cite[typically referred as empirical Bayes;][]{casella1985introduction} or use a completely frequentist approach, if predictions are good enough.
 

### 2019-07-17 paper/ref_approach.tex
edit the discussion

--- 2019-07-17 paper/ref_approach.tex
@@
 
-This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction.
-We want to highlight that the goal of this paper is not to provide a specific algorithm or procedure to carry out the selection, but rather to bring motivations and attentions to the general use of a reference model.
-\\
-The reference model acts as an approximation of the data generation mechanism through its predictive distribution.
-Such approximation is generally less noisy than the sample estimation available from the observed data, leading to the main benefits of the reference model approach.
-In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used.
-The overall benefits we have showed independently of the specific method applied, consisting in stability and goodness of the selection, motivate what we refer to as the reference model approach for the model reduction framework.
-Such approach translates into a family of different methods, some of which have been present in the literature for several years.
-\\
-In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}.
+In this paper, we discussed the importance of using a reference model to improve feature selection, or more generally, model reduction.
+We want to highlight that the goal of this paper is not to provide a specific procedure to carry out the selection, but rather to explain and motivate the general use and benefits of a reference model.
+We have seen how the reference model acts as an approximation of the data generation mechanism through its predictive distribution.
+Such approximation is generally less noisy than the sample estimation available purely from the observed data, leading to the main benefits of the reference model approach.
+In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different widely used variable selection methods.
+Overall, using a reference model lead to more accurate and stable selection results independently of the specific selection method.
+These benefits apply to a large family of different approaches all involving a reference model in one way or the other.
+Some of these approches have been present in the literature for several years (cite) but often without a clear explanation of \emph{why} they are actually favorable and how they connect to other (as it turns out) related approaches.
+We hope that the present paper can fill some of these gaps by providing a unifying framework and understanding of reference models.
+
+%In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}.
 The selection via projection resulted to be more stable and led to a sparser representation.
@@
 Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching the projection predictive approach results.
+
+We argue that, whenever it is possible to come up with a reasonable reference model, it should be employed on top of the preferred selection procedure or as an integral part of more complex methods, for example, the projective prediction approach \citep{paper:projpred}.
+Note that one of the main challenges in many real world application will consist in devising a sensible reference model itself and assessing its predictive performance.
+We did provide a generic way to build simple reference models, but those may not necessarily be appropriate in all situations.
+If more sophisticated reference models are required, which are more specifically tuned to the data and problem at hand, we recommend them to be developed using a robust (Bayesian) modelling workflow, for instance, as outlined in \cite{gabry2019visualization}.
 \\
-Whenever it is possible to come up with a reasonable reference model, our suggestion is to employ it when selecting models, because of its nature as baseline of the comparisons and its ability to improve the selection.
-Note that one of the main challenges in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
-\\
-All Bayesian models have been implemented using \texttt{Stan} \citep{paper:stan}, which uses HMC-NUTS sampler \citep{hoffman2014no} and allows full posterior Bayesian inference.
-The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.
+
+All Bayesian models used in the this paper have been implemented in the probabilistic programming language \texttt{Stan} \citep{paper:stan} and fit via adaptive Hamiltonian Monte-Carlo \citep{hoffman2014no}.
+The code to run all the experiments is available on GitHub (\url{https://github.com/fpavone/ref-approach-paper}).
 

### 2019-07-17 paper/ref_approach.tex
fixed section 3: references and other things

--- 2019-07-17 paper/ref_approach.tex
@@
 This formulation can be found in practice at various places,
-for example, in the analysis of microarray data, where a large set of genes are tested in two groups of patients labeled as positive or negative to some disease (cite).
+for example, in the analysis of microarray data, where a large set of genes are tested in two groups of patients labeled as positive or negative to some disease \citep{paper:efron,efron2012large}.
 The objective of the analysis is to select the subset of genes statistically relevant to the disease.
@@
 They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
-If these priors have continuous support, as is the case for the Dirichlet-Laplace (DL; cite) or horseshoe-like priors (cite), there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero.
+If these priors have continuous support, as is the case for the Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} or horseshoe-like priors \citep{paper:hs,bhadra2017horseshoe+,paper:rhs}, there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero.
 Whereas \cite{paper:dirichlet_laplace} used k-means clustering over the posterior samples to perform the actual selection, \cite{bhadra2017horseshoe+} just focused their analysis on the obtained shrinkage and the correct estimation of the sparse signals without any actual selection.
@@
 
-For shrinkage priors, one centeral aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features.
+For shrinkage priors, one central aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features.
 Ideally, the irrelevant features should be completely shrunken to zero while the relevant features should not be shrunken at all.
-The amount of shrinkage can be quantitified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage).
+The amount of shrinkage can be quantified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage).
 For model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type
@@
 In the above, $u_{ij}$ represents the $j$-th SPC evaluated at observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
-As screening threshold for the SPCs, we use the value $0.6s_{max}$, which has shown satisfying predictive performance (TODO: clarify this sentence).
-In our experiments the results are not very sensible to this choice, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
+The SPCs are computed through the \texttt{R}-package \texttt{dimreduce} setting the screening threshold parameter at $0.6s_{max}$. 
+In our experiments the results are not very sensible to such a choice of the screening threshold, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
 
@@
 For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we use an uniform prior on the interval $(1/p,1/2)$.
-For the reguelarised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage.
+For the regularised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage.
 We have not observed any sensibility of the results due to such a choice.
 \
-Since, as explained at the start of Section \ref{comparison}, continuous priors usually do not provide an automatic selection procedure, we study the amount of shrinkage and the bias of the posterior medians looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrinkarge factors.
+Since, as explained at the start of Section \ref{comparison}, continuous priors usually do not provide an automatic selection procedure, we study the amount of shrinkage and the bias of the posterior medians looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrinkage factors.
 
@@
 The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists of fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
-As suggested by (cite), we use a Laplace distribution resulting in a thresholding property, that is, there exists a threshold value such that all the data under that threshold have posterior median equal to zero.
+As suggested by \cite{johnstone2004needles}, we use a Laplace distribution resulting in a thresholding property, that is, there exists a threshold value such that all the data under that threshold have posterior median equal to zero.
 Therefore the selection is done by selecting only those parameters whose posterior median is different from zero.
@@
 Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process.
-Further details are available in (cite).
+Further details are available in \cite{paper:stability}.
 The reference model helps in improving the stability of the selection: Again, such benefit is more notable when the problem is more difficult (small $n$ and $\rho$).

### 2019-07-17 paper/ref_approach.tex
edit title and abstract

--- 2019-07-17 paper/ref_approach.tex
@@
 
-\title{The reference model approach in feature selection problems 
+\title{Using reference models in feature selection problems 
 	\vspace{.1in}}
@@
 \begin{abstract}
-When a reference model is used to guide the variable selection problem, it acts as a noise-filter modelling the data generation mechanism.
+
+Feature selection, or more generally, model reduction is an important aspect of statistical workflows aiming to provide insides from data.
+While a vast number of feature selection procedures are available, it often remains unclear what are the underlying principles explaining why certain methods are working better than others.
+We investigate and discuss one of these principles in detail, which we identify with the use of a reference model.
+We demonstrate how such a model acts as a noise-filter on the target variable by approximating its data generation mechanism.
+To this end, we devise a simple reference model approach that can be used on top of any feature selection method.
+In several numerical experiments, we show how this translates into better and more stable feature selection independently of the specific selection procedure.
+These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
+
+%When a reference model is used to guide the variable selection problem, it acts as a noise-filter modelling the data generation mechanism.
 We show how this translate into higher stability and better selection of variables.
@@
 Furthermore we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
+
 \end{abstract}

### 2019-07-17 code/plots.R
removed y-axis labels for histogram

@@ -562,7 +562,9 @@ plot1 <- ggplot(data.plot,aes(x=stat,fill=method,color=method)) +
     labs(x='',y='',fill='Approach') +
     guides(color=FALSE) +
     scale_fill_manual(values=c("#819FF7","#FAAC58")) +
-    scale_color_manual(values=c("#819FF7","#FAAC58"))
+    scale_color_manual(values=c("#819FF7","#FAAC58")) +
+    theme(axis.text.y = element_blank(),
+          axis.ticks.y = element_blank())
 #    theme_light()
 
 ggsave("../paper/graphics/bodyfat_step_refvsdata.pdf",plot1,width=10,height=2)

### 2019-07-17 paper/ref_approach.tex
conclusion and typo edits

@@
 
-In statistical applications, one of the main steps in the modeling
+In statistical applications, one of the main steps in the modelling
 workflow is covariate or feature selection, which is a special case of
@@
 \citep{tibshirani1996regression} or stepwise backward/forward 
-regression \citep{venables2013modern,harrell2015regression}, the observed empirical data distribution is utilized as a
+regression \citep{venables2013modern,harrell2015regression}, the observed empirical data distribution is utilised as a
 proxy of future data usually in combination with cross-validation
@@
 The projected samples $\boldsymbol{\theta}_{\perp}^{s}$ then correspond to the submodel's parameter distribution.
-\item For each submodel (size), test the predictive performance for instance via cross-valdiation.
+\item For each submodel (size), test the predictive performance for instance via cross-validation.
 \item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
@@
 Here, we implement steplm via AIC without fixing any variable.
-For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+For selection via projpred, the reference model includes all the covariates, we regularise model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
 The experiments are implemented in \texttt{R} \citep{Rcore2018}.
@@
 Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
-For exaple, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm.
+For example, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm.
 In addition, we note that the size of the selected model is much smaller when using projpred.
@@
 Whilst, with the original data, we do not observe any gain using projpred in terms of predictive performance, what we do observe is a smaller size for the selected submodel, at the cost of a higher computation time compared to steplm.
-However, when additional irrelevant features are added, projpred is able to notably improve the predictive performance keeping the same submodel size, whereas steplm selects a much larger submodel also including a large number of irrelvant features (13 irrelevant out of a total of 19 selected features).
+However, when additional irrelevant features are added, projpred is able to notably improve the predictive performance keeping the same submodel size, whereas steplm selects a much larger submodel also including a large number of irrelevant features (13 irrelevant out of a total of 19 selected features).
 
@@
 One common way to proceed is to compute the two-samples $t$-statistic for every gene separately.
-After normalizing these statistics, they then become the data, $Z$, in the normal means problem \eqref{eq:normal_means_problem}.
+After normalising these statistics, they then become the data, $Z$, in the normal means problem \eqref{eq:normal_means_problem}.
 For further details see the examples in \cite{paper:efron, efron2012large}.
@@
 \end{equation}
-Note that in thise cse the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
+Note that in this case the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
 There are different ways to proceed with the selection in the normal means problem.
@@
 Since we do not have a ground truth available with regard the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
-The artificially added featues as of course irrelvant by construction.
-In almost all the bootstrapped subsamples, the reference model improves the seleciton both in terms of sensitivity and false discovery rate.
+The artificially added features as of course irrelevant by construction.
+In almost all the bootstrapped subsamples, the reference model improves the selection both in terms of sensitivity and false discovery rate.
 When $n=50$, we observe a worsening in terms of false discovery rate, yet by a lower amount compared to the gain in sensitivity.
@@
   \caption{Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelvant features on the left and the out-of-sample RMSE on the right-hand side after 100 bootstrap samples.\\}
+The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side after 100 bootstrap samples.\\}
   \label{fig:bodyfat_step_refvsdata}
@@
 These benefits apply to a large family of different approaches all involving a reference model in one way or the other.
-Some of these approches have been present in the literature for several years (cite) but often without a clear explanation of \emph{why} they are actually favorable and how they connect to other (as it turns out) related approaches.
+Some of these approaches have been present in the literature for several years \cite[e.g.
+see][]{vehtari2012survey,paper:projpred} but often without a clear explanation of \emph{why} they are actually favourable and how they connect to other (as it turns out) related approaches.
 We hope that the present paper can fill some of these gaps by providing a unifying framework and understanding of reference models.

### 2019-07-22 paper/ref_approach.tex
minor edits

@@
 Here, we implement steplm via AIC without fixing any variable.
-For selection via projpred, the reference model includes all the covariates, we regularise model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
+For the selection via projpred, the reference model includes all the covariates, we regularise model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
 The experiments are implemented in \texttt{R} \citep{Rcore2018}.
@@
 The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}.
-The projpred approach has only two variables, 'abdomen' and 'weight', with inclusion frequencies above 50\% ('abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
+The projpred approach has only two variables, `abdomen' and `weight', with inclusion frequencies above 50\% (`abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
 Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
@@
 It is possible to identify a common and inevitable overhead, though, which is the cost of fitting the reference model.
-In the simple ''bare-bones'' reference model approach we have described above, it is actually the only added cost.
+In the simple ``bare-bones'' reference model approach we have described above, it is actually the only added cost.
 In general, a full Bayesian model is advisable in order to have the best predictive performance.
@@
 Further, we use a method to control for the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}.
-Further, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90).
+Finally, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90).
 All of these methods provide a complete selection procedure and we compare their performance with and without using a reference model on top of them.
@@
 
-We conclude our experiments using the real world 'body fat' dataset one more time, which was already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
-We carry out two different analyses: One using the normal means problem framework and another one using selection via stepwise backward regression.
+We conclude our experiments using the real world `body fat' dataset one more time, which was already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
+We carry out two different analyses: one using the normal means problem framework and another one using selection via stepwise backward regression.
 In the former, we add noisy uncorrelated covariates to the original data up to a total of 1000 features.

### 2019-07-24 paper/ref_approach.tex
edits

@@
 \begin{abstract}
-
-Feature selection, or more generally, model reduction is an important aspect of statistical workflows aiming to provide insides from data.
+Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data.
 While a vast number of feature selection procedures are available, it often remains unclear what are the underlying principles explaining why certain methods are working better than others.
 We investigate and discuss one of these principles in detail, which we identify with the use of a reference model.
-We demonstrate how such a model acts as a noise-filter on the target variable by approximating its data generation mechanism.
+We demonstrate how reference models act as a noise-filters on the target variable by approximating its data generation mechanism.
 To this end, we devise a simple reference model approach that can be used on top of any feature selection method.
@@
 model reduction. Variable selection may have multiple goals. 
-First, if the covariates themselves are of interest,
-we can use variable selection as an inferential tool to find the entire 
-collection of variables which have some predictive information about the target variable.
+First, if the covariates themselves are of interest, we can use
+variable selection to infer which variables contain predictive
+information about the target variable.
 Second, as simpler models come with the advantages of reduced
@@
 finding the minimal subset of covariates which
-provides good predictive performance (or good balance between simplicity and
+still provides good predictive performance (or good balance between simplicity and
 predictive performance). 
-Whenever the predictive capability is guiding the selection, the true data generation
-mechanism of future data can be approximated either by using the observed data directly or
-alternatively by using predictions from a \emph{reference model}.
+When the predictive capability is guiding the selection, the true
+data generation mechanism of future data can be approximated either by
+using the observed data directly or alternatively by using predictions
+from a \emph{reference model} \citep{vehtari2012survey}.
 
@@
 since the seminal work of \citet{paper:reference_lindley}. For more
-historical references, see the review by \citet{vehtari2012survey}, and for
+historical references, see papers by \citet{vehtari2012survey} and
+\citet{paper:model_selection}, and for
 most recent methodological development see 
 \citet{paper:projpred}.
+
 Reference models have been also used in non-Bayesian contexts,
@@
 models in detail. We illustrate how a properly designed reference model is able 
-to filter parts of the noise present in the data, and hence provides an improved and more
-stable selection process. This holds even if the reference model does not actually resemble the
+to filter parts of the noise present in the data, and hence provide an improved and more
+stable selection process. This holds even if the reference model does not perfectly resemble the
 true data generating process. Moreover, our analyses indicate that the substantial reduction of
 variance attributable to noise is usually
-more important than small potential bias due model misspecification.
+more important than small potential bias due to model misspecification.
 We argue that, regardless of how the reference model is set up and used in the
@@
 properties it has, thus it remains fundamental to investigate and
-develop such different procedures. We want to note that, although we focus on
+develop such different procedures. Although we focus on
 Bayesian approach in this paper, the benefits of the reference model 
@@
 operate in an $\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}.
-That is, we assume to be able to construct a model whose predictions reflect the best available description of the uncertainty of future data.
-In practice, this will often be the full-encompassing model
+\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
+model which reflects in the best way our beliefs about the future
+data. In practice, this would often be the full-encompassing model
 (including all models we consider having non-zero prior
@@
 
-A good predictive model is able to filter parts of the noise present in the data.
+A good predictive model is able to filter part of the noise present in the data.
 The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
@@
 If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we conditioned on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true data generation mechanism $p_{t}(\tilde{y})$.
-The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model's and the submodel's predictive distributions:
+The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the Kullback-Leibler (KL) divergence from the reference model's predictive distribution to the submodel's predictive distribution:
 \
@@
 Afterwards, any method for feature selection can be used.
-Note that we do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications.
+We do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications.
 There are several more sophisticated reference model approaches available in the literature \cite[see, e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning}, which are likely to yield even better results.
-Rather, the reason for focussing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures.
-Other kinds of comparisons, as the one presented in Section \ref{projection}, work well as motivational examples but fail in terms of generality since the presence or absence of a reference model is not the only aspect differentiating the two procedures.
+Rather, the reason for focusing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures.
+Other kinds of comparisons, as the one presented in Section \ref{projection}, work well as motivational examples but lack in terms of generality since the presence or absence of a reference model is not the only aspect differentiating the two procedures.
 We will come back to the more general comparison in Section \ref{comparison}.
@@
 
-As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples to the submodels \citep{paper:original_proj}.
+As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior draws to the submodels \citep{paper:original_proj}.
 The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
@@
 \begin{enumerate}
-\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ posterior samples of the reference model's parameters.
+\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
 \item Rank the covariates according to their relevance using some heuristics and consider as candidate submodels only those which preserve this order,  starting from including only the highest ranked covariate (the submodels are then naturally identified by their model size).
 This is not strictly necessary but reduces the number of submodels to consider in the following steps.
-\item For each submodel, project the reference model's samples as follows:
+\item For each submodel, project the reference model posterior draws as follows:
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right) \quad s=1,..,S
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,..,S \,,
 \end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the predictive distribution of the reference model with parameters fixed at the posterior sample $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate values related to the statistical unit (identified by the subscript $i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the predictive distribution of the submodel.
-The projected samples $\boldsymbol{\theta}_{\perp}^{s}$ then correspond to the submodel's parameter distribution.
-\item For each submodel (size), test the predictive performance for instance via cross-validation.
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the predictive distribution of the reference model with parameters fixed at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate values related to the statistical unit (identified by the subscript $i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the predictive distribution of the submodel.
+The projected draws $\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior for the submodel.
+\item For each submodel (size), test the predictive performance, for example, via cross-validation.
 \item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
@@
 
-We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}.
-The analysis is based on Vehtari's \texttt{R}-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}.
+\subsubsection{Example: Variable selection in bodyfat prediction}
+
+We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}\footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
 The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure.
@@
 The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}.
-The projpred approach has only two variables, `abdomen' and `weight', with inclusion frequencies above 50\% (`abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
-Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
+The projpred approach has only two variables, `abdomen' and `weight', with inclusion frequencies above 50\% (`abdomen' is the only one included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
+Such a higher variability and lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
 For example, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm.
-In addition, we note that the size of the selected model is much smaller when using projpred.
+In addition, the size of the selected model is much smaller when using projpred.
 
@@
 
-Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the corresponding selected submodel using both projpred and steplm.
-We also repeat the selection after adding truly uncorrelated (i.e., irrelevant) features up to a total of 100 covariates.
-For this experiment, we report both the size of the selected submodel and the number of selected irrelevant features.
-Whilst, with the original data, we do not observe any gain using projpred in terms of predictive performance, what we do observe is a smaller size for the selected submodel, at the cost of a higher computation time compared to steplm.
-However, when additional irrelevant features are added, projpred is able to notably improve the predictive performance keeping the same submodel size, whereas steplm selects a much larger submodel also including a large number of irrelevant features (13 irrelevant out of a total of 19 selected features).
+First two rows of Table \ref{tab:model_performances} report the predictive performances, in terms of root mean square error (RMSE), of the full model and the selected models using either the projection predictive approach or the stepwise backward elimination.
+There is no difference in predictive performance of the selected models by different approaches even if there is difference in the selected features.
+
+We repeat the experiment with a modified data set by adding 84 unrelated noisy features.
+Last two rows of Table \ref{tab:model_performances} report RMSE, the size of the selected model and the number of selected noisy features using either the projection predictive approach or the stepwise backward elimination.
+The projection predictive approach has similar predictive performance and the same submodel size as in the first experiment, whereas the stepwise regression has worse predictive performance and selects a much larger submodel including a large number of irrelevant features.
 
@@
 \hypertarget{computational-burden}{%
-\subsection{Computational burden} \label{computational-burden}}
+\subsection{Computational cost} \label{computational-burden}}
 
-We consider the reference model approach as a family of methods, thus providing a general answer to the question of computational burden is not possible because not unique.
-It is possible to identify a common and inevitable overhead, though, which is the cost of fitting the reference model.
-In the simple ``bare-bones'' reference model approach we have described above, it is actually the only added cost.
-In general, a full Bayesian model is advisable in order to have the best predictive performance.
+There are various ways to implement a reference model approach.
+A common term in the computational cost is the inference for the reference model.
+In the simple ``bare-bones'' reference model approach we have described above, it is the only added cost.
+In general, a full Bayesian reference model is advisable in order to have the best predictive performance.
 However, including all the available features can often be quite computationally demanding.
@@
 However, in some cases, this does not always result in an appreciable speed-up.
-For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model anyway.
-Other alternatives could be fixing some parameters to their maximum marginal likelihood value \cite[typically referred as empirical Bayes;][]{casella1985introduction} or use a completely frequentist approach, if predictions are good enough.
+For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model.
+Other alternatives could be using point estimates such maximum a posteriori estimatge if predictions from such reference model without full Bayesian inference are good enough.
 
-The comparison example between projpred and steplm shows that such additional computational burden can be worth it.
-We found that the reference model approach (projpred) selected much sparser submodels, which can result in saving time and general costs using the selected model for future predictions.
-Table \ref{tab:model_performances} displays that there could even be an improvement in the predictive ability compared to the full model, thus justifying more additional computational costs in the selection procedure.
+The comparison example between projpred and steplm shows that such additional computational cost can be worth it.
+We found that the reference model approach (projpred) selected much sparser submodels, which can result in improved and more stable interpretability and saving time and general costs using the selected model for future predictions.
+Table \ref{tab:model_performances} and results by \citet{paper:model_selection} demonstrate also that in case of large number of features, there can be a significant improvement in the predictive ability compared to feature selection without a reference model, thus justifying additional computational costs in the selection procedure.
 More benefits obtainable through a reference model approach are provided in the experiments discussed in the upcoming section.
@@
 
-In this section, we demonstrate the benefits of reference model approaches using the normal means problem as a benchmark.
+In this section, we analyse in more detail the benefits of reference model approaches using the normal means problem as a benchmark.
 The normal means problem consists of estimating the (usually sparse) vector of means of a vector of normally distributed observations.
-Let us denote the dimensionality of the vector of means by $p$ and let $\{z_{j}\}_{j=1}^{p}$ be the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$.
+The dimensionality of the vector of means is denoted by $p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$.
 In the normal means problem, the task is to estimate the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:
@@
 \begin{equation}\label{eq:normal_means_problem}
-Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}) \quad j=1,..,p
+Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}), \quad j=1,..,p.
 \end{equation}
-Note that it is equivalent to a linear regression where the design matrix is the identity matrix with the number of features being equal to the number of observations.
-This formulation can be found in practice at various places,
+This is equivalent to a linear regression where the design matrix is the identity matrix with the number of features being equal to the number of observations.
+This formulation can be found in practice,
 for example, in the analysis of microarray data, where a large set of genes are tested in two groups of patients labeled as positive or negative to some disease \citep{paper:efron,efron2012large}.
 The objective of the analysis is to select the subset of genes statistically relevant to the disease.
-One common way to proceed is to compute the two-samples $t$-statistic for every gene separately.
+One common way to proceed is to compute the two-sample $t$-statistic for every gene separately.
 After normalising these statistics, they then become the data, $Z$, in the normal means problem \eqref{eq:normal_means_problem}.
@@
 
-In our examples, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}.
-Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and let us denote $\rho_{j}=Cor(Y,X_{j})$.
+In our experiments, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}.
+Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and denote $\rho_{j}=Cor(Y,X_{j})$.
 Further, suppose we have observed $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the $j$-th covariate $\{x_{ij}\}_{i=1}^{n}$.
 Finally, we refer to the Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$.
-Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed as well with known variance:
+Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed with known variance:
 \
 \begin{equation} \label{eq:fisher_transformation}
-T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p
+T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p.
 \end{equation}
-Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we again find the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
+Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and denoting the results as $z_{j}$, we have the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
 \
 \begin{equation} \label{eq:normal_means_problem2}
-Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p
+Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p.
 \end{equation}
-Note that in this case the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
+Now the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
 There are different ways to proceed with the selection in the normal means problem.
@@
 
-We begin by explaining some Bayesian estimation methods to solving the normal means problem.
+We briefly review some Bayesian estimation methods to solving the normal means problem.
 They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
@@
 \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
-&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
+&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}], \label{eq:SESE}
 \end{align}
@@
 We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units.
-Note that the SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates.
-Note that actually any kind of point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median.
-The results that we show later on in Section \ref{shrinkage-signal} are not sensible to such a choice.
+The SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates.
+Any (sensible) point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median.
+The results that we show later on in Section \ref{shrinkage-signal} are not sensitive to the choice of this point estimate.
 
 For shrinkage priors, one central aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features.
-Ideally, the irrelevant features should be completely shrunken to zero while the relevant features should not be shrunken at all.
+Ideally, the irrelevant features should be completely shrunk to zero while the relevant features should not be shrunk at all.
 The amount of shrinkage can be quantified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage).
@@
 \
-In our case, $\kappa_{j}$ can be computed as
+For RHS and DL priors we have
 \begin{equation}
-\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}
+\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
 \end{equation}
-for the regularised horseshoe and the Dirichlet-Laplace prior respectively.
 In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}.
-We will use the posterior mean of $\kappa_{j}$ as a point estimate.
+We use the posterior mean of $\kappa_{j}$ as a point estimate.
 
 Within the set of complete selection procedures, we consider three
-Bayesian methods which are described in the following.
-\cite{johnstone2004needles} use a spike-and-slab type prior given by a mixture of a delta distribution in zero and a heavy-tailed distribution \cite[see also][]{paper:spike_slab_mitchell}.
-When the latter is a Laplace distribution, they show an interesting thresholding property of the median estimator and, based on this observation, present a complete selection procedure using their prior.
-We refer to this method as EB.med.
-Further, we use a method to control for the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}.
-Finally, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90).
-All of these methods provide a complete selection procedure and we compare their performance with and without using a reference model on top of them.
-As criteria of selection performance, we evaluate the average false discovery rate (i.e., the ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e., the ratio of the number of relevant selected features over the total number of relevant features).
-We also provide a comparison of the stability of the selection by means of a stability measure proposed by \cite{paper:stability}.
-Table \ref{tab:comparison} summarises the methods used in out numerical experiments.
+Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
+type prior given by a mixture of a delta distribution in zero and a
+heavy-tailed distribution \cite[see
+also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
+distribution, they show an interesting thresholding property of the
+median estimator and, based on this observation, present a complete
+selection procedure using their prior. We refer to this method as
+EB.med. Further, we use a method to control for the local false
+discovery rate (loc.fdr) as described in \cite{paper:efron,
+  efron2012large}. Finally, we device a simple selection procedure
+based on posterior credible intervals using the regularised horseshoe
+prior in which we select covariates whose 90\% credible intervals
+excludes zero (ci.90). All of these methods provide a complete
+selection procedure and we compare their performance with and without
+using a reference model on top of them. As criteria of selection
+performance, we evaluate the average false discovery rate (i.e., the
+ratio of the number of non-relevant selected features over the number
+of selected features) and the average sensitivity (i.e., the ratio of
+the number of relevant selected features over the total number of
+relevant features). We also provide a comparison of the stability of
+the selection by means of a stability measure proposed by
+\cite{paper:stability}. Table \ref{tab:comparison} summarises the
+methods used in the numerical experiments.
 
@@
     \end{aligned} &j=1,..,5 \\ 
-    &\sigma \sim t_{3}^{+}(0,10) \\
+    &\sigma \sim t_{3}^{+}(0,10). \\
 \end{aligned}
@@
 The SPCs are computed through the \texttt{R}-package \texttt{dimreduce} setting the screening threshold parameter at $0.6s_{max}$. 
-In our experiments the results are not very sensible to such a choice of the screening threshold, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
+In our experiments the results are not sensible to such a choice of the screening threshold, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
 
@@
 For the regularised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage.
-We have not observed any sensibility of the results due to such a choice.
+The results are not sensitive with respect to the specific choice.
 \
@@
 It is evident how the reference model helps in tearing apart the signal from the noise, resulting in less biased estimates and clearer separation between relevant and irrelevant features.
-This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations.
+This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted based on 100 simulations.
 We observe that the reference approach (in orange) has a clearly lower estimate for both the SESE and the SSE.
 As $n$ and $\rho$ increase, the amount of error diminishes, as expected, due to a larger amount of information of the relevance of each variable provided by the data.
-We also note that the two priors seem to achieve very similar results under all conditions.
+The two priors (RHS and DL) seem to achieve similar results under all conditions.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
-  \caption{Average SESE and SSE with one standard deviation intervals after 100 simulations.\\}
+  \caption{Average SESE and SSE with one standard deviation intervals based on 100 simulations.\\}
   \label{fig:SESE_SSE}
@@
 
-Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged after 100 data simulations.
+Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged over 100 data simulations.
 Relevant and non-relevant features are highlighted in red and blue respectively.
@@
 If the reference model did not make any difference, we would expect the points to lie on the diagonal.
-In our simulations, non-relevant features were indeed on the diagonal on average for all the simulated scenarios, which implies that their shrinkage was not improved by the reference approach.
-However, when considering the amount of shrinkage for the relevant feature, the points are always located under the diagonal, which means that the reference model helped in shrinking true signals less.
-Such benefit is roughly proportional to the difficulty of the problem, that is it increases with lower correlations and lower number of observations.
-Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
-In a single data realisation, there would be more noise and the clusters would be closer and overlapping.
-The results for the Dirichlet-Laplace prior are very similar and we do not display them in the paper.
+For the non-relevant features points are on the diagonal on average for all the simulated scenarios, which implies that their shrinkage was not improved by the reference approach.
+For the relevant features, the points are always located under the diagonal, which means that the reference model helps and true signals are shrunk less.
+This benefit is roughly proportional to the difficulty of the problem, that is, the benefit increases with lower correlations and a smaller number of observations.
+The perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
+In a single data realisation, there is more noise and the cluster are closer and overlapping.
+The results for the Dirichlet-Laplace prior are very similar.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
-  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations.
+  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior based on 100 simulations.
 Relevant and non-relevant variables are displayed in red and blue respectively.\\}
@@
 \
+
 The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}.
@@
 \begin{equation}
-\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
+\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
 \end{equation}
@@
 The latter is estimated using splines with 7 degrees of freedom.
-We select features with local false discovery rate below $0.2$.
-Such a value is commonly suggested only because it corresponds to a Bayes factor larger than 36 (assuming $\pi_{0}\geq0.9$).
-Other values can be considered and, in our experience, do not affect the results of the comparison.
+We select features with local false discovery rate below $0.2$, which is suggested by \citet{efron2012large} as it corresponds to a Bayes factor larger than 36 (assuming $\pi_{0}\geq0.9$).
+The results of the comparison are not sensitive to the specific value.
 We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
+
 The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists of fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
@@
 
-Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on the y-axis) versus the average false discovery rate on the x-axis after 100 data simulations for the different combinations of $n$ and $\rho$.
+Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on the vertical axis versus the average false discovery rate on the horizontal axis based on 100 data simulations for the different combinations of $n$ and $\rho$.
 For each method (different colours) the squares and the circles correspond to using the reference and approach respectively.
 The best selection performance is on the top-left corner of each plot, as it implies the lowest false discovery rate and the highest sensitivity.
-We see that regardless of the applied selection method, the use of a reference model improves the goodness of the selection as it reduces the false discovery rate (shifting to the left) and/or increasing the sensitivity (shifting upwards).
-In accordance with what can be expected, the higher number of observations and the higher the true correlations, the easier the selection is.
-Thus, for easier selection scenarios, the benefits of the reference model are less notable since the unprocessed data already provide enough information to identify the relevant covariates.
+We see that regardless of the applied selection method, the use of a reference model improves the selection performance as it reduces the false discovery rate (shifting to the left) or increases the sensitivity (shifting upwards).
+In accordance with what can be expected, the larger number of observations and the higher the true correlations, the easier the selection is.
+Thus, for easier selection scenarios, the benefits of the reference model are smaller since the raw data already provide enough information to identify the relevant covariates.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
   \label{fig:sensitivity_vs_fdr}
@@
 
-Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals after 100 simulations.
+Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals based on 100 simulations.
 Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process.
 Further details are available in \cite{paper:stability}.
-The reference model helps in improving the stability of the selection: Again, such benefit is more notable when the problem is more difficult (small $n$ and $\rho$).
-In addition, we observe less uncertainty in the stability estimates for the reference approach (i.e., smaller width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.
+The reference model helps in improving the stability of the selection: Again, the benefits are bigger when the problem is more difficult (small $n$ and $\rho$).
+In addition, we observe less uncertainty in the stability estimates for the reference approach (i.e., smaller width of the 95\% intervals), which can be still connected to the overall stability of the procedure.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
-  \caption{Stability estimates with 95\% confidence intervals after 100 data simulations.\\}
+  \caption{Stability estimates with 95\% intervals based on 100 data simulations.\\}
   \label{fig:stability}
@@
 
-We conclude our experiments using the real world `body fat' dataset one more time, which was already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}.
+We conclude our experiments using the real world `body fat' dataset one more time, which was already described in the motivational example comparing the projection predictive approach and the stepwise regression in Section \ref{projection}.
 We carry out two different analyses: one using the normal means problem framework and another one using selection via stepwise backward regression.
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate after 100 bootstrap samples.\\}
+  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples.\\}
   \label{fig:bodyfat_sensitivity_vs_fdr}
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
-  \caption{Stability estimates with 0.95 confidence intervals after 100 bootstrap samples.\\}
+  \caption{Stability estimates with 0.95 confidence intervals based on 100 bootstrap samples.\\}
   \label{fig:bodyfat_stability}
@@
 Since we do not have a ground truth available with regard the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
-The artificially added features as of course irrelevant by construction.
+The artificially added features are naturally irrelevant by construction.
 In almost all the bootstrapped subsamples, the reference model improves the selection both in terms of sensitivity and false discovery rate.
@@
 Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefits of the reference model are here marginal: small improvements can be observed, but overall not very noteworthy.
+The benefits of the reference model are here marginal with only small improvements.
 
@@
 %  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
-%  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
+%  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
 %  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
@@
 %  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
-%  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
+%  \caption{Stability estimates with 0.95 confidence intervals based on 100 data simulations.\\}
 %  \label{fig:bodyfat_varyingP_stability}
@@
   \caption{Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side after 100 bootstrap samples.\\}
+The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
   \label{fig:bodyfat_step_refvsdata}
@@
 Figure \ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant features included in the final model and the out-of-sample root mean square error (RMSE).
-Results are after 100 bootstrap samples on the whole dataset, and the predictive performance is tested on the observations excluded at each bootstrap sample.
+Results are based on 100 bootstrap samples on the whole dataset, and the predictive performance is tested on the observations excluded at each bootstrap sample.
 We observe that the reference model reduces the number of irrelevant features included in the final model.
 This leads to less overfitting and thus to improved out-of-sample predictive performance in terms of RMSE.
-Our reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, for instance, the projective prediction approach (see results of Section \ref{projection}).
+The reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, for instance, the projective prediction approach (see results of Section \ref{projection}).
 
@@
 
-We would like the reader to note that, in this example, we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and efficient estimation.
+In this example, we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and efficient estimation.
 We do not argue that this is always a good choice and more sophisticated models can lead to even better results.
@@
 
-In this paper, we discussed the importance of using a reference model to improve feature selection, or more generally, model reduction.
-We want to highlight that the goal of this paper is not to provide a specific procedure to carry out the selection, but rather to explain and motivate the general use and benefits of a reference model.
+In this paper, we demonstrated the benefits of using a reference model to improve feature selection, or more generally, model reduction.
+The goal of this paper is not to provide a specific procedure to carry out the selection, but rather to explain and motivate the general benefits of a reference model.
 We have seen how the reference model acts as an approximation of the data generation mechanism through its predictive distribution.
@@
 In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different widely used variable selection methods.
-Overall, using a reference model lead to more accurate and stable selection results independently of the specific selection method.
+Overall, using a reference model leads to more accurate and stable selection results independently of the specific selection method.
 These benefits apply to a large family of different approaches all involving a reference model in one way or the other.
 Some of these approaches have been present in the literature for several years \cite[e.g.
-see][]{vehtari2012survey,paper:projpred} but often without a clear explanation of \emph{why} they are actually favourable and how they connect to other (as it turns out) related approaches.
+see][]{vehtari2012survey,paper:projpred} but often without a clear explanation of \emph{why} they are actually favourable and how they connect to other related approaches.
 We hope that the present paper can fill some of these gaps by providing a unifying framework and understanding of reference models.
@@
 
-All Bayesian models used in the this paper have been implemented in the probabilistic programming language \texttt{Stan} \citep{paper:stan} and fit via adaptive Hamiltonian Monte-Carlo \citep{hoffman2014no}.
+All Bayesian models used in the this paper have been implemented in the probabilistic programming language \texttt{Stan} \citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo \citep{hoffman2014no,betancourt2017conceptual}.
 The code to run all the experiments is available on GitHub (\url{https://github.com/fpavone/ref-approach-paper}).
@@
 %  \includegraphics[width=0.98\textwidth]{graphics/k_DL.pdf}
-%  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
+%  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior based on 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
 %  \label{fig:k_DL}

### 2019-07-24 paper/ref_approach.tex
clean and break long lines for easier diffing

@@
 workflow is covariate or feature selection, which is a special case of
-model reduction. Variable selection may have multiple goals. 
-First, if the covariates themselves are of interest, we can use
-variable selection to infer which variables contain predictive
-information about the target variable.
-Second, as simpler models come with the advantages of reduced
-measurement costs and improved interpretability, we may be interested in
-finding the minimal subset of covariates which
-still provides good predictive performance (or good balance between simplicity and
-predictive performance). 
-When the predictive capability is guiding the selection, the true
-data generation mechanism of future data can be approximated either by
-using the observed data directly or alternatively by using predictions
-from a \emph{reference model} \citep{vehtari2012survey}.
+model reduction. Variable selection may have multiple goals.  First,
+if the covariates themselves are of interest, we can use variable
+selection to infer which variables contain predictive information
+about the target variable.  Second, as simpler models come with the
+advantages of reduced measurement costs and improved interpretability,
+we may be interested in finding the minimal subset of covariates which
+still provides good predictive performance (or good balance between
+simplicity and predictive performance).  When the predictive
+capability is guiding the selection, the true data generation
+mechanism of future data can be approximated either by using the
+observed data directly or alternatively by using predictions from a
+\emph{reference model} \citep{vehtari2012survey}.
 
@@
 \citep{tibshirani1996regression} or stepwise backward/forward
-regression \citep{venables2013modern,harrell2015regression}, the observed empirical data distribution is utilised as a
-proxy of future data usually in combination with cross-validation
-or information criteria to provide estimates for out-of-sample
-predictive performance.
-In contrast, reference model based methods approximate the future data generation
-mechanism using the predictive distribution of a reference model,
-which can be, for example, a full-encompassing model including all
-covariates. The reference
-model approach has been used for long time in Bayesian statistics
-since the seminal work of \citet{paper:reference_lindley}. For more
-historical references, see papers by \citet{vehtari2012survey} and
-\citet{paper:model_selection}, and for
-most recent methodological development see 
+regression \citep{venables2013modern,harrell2015regression}, the
+observed empirical data distribution is utilised as a proxy of future
+data usually in combination with cross-validation or information
+criteria to provide estimates for out-of-sample predictive
+performance.  In contrast, reference model based methods approximate
+the future data generation mechanism using the predictive distribution
+of a reference model, which can be, for example, a full-encompassing
+model including all covariates. The reference model approach has been
+used for long time in Bayesian statistics since the seminal work of
+\citet{paper:reference_lindley}. For more historical references, see
+papers by \citet{vehtari2012survey} and \citet{paper:model_selection},
+and for most recent methodological development see
 \citet{paper:projpred}.
 
-Reference models have been also used in non-Bayesian contexts,
-where \cite{harrell2015regression} describes them as full models that
-can be thought of as a ``gold standard'' (for a given application).
-For example,
-\cite{faraggi2001understanding} deal with the necessity of identifying
-interpretable risk groups in the context of survival data using neural
-networks, which typically perform very well in terms of prediction,
-but whose covariates are difficult to be understood in terms of
-relevance. 
-\cite{paul2008preconditioning}, using the term preconditioning,
-explore approximating models fitting Lasso or stepwise regression
-against consistent estimates $\hat{y}$ of a reference model instead of
-the observed responses $y$.
-
-In this paper, we examine the benefits of using reference
-models in detail. We illustrate how a properly designed reference model is able 
-to filter parts of the noise present in the data, and hence provide an improved and more
-stable selection process. This holds even if the reference model does not perfectly resemble the
-true data generating process. Moreover, our analyses indicate that the substantial reduction of
-variance attributable to noise is usually
-more important than small potential bias due to model misspecification.
-We argue that, regardless of how the reference model is set up and used in the
-inference procedure, it can be always seen as acting as a filter on the observed 
-data. Following this idea, we devise a simple reference model approach that can
-be applied on top of any variable selection procedure.
-
-In our simulations and analysis of real data, we apply several state-of-the-art methods for variable selection and compare,
-for each of these methods, the results obtained by using a data based and a
-reference model based approach. When a full 
-variable selection is carried out, we report and compare quantities such as 
-the false discovery rate \citep{paper:fdr_BH}, sensitivity and stability of the selection \citep{paper:stability}.
-For fully Bayesian methods, we additionally report results in terms of shrinkage and accuracy of the posterior estimates.
-We show the benefits
-of a reference model approach, regardless of what specific procedure is applied, using 
-the normal means estimation problem as a benchmark. 
-Variable selection is typically most challenging in 
-\textit{small n large p} scenarios, that is, scenarios with small number of
-observations but a lot of unknown model parameters. 
-These occur frequently, for example, 
-in microarray data analysis in medicine or biology \citep{dudoit2003multiple,liao2007logistic,paper:efron}.
-In general, the less data we have and the more complex 
-the estimated models, the higher the benefit of using a reference
-models as the basis for variable selection.
-Our results indicate that the core reason why the reference model based
-methods perform well is the reference model itself, rather than the
-specific way of using it. We do recognise that all these methods
-diversify how the subset of variables is actually chosen and which
-properties it has, thus it remains fundamental to investigate and
-develop such different procedures. Although we focus on
-Bayesian approach in this paper, the benefits of the reference model 
-approach can also be obtained in non-Bayesian settings.
-
-The remainder of the paper is structured as follows.
-In Section \ref{reference-model-approach}, we review the concept of the reference model, its benefits with examples, including the projection predictive approach, and how it can be used as a filter on data in a simple way.
-In Section \ref{comparison}, we use different methods for feature selection comparing the selection results with and without using a reference model in the framework of the normal means problem.
-Finally, we end with a conclusion in Section \ref{conclusion}.
-
-%In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which can be seen as a special case of model reduction.
-From a full Bayesian perspective, when the goal of the analysis is to do prediction, no selection should be carried out and integration over all parameters uncertainties, i.e.
-posterior distributions, is the recommended procedure.
-In a high dimensional parameter space the choice of the prior plays an even more key role due to different difficulties that can rise, as computation burden and overfitting.
-In addition to that, sometimes collecting all the features for a future observation is not possible or too expensive.
-In order to solve or, at least, simplify these problems, different feature selection procedures have been proposed both in the frequentist and the Bayesian setting \cite[e.g.
-see][]{paper:feature_selection,vehtari2012survey,paper:model_selection}.
-Sometimes the task of the analysis is not prediction, but rather inference on which variables are substantially related to the phenomenon of interest.
-This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
-A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease.
-The main goal of the analysis is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
-
-% The necessity of carrying out the selection arises from different problematics.
-Sometimes the leading objective of the analysis is to predict future observationgs, thus the main focus in building the model is on the predictive performance.
-Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features for future observations or computational and memory burdens (e.g.
-when operating on limited resources), and thus a sparser representation of the model would be preferred.
-In addition to that, simpler models bring also advantages in terms of interpretability.
-Some other times,
-% variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest.
-% This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology.
-
-% A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.
-
-% process is going to be based on assumptions regarding the ``true''
-% data generation mechanism.  Making assumptions means making models,
-% thus we identify two families of feature selection, or more in general
-% model reduction, approaches depending on how the data generation
-% mechanism is modelled: the data based and the reference model based
-% ones.
-
-% The reference model approach has been used for long time in the Bayesian framework, an example the pioneering work by \cite{paper:reference_lindley}.
-Following \cite{goutis1998model}, \cite{paper:original_proj} project the posterior distribution of the reference model in each candidate model by minimisation of the Kullback-Liebler divergence, and then select the smallest one with enough explanatory power avoiding any prior elicitation for the submodels.
-In the special case of candidate models being GLMs from the exponential family, the optimisation problem corresponds to the task of finding the maximum likelihood estimate using the expected pointwise predictions of the reference model instead of the observed target values.
-Different extensions have followed \cite{paper:original_proj}, as \cite{nott2010bayesian} that add an $l_{1}$ penalty to select the best approximating model and \cite{tran2012predictive}, who select the best approximating model by optimising the Kullback-Liebler divergence between the predictive distribution of the reference model and the approximating model plus an $l_{1}$ penalty on the submodel coefficients.
-A recent review of these methods together with some methodological improvements, as clustered projection and selection by comparison of a predictive performance utility, is given by \cite{paper:projpred}.
-
-% and shows some examples of how it can be used to seek a sparser approximation.
-He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model.
-
-% \cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups.
-
-%\cite{harrell2015regression} includes also the possibility of using simple least squares for the approximating models as long as the target is the linear predictor of a full regression model \hl{CHECK}.
-%\cite{paper:projpred} extend the projection algorithm with the clustered projection and choose the best model comparing the predictive performance of the explored submodels with the reference model one.
-%\cite{paper:projpred} show in their experiments the benefits of the projection predictive approach in terms of predictive ability of the selected model and smaller size compared to other methods.
-It could be of interest to know how often a certain method includes non-relevant features.
-One could argue that such question can not have a general answer, because it depends both on the data and, when it is used, on the choice of the reference model.
-Moreover in real settings it is hard to define what relevant means, in most of the cases all the features have some level of relevance in term of prediction ability and thus the question looses of meaning.
-However, it is still possible to simulate certain artificial scenarios and control which features are included.
-\cite{paper:model_selection} report results about the proportion of relevant and non-relevant features selected with different variable selection methods, showing overall better results in favour of the projection predictive approach.
-The explored submodels using the projection show also a higher performance and stability with respect to the compared methods, given the same submodel size.
-
-% We hope that this work can increase
-% the attractiveness on this family of methods and, therefore, it can be
-% of interest to a large number of practitioners.
+Reference models have been also used in non-Bayesian contexts, where
+\cite{harrell2015regression} describes them as full models that can be
+thought of as a ``gold standard'' (for a given application).  For
+example, \cite{faraggi2001understanding} deal with the necessity of
+identifying interpretable risk groups in the context of survival data
+using neural networks, which typically perform very well in terms of
+prediction, but whose covariates are difficult to be understood in
+terms of relevance.  \cite{paul2008preconditioning}, using the term
+preconditioning, explore approximating models fitting Lasso or
+stepwise regression against consistent estimates $\hat{y}$ of a
+reference model instead of the observed responses $y$.
+
+In this paper, we examine the benefits of using reference models in
+detail. We illustrate how a properly designed reference model is able
+to filter parts of the noise present in the data, and hence provide an
+improved and more stable selection process. This holds even if the
+reference model does not perfectly resemble the true data generating
+process. Moreover, our analyses indicate that the substantial
+reduction of variance attributable to noise is usually more important
+than small potential bias due to model misspecification.  We argue
+that, regardless of how the reference model is set up and used in the
+inference procedure, it can be always seen as acting as a filter on
+the observed data. Following this idea, we devise a simple reference
+model approach that can be applied on top of any variable selection
+procedure.
+
+In our simulations and analysis of real data, we apply several
+state-of-the-art methods for variable selection and compare, for each
+of these methods, the results obtained by using a data based and a
+reference model based approach. When a full variable selection is
+carried out, we report and compare quantities such as the false
+discovery rate \citep{paper:fdr_BH}, sensitivity and stability of the
+selection \citep{paper:stability}. For fully Bayesian methods, we
+additionally report results in terms of shrinkage and accuracy of the
+posterior estimates.  We show the benefits of a reference model
+approach, regardless of what specific procedure is applied, using the
+normal means estimation problem as a benchmark.  Variable selection is
+typically most challenging in \textit{small n large p} scenarios, that
+is, scenarios with small number of observations but a lot of unknown
+model parameters.  These occur frequently, for example, in microarray
+data analysis in medicine or biology
+\citep{dudoit2003multiple,liao2007logistic,paper:efron}.  In general,
+the less data we have and the more complex the estimated models, the
+higher the benefit of using a reference models as the basis for
+variable selection.  Our results indicate that the core reason why the
+reference model based methods perform well is the reference model
+itself, rather than the specific way of using it. We do recognise that
+all these methods diversify how the subset of variables is actually
+chosen and which properties it has, thus it remains fundamental to
+investigate and develop such different procedures. Although we focus
+on Bayesian approach in this paper, the benefits of the reference
+model approach can also be obtained in non-Bayesian settings.
+
+The remainder of the paper is structured as follows. In Section
+\ref{reference-model-approach}, we review the concept of the reference
+model, its benefits with examples, including the projection predictive
+approach, and how it can be used as a filter on data in a simple
+way. In Section \ref{comparison}, we use different methods for feature
+selection comparing the selection results with and without using a
+reference model in the framework of the normal means problem. Finally,
+we end with a conclusion in Section \ref{conclusion}.
 
@@
 
-A good predictive model is able to filter part of the noise present in the data.
-The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest.
-Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}.
-The data generation mechanism is
+A good predictive model is able to filter part of the noise present in
+the data. The noise is the main source of the instability and tends to
+obscure the relevance of the covariates in relation to the target
+variable of interest. Indeed, let us consider the following
+explanatory example taken from \cite{paper:projpred}. The data
+generation mechanism is
 \begin{alignat}{2} \label{eq:simulated_data}
@@
 \end{alignat}
-where $f$ is the latent variable of interest of which $Y$ is a noisy observation.
-The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves.
-Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and, respectively, $f$ and $Y$.
-If we had an infinite amount of observations, the sample correlation would be equal to the true correlation between $X_j$ and $Y$.
-However, even in this ideal asymptotic regime, this  correlation would still remain a biased indicator of the true relevance of each covariate (represented by the correlation between $X_j$ and $f$) due to the intrinsic noisy nature of $Y$.
-
-When using a reference model, we first obtain predictions for $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we have only observed the noisy representation $Y$ of $f$.
-If our model is good, we are able to describe $f$ better than $Y$ itself can, which improves the accuracy in the estimation of the relevance of the covariates.
-Figure \ref{fig:correlation} illustrates this process in the form of a scatter plot of (absolute) correlations of the covariates with $Y$ against the corresponding correlations with the predictions of a reference model (in this case the posterior predictive means of model \eqref{eq:ref_mod}; see Section \ref{simulated-data}).
-Looking at the marginal distributions, we see that using a reference model to filter out noise in the data, the two groups of features (relevant and non-relevant) can be distinguished much better than when the correlation is computed using the observed noisy data directly.
+where $f$ is the latent variable of interest of which $Y$ is a noisy
+observation. The first $k$ covariates are strongly related to the
+target variable $Y$ and correlated among themselves. Precisely, $\rho$
+is the correlation among any pair of the first $k$ covariates, whereas
+$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
+any relevant covariate and, respectively, $f$ and $Y$. If we had an
+infinite amount of observations, the sample correlation would be equal
+to the true correlation between $X_j$ and $Y$. However, even in this
+ideal asymptotic regime, this correlation would still remain a biased
+indicator of the true relevance of each covariate (represented by the
+correlation between $X_j$ and $f$) due to the intrinsic noisy nature
+of $Y$.
+
+When using a reference model, we first obtain predictions for $f$
+using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account
+that we have only observed the noisy representation $Y$ of $f$. If our
+model is good, we are able to describe $f$ better than $Y$ itself can,
+which improves the accuracy in the estimation of the relevance of the
+covariates.  Figure \ref{fig:correlation} illustrates this process in
+the form of a scatter plot of (absolute) correlations of the
+covariates with $Y$ against the corresponding correlations with the
+predictions of a reference model (in this case the posterior
+predictive means of model \eqref{eq:ref_mod}; see Section
+\ref{simulated-data}). Looking at the marginal distributions, we see
+that using a reference model to filter out noise in the data, the two
+groups of features (relevant and non-relevant) can be distinguished
+much better than when the correlation is computed using the observed
+noisy data directly.
 
@@
 
-% In Figure \ref{fig:correlation} the reference model filters the noise.
-% This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
-% Above the correlation was used to estimate the relevance of a covariate.  
-As an another example, let us consider a candidate submodel in a feature selection process and let us refer to the parameter distribution of the submodel by $\pi$ and to the induced predictive distribution by $q_{\pi}(\tilde{y})$.
-We would like to choose $\pi$ so that $q_{\pi}(\tilde{y})$ maximises some predictive performance utility, for example, the expected log-predictive density (elpd) defined as:
-\
+As an another example, let us consider a candidate submodel in a
+feature selection process and let us refer to the parameter
+distribution of the submodel by $\pi$ and to the induced predictive
+distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
+that $q_{\pi}(\tilde{y})$ maximises some predictive performance
+utility, for example, the expected log-predictive density (elpd)
+defined as: \
 \begin{equation}\label{eq:elpd}
@@
 \end{equation}
-where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating mechanism of future data $\tilde{y}$.
-If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we conditioned on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true data generation mechanism $p_{t}(\tilde{y})$.
-The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the Kullback-Leibler (KL) divergence from the reference model's predictive distribution to the submodel's predictive distribution:
-\
+where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
+mechanism of future data $\tilde{y}$. If we refer to the posterior
+predictive distribution of a reference model with $p(\tilde{y}|D)$,
+where $D$ stands for the data on which we conditioned on, we can
+approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
+data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
+elpd using the reference model predictive distribution is equivalent
+to the minimisation of the Kullback-Leibler (KL) divergence from the
+reference model's predictive distribution to the submodel's predictive
+distribution: \
 \begin{equation} \label{proj_as_filter}
@@
 \end{equation}
-The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred to as the projection of the predictive distribution, which is the general idea behind the projection predictive approach \cite[see][]{paper:projpred}.
-Again the reference model is acting as a filter, or substitute, on data.
-
-%--- OR ---
-
-%What we do in Figure \ref{fig:correlation} is to use the reference model predictive ability as a noise-filter on the observed data.
-This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.
-Also the general idea of the projection of the predictive can be seen under this perspective.
-Indeed, let us call $p_{\text{ref}}(\tilde{y}|D)$ the posterior predictive distribution for a new observation $\tilde{y}$ for the reference model and let $\pi(\theta)$ and $q_{\pi}(\tilde{y})$ be respectively the submodel parameter and the induced predictive distributions.
-The projection of the predictive distribution allows to find the optimal parameter distribution $\pi^{*}$ minimising the KL discrepancy among the induced predictive distribution of the submodel and the reference model one:
-%\
-%\begin{equation} 
-%\pi^{*}\quad \text{s.t.} \quad \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi^{*}}(\tilde{y})]=\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
-%\end{equation}
-%Consider now the predictive performance of such submodel, a common utility in Bayesian context is the expected log-predictive density defined as:
-%\
-%\begin{equation} 
-%\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
-%\end{equation}
-%where $p_{t}$ is the distribution of a new observation under the true data generation mechanism.
-Maximising the elpd of a model is equivalent to minimising the KL-divergence of its predictive distribution from the true data generation mechanism.
-Therefore the projection corresponds to maximising the elpd using as distribution of the true data generation mechanism the posterior predictive distribution of the reference model, i.e.:
-%\
-%\begin{equation} \label{proj_as_filter}
-%\underset{\pi}{\text{min}} \; \text{KL}[p_{\text{ref}}(\tilde{y}|D)||q_{\pi}(\tilde{y})] \leftrightarrow \underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p_{\text{ref}}(\tilde{y}|D)d\tilde{y}
-%\end{equation}
-%Equation \eqref{proj_as_filter} clearly shows the action of the reference model as a filter on our target observations, substituting the unknown true data generation mechanism, that is usually estimated with the data empirical distribution, with the best known approximation that is available, i.e.
-the reference model posterior predictive distribution.
-
-%------------------
-
-Relying on the idea of the reference model as a noise-filter, a generic reference model approach, which can be used on top of any feature selection procedure, consists of simply substituting the target observations with corresponding point predictions of the reference model, for instance, the posterior predictive means.
-Afterwards, any method for feature selection can be used.
-We do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications.
-There are several more sophisticated reference model approaches available in the literature \cite[see, e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning}, which are likely to yield even better results.
-Rather, the reason for focusing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures.
-Other kinds of comparisons, as the one presented in Section \ref{projection}, work well as motivational examples but lack in terms of generality since the presence or absence of a reference model is not the only aspect differentiating the two procedures.
-We will come back to the more general comparison in Section \ref{comparison}.
-
-%we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.
+The term on the right-hand side of Equation \eqref{proj_as_filter}
+describes what is referred to as the projection of the predictive
+distribution, which is the general idea behind the projection
+predictive approach \cite[see][]{paper:projpred}. Again the reference
+model is acting as a filter, or substitute, on data.
+
+Relying on the idea of the reference model as a noise-filter, a
+generic reference model approach, which can be used on top of any
+feature selection procedure, consists of simply substituting the
+target observations with corresponding point predictions of the
+reference model, for instance, the posterior predictive
+means. Afterwards, any method for feature selection can be used. We do
+not argue that such a reference model approach should necessarily be
+used as is for feature selection in real applications. There are
+several more sophisticated reference model approaches available in the
+literature \cite[see,
+e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
+which are likely to yield even better results. Rather, the reason for
+focusing on this simple version is to enable a fair comparison between
+a reference model and a purely data based approach when otherwise
+using the same selection procedures. Other kinds of comparisons, as
+the one presented in Section \ref{projection}, work well as
+motivational examples but lack in terms of generality since the
+presence or absence of a reference model is not the only aspect
+differentiating the two procedures. We will come back to the more
+general comparison in Section \ref{comparison}.
 
@@
 
-As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior draws to the submodels \citep{paper:original_proj}.
-The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model.
-\\
-We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}.
-Suppose we have observed $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates for which we want to obtain a minimally relevant subset.
-Than, the main steps are the following:
+As a motivational example to the implications of using a reference
+model in feature selection problems, we show its application in the
+form of the projection predictive approach, which uses the reference
+model to project the posterior draws to the submodels
+\citep{paper:original_proj}. The \texttt{R}-package \texttt{projpred}
+(available at \url{https://CRAN.R-project.org/package=projpred})
+implements the projection in case of submodels in the family of the
+generalised linear models and, additionally, it provides a framework
+to choose the optimal submodel size through a predictive utility
+comparison between the submodels and the reference model.
+
+We now summarise the workflow of the projection predictive approach in
+the particular case of the draw-by-draw projection \cite[original
+formulation by][]{paper:original_proj}, following
+\cite{paper:projpred}. Suppose we have observed $n$ statistical units
+with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
+covariates for which we want to obtain a minimally relevant
+subset. Than, the main steps are the following:
 \begin{enumerate}
 \item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
-\item Rank the covariates according to their relevance using some heuristics and consider as candidate submodels only those which preserve this order,  starting from including only the highest ranked covariate (the submodels are then naturally identified by their model size).
-This is not strictly necessary but reduces the number of submodels to consider in the following steps.
+\item Rank the covariates according to their relevance using some
+  heuristics and consider as candidate submodels only those which
+  preserve this order, starting from including only the highest ranked
+  covariate (the submodels are then naturally identified by their
+  model size). This is not strictly necessary but reduces the number
+  of submodels to consider in the following steps.
 \item For each submodel, project the reference model posterior draws as follows:
@@
 \end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the predictive distribution of the reference model with parameters fixed at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate values related to the statistical unit (identified by the subscript $i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the predictive distribution of the submodel.
-The projected draws $\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior for the submodel.
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
+predictive distribution of the reference model with parameters fixed
+at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
+values related to the statistical unit (identified by the subscript
+$i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
+predictive distribution of the submodel. The projected draws
+$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
+for the submodel.
 \item For each submodel (size), test the predictive performance, for example, via cross-validation.
@@
 
-Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem in general, but in the special case of submodels for the family of generalised linear models, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised \citep{paper:original_proj}.
-For further details on the projective prediction workflow and implementation see \cite{paper:projpred}.
+Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
+in general, but in the special case of submodels for the family of
+generalised linear models, \eqref{eq:draw_by_draw} reduces to a
+maximum likelihood estimation problem, which can be easily optimised
+\citep{paper:original_proj}. For further details on the projective
+prediction workflow and implementation see \cite{paper:projpred}.
 
@@
 
-We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}\footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
-The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure.
-Additionally, we have information about 13 covariates which are anthropometric measurements (e.g., height and weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection.
-In total, we have 251 observations.
-The goal is to find the simplest model which is able to predict the amount of fat sufficiently well.
-We use the same data again later on in Section \ref{real-world-data}.
-
-\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection \citep{akaike1974new}, fixing abdomen and height to be always included in the model.
-Here, we implement steplm via AIC without fixing any variable.
-For the selection via projpred, the reference model includes all the covariates, we regularise model complexity with a regularised horseshoe prior on the covariate coefficients \citep{paper:rhs}, submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}.
-The experiments are implemented in \texttt{R} \citep{Rcore2018}.
-The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package.
-In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher (i.e., better) than the reference model score with probability of at least 5\%.
-The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}.
-The projpred approach has only two variables, `abdomen' and `weight', with inclusion frequencies above 50\% (`abdomen' is the only one included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%.
-Such a higher variability and lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}.
-For example, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm.
-In addition, the size of the selected model is much smaller when using projpred.
+We show the benefits of the reference model in the form of the
+projection approach (projpred) with respect to the stepwise backward
+regression (steplm) using the body fat data
+\citep{johnson1996fitting}\footnote{The analysis is based on
+  \texttt{R}-notebook by Vehtari available at
+  \url{https://avehtari.github.io/modelselection/bodyfat.html}.}. The
+target variable of interest is the amount of body fat, which is
+measured with a complex and expensive procedure. Additionally, we have
+information about 13 covariates which are anthropometric measurements
+(e.g., height and weight), some of which are highly correlated among
+themselves and thus provide some challenges in the model selection. In
+total, we have 251 observations. The goal is to find the simplest
+model which is able to predict the amount of fat sufficiently well. We
+use the same data again later on in Section \ref{real-world-data}.
+
+\cite{paper:bodyfat} report results using steplm with a significance
+level of 0.157 with AIC selection \citep{akaike1974new}, fixing
+abdomen and height to be always included in the model. Here, we
+implement steplm via AIC without fixing any variable. For the
+selection via projpred, the reference model includes all the
+covariates, we regularise model complexity with a regularised
+horseshoe prior on the covariate coefficients \citep{paper:rhs},
+submodels are explored using forward search, and the predictive
+utility is the expected log-predictive density (elpd) estimated using
+PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in
+\texttt{R} \citep{Rcore2018}. The steplm approach is carried out
+combining the \texttt{step} and \texttt{lm} functions, whereas the
+selection via projpred is done with the \texttt{projpred} package. In
+order to automatise the latter, we select the submodel as the one with
+the smallest size which has an elpd score higher (i.e., better) than
+the reference model score with probability of at least 5\%. The
+inclusion frequencies of each feature in the final model after 100
+bootstrap samples are depicted in Figure
+\ref{fig:inclusion_frequencies}. The projpred approach has only two
+variables, `abdomen' and `weight', with inclusion frequencies above
+50\% (`abdomen' is the only one included always), the third most
+included is `wrist' at 44\%, and the fourth is `height' at 35\%, while
+steplm has seven features above 50\%. Such a higher variability and
+lower stability of steplm can be observed also in the bootstrap model
+selection frequencies reported in Table
+\ref{tab:model_frequencies}. For example, the first five selected
+models have a cumulative frequency of 76\% with projpred, but only of
+14\% with steplm. In addition, the size of the selected model is much
+smaller when using projpred.
 
@@
 
-%\begin{table}[tp]
-%\scriptsize
-%\centering
-%\begin{tabular}{l||l|r||l|r}
-%  \hline
-%M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
-%  \hline
-%1 & abdomen, weight & 34.2 & abdomen, height, wrist, age, chest, biceps & 3.2 \\
-%2 & abdomen, wrist & 13.3 & abdomen, height, wrist, age, neck, forearm, thigh, hip & 2.9 \\
-%3 & abdomen, weight, wrist & 7.6 & abdomen, height, wrist, age, forearm, chest & 1.9 \\
-%4 & abdomen, height & 7.4 & abdomen, height, wrist, age, neck, forearm, chest & 1.9 \\
-%5 & abdomen, height, wrist & 6.7 & abdomen, height, wrist, age, neck, forearm, chest, thigh, hip & 1.9 \\
-%6 & abdomen, age, wrist & 2.9 & abdomen, height, wrist, age, neck, chest, biceps & 1.8 \\
-%7 & abdomen, height, neck & 2.2 & abdomen, height, wrist, age, neck, thigh, biceps, hip & 1.6 \\
-%8 & abdomen, age, height, wrist & 1.2 & abdomen, height, wrist, age, neck, forearm & 1.5 \\
-%9 & abdomen, weight, thigh & 1.1 & abdomen, height, wrist, age, neck, biceps & 1.5 \\
-%10 & abdomen, weight, neck & 1.0 & abdomen, height, wrist, age, beck, forearm, chest, biceps & 1.4 \\
-%   \hline
-%\end{tabular}
-%\caption{Bootstrap model selection frequencies after 1000 bootstrap samples.}
-%\label{tab:model_frequencies}
-%\end{table}
-
-First two rows of Table \ref{tab:model_performances} report the predictive performances, in terms of root mean square error (RMSE), of the full model and the selected models using either the projection predictive approach or the stepwise backward elimination.
-There is no difference in predictive performance of the selected models by different approaches even if there is difference in the selected features.
-
-We repeat the experiment with a modified data set by adding 84 unrelated noisy features.
-Last two rows of Table \ref{tab:model_performances} report RMSE, the size of the selected model and the number of selected noisy features using either the projection predictive approach or the stepwise backward elimination.
-The projection predictive approach has similar predictive performance and the same submodel size as in the first experiment, whereas the stepwise regression has worse predictive performance and selects a much larger submodel including a large number of irrelevant features.
+First two rows of Table \ref{tab:model_performances} report the
+predictive performances, in terms of root mean square error (RMSE), of
+the full model and the selected models using either the projection
+predictive approach or the stepwise backward elimination.  There is no
+difference in predictive performance of the selected models by
+different approaches even if there is difference in the selected
+features.
+
+We repeat the experiment with a modified data set by adding 84
+unrelated noisy features. Last two rows of Table
+\ref{tab:model_performances} report RMSE, the size of the selected
+model and the number of selected noisy features using either the
+projection predictive approach or the stepwise backward elimination.
+The projection predictive approach has similar predictive performance
+and the same submodel size as in the first experiment, whereas the
+stepwise regression has worse predictive performance and selects a
+much larger submodel including a large number of irrelevant features.
 
@@
 \end{tabular}
-\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation.
-Abbreviations: Full = full model; Sel = selected submodel; Size = total number of included covariates; SizeIr = number of included irrelevant covariates.}
+\caption{Model predictive performances with original data (first two
+  rows) and adding noisy features (last two rows) estimated with
+  10-fold cross-validation. Abbreviations: Full = full model; Sel =
+  selected submodel; Size = total number of included covariates;
+  SizeIr = number of included irrelevant covariates.}
 \label{tab:model_performances}
@@
 
-%\begin{table}[tp]
-%\scriptsize
-%\centering
-%\begin{tabular}{l|r|r|r|r}
-%  \hline
-% & rmse.full & rmse.sel & size.sel & noisy.sel \\ 
-%  \hline
-%projpred & 4.4 & 4.5 & 2 & -  \\
-%steplm & 4.4 & 4.5 & 7 & - \\
-%\hline
-%\hline
-%projpred & $^{*}$4.4 & $^{*}$4.5 & 2 & 0  \\
-%steplm & 5.3 & 5.5 & 38 & 32 \\
-%   \hline
-%\end{tabular}
-%\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows). Results with an asterisk using 10-fold CV, otherwise 20-fold CV.}
-%\label{tab:model_performances}
-%\end{table}
-
 \hypertarget{computational-burden}{%
@@
 
-There are various ways to implement a reference model approach.
-A common term in the computational cost is the inference for the reference model.
-In the simple ``bare-bones'' reference model approach we have described above, it is the only added cost.
-In general, a full Bayesian reference model is advisable in order to have the best predictive performance.
-However, including all the available features can often be quite computationally demanding.
-In such a case, a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}.
-However, in some cases, this does not always result in an appreciable speed-up.
-For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model.
-Other alternatives could be using point estimates such maximum a posteriori estimatge if predictions from such reference model without full Bayesian inference are good enough.
-
-The comparison example between projpred and steplm shows that such additional computational cost can be worth it.
-We found that the reference model approach (projpred) selected much sparser submodels, which can result in improved and more stable interpretability and saving time and general costs using the selected model for future predictions.
-Table \ref{tab:model_performances} and results by \citet{paper:model_selection} demonstrate also that in case of large number of features, there can be a significant improvement in the predictive ability compared to feature selection without a reference model, thus justifying additional computational costs in the selection procedure.
-More benefits obtainable through a reference model approach are provided in the experiments discussed in the upcoming section.
+There are various ways to implement a reference model approach. A
+common term in the computational cost is the inference for the
+reference model. In the simple ``bare-bones'' reference model approach
+we have described above, it is the only added cost. In general, a full
+Bayesian reference model is advisable in order to have the best
+predictive performance. However, including all the available features
+can often be quite computationally demanding. In such a case, a first
+possible speed-up could be using screening or dimensionality reduction
+techniques, as for example the supervised principal components
+\citep{bair2006prediction,piironen2018}. However, in some cases, this
+does not always result in an appreciable speed-up. For example, when
+there are several predictive but mutually uncorrelated features, all
+of them have to be included in the reference model. Other alternatives
+could be using point estimates such maximum a posteriori estimatge if
+predictions from such reference model without full Bayesian inference
+are good enough.
+
+The comparison example between projpred and steplm shows that such
+additional computational cost can be worth it. We found that the
+reference model approach (projpred) selected much sparser submodels,
+which can result in improved and more stable interpretability and
+saving time and general costs using the selected model for future
+predictions. Table \ref{tab:model_performances} and results by
+\citet{paper:model_selection} demonstrate also that in case of large
+number of features, there can be a significant improvement in the
+predictive ability compared to feature selection without a reference
+model, thus justifying additional computational costs in the selection
+procedure. More benefits obtainable through a reference model approach
+are provided in the experiments discussed in the upcoming section.
 
@@
 
-In this section, we analyse in more detail the benefits of reference model approaches using the normal means problem as a benchmark.
-The normal means problem consists of estimating the (usually sparse) vector of means of a vector of normally distributed observations.
-The dimensionality of the vector of means is denoted by $p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the random variables $\{Z_{j}\}_{j=1}^{p}$.
-In the normal means problem, the task is to estimate the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model:
-\
+In this section, we analyse in more detail the benefits of reference
+model approaches using the normal means problem as a benchmark. The
+normal means problem consists of estimating the (usually sparse)
+vector of means of a vector of normally distributed observations. The
+dimensionality of the vector of means is denoted by $p$ and
+$\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the random
+variables $\{Z_{j}\}_{j=1}^{p}$. In the normal means problem, the task
+is to estimate the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the
+following model: \
 \begin{equation}\label{eq:normal_means_problem}
@@
 \end{equation}
-This is equivalent to a linear regression where the design matrix is the identity matrix with the number of features being equal to the number of observations.
-This formulation can be found in practice,
-for example, in the analysis of microarray data, where a large set of genes are tested in two groups of patients labeled as positive or negative to some disease \citep{paper:efron,efron2012large}.
-The objective of the analysis is to select the subset of genes statistically relevant to the disease.
-One common way to proceed is to compute the two-sample $t$-statistic for every gene separately.
-After normalising these statistics, they then become the data, $Z$, in the normal means problem \eqref{eq:normal_means_problem}.
-For further details see the examples in \cite{paper:efron, efron2012large}.
-
-In our experiments, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}.
-Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and denote $\rho_{j}=Cor(Y,X_{j})$.
-Further, suppose we have observed $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the $j$-th covariate $\{x_{ij}\}_{i=1}^{n}$.
-Finally, we refer to the Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$.
-Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed with known variance:
-\
+This is equivalent to a linear regression where the design matrix is
+the identity matrix with the number of features being equal to the
+number of observations. This formulation can be found in practice, for
+example, in the analysis of microarray data, where a large set of
+genes are tested in two groups of patients labeled as positive or
+negative to some disease \citep{paper:efron,efron2012large}. The
+objective of the analysis is to select the subset of genes
+statistically relevant to the disease. One common way to proceed is to
+compute the two-sample $t$-statistic for every gene separately.  After
+normalising these statistics, they then become the data, $Z$, in the
+normal means problem \eqref{eq:normal_means_problem}. For further
+details see the examples in \cite{paper:efron, efron2012large}.
+
+In our experiments, we retrieve the normal means problem from the
+sample correlations between the target and the covariates using the
+Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
+continuous target random variable $Y$, a set of $p$ continuous
+covariates $\{X_{j}\}_{j=1}^{p}$, and denote
+$\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$
+statistical units and define $r_{j}$ the sample correlation between
+the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
+$j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
+Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
+$T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate
+normally distributed, the corresponding transformed correlations are
+approximately normally distributed with known variance: \
 \begin{equation} \label{eq:fisher_transformation}
@@
 \end{equation}
-Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and denoting the results as $z_{j}$, we have the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
-\
+Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and
+denoting the results as $z_{j}$, we have the formulation
+\eqref{eq:normal_means_problem} of the normal means problem, this time
+with unit variance: \
 \begin{equation} \label{eq:normal_means_problem2}
@@
 \end{equation}
-Now the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$.
-There are different ways to proceed with the selection in the normal means problem.
-Here, we consider several state-of-the-art approaches primarily from Bayesian statistics.
-
-We briefly review some Bayesian estimation methods to solving the normal means problem.
-They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.
-If these priors have continuous support, as is the case for the Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} or horseshoe-like priors \citep{paper:hs,bhadra2017horseshoe+,paper:rhs}, there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero.
-Whereas \cite{paper:dirichlet_laplace} used k-means clustering over the posterior samples to perform the actual selection, \cite{bhadra2017horseshoe+} just focused their analysis on the obtained shrinkage and the correct estimation of the sparse signals without any actual selection.
-In our experiments, we include the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better to higher number of covariates as compared to other horseshoe-like priors.
-For the Bayesian regression models with these priors, we compare the posterior shrinkage and the correct estimation of the sparse signals with and without using a reference model as a noise filter.
-For this purpose, we consider the   average SSE (sum of square errors) and the average SESE (sum of expected square errors) as quantities measuring estimation accuracy.
-They are defined as
-\
+Now the quantities of interest $\theta_{j}$ are equal to
+$\sqrt{n-3}\,T_{F}(\rho_{j})$. There are different ways to proceed
+with the selection in the normal means problem. Here, we consider
+several state-of-the-art approaches primarily from Bayesian
+statistics.
+
+We briefly review some Bayesian estimation methods to solving the
+normal means problem. They all have in common that a Bayesian
+regression model is fitted using some sparsifying prior on the
+regression coefficients, for example, as discussed in
+\cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
+\cite{johnstone2004needles}. If these priors have continuous support,
+as is the case for the Dirichlet-Laplace
+\cite[DL;][]{paper:dirichlet_laplace} or horseshoe-like priors
+\citep{paper:hs,bhadra2017horseshoe+,paper:rhs}, there is no canonical
+way to complete the selection since the posterior probability of an
+exactly zero signal is always zero. Whereas
+\cite{paper:dirichlet_laplace} used k-means clustering over the
+posterior samples to perform the actual selection,
+\cite{bhadra2017horseshoe+} just focused their analysis on the
+obtained shrinkage and the correct estimation of the sparse signals
+without any actual selection. In our experiments, we include the DL
+prior and the regularised horseshoe (RHS) prior \citep{paper:rhs},
+which we think scales better to higher number of covariates as
+compared to other horseshoe-like priors. For the Bayesian regression
+models with these priors, we compare the posterior shrinkage and the
+correct estimation of the sparse signals with and without using a
+reference model as a noise filter. For this purpose, we consider the
+average SSE (sum of square errors) and the average SESE (sum of
+expected square errors) as quantities measuring estimation
+accuracy. They are defined as \
 \begin{align}
@@
 \end{align}
-where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$.
-We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units.
-The SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates.
-Any (sensible) point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median.
-The results that we show later on in Section \ref{shrinkage-signal} are not sensitive to the choice of this point estimate.
-
-For shrinkage priors, one central aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features.
-Ideally, the irrelevant features should be completely shrunk to zero while the relevant features should not be shrunk at all.
-The amount of shrinkage can be quantified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage).
-For model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type
+where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
+$\hat{\theta}_{j}$ is the posterior median of each parameter
+$\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
+independent of the number of statistical units.  The SESE takes the
+posterior uncertainty in account and thus also the shrinkage of the
+posterior distributions, whereas the SSE only measures the bias in the
+point estimates.  Any (sensible) point estimate could be used to
+compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
+use the posterior median. The results that we show later on in Section
+\ref{shrinkage-signal} are not sensitive to the choice of this point
+estimate.
+
+For shrinkage priors, one central aspect is the amount of shrinkage
+they actually impose on the relevant and irrelevant features. Ideally,
+the irrelevant features should be completely shrunk to zero while the
+relevant features should not be shrunk at all. The amount of shrinkage
+can be quantified by the shrinkage factor $\kappa_{j}$ for each
+parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
+(complete shrinkage). For model \eqref{eq:normal_means_problem2} with
+a hierarchical shrinkage prior of the type
 \begin{align}
@@
 \end{equation}
-In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}.
-We use the posterior mean of $\kappa_{j}$ as a point estimate.
+In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
+the global and local shrinkage parameters of the regularised horseshoe
+prior \cite[for further details see][]{paper:rhs}, whereas on the
+right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
+the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
+notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
+of $\kappa_{j}$ as a point estimate.
 
@@
 
-Here we use simulated data in order to control the difficulty of the selection problem.
-We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation $\rho\in\{0.3,0.5\}$ and number observation $n\in\{50,70,100\}$.
-The total number of covariates $p$ and the number of relevant covariates $k$ are fixed to $p = 1000$ and $k = 100$, respectively.
-In general, the lower $\rho$ and $n$, the more challenging the selection.
-As mentioned, this data generation mechanism was originally proposed by \cite{paper:projpred} who also devise a reference model performing sufficiently well in this situation.
-It consists of a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as covariates and imposing an
-hierarchical prior on their coefficients:
-\
+Here we use simulated data in order to control the difficulty of the
+selection problem. We rely on the scheme \eqref{eq:simulated_data}
+using different levels of correlation $\rho\in\{0.3,0.5\}$ and number
+observation $n\in\{50,70,100\}$. The total number of covariates $p$
+and the number of relevant covariates $k$ are fixed to $p = 1000$ and
+$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
+more challenging the selection. As mentioned, this data generation
+mechanism was originally proposed by \cite{paper:projpred} who also
+devise a reference model performing sufficiently well in this
+situation. It consists of a linear regression using the first five
+supervised principal components (SPCs) \citep{bair2006prediction,
+  piironen2018} as covariates and imposing an hierarchical prior on
+their coefficients: \
 \begin{equation}
@@
 \end{equation}
-In the above, $u_{ij}$ represents the $j$-th SPC evaluated at observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC.
-The SPCs are computed through the \texttt{R}-package \texttt{dimreduce} setting the screening threshold parameter at $0.6s_{max}$. 
-In our experiments the results are not sensible to such a choice of the screening threshold, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.
-
-The normal means problem formulation is obtained as explained in Section \ref{comparison} by applying the Fisher-z-transformation to the empirical correlations.
-We label the reference approach as ``ref'', which consists of using the reference model on top of the computation of the z-values, and the standard approach based on the observed data simply as ``data''.
-In Section \ref{shrinkage-signal}, we analyse the different shrinkage and signal estimates in the context of the full Bayes estimation methods by comparing the ref and data approach.
-In Section \ref{complete-selection}, we present results for the complete selection procedures.
+In the above, $u_{ij}$ represents the $j$-th SPC evaluated at
+observation $i$, and $s_{max}$ denotes the sample standard deviation
+of the largest SPC.  The SPCs are computed through the
+\texttt{R}-package \texttt{dimreduce} setting the screening threshold
+parameter at $0.6s_{max}$.  In our experiments the results are not
+sensible to such a choice of the screening threshold, yet a more
+principled approach would be to use cross-validation to select the
+threshold as done in \cite{paper:projpred}.
+
+The normal means problem formulation is obtained as explained in
+Section \ref{comparison} by applying the Fisher-z-transformation to
+the empirical correlations. We label the reference approach as
+``ref'', which consists of using the reference model on top of the
+computation of the z-values, and the standard approach based on the
+observed data simply as ``data''. In Section \ref{shrinkage-signal},
+we analyse the different shrinkage and signal estimates in the context
+of the full Bayes estimation methods by comparing the ref and data
+approach. In Section \ref{complete-selection}, we present results for
+the complete selection procedures.
 
@@
 \subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
-In the framework of fully Bayesian estimation methods, we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}.
-% Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
-For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we use an uniform prior on the interval $(1/p,1/2)$.
-For the regularised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage.
-The results are not sensitive with respect to the specific choice.
-\
-Since, as explained at the start of Section \ref{comparison}, continuous priors usually do not provide an automatic selection procedure, we study the amount of shrinkage and the bias of the posterior medians looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrinkage factors.
+In the framework of fully Bayesian estimation methods, we analyse the
+effect of the reference model using two continuous hierarchical
+shrinkage priors: the Dirichlet-Laplace
+\citep{paper:dirichlet_laplace} and the regularised horseshoe prior
+\citep{paper:rhs}.
+%
+For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we
+use an uniform prior on the interval $(1/p,1/2)$. For the regularised
+horseshoe prior, we follow the recommendations provided in
+\cite{paper:rhs} by setting the prior guess of the number of relevant
+covariates to one in order to achieve the highest possible
+shrinkage. The results are not sensitive with respect to the specific
+choice.  \ Since, as explained at the start of Section
+\ref{comparison}, continuous priors usually do not provide an
+automatic selection procedure, we study the amount of shrinkage and
+the bias of the posterior medians looking at the SESE and the SSE (see
+definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the
+posterior mean of the shrinkage factors.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
-  \caption{Posterior intervals for the parameters of the normal means problem ($n=50$, $\rho=0.3$) using the regularised horseshoe prior.
-Posterior means and one standard deviation intervals are depicted.
-Relevant and non-relevant features are displayed in red and in blue respectively.
-Horizontal dashed lines corresponds to the true value of the mean for the relevant features.\\}
+  \caption{Posterior intervals for the parameters of the normal means
+    problem ($n=50$, $\rho=0.3$) using the regularised horseshoe
+    prior. Posterior means and one standard deviation intervals are
+    depicted. Relevant and non-relevant features are displayed in red
+    and in blue respectively. Horizontal dashed lines corresponds to
+    the true value of the mean for the relevant features.\\}
   \label{fig:posterior_intervals}
@@
 
-Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior with the data approach on the left and the ref approach on the right-hand side.
-It is evident how the reference model helps in tearing apart the signal from the noise, resulting in less biased estimates and clearer separation between relevant and irrelevant features.
-This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted based on 100 simulations.
-We observe that the reference approach (in orange) has a clearly lower estimate for both the SESE and the SSE.
-As $n$ and $\rho$ increase, the amount of error diminishes, as expected, due to a larger amount of information of the relevance of each variable provided by the data.
-The two priors (RHS and DL) seem to achieve similar results under all conditions.
+Figure \ref{fig:posterior_intervals} shows an example of posterior
+distributions for the model \eqref{eq:normal_means_problem2} using the
+regularised horseshoe prior with the data approach on the left and the
+ref approach on the right-hand side. It is evident how the reference
+model helps in tearing apart the signal from the noise, resulting in
+less biased estimates and clearer separation between relevant and
+irrelevant features. This is quantified in Figure \ref{fig:SESE_SSE}
+where average SESE and SSE are depicted based on 100 simulations. We
+observe that the reference approach (in orange) has a clearly lower
+estimate for both the SESE and the SSE. As $n$ and $\rho$ increase,
+the amount of error diminishes, as expected, due to a larger amount of
+information of the relevance of each variable provided by the
+data. The two priors (RHS and DL) seem to achieve similar results
+under all conditions.
 
@@
 
-Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged over 100 data simulations.
-Relevant and non-relevant features are highlighted in red and blue respectively.
-The ideal shrinkage would be $\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is noise.
-The shrinkage factors using the data and reference approach are depicted on the y-axis and on the x-axis respectively.
-If the reference model did not make any difference, we would expect the points to lie on the diagonal.
-For the non-relevant features points are on the diagonal on average for all the simulated scenarios, which implies that their shrinkage was not improved by the reference approach.
-For the relevant features, the points are always located under the diagonal, which means that the reference model helps and true signals are shrunk less.
-This benefit is roughly proportional to the difficulty of the problem, that is, the benefit increases with lower correlations and a smaller number of observations.
-The perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations.
-In a single data realisation, there is more noise and the cluster are closer and overlapping.
-The results for the Dirichlet-Laplace prior are very similar.
+Figure \ref{fig:k} shows the posterior means for the shrinkage factors
+of each parameter using the regularised horseshoe prior, averaged over
+100 data simulations. Relevant and non-relevant features are
+highlighted in red and blue respectively. The ideal shrinkage would be
+$\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is
+noise. The shrinkage factors using the data and reference approach are
+depicted on the y-axis and on the x-axis respectively. If the
+reference model did not make any difference, we would expect the
+points to lie on the diagonal. For the non-relevant features points
+are on the diagonal on average for all the simulated scenarios, which
+implies that their shrinkage was not improved by the reference
+approach. For the relevant features, the points are always located
+under the diagonal, which means that the reference model helps and
+true signals are shrunk less. This benefit is roughly proportional to
+the difficulty of the problem, that is, the benefit increases with
+lower correlations and a smaller number of observations. The perfect
+distinction of the two clusters of features (relevant and
+non-relevant) observable on both the marginal distributions of the
+shrinkage factors is due to the averaging over the 100 data
+simulations. In a single data realisation, there is more noise and the
+cluster are closer and overlapping. The results for the
+Dirichlet-Laplace prior are very similar.
 
@@
   \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
-  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior based on 100 simulations.
-Relevant and non-relevant variables are displayed in red and blue respectively.\\}
+  \caption{Average posterior mean values for the shrinkage factors
+    using the regularised horseshoe prior based on 100
+    simulations. Relevant and non-relevant variables are displayed in
+    red and blue respectively.\\}
   \label{fig:k}
@@
 \subsubsection{Complete selection analysis}\label{complete-selection}}
-As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals.
-\
-
-The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}.
-It consists of testing the z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$ meaning no relevance) against the alternative hypothesis distribution $f_{1}$.
-In our case $f_{0}$ corresponds to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}).
-The quantity of interest is the local false discovery rate (loc.fdr) defined as:
-\
+As complete selection procedures we consider the control of the local
+false discovery rate \citep{paper:efron, efron2012large}, the
+empirical Bayes median \citep{johnstone2004needles} and the selection
+by posterior credible intervals.  \
+
+The control of the local false discovery rate is applied through the
+\texttt{R}-package \texttt{locfdr}. It consists of testing the
+z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the
+theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
+meaning no relevance) against the alternative hypothesis distribution
+$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
+distribution (see expression \eqref{eq:normal_means_problem2}). The
+quantity of interest is the local false discovery rate (loc.fdr)
+defined as: \
 \begin{equation}
@@
 \end{equation}
-where $\pi_{0}$ is the prior probability of $H_0$ and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values.
-The latter is estimated using splines with 7 degrees of freedom.
-We select features with local false discovery rate below $0.2$, which is suggested by \citet{efron2012large} as it corresponds to a Bayes factor larger than 36 (assuming $\pi_{0}\geq0.9$).
-The results of the comparison are not sensitive to the specific value.
-We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
-
-The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists of fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution.
-As suggested by \cite{johnstone2004needles}, we use a Laplace distribution resulting in a thresholding property, that is, there exists a threshold value such that all the data under that threshold have posterior median equal to zero.
-Therefore the selection is done by selecting only those parameters whose posterior median is different from zero.
-The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood.
-The selection by 90\% posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 5\% and the 95\% quantiles.
-
-Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on the vertical axis versus the average false discovery rate on the horizontal axis based on 100 data simulations for the different combinations of $n$ and $\rho$.
-For each method (different colours) the squares and the circles correspond to using the reference and approach respectively.
-The best selection performance is on the top-left corner of each plot, as it implies the lowest false discovery rate and the highest sensitivity.
-We see that regardless of the applied selection method, the use of a reference model improves the selection performance as it reduces the false discovery rate (shifting to the left) or increases the sensitivity (shifting upwards).
-In accordance with what can be expected, the larger number of observations and the higher the true correlations, the easier the selection is.
-Thus, for easier selection scenarios, the benefits of the reference model are smaller since the raw data already provide enough information to identify the relevant covariates.
+where $\pi_{0}$ is the prior probability of $H_0$ and
+$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
+distribution of the z-values. The latter is estimated using splines
+with 7 degrees of freedom. We select features with local false
+discovery rate below $0.2$, which is suggested by
+\citet{efron2012large} as it corresponds to a Bayes factor larger than
+36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
+sensitive to the specific value. We use the default setting to
+estimate $\pi_{0}$ from the data provided by the package.
+
+The empirical Bayes median procedure is given by the
+\texttt{R}-package \texttt{EbayesThresh} and consists of fitting a
+Bayesian model with a prior composed by a mixture of a delta in zero
+and a heavy-tailed distribution. As suggested by
+\cite{johnstone2004needles}, we use a Laplace distribution resulting
+in a thresholding property, that is, there exists a threshold value
+such that all the data under that threshold have posterior median
+equal to zero. Therefore the selection is done by selecting only those
+parameters whose posterior median is different from zero. The
+hyperparameter of the Laplace distribution and the mixing weight of
+the prior are estimated by marginal maximum likelihood.  The selection
+by 90\% posterior credible intervals is done using the regularised
+horseshoe prior and selecting those features whose posterior
+distribution does not include zero in the interval between the 5\% and
+the 95\% quantiles.
+
+Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on
+the vertical axis versus the average false discovery rate on the
+horizontal axis based on 100 data simulations for the different
+combinations of $n$ and $\rho$. For each method (different colours)
+the squares and the circles correspond to using the reference and
+approach respectively. The best selection performance is on the
+top-left corner of each plot, as it implies the lowest false discovery
+rate and the highest sensitivity. We see that regardless of the
+applied selection method, the use of a reference model improves the
+selection performance as it reduces the false discovery rate (shifting
+to the left) or increases the sensitivity (shifting upwards). In
+accordance with what can be expected, the larger number of
+observations and the higher the true correlations, the easier the
+selection is. Thus, for easier selection scenarios, the benefits of
+the reference model are smaller since the raw data already provide
+enough information to identify the relevant covariates.
 
@@
 
-Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals based on 100 simulations.
-Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process.
-Further details are available in \cite{paper:stability}.
-The reference model helps in improving the stability of the selection: Again, the benefits are bigger when the problem is more difficult (small $n$ and $\rho$).
-In addition, we observe less uncertainty in the stability estimates for the reference approach (i.e., smaller width of the 95\% intervals), which can be still connected to the overall stability of the procedure.
+Figure \ref{fig:stability} shows the estimates of the stability
+measure proposed by \cite{paper:stability} with 0.95 confidence
+intervals based on 100 simulations. Such a measure takes in account
+the variability of the subset of the selected features at each
+simulation (originally at each bootstrap sample), modelling the
+selection of each variable as a Bernoulli process. Further details are
+available in \cite{paper:stability}. The reference model helps in
+improving the stability of the selection: Again, the benefits are
+bigger when the problem is more difficult (small $n$ and $\rho$). In
+addition, we observe less uncertainty in the stability estimates for
+the reference approach (i.e., smaller width of the 95\% intervals),
+which can be still connected to the overall stability of the
+procedure.
 
@@
 
-We conclude our experiments using the real world `body fat' dataset one more time, which was already described in the motivational example comparing the projection predictive approach and the stepwise regression in Section \ref{projection}.
-We carry out two different analyses: one using the normal means problem framework and another one using selection via stepwise backward regression.
-In the former, we add noisy uncorrelated covariates to the original data up to a total of 1000 features.
-These covariates are normally distributed and scaled as the original covariates.
-We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher-Z-transformation.
-The original assumption in order for \eqref{eq:fisher_transformation} to hold is that the variables are jointly normally distributed.
-In our experience the normal approximation in \eqref{eq:fisher_transformation} is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and instead estimate it from the data.
-The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 90\% (ci.90).
-In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$ (i.e., the full size of the data).
-For each condition, results are averaged over 100 bootstrap samples of the respective size.
-
-%The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap.
-6]{efron2012large}, whereas the median absolute deviation from zero for the empirical Bayes median method.
-The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance
+We conclude our experiments using the real world `body fat' dataset
+one more time, which was already described in the motivational example
+comparing the projection predictive approach and the stepwise
+regression in Section \ref{projection}. We carry out two different
+analyses: one using the normal means problem framework and another one
+using selection via stepwise backward regression. In the former, we
+add noisy uncorrelated covariates to the original data up to a total
+of 1000 features. These covariates are normally distributed and scaled
+as the original covariates. We compute correlations between each
+variable and the target variable, that is the amount of fat, and
+transform them by Fisher-Z-transformation. The original assumption in
+order for \eqref{eq:fisher_transformation} to hold is that the
+variables are jointly normally distributed. In our experience the
+normal approximation in \eqref{eq:fisher_transformation} is still
+reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the
+variance to be one, and instead estimate it from the data. The methods
+we compare are those used in Section \ref{complete-selection}: the
+control of the local false discovery rate (loc.fdr), the empirical
+Bayes median (EB.med) and the selection by posterior credible
+intervals at level 90\% (ci.90).  In order to vary the difficulty of
+the selection, we bootstrap subsamples of different sizes, going from
+$n=50$ up to $n=251$ (i.e., the full size of the data). For each
+condition, results are averaged over 100 bootstrap samples of the
+respective size.
 
@@
 
-Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate.
-Since we do not have a ground truth available with regard the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree.
-The artificially added features are naturally irrelevant by construction.
-In almost all the bootstrapped subsamples, the reference model improves the selection both in terms of sensitivity and false discovery rate.
-When $n=50$, we observe a worsening in terms of false discovery rate, yet by a lower amount compared to the gain in sensitivity.
-Again, we observe that the benefits are more evident as the selection becomes more challenging (i.e., lower number of observations).
-Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}.
-The benefits of the reference model are here marginal with only small improvements.
-
-%\begin{figure}[tp]
-%  \centering
-%  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
-%  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
-%  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
-%\end{figure}
-
-%\begin{figure}[tp]
-%  \centering
-%  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
-%  \caption{Stability estimates with 0.95 confidence intervals based on 100 data simulations.\\}
-%  \label{fig:bodyfat_varyingP_stability}
-%\end{figure}
-
-% As an additional experiment, we run the selection bootstrapping from the whole dataset, but varying the overall number of covariates from $p=100$ up to $p=5000$.
-Figures \ref{fig:bodyfat_varyingP_sensitivity_vs_fdr} and \ref{fig:bodyfat_varyingP_stability} respectively show the sensitivity against the false discovery rate and the stability results.
-As in the previous experiment, we note that the reference model has a larger impact as the complexity of the problem increases: previously as $n$ decreases, now as $p$ increases.
-Note the different scale of the sensitivity and the false discovery rate axes.
-We observe an odd behaviour of the selection via credible intervals (ci.90): when $p=100$ and $p=5000$ the results are strongly different from the other methods, both in terms of sensitivity/false discovery rate and stability.
-%Such behaviour can be in part explained by the connection between low stability and high uncertainty in the estimates.
+Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
+against the false discovery rate. Since we do not have a ground truth
+available with regard the original covariates of the data, we believe
+it is reasonable to consider all of them relevant, at least at some
+degree. The artificially added features are naturally irrelevant by
+construction. In almost all the bootstrapped subsamples, the reference
+model improves the selection both in terms of sensitivity and false
+discovery rate. When $n=50$, we observe a worsening in terms of false
+discovery rate, yet by a lower amount compared to the gain in
+sensitivity. Again, we observe that the benefits are more evident as
+the selection becomes more challenging (i.e., lower number of
+observations). Figure \ref{fig:bodyfat_stability} shows the stability
+results, still using the measure provided by
+\cite{paper:stability}. The benefits of the reference model are here
+marginal with only small improvements.
 
@@
 
-In the second analysis, we repeat the selection of Section \ref{projection} via stepwise backward regression.
-In this case, the overall number of covariates (original plus noisy) is 100, as it was in the last part of Section \ref{projection}.
-We compare results with and without using a reference model on top of the procedure following our simple reference model approach outlined in \eqref{eq:ref_mod}.
-Figure \ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant features included in the final model and the out-of-sample root mean square error (RMSE).
-Results are based on 100 bootstrap samples on the whole dataset, and the predictive performance is tested on the observations excluded at each bootstrap sample.
-We observe that the reference model reduces the number of irrelevant features included in the final model.
-This leads to less overfitting and thus to improved out-of-sample predictive performance in terms of RMSE.
-The reference model approach applied to the stepwise backward regression achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, for instance, the projective prediction approach (see results of Section \ref{projection}).
-
-%Also, in this case, we see that there is no notable difference in terms of the stability of the two approaches, which in this case is qualitatively assessed through the variability of the histogram.
-We can not use the stability measure provided by \cite{paper:stability}, since it does not take in account possibly swaps in the set of selected features due to high correlation between the covariates, which in this case can occur.
-
-In this example, we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and efficient estimation.
-We do not argue that this is always a good choice and more sophisticated models can lead to even better results.
-Since, in our case, the sake of the analysis was only to motivate the use of reference models in general, and since we needed to average results over a lot of repetitions per simulation condition, we preferred to stick to such a comparably simple reference model.
+In the second analysis, we repeat the selection of Section
+\ref{projection} via stepwise backward regression. In this case, the
+overall number of covariates (original plus noisy) is 100, as it was
+in the last part of Section \ref{projection}. We compare results with
+and without using a reference model on top of the procedure following
+our simple reference model approach outlined in
+\eqref{eq:ref_mod}. Figure \ref{fig:bodyfat_step_refvsdata} shows the
+number of irrelevant features included in the final model and the
+out-of-sample root mean square error (RMSE). Results are based on 100
+bootstrap samples on the whole dataset, and the predictive performance
+is tested on the observations excluded at each bootstrap sample. We
+observe that the reference model reduces the number of irrelevant
+features included in the final model. This leads to less overfitting
+and thus to improved out-of-sample predictive performance in terms of
+RMSE. The reference model approach applied to the stepwise backward
+regression achieves outstanding improvements considering its
+simplicity, yet it does not reach the goodness of more thoughtful
+implementations, for instance, the projective prediction approach (see
+results of Section \ref{projection}).
+
+In this example, we have still used the reference model defined as a
+linear regression over some supervised principal components, because
+of its fairly good predictive performance and efficient estimation. We
+do not argue that this is always a good choice and more sophisticated
+models can lead to even better results. Since, in our case, the sake
+of the analysis was only to motivate the use of reference models in
+general, and since we needed to average results over a lot of
+repetitions per simulation condition, we preferred to stick to such a
+comparably simple reference model.
 
@@
 
-In this paper, we demonstrated the benefits of using a reference model to improve feature selection, or more generally, model reduction.
-The goal of this paper is not to provide a specific procedure to carry out the selection, but rather to explain and motivate the general benefits of a reference model.
-We have seen how the reference model acts as an approximation of the data generation mechanism through its predictive distribution.
-Such approximation is generally less noisy than the sample estimation available purely from the observed data, leading to the main benefits of the reference model approach.
-In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different widely used variable selection methods.
-Overall, using a reference model leads to more accurate and stable selection results independently of the specific selection method.
-These benefits apply to a large family of different approaches all involving a reference model in one way or the other.
-Some of these approaches have been present in the literature for several years \cite[e.g.
-see][]{vehtari2012survey,paper:projpred} but often without a clear explanation of \emph{why} they are actually favourable and how they connect to other related approaches.
-We hope that the present paper can fill some of these gaps by providing a unifying framework and understanding of reference models.
-
-%In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}.
-The selection via projection resulted to be more stable and led to a sparser representation.
-After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features.
-Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching the projection predictive approach results.
-
-We argue that, whenever it is possible to come up with a reasonable reference model, it should be employed on top of the preferred selection procedure or as an integral part of more complex methods, for example, the projective prediction approach \citep{paper:projpred}.
-Note that one of the main challenges in many real world application will consist in devising a sensible reference model itself and assessing its predictive performance.
-We did provide a generic way to build simple reference models, but those may not necessarily be appropriate in all situations.
-If more sophisticated reference models are required, which are more specifically tuned to the data and problem at hand, we recommend them to be developed using a robust (Bayesian) modelling workflow, for instance, as outlined in \cite{gabry2019visualization}.
+In this paper, we demonstrated the benefits of using a reference model
+to improve feature selection, or more generally, model reduction. The
+goal of this paper is not to provide a specific procedure to carry out
+the selection, but rather to explain and motivate the general benefits
+of a reference model.  We have seen how the reference model acts as an
+approximation of the data generation mechanism through its predictive
+distribution. Such approximation is generally less noisy than the
+sample estimation available purely from the observed data, leading to
+the main benefits of the reference model approach. In our comparisons,
+we have analysed the effect of a reference model in the form of a
+filter on the observed target values on top of different widely used
+variable selection methods. Overall, using a reference model leads to
+more accurate and stable selection results independently of the
+specific selection method. These benefits apply to a large family of
+different approaches all involving a reference model in one way or the
+other. Some of these approaches have been present in the literature
+for several years \cite[e.g. see][]{vehtari2012survey,paper:projpred}
+but often without a clear explanation of \emph{why} they are actually
+favourable and how they connect to other related approaches. We hope
+that the present paper can fill some of these gaps by providing a
+unifying framework and understanding of reference models.
+
+We argue that, whenever it is possible to come up with a reasonable
+reference model, it should be employed on top of the preferred
+selection procedure or as an integral part of more complex methods,
+for example, the projective prediction approach
+\citep{paper:projpred}. Note that one of the main challenges in many
+real world application will consist in devising a sensible reference
+model itself and assessing its predictive performance. We did provide
+a generic way to build simple reference models, but those may not
+necessarily be appropriate in all situations. If more sophisticated
+reference models are required, which are more specifically tuned to
+the data and problem at hand, we recommend them to be developed using
+a robust (Bayesian) modelling workflow, for instance, as outlined in
+\cite{gabry2019visualization}.
 \\
 
-All Bayesian models used in the this paper have been implemented in the probabilistic programming language \texttt{Stan} \citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo \citep{hoffman2014no,betancourt2017conceptual}.
-The code to run all the experiments is available on GitHub (\url{https://github.com/fpavone/ref-approach-paper}).
+All Bayesian models used in the this paper have been implemented in
+the probabilistic programming language \texttt{Stan}
+\citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo
+\citep{hoffman2014no,betancourt2017conceptual}. The code to run all
+the experiments is available on GitHub
+(\url{https://github.com/fpavone/ref-approach-paper}).
 

### 2019-07-30 paper/ref_approach.tex
start of the re-organization interrupted by vacation

@@
   Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data.
-While a vast number of feature selection procedures are available, it often remains unclear what are the underlying principles explaining why certain methods are working better than others.
-We investigate and discuss one of these principles in detail, which we identify with the use of a reference model.
-We demonstrate how reference models act as a noise-filters on the target variable by approximating its data generation mechanism.
-To this end, we devise a simple reference model approach that can be used on top of any feature selection method.
+In this paper we discuss and demonstrate the benefits of using a reference model in model selection in general.
+A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism.
+Using the reference model predictions in the model selection reduces tha variability and improves stability leading to improved model selection performance.
+The simplest reference model approach can be used in combination of common feature selection methods .
 In several numerical experiments, we show how this translates into better and more stable feature selection independently of the specific selection procedure.
-These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
-
-%When a reference model is used to guide the variable selection problem, it acts as a noise-filter modelling the data generation mechanism.
-We show how this translate into higher stability and better selection of variables.
-We devise a simple reference model approach that can be used on top of any feature selection procedure and use the normal means problem as a benchmark comparing different methods using or not a reference model.
-We include in our comparisons state-of-the-art complete selection procedures showing improved stability, false discovery rate and sensitivity of the selection, and also Bayesian methods controlling the amount of posterior shrinkage and bias.
-Furthermore we show in a real-world example the benefits achieved by the reference model through the projection predictive approach compared to the selection via stepwise backward regression.
-
+% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
 \end{abstract}
@@
 of a reference model, which can be, for example, a full-encompassing
-model including all covariates. The reference model approach has been
-used for long time in Bayesian statistics since the seminal work of
-\citet{paper:reference_lindley}. For more historical references, see
-papers by \citet{vehtari2012survey} and \citet{paper:model_selection},
-and for most recent methodological development see
-\citet{paper:projpred}.
+model including all covariates.  The main assumption under any
+reference model approach is that we operate in an
+$\mathcal{M}$-\textit{complete} framework
+\citep{book:bernardo_smith,vehtari2012survey}, that is we have
+constructed a model which reflects in the best way our beliefs about
+the future data and which has passed model checking and criticism
+\citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
+has been used for long time in Bayesian statistics since the seminal
+work of \citet{paper:reference_lindley}. For more historical
+references, see papers by \citet{vehtari2012survey} and
+\citet{paper:model_selection}, and for most recent methodological
+development see \citet{paper:projpred}.
 
@@
 
-In this paper, we examine the benefits of using reference models in
-detail. We illustrate how a properly designed reference model is able
-to filter parts of the noise present in the data, and hence provide an
-improved and more stable selection process. This holds even if the
-reference model does not perfectly resemble the true data generating
-process. Moreover, our analyses indicate that the substantial
-reduction of variance attributable to noise is usually more important
-than small potential bias due to model misspecification.  We argue
-that, regardless of how the reference model is set up and used in the
-inference procedure, it can be always seen as acting as a filter on
-the observed data. Following this idea, we devise a simple reference
-model approach that can be applied on top of any variable selection
-procedure.
-
-In our simulations and analysis of real data, we apply several
-state-of-the-art methods for variable selection and compare, for each
-of these methods, the results obtained by using a data based and a
-reference model based approach. When a full variable selection is
-carried out, we report and compare quantities such as the false
-discovery rate \citep{paper:fdr_BH}, sensitivity and stability of the
-selection \citep{paper:stability}. For fully Bayesian methods, we
-additionally report results in terms of shrinkage and accuracy of the
-posterior estimates.  We show the benefits of a reference model
-approach, regardless of what specific procedure is applied, using the
-normal means estimation problem as a benchmark.  Variable selection is
-typically most challenging in \textit{small n large p} scenarios, that
-is, scenarios with small number of observations but a lot of unknown
-model parameters.  These occur frequently, for example, in microarray
-data analysis in medicine or biology
-\citep{dudoit2003multiple,liao2007logistic,paper:efron}.  In general,
-the less data we have and the more complex the estimated models, the
-higher the benefit of using a reference models as the basis for
-variable selection.  Our results indicate that the core reason why the
-reference model based methods perform well is the reference model
-itself, rather than the specific way of using it. We do recognise that
-all these methods diversify how the subset of variables is actually
-chosen and which properties it has, thus it remains fundamental to
-investigate and develop such different procedures. Although we focus
-on Bayesian approach in this paper, the benefits of the reference
-model approach can also be obtained in non-Bayesian settings.
-
-The remainder of the paper is structured as follows. In Section
-\ref{reference-model-approach}, we review the concept of the reference
-model, its benefits with examples, including the projection predictive
-approach, and how it can be used as a filter on data in a simple
-way. In Section \ref{comparison}, we use different methods for feature
-selection comparing the selection results with and without using a
-reference model in the framework of the normal means problem. Finally,
-we end with a conclusion in Section \ref{conclusion}.
-
-\hypertarget{reference-model-approach}{%
-\section{Why the reference model helps}\label{reference-model-approach}}
-
-The main assumption under any reference model approach is that we
-operate in an $\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
-model which reflects in the best way our beliefs about the future
-data. In practice, this would often be the full-encompassing model
-(including all models we consider having non-zero prior
-probability as submodels) which has passed model checking and criticism \citep[see,
-e.g.][]{gelman2013bayesian}.
-
-A good predictive model is able to filter part of the noise present in
-the data. The noise is the main source of the instability and tends to
-obscure the relevance of the covariates in relation to the target
-variable of interest. Indeed, let us consider the following
-explanatory example taken from \cite{paper:projpred}. The data
-generation mechanism is
-\begin{alignat}{2} \label{eq:simulated_data}
-     &f\sim N(0,1) && \nonumber \\ 
-     Y|&f\sim N(f,1) && \\
-     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
-     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
-\end{alignat}
-where $f$ is the latent variable of interest of which $Y$ is a noisy
-observation. The first $k$ covariates are strongly related to the
-target variable $Y$ and correlated among themselves. Precisely, $\rho$
-is the correlation among any pair of the first $k$ covariates, whereas
-$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
-any relevant covariate and, respectively, $f$ and $Y$. If we had an
-infinite amount of observations, the sample correlation would be equal
-to the true correlation between $X_j$ and $Y$. However, even in this
-ideal asymptotic regime, this correlation would still remain a biased
-indicator of the true relevance of each covariate (represented by the
-correlation between $X_j$ and $f$) due to the intrinsic noisy nature
-of $Y$.
-
-When using a reference model, we first obtain predictions for $f$
-using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account
-that we have only observed the noisy representation $Y$ of $f$. If our
-model is good, we are able to describe $f$ better than $Y$ itself can,
-which improves the accuracy in the estimation of the relevance of the
-covariates.  Figure \ref{fig:correlation} illustrates this process in
-the form of a scatter plot of (absolute) correlations of the
-covariates with $Y$ against the corresponding correlations with the
-predictions of a reference model (in this case the posterior
-predictive means of model \eqref{eq:ref_mod}; see Section
-\ref{simulated-data}). Looking at the marginal distributions, we see
-that using a reference model to filter out noise in the data, the two
-groups of features (relevant and non-relevant) can be distinguished
-much better than when the correlation is computed using the observed
-noisy data directly.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
-  \caption{Sample correlation plot of each feature (relevant in red, non-relevant in blue) with the target variable $y$ and the latent variable $f$ respectively on the x and y axis.
-Data are generated according to procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
-  \label{fig:correlation}
-\end{figure}
-
-As an another example, let us consider a candidate submodel in a
-feature selection process and let us refer to the parameter
-distribution of the submodel by $\pi$ and to the induced predictive
-distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
-that $q_{\pi}(\tilde{y})$ maximises some predictive performance
-utility, for example, the expected log-predictive density (elpd)
-defined as: \
-\begin{equation}\label{eq:elpd}
-\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
-\end{equation}
-where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
-mechanism of future data $\tilde{y}$. If we refer to the posterior
-predictive distribution of a reference model with $p(\tilde{y}|D)$,
-where $D$ stands for the data on which we conditioned on, we can
-approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
-data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
-elpd using the reference model predictive distribution is equivalent
-to the minimisation of the Kullback-Leibler (KL) divergence from the
-reference model's predictive distribution to the submodel's predictive
-distribution: \
-\begin{equation} \label{proj_as_filter}
-\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
-\end{equation}
-The term on the right-hand side of Equation \eqref{proj_as_filter}
-describes what is referred to as the projection of the predictive
-distribution, which is the general idea behind the projection
-predictive approach \cite[see][]{paper:projpred}. Again the reference
-model is acting as a filter, or substitute, on data.
-
-Relying on the idea of the reference model as a noise-filter, a
-generic reference model approach, which can be used on top of any
-feature selection procedure, consists of simply substituting the
-target observations with corresponding point predictions of the
-reference model, for instance, the posterior predictive
-means. Afterwards, any method for feature selection can be used. We do
-not argue that such a reference model approach should necessarily be
-used as is for feature selection in real applications. There are
-several more sophisticated reference model approaches available in the
-literature \cite[see,
-e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
-which are likely to yield even better results. Rather, the reason for
-focusing on this simple version is to enable a fair comparison between
-a reference model and a purely data based approach when otherwise
-using the same selection procedures. Other kinds of comparisons, as
-the one presented in Section \ref{projection}, work well as
-motivational examples but lack in terms of generality since the
-presence or absence of a reference model is not the only aspect
-differentiating the two procedures. We will come back to the more
-general comparison in Section \ref{comparison}.
-
-\hypertarget{projection}{%
-\subsection{Benefits of the reference model: an example with the projection predictive approach}\label{projection}}
-
-As a motivational example to the implications of using a reference
-model in feature selection problems, we show its application in the
-form of the projection predictive approach, which uses the reference
-model to project the posterior draws to the submodels
-\citep{paper:original_proj}. The \texttt{R}-package \texttt{projpred}
-(available at \url{https://CRAN.R-project.org/package=projpred})
-implements the projection in case of submodels in the family of the
-generalised linear models and, additionally, it provides a framework
-to choose the optimal submodel size through a predictive utility
-comparison between the submodels and the reference model.
-
-We now summarise the workflow of the projection predictive approach in
-the particular case of the draw-by-draw projection \cite[original
-formulation by][]{paper:original_proj}, following
-\cite{paper:projpred}. Suppose we have observed $n$ statistical units
-with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
-covariates for which we want to obtain a minimally relevant
-subset. Than, the main steps are the following:
-\begin{enumerate}
-\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
-\item Rank the covariates according to their relevance using some
-  heuristics and consider as candidate submodels only those which
-  preserve this order, starting from including only the highest ranked
-  covariate (the submodels are then naturally identified by their
-  model size). This is not strictly necessary but reduces the number
-  of submodels to consider in the following steps.
-\item For each submodel, project the reference model posterior draws as follows:
-\begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,..,S \,,
-\end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
-predictive distribution of the reference model with parameters fixed
-at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
-values related to the statistical unit (identified by the subscript
-$i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
-predictive distribution of the submodel. The projected draws
-$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
-for the submodel.
-\item For each submodel (size), test the predictive performance, for example, via cross-validation.
-\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
-\end{enumerate}
-
-Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
-in general, but in the special case of submodels for the family of
-generalised linear models, \eqref{eq:draw_by_draw} reduces to a
-maximum likelihood estimation problem, which can be easily optimised
-\citep{paper:original_proj}. For further details on the projective
-prediction workflow and implementation see \cite{paper:projpred}.
-
-\subsubsection{Example: Variable selection in bodyfat prediction}
-
-We show the benefits of the reference model in the form of the
-projection approach (projpred) with respect to the stepwise backward
-regression (steplm) using the body fat data
+\subsection{Example of model selection with or without reference model}
+
+To motivate the further discussion and experiments, we start by simple
+example comparing projection predictive approach (projpred,
+\citet{paper:projpred}) which uses a reference model and classic
+stepwise backward regression (steplm).  using the body fat data
 \citep{johnson1996fitting}\footnote{The analysis is based on
@@
   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.  The
-target variable of interest is the amount of body fat, which is
-measured with a complex and expensive procedure. Additionally, we have
-information about 13 covariates which are anthropometric measurements
-(e.g., height and weight), some of which are highly correlated among
-themselves and thus provide some challenges in the model selection. In
-total, we have 251 observations. The goal is to find the simplest
-model which is able to predict the amount of fat sufficiently well. We
-use the same data again later on in Section \ref{real-world-data}.
+experiments are implemented in \texttt{R} \citep{Rcore2018}.
+
+The target variable of interest is the amount of body fat, which is
+measured by immersing a person in water tank which is a complex and
+expensive procedure. Additionally, we have information about 13
+covariates which are anthropometric measurements (e.g., height, weight
+and thicknes of skin and fat in different body locations). The
+covariates are are highly correlated whichs causes additional
+challenge in the model selection. In total, we have 251
+observations. The goal is to find the model which is able to predict
+the amount of fat sufficiently well while requiring least amount of
+measurements for a new person.
 
@@
 level of 0.157 with AIC selection \citep{akaike1974new}, fixing
-abdomen and height to be always included in the model. Here, we
-implement steplm via AIC without fixing any variable. For the
-selection via projpred, the reference model includes all the
-covariates, we regularise model complexity with a regularised
-horseshoe prior on the covariate coefficients \citep{paper:rhs},
-submodels are explored using forward search, and the predictive
-utility is the expected log-predictive density (elpd) estimated using
-PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in
-\texttt{R} \citep{Rcore2018}. The steplm approach is carried out
-combining the \texttt{step} and \texttt{lm} functions, whereas the
-selection via projpred is done with the \texttt{projpred} package. In
-order to automatise the latter, we select the submodel as the one with
-the smallest size which has an elpd score higher (i.e., better) than
-the reference model score with probability of at least 5\%. The
-inclusion frequencies of each feature in the final model after 100
+abdomen and height to be always included in the model. For better
+comparison we don't fix any of the variables.  The steplm approach is
+carried out combining the \texttt{step} and \texttt{lm} functions
+
+For the selection via projpred, the Bayesian reference model includes
+all the covariates using a regularised horseshoe prior on the
+covariate coefficients \citep{paper:rhs}. Submodels are explored using
+forward search (the results are not sensitive to whether forward or
+backward search is used), and the predictive utility is the expected
+log-predictive density (elpd) estimated using PSIS-LOO
+\citep{paper:psis_loo}.  We select the submodel as the one with the
+smallest size which has an elpd score higher (i.e., better) than the
+reference model score with probability of at least 5\%. See Appendix A
+for brief review of projection predictive approach and papers by
+\citet{paper:model_selection} and \citet{paper:projpred} for more
+details. projpred selection is made using the \texttt{projpred} package.
+
+The inclusion frequencies of each feature in the final model given 100
 bootstrap samples are depicted in Figure
@@
 smaller when using projpred.
-
 \begin{figure}[tp]
@@
 First two rows of Table \ref{tab:model_performances} report the
-predictive performances, in terms of root mean square error (RMSE), of
-the full model and the selected models using either the projection
-predictive approach or the stepwise backward elimination.  There is no
-difference in predictive performance of the selected models by
-different approaches even if there is difference in the selected
-features.
+predictive performances, in terms of cross-validated root mean square
+error (RMSE), of the full model and the selected models using either
+the projection predictive approach or the stepwise backward
+elimination.  There is no difference in predictive performance of the
+selected models by different approaches even if there is difference in
+the selected features.
 
@@
 unrelated noisy features. Last two rows of Table
-\ref{tab:model_performances} report RMSE, the size of the selected
-model and the number of selected noisy features using either the
-projection predictive approach or the stepwise backward elimination.
-The projection predictive approach has similar predictive performance
-and the same submodel size as in the first experiment, whereas the
-stepwise regression has worse predictive performance and selects a
-much larger submodel including a large number of irrelevant features.
+\ref{tab:model_performances} report cross-validated RMSE, the size of
+the selected model and the number of selected noisy features using
+either the projection predictive approach or the stepwise backward
+elimination.  The projection predictive approach has similar
+predictive performance and the same submodel size as in the first
+experiment, whereas the stepwise regression has worse predictive
+performance and selects a much larger submodel including a large
+number of irrelevant features.
 
@@
 
-\hypertarget{computational-burden}{%
-\subsection{Computational cost} \label{computational-burden}}
-
-There are various ways to implement a reference model approach. A
-common term in the computational cost is the inference for the
-reference model. In the simple ``bare-bones'' reference model approach
-we have described above, it is the only added cost. In general, a full
-Bayesian reference model is advisable in order to have the best
-predictive performance. However, including all the available features
-can often be quite computationally demanding. In such a case, a first
-possible speed-up could be using screening or dimensionality reduction
-techniques, as for example the supervised principal components
-\citep{bair2006prediction,piironen2018}. However, in some cases, this
-does not always result in an appreciable speed-up. For example, when
-there are several predictive but mutually uncorrelated features, all
-of them have to be included in the reference model. Other alternatives
-could be using point estimates such maximum a posteriori estimatge if
-predictions from such reference model without full Bayesian inference
-are good enough.
-
-The comparison example between projpred and steplm shows that such
-additional computational cost can be worth it. We found that the
-reference model approach (projpred) selected much sparser submodels,
-which can result in improved and more stable interpretability and
-saving time and general costs using the selected model for future
-predictions. Table \ref{tab:model_performances} and results by
-\citet{paper:model_selection} demonstrate also that in case of large
-number of features, there can be a significant improvement in the
-predictive ability compared to feature selection without a reference
-model, thus justifying additional computational costs in the selection
-procedure. More benefits obtainable through a reference model approach
-are provided in the experiments discussed in the upcoming section.
+Both projpred and steplm compare a large number of models using either
+forward or backward search, which can lead to selection induced
+overfitting, but even with 100 covariates projpred is able to select a
+submodel with similar performance as the full model. Although projpred
+uses Bayesian inference and steplm maximum likelihood, it is not
+decisive feature explaining the difference in the performance.  The
+main difference between the approaches is whether a reference model is
+used or not, and in the rest of the paper we look into more detail how
+the use of reference model helps and limitations of the approach.
+
+\subsection{Benefits and cost of using a reference model}
+
+A properly designed reference model is able to filter parts of the
+noise present in the data, and hence provide an improved and more
+stable selection process. This holds even if the reference model does
+not perfectly resemble the true data generating process. Moreover, our
+analyses indicate that the substantial reduction of variance
+attributable to noise is usually more important than small potential
+bias due to model misspecification.  We argue that, regardless of how
+the reference model is set up and used in the inference procedure, it
+can be always seen as acting as a filter on the observed
+data. Furthermore, regardless of what specific model selection method
+is used, a reference model can be used instead of raw data during the
+selection process to improve the stability and selection
+performance. Our results indicate that the core reason why the
+reference model based methods perform well is the reference model
+itself, rather than the specific way of using it.  In general, the
+less data we have and the more complex the estimated models, the
+higher the benefit of using a reference models as the basis for
+variable selection.
+
+If one of the models to be compared is the full model which can be
+used as a reference model, there is no additional cost of using a
+reference model. Sometimes including all the available features in an
+elaborate model can often be computationally demanding.  In such a
+case, even simpler screening or dimensionality reduction techniques,
+as for example the supervised principal components
+\citep{bair2006prediction,piironen2018} can produce useful reference
+models.
+
+The remainder of the paper is structured as follows. In Section
+\ref{reference-model-approach}, we review the concept of the reference
+model, its benefits with examples and how it can be used as a filter
+on data in a simple way. In Section \ref{comparison}, we show the
+benefits of a reference model approach, regardless of what specific
+procedure is applied, using the normal means estimation problem as a
+benchmark. Finally, we end with a conclusion in Section
+\ref{conclusion}.
+
+\hypertarget{reference-model-approach}{%
+\section{Why the reference model helps}\label{reference-model-approach}}
+
+A good predictive model is able to filter part of the noise present in
+the data. The noise is the main source of the instability and tends to
+obscure the relevance of the covariates in relation to the target
+variable of interest. Let us consider the following simple
+explanatory example taken from \cite{paper:projpred}. The data
+generation mechanism is
+\begin{alignat}{2} \label{eq:simulated_data}
+     &f\sim N(0,1) && \nonumber \\ 
+     Y|&f\sim N(f,1) && \\
+     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
+     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
+\end{alignat}
+where $f$ is the latent variable of interest of which $Y$ is a noisy
+observation. The first $k$ covariates are strongly related to the
+target variable $Y$ and correlated among themselves. Precisely, $\rho$
+is the correlation among any pair of the first $k$ covariates, whereas
+$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
+any relevant covariate and, respectively, $f$ and $Y$. If we had an
+infinite amount of observations, the sample correlation would be equal
+to the true correlation between $X_j$ and $Y$. However, even in this
+ideal asymptotic regime, this correlation would still remain a biased
+indicator of the true relevance of each covariate (represented by the
+correlation between $X_j$ and $f$) due to the intrinsic noisy nature
+of $Y$.
+
+When using a reference model, we first obtain predictions for $f$
+using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account
+that we have only observed the noisy representation $Y$ of $f$. If our
+model is good, we are able to describe $f$ better than $Y$ itself can,
+which improves the accuracy in the estimation of the relevance of the
+covariates.  Figure \ref{fig:correlation} illustrates this process in
+the form of a scatter plot of (absolute) correlations of the
+covariates with $Y$ against the corresponding correlations with the
+predictions of a reference model (in this case the posterior
+predictive means of model \eqref{eq:ref_mod}; see Section
+\ref{simulated-data}). Looking at the marginal distributions, we see
+that using a reference model to filter out noise in the data, the two
+groups of features (relevant and non-relevant) can be distinguished
+much better than when the correlation is computed using the observed
+noisy data directly.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
+  \caption{Sample correlation plot of each feature (relevant in red, non-relevant in blue) with the target variable $y$ and the latent variable $f$ respectively on the x and y axis.
+Data are generated according to procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
+  \label{fig:correlation}
+\end{figure}
 
@@
 In this section, we analyse in more detail the benefits of reference
-model approaches using the normal means problem as a benchmark. The
-normal means problem consists of estimating the (usually sparse)
-vector of means of a vector of normally distributed observations. The
-dimensionality of the vector of means is denoted by $p$ and
-$\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the random
-variables $\{Z_{j}\}_{j=1}^{p}$. In the normal means problem, the task
-is to estimate the latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the
-following model: \
+model approaches in combination of a few common variable selection
+approach.
+
+\subsection{Simulated data}
+
+The normal means problem consists of estimating the (usually
+sparse) vector of means of a vector of normally distributed
+observations. The dimensionality of the vector of means is denoted by
+$p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the
+random variables $\{Z_{j}\}_{j=1}^{p}$. The task is to estimate the
+latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model: \
 \begin{equation}\label{eq:normal_means_problem}
@@
 Now the quantities of interest $\theta_{j}$ are equal to
-$\sqrt{n-3}\,T_{F}(\rho_{j})$. There are different ways to proceed
-with the selection in the normal means problem. Here, we consider
-several state-of-the-art approaches primarily from Bayesian
-statistics.
-
-We briefly review some Bayesian estimation methods to solving the
-normal means problem. They all have in common that a Bayesian
-regression model is fitted using some sparsifying prior on the
-regression coefficients, for example, as discussed in
-\cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
-\cite{johnstone2004needles}. If these priors have continuous support,
-as is the case for the Dirichlet-Laplace
-\cite[DL;][]{paper:dirichlet_laplace} or horseshoe-like priors
-\citep{paper:hs,bhadra2017horseshoe+,paper:rhs}, there is no canonical
-way to complete the selection since the posterior probability of an
-exactly zero signal is always zero. Whereas
-\cite{paper:dirichlet_laplace} used k-means clustering over the
-posterior samples to perform the actual selection,
-\cite{bhadra2017horseshoe+} just focused their analysis on the
-obtained shrinkage and the correct estimation of the sparse signals
-without any actual selection. In our experiments, we include the DL
-prior and the regularised horseshoe (RHS) prior \citep{paper:rhs},
-which we think scales better to higher number of covariates as
-compared to other horseshoe-like priors. For the Bayesian regression
-models with these priors, we compare the posterior shrinkage and the
-correct estimation of the sparse signals with and without using a
-reference model as a noise filter. For this purpose, we consider the
-average SSE (sum of square errors) and the average SESE (sum of
-expected square errors) as quantities measuring estimation
-accuracy. They are defined as \
-\begin{align}
-\text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-\text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
-&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}], \label{eq:SESE}
-\end{align}
-where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
-$\hat{\theta}_{j}$ is the posterior median of each parameter
-$\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
-independent of the number of statistical units.  The SESE takes the
-posterior uncertainty in account and thus also the shrinkage of the
-posterior distributions, whereas the SSE only measures the bias in the
-point estimates.  Any (sensible) point estimate could be used to
-compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
-use the posterior median. The results that we show later on in Section
-\ref{shrinkage-signal} are not sensitive to the choice of this point
-estimate.
-
-For shrinkage priors, one central aspect is the amount of shrinkage
-they actually impose on the relevant and irrelevant features. Ideally,
-the irrelevant features should be completely shrunk to zero while the
-relevant features should not be shrunk at all. The amount of shrinkage
-can be quantified by the shrinkage factor $\kappa_{j}$ for each
-parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
-(complete shrinkage). For model \eqref{eq:normal_means_problem2} with
-a hierarchical shrinkage prior of the type
-\begin{align}
-Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
-&\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
-\end{align}
-the shrinkage factor $\kappa_{j}$ is defined as
-\begin{equation}
-\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
-\end{equation}
-\
-For RHS and DL priors we have
-\begin{equation}
-\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
-\end{equation}
-In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
-the global and local shrinkage parameters of the regularised horseshoe
-prior \cite[for further details see][]{paper:rhs}, whereas on the
-right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
-the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
-notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
-of $\kappa_{j}$ as a point estimate.
+$\sqrt{n-3}\,T_{F}(\rho_{j})$.
+
+We use different levels of correlation $\rho\in\{0.3,0.5\}$ and number
+observation $n\in\{50,70,100\}$. The total number of covariates $p$
+and the number of relevant covariates $k$ are fixed to $p = 1000$ and
+$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
+more challenging the selection.
+
+\subsection{Model selection approach to be compared}
+
+The Bayesian estimation methods we use to solve the normal means
+problem have in common that first a Bayesian regression model is
+fitted using some sparsifying prior on the regression coefficients,
+for example, as discussed in \cite{paper:dirichlet_laplace},
+\cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.  In our
+experiments, we include the Dirichlet-Laplace
+\cite[DL;][]{paper:dirichlet_laplace} prior and the regularised
+horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better
+to higher number of covariates as compared to other horseshoe-like
+priors.
+
+% If these priors have continuous support, as is the case for the DL and
+% horseshoe-like priors \citep{paper:hs,bhadra2017horseshoe+,paper:rhs},
+% there is no canonical way to complete the selection since the
+% posterior probability of an exactly zero signal is always
+% zero. Whereas \cite{paper:dirichlet_laplace} used k-means clustering
+% over the posterior samples to perform the actual selection,
+% \cite{bhadra2017horseshoe+} just focused their analysis on the
+% obtained shrinkage and the correct estimation of the sparse signals
+% without any actual selection.
+
+% For the Bayesian regression
+% models with these priors, we compare the posterior shrinkage and the
+% correct estimation of the sparse signals with and without using a
+% reference model as a noise filter. For this purpose, we consider the
+% average SSE (sum of square errors) and the average SESE (sum of
+% expected square errors) as quantities measuring estimation
+% accuracy. They are defined as \
+% \begin{align}
+% \text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
+% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
+% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}], \label{eq:SESE}
+% \end{align}
+% where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
+% $\hat{\theta}_{j}$ is the posterior median of each parameter
+% $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
+% independent of the number of statistical units.  The SESE takes the
+% posterior uncertainty in account and thus also the shrinkage of the
+% posterior distributions, whereas the SSE only measures the bias in the
+% point estimates.  Any (sensible) point estimate could be used to
+% compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
+% use the posterior median. The results that we show later on in Section
+% \ref{shrinkage-signal} are not sensitive to the choice of this point
+% estimate.
+
+% For shrinkage priors, one central aspect is the amount of shrinkage
+% they actually impose on the relevant and irrelevant features. Ideally,
+% the irrelevant features should be completely shrunk to zero while the
+% relevant features should not be shrunk at all. The amount of shrinkage
+% can be quantified by the shrinkage factor $\kappa_{j}$ for each
+% parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
+% (complete shrinkage). For model \eqref{eq:normal_means_problem2} with
+% a hierarchical shrinkage prior of the type
+% \begin{align}
+% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
+% &\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
+% \end{align}
+% the shrinkage factor $\kappa_{j}$ is defined as
+% \begin{equation}
+% \kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
+% \end{equation}
+% \
+% For RHS and DL priors we have
+% \begin{equation}
+% \kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
+% \end{equation}
+% In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
+% the global and local shrinkage parameters of the regularised horseshoe
+% prior \cite[for further details see][]{paper:rhs}, whereas on the
+% right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
+% the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
+% notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
+% of $\kappa_{j}$ as a point estimate.
 
@@
 
-\hypertarget{shrinkage-signal}{%
-\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
-In the framework of fully Bayesian estimation methods, we analyse the
-effect of the reference model using two continuous hierarchical
-shrinkage priors: the Dirichlet-Laplace
-\citep{paper:dirichlet_laplace} and the regularised horseshoe prior
-\citep{paper:rhs}.
-%
-For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we
-use an uniform prior on the interval $(1/p,1/2)$. For the regularised
-horseshoe prior, we follow the recommendations provided in
-\cite{paper:rhs} by setting the prior guess of the number of relevant
-covariates to one in order to achieve the highest possible
-shrinkage. The results are not sensitive with respect to the specific
-choice.  \ Since, as explained at the start of Section
-\ref{comparison}, continuous priors usually do not provide an
-automatic selection procedure, we study the amount of shrinkage and
-the bias of the posterior medians looking at the SESE and the SSE (see
-definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the
-posterior mean of the shrinkage factors.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
-  \caption{Posterior intervals for the parameters of the normal means
-    problem ($n=50$, $\rho=0.3$) using the regularised horseshoe
-    prior. Posterior means and one standard deviation intervals are
-    depicted. Relevant and non-relevant features are displayed in red
-    and in blue respectively. Horizontal dashed lines corresponds to
-    the true value of the mean for the relevant features.\\}
-  \label{fig:posterior_intervals}
-\end{figure}
-
-Figure \ref{fig:posterior_intervals} shows an example of posterior
-distributions for the model \eqref{eq:normal_means_problem2} using the
-regularised horseshoe prior with the data approach on the left and the
-ref approach on the right-hand side. It is evident how the reference
-model helps in tearing apart the signal from the noise, resulting in
-less biased estimates and clearer separation between relevant and
-irrelevant features. This is quantified in Figure \ref{fig:SESE_SSE}
-where average SESE and SSE are depicted based on 100 simulations. We
-observe that the reference approach (in orange) has a clearly lower
-estimate for both the SESE and the SSE. As $n$ and $\rho$ increase,
-the amount of error diminishes, as expected, due to a larger amount of
-information of the relevance of each variable provided by the
-data. The two priors (RHS and DL) seem to achieve similar results
-under all conditions.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
-  \caption{Average SESE and SSE with one standard deviation intervals based on 100 simulations.\\}
-  \label{fig:SESE_SSE}
-\end{figure}
-
-Figure \ref{fig:k} shows the posterior means for the shrinkage factors
-of each parameter using the regularised horseshoe prior, averaged over
-100 data simulations. Relevant and non-relevant features are
-highlighted in red and blue respectively. The ideal shrinkage would be
-$\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is
-noise. The shrinkage factors using the data and reference approach are
-depicted on the y-axis and on the x-axis respectively. If the
-reference model did not make any difference, we would expect the
-points to lie on the diagonal. For the non-relevant features points
-are on the diagonal on average for all the simulated scenarios, which
-implies that their shrinkage was not improved by the reference
-approach. For the relevant features, the points are always located
-under the diagonal, which means that the reference model helps and
-true signals are shrunk less. This benefit is roughly proportional to
-the difficulty of the problem, that is, the benefit increases with
-lower correlations and a smaller number of observations. The perfect
-distinction of the two clusters of features (relevant and
-non-relevant) observable on both the marginal distributions of the
-shrinkage factors is due to the averaging over the 100 data
-simulations. In a single data realisation, there is more noise and the
-cluster are closer and overlapping. The results for the
-Dirichlet-Laplace prior are very similar.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
-  \caption{Average posterior mean values for the shrinkage factors
-    using the regularised horseshoe prior based on 100
-    simulations. Relevant and non-relevant variables are displayed in
-    red and blue respectively.\\}
-  \label{fig:k}
-\end{figure}
+% \hypertarget{shrinkage-signal}{%
+% \subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
+% In the framework of fully Bayesian estimation methods, we analyse the
+% effect of the reference model using two continuous hierarchical
+% shrinkage priors: the Dirichlet-Laplace
+% \citep{paper:dirichlet_laplace} and the regularised horseshoe prior
+% \citep{paper:rhs}.
+% %
+% For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we
+% use an uniform prior on the interval $(1/p,1/2)$. For the regularised
+% horseshoe prior, we follow the recommendations provided in
+% \cite{paper:rhs} by setting the prior guess of the number of relevant
+% covariates to one in order to achieve the highest possible
+% shrinkage. The results are not sensitive with respect to the specific
+% choice.  \ Since, as explained at the start of Section
+% \ref{comparison}, continuous priors usually do not provide an
+% automatic selection procedure, we study the amount of shrinkage and
+% the bias of the posterior medians looking at the SESE and the SSE (see
+% definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the
+% posterior mean of the shrinkage factors.
+
+% \begin{figure}[tp]
+%   \centering
+%   \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
+%   \caption{Posterior intervals for the parameters of the normal means
+%     problem ($n=50$, $\rho=0.3$) using the regularised horseshoe
+%     prior. Posterior means and one standard deviation intervals are
+%     depicted. Relevant and non-relevant features are displayed in red
+%     and in blue respectively. Horizontal dashed lines corresponds to
+%     the true value of the mean for the relevant features.\\}
+%   \label{fig:posterior_intervals}
+% \end{figure}
+
+% Figure \ref{fig:posterior_intervals} shows an example of posterior
+% distributions for the model \eqref{eq:normal_means_problem2} using the
+% regularised horseshoe prior with the data approach on the left and the
+% ref approach on the right-hand side. It is evident how the reference
+% model helps in tearing apart the signal from the noise, resulting in
+% less biased estimates and clearer separation between relevant and
+% irrelevant features. This is quantified in Figure \ref{fig:SESE_SSE}
+% where average SESE and SSE are depicted based on 100 simulations. We
+% observe that the reference approach (in orange) has a clearly lower
+% estimate for both the SESE and the SSE. As $n$ and $\rho$ increase,
+% the amount of error diminishes, as expected, due to a larger amount of
+% information of the relevance of each variable provided by the
+% data. The two priors (RHS and DL) seem to achieve similar results
+% under all conditions.
+
+% \begin{figure}[tp]
+%   \centering
+%   \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
+%   \caption{Average SESE and SSE with one standard deviation intervals based on 100 simulations.\\}
+%   \label{fig:SESE_SSE}
+% \end{figure}
+
+% Figure \ref{fig:k} shows the posterior means for the shrinkage factors
+% of each parameter using the regularised horseshoe prior, averaged over
+% 100 data simulations. Relevant and non-relevant features are
+% highlighted in red and blue respectively. The ideal shrinkage would be
+% $\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is
+% noise. The shrinkage factors using the data and reference approach are
+% depicted on the y-axis and on the x-axis respectively. If the
+% reference model did not make any difference, we would expect the
+% points to lie on the diagonal. For the non-relevant features points
+% are on the diagonal on average for all the simulated scenarios, which
+% implies that their shrinkage was not improved by the reference
+% approach. For the relevant features, the points are always located
+% under the diagonal, which means that the reference model helps and
+% true signals are shrunk less. This benefit is roughly proportional to
+% the difficulty of the problem, that is, the benefit increases with
+% lower correlations and a smaller number of observations. The perfect
+% distinction of the two clusters of features (relevant and
+% non-relevant) observable on both the marginal distributions of the
+% shrinkage factors is due to the averaging over the 100 data
+% simulations. In a single data realisation, there is more noise and the
+% cluster are closer and overlapping. The results for the
+% Dirichlet-Laplace prior are very similar.
+
+% \begin{figure}[tp]
+%   \centering
+%   \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
+%   \caption{Average posterior mean values for the shrinkage factors
+%     using the regularised horseshoe prior based on 100
+%     simulations. Relevant and non-relevant variables are displayed in
+%     red and blue respectively.\\}
+%   \label{fig:k}
+% \end{figure}
 
@@
 
+As an another example, let us consider a candidate submodel in a
+feature selection process and let us refer to the parameter
+distribution of the submodel by $\pi$ and to the induced predictive
+distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
+that $q_{\pi}(\tilde{y})$ maximises some predictive performance
+utility, for example, the expected log-predictive density (elpd)
+defined as: \
+\begin{equation}\label{eq:elpd}
+\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
+\end{equation}
+where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
+mechanism of future data $\tilde{y}$. If we refer to the posterior
+predictive distribution of a reference model with $p(\tilde{y}|D)$,
+where $D$ stands for the data on which we conditioned on, we can
+approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
+data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
+elpd using the reference model predictive distribution is equivalent
+to the minimisation of the Kullback-Leibler (KL) divergence from the
+reference model's predictive distribution to the submodel's predictive
+distribution: \
+\begin{equation} \label{proj_as_filter}
+\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
+\end{equation}
+The term on the right-hand side of Equation \eqref{proj_as_filter}
+describes what is referred to as the projection of the predictive
+distribution, which is the general idea behind the projection
+predictive approach \cite[see][]{paper:projpred}. Again the reference
+model is acting as a filter, or substitute, on data.
+
+Relying on the idea of the reference model as a noise-filter, a
+generic reference model approach, which can be used on top of any
+feature selection procedure, consists of simply substituting the
+target observations with corresponding point predictions of the
+reference model, for instance, the posterior predictive
+means. Afterwards, any method for feature selection can be used. We do
+not argue that such a reference model approach should necessarily be
+used as is for feature selection in real applications. There are
+several more sophisticated reference model approaches available in the
+literature \cite[see,
+e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
+which are likely to yield even better results. Rather, the reason for
+focusing on this simple version is to enable a fair comparison between
+a reference model and a purely data based approach when otherwise
+using the same selection procedures. Other kinds of comparisons, as
+the one presented in Section \ref{projection}, work well as
+motivational examples but lack in terms of generality since the
+presence or absence of a reference model is not the only aspect
+differentiating the two procedures. We will come back to the more
+general comparison in Section \ref{comparison}.
+
+As a motivational example to the implications of using a reference
+model in feature selection problems, we show its application in the
+form of the projection predictive approach, which uses the reference
+model to project the posterior draws to the submodels
+\citep{paper:original_proj}. The \texttt{R}-package \texttt{projpred}
+(available at \url{https://CRAN.R-project.org/package=projpred})
+implements the projection in case of submodels in the family of the
+generalised linear models and, additionally, it provides a framework
+to choose the optimal submodel size through a predictive utility
+comparison between the submodels and the reference model.
+
+We now summarise the workflow of the projection predictive approach in
+the particular case of the draw-by-draw projection \cite[original
+formulation by][]{paper:original_proj}, following
+\cite{paper:projpred}. Suppose we have observed $n$ statistical units
+with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
+covariates for which we want to obtain a minimally relevant
+subset. Than, the main steps are the following:
+\begin{enumerate}
+\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
+\item Rank the covariates according to their relevance using some
+  heuristics and consider as candidate submodels only those which
+  preserve this order, starting from including only the highest ranked
+  covariate (the submodels are then naturally identified by their
+  model size). This is not strictly necessary but reduces the number
+  of submodels to consider in the following steps.
+\item For each submodel, project the reference model posterior draws as follows:
+\begin{equation}\label{eq:draw_by_draw}
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,..,S \,,
+\end{equation}
+where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
+predictive distribution of the reference model with parameters fixed
+at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
+values related to the statistical unit (identified by the subscript
+$i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
+predictive distribution of the submodel. The projected draws
+$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
+for the submodel.
+\item For each submodel (size), test the predictive performance, for example, via cross-validation.
+\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
+\end{enumerate}
+
+Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
+in general, but in the special case of submodels for the family of
+generalised linear models, \eqref{eq:draw_by_draw} reduces to a
+maximum likelihood estimation problem, which can be easily optimised
+\citep{paper:original_proj}. For further details on the projective
+prediction workflow and implementation see \cite{paper:projpred}.
+
 \end{document}

### 2019-08-15 code/bodyfat_comparison_varying_features.R
deleted old files

@@ -1,173 +1,0 @@
-## BODYFAT COMPARISON ##
-rm(list=ls())
-args = commandArgs(trailingOnly=TRUE) 
-library(rstan)
-library(rstanarm)
-library(locfdr)
-library(dimreduce)
-library(EbayesThresh)
-set.seed(3428954)
-
-df <- read.table("bodyfat.txt", header = T, sep = ";")
-df[,4:19] <- scale(df[,4:19])
-df <- as.data.frame(df)
-n_full <- nrow(df)
-colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
-pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip", 
-          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
-target <- "siri"
-formula <- paste("siri~", paste(pred, collapse = "+"))
-df <- df[,c(target,pred)]
-
-p <- as.numeric(args[1])
-n <- n_full
-times <- 100
-
-## Control of the local false discovery rate
-lfdr_X_ref <- matrix(0,nrow=times,ncol=p)
-lfdr_X_data <- matrix(0,nrow=times,ncol=p)
-
-## Empirical Bayes median thresholding
-ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
-ebmt_X_data <- matrix(0,nrow=times,ncol=p)
-
-## Confidence intervals inclusion probabilities 
-ci80_X_ref <- matrix(0,nrow=times,ncol=p)
-ci90_X_ref <- matrix(0,nrow=times,ncol=p)
-ci95_X_ref <- matrix(0,nrow=times,ncol=p)
-ci80_X_data <- matrix(0,nrow=times,ncol=p)
-ci90_X_data <- matrix(0,nrow=times,ncol=p)
-ci95_X_data <- matrix(0,nrow=times,ncol=p)
-
-## Stan models
-fit_model <- stan_model("model.stan", model_name = "reference_model",
-                        auto_write = rstan_options("auto_write"=TRUE))
-rhs_model <- stan_model("mht_rhs_sigmaprior.stan", model_name = "rhs_model",
-                        auto_write = rstan_options("auto_write"=TRUE))
-
-noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
-dfr<-cbind(df,noise=noise)
[…]

### 2019-08-15 code/prostate_cancer.R

@@ -1,119 +1,0 @@
-library(tidyverse)
-library(corrplot)
-library(bayesplot)
-theme_set(bayesplot::theme_default(base_family = "sans"))
-library(rstanarm)
-options(mc.cores = parallel::detectCores())
-library(loo)
-library(dimreduce)
-library(locfdr)
-SEED=14124869
-
-# file preview shows a header row
-diabetes <- read.csv("prostmat.csv", header = TRUE)
-
-data <- diabetes %>% 
-  rownames_to_column() %>%
-  gather(target,value,-rowname) %>%
-  spread(rowname,value) %>%
-  mutate_at('target',~as.numeric(grepl('cancer',.)))
-
-order <- as.numeric(colnames(data)[-1])
-  
-n <- nrow(data)
-p <- ncol(data)-1
-
-x <- data[,-1]
-y <- data$target
-
-nc <- 10
-
-dr1 <- spca(as.matrix(data[,-1]),data$target, nctot=1, screenthresh = NULL, window = p, sup.only = F, verbose = F)
-aa <- prcomp(as.matrix(data[,-1]))
-ggplot(data.frame(spc1=aa$x[,1],spc2=aa$x[,2],label=as.factor(y)),aes(x=spc1,y=spc2,color=label)) + geom_point()
-
-
-dr <- spca(as.matrix(data[,-1]),data$target, nctot=nc, screenthresh = NULL, window = p, sup.only = T, verbose = F)
-z <- predict(dr, x)
-
-# fit the model
-fit <- stan_glm('y~.', family = binomial(link="logit"), data = data.frame(y=y,X=z),
-                prior = normal(), prior_intercept = normal(), chains=4)
-
-folds <- sample(1:5,n,replace=TRUE)
-acc <- numeric(5)
-for(k in 1:5){
-  sel <- which(folds==k)
-  x_k <- x[sel,]
-  y_k <- y[sel]
-  
-  nc <- 10
-  dr_k <- spca(as.matrix(x_k),y_k, nctot=nc, screenthresh = NULL, window = p, sup.only = T, verbose = F)
-  z_k <- predict(dr_k, x_k)
-  
-  fit_k <- stan_glm('y~.', family = binomial(link="logit"), data = data.frame(y=y_k,X=z_k),
[…]

### 2019-08-16 code/iterated_projection.R
iterated projection analysis scripts

@@ -1,0 +1,205 @@
+library(rstan)
+options(mc.cores = parallel::detectCores())
+library(loo)
+library(projpred)
+library(dimreduce)
+SEED=1513306866
+source("getStability.R")
+args = commandArgs(trailingOnly=TRUE)
+
+n <- as.numeric(args[1])
+p <- 1000
+k <- 100
+rho <- as.numeric(args[2])
+nc <- 5
+
+times <- 100
+
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+X_proj_test_list <- list()
+X_lasso_test_list <- list()
+X_proj_cv_list <- list()
+X_lasso_cv_list <- list()
+
+alpha_vec <- c(0.05,0.16,0.25) ##c(0.05,0.1,0.16,0.2,0.25)
+
+for(aaa in alpha_vec){
+  alpha_lev <- 2*aaa
+  X_proj_test <- matrix(0,nrow=times,ncol=p)
+  X_lasso_test <- matrix(0,nrow=times,ncol=p)
+  X_proj_cv <- matrix(0,nrow=times,ncol=p)
+  X_lasso_cv <- matrix(0,nrow=times,ncol=p)
+  for(j in 1:times){
+    print(j)
+
+    f <- rnorm(n) # the true underlying function
+    x <- sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f # features are noisy observations from f
+    x <- cbind(x,matrix(rnorm(n*(p-k)), ncol=p-k))
+    x <- as.data.frame(x)
+    y <- f + rnorm(n) # target variable
+    names(x) <- c(paste("r",1:k,sep="."),paste("s",(k+1):p,sep="."))
+
+    ntest <- 1000
+    ftest <- rnorm(ntest) # the true underlying function
+    xtest <- sqrt(1-rho)*matrix(rnorm(ntest*k), ncol=k) + sqrt(rho)*ftest # features are noisy observations from f
+    xtest <- cbind(xtest,matrix(rnorm(ntest*(p-k)), ncol=p-k))
+    ytest <- ftest + rnorm(ntest) # target variable
+
+    cvfun <- function(folds) {
+      lapply(1:max(folds), function (k) {
+        w <- which(folds!=k)
+
[…]

### 2019-08-16 code/minimal_subset.R
minimal subset selection scripts

@@ -1,0 +1,216 @@
+library(tidyverse)
+library(projpred)
+library(dimreduce)
+library(rstan)
+library(rstanarm)
+library(loo)
+options(mc.cores = parallel::detectCores())
+set.seed(453876)
+
+args = commandArgs(trailingOnly=TRUE) # n rho nc
+
+## Simulation parameters
+n <- as.numeric(args[1])  # number of observations
+rho <- as.numeric(args[2])  # correlation level
+p <- 100   # total number of features
+k <- 20    # number of relevant features
+
+times <- 100
+
+## Data simulation mechanism
+simulate_data <- function(n){ # n, rho, p and k from global environment
+  f <- rnorm(n) # the true underlying function
+  data <- as_tibble(f + rnorm(n)) %>%   # observed targe variable y
+    bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
+    bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
+    set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
+  return(data)
+}
+## Outputs
+X.step.ref <- matrix(0,nrow=times,ncol=p)
+X.step.data <- matrix(0,nrow=times,ncol=p)
+X.bayes.step.ref <- matrix(0,nrow=times,ncol=p)
+X.bayes.step.data <- matrix(0,nrow=times,ncol=p)
+X.projpred <- matrix(0,nrow=times,ncol=p)
+rmse.projpred <- numeric(times)
+rmse.step.data <- numeric(times)
+rmse.step.ref <- numeric(times)
+rmse.bayes.step.data <- numeric(times)
+rmse.bayes.step.ref <- numeric(times)
+NA_count <- 0
+## Experiment
+
+for(i in 1:times){
+
+    print(paste('iteration:',i))
+    data <- simulate_data(n)
+    test <- simulate_data(1000)
+    y <- dplyr::pull(data, var="y")
+    x <- dplyr::select(data, -contains("y"))
+    y.test <- dplyr::pull(test, var="y")
+    x.test <- dplyr::select(test, -contains("y"))
+    ## Fitting the reference model
+    nc <- 5
+    dr <- spca(x,y, nctot=nc, screenthresh = 0.6,
+               window=p, sup.only = T, verbose = F)
+    z <- predict(dr, x)
[…]

### 2019-08-16 code/minimal_subset_nlessp.R

@@ -1,0 +1,178 @@
+library(tidyverse)
+library(projpred)
+library(dimreduce)
+library(rstan)
+library(rstanarm)
+library(loo)
+options(mc.cores = parallel::detectCores())
+set.seed(453876)
+
+args = commandArgs(trailingOnly=TRUE) # n rho nc
+
+## Simulation parameters
+n <- as.numeric(args[1])  # number of observations
+rho <- as.numeric(args[2])  # correlation level
+p <- 100   # total number of features
+k <- 20    # number of relevant features
+
+times <- 100
+
+## Data simulation mechanism
+simulate_data <- function(n){ # n, rho, p and k from global environment
+  f <- rnorm(n) # the true underlying function
+  data <- as_tibble(f + rnorm(n)) %>%   # observed targe variable y
+    bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
+    bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
+    set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
+
+  return(data)
+}
+## Outputs
+## X.step.ref <- matrix(0,nrow=times,ncol=p)
+## X.step.data <- matrix(0,nrow=times,ncol=p)
+X.bayes.step <- matrix(0,nrow=times,ncol=p)
+X.projpred <- matrix(0,nrow=times,ncol=p)
+rmse.projpred <- numeric(times)
+## rmse.step.data <- numeric(times)
+## rmse.step.ref <- numeric(times)
+rmse.bayes.step <- numeric(times)
+NA_count <- 0
+## Experiment
+for(i in 1:times){
+    print(paste('iteration:',i))
+    data <- simulate_data(n)
+    test <- simulate_data(1000)
+    y <- dplyr::pull(data, var="y")
+    x <- dplyr::select(data, -contains("y"))
+    y.test <- dplyr::pull(test, var="y")
+    x.test <- dplyr::select(test, -contains("y"))
+    ## Fitting the reference model
+    nc <- 5
+    dr <- spca(x,y, nctot=nc, screenthresh = 0.6,
+               window=p, sup.only = T, verbose = F)
+    z <- predict(dr, x)
+    model_data <- list(y = y,
+                       X = z,
+                       p = nc,
+                       n = n,
+                       s_max = dr$sdev[1])
[…]

### 2019-08-16 code/plots.R
updated plots script

@@ -54,37 +54,58 @@ for(nn in c(50,70,100)){
               rho = rep(rho,2),
               method = rep("ci.90",2),
               approach = c("ref","data"),
-              sensitivity = c(avg.sensitivity(ci90_X_ref),avg.sensitivity(ci90_X_data)),
-              sensitivity.sd = c(sd.sensitivity(ci90_X_ref),sd.sensitivity(ci90_X_data)),
-              fdr = c(avg.fdr(ci90_X_ref),avg.fdr(ci90_X_data)),
-              fdr.sd = c(sd.fdr(ci90_X_ref),sd.fdr(ci90_X_data)),
-              stab.low = c(getStability(ci90_X_ref)$lower,getStability(ci90_X_data)$lower),
-              stab.mean = c(getStability(ci90_X_ref)$stability,getStability(ci90_X_data)$stability),
-              stab.up = c(getStability(ci90_X_ref)$upper,getStability(ci90_X_data)$upper))) %>%
+              sensitivity = c(avg.sensitivity(ci90_X_ref),
+                              avg.sensitivity(ci90_X_data)),
+              sensitivity.sd = c(sd.sensitivity(ci90_X_ref),
+                                 sd.sensitivity(ci90_X_data)),
+              fdr = c(avg.fdr(ci90_X_ref),
+                      avg.fdr(ci90_X_data)),
+              fdr.sd = c(sd.fdr(ci90_X_ref),
+                         sd.fdr(ci90_X_data)),
+              stab.low = c(getStability(ci90_X_ref)$lower,
+                           getStability(ci90_X_data)$lower),
+              stab.mean = c(getStability(ci90_X_ref)$stability,
+                            getStability(ci90_X_data)$stability),
+              stab.up = c(getStability(ci90_X_ref)$upper,
+                          getStability(ci90_X_data)$upper))) %>%
       # Control of the local false discovery rate
       bind_rows(tibble(n = rep(n,2),
               rho = rep(rho,2),
               method = rep("loc.fdr",2),
               approach = c("ref","data"),
-              sensitivity = c(avg.sensitivity(lfdr_X_ref),avg.sensitivity(lfdr_X_data)),
-              sensitivity.sd = c(sd.sensitivity(lfdr_X_ref),sd.sensitivity(lfdr_X_data)),
-              fdr = c(avg.fdr(lfdr_X_ref),avg.fdr(lfdr_X_data)),
-              fdr.sd = c(sd.fdr(lfdr_X_ref),sd.fdr(lfdr_X_data)),
[…]

### 2019-08-16 code/ref_approach.R
updated code - minor changes

@@ -22,12 +22,12 @@ times <- 100
 ## Data simulation mechanism
 simulate_data <- function(){ # n, rho, p and k from global environment
   f <- rnorm(n) # the true underlying function
-  
+
   data <- as_tibble(f + rnorm(n)) %>%   # observed targe variable y
     bind_cols(as_tibble(sqrt(1-rho)*matrix(rnorm(n*k), ncol=k) + sqrt(rho)*f)) %>%  # set of relevant covariates
     bind_cols(as_tibble(matrix(rnorm(n*(p-k)), ncol=p-k))) %>%  # set of spurious covariates
     set_names(c("y",paste("r.",1:k,sep=""),paste("s.",(k+1):p,sep="")))
-  
+
   return(data)
 }
 
@@ -43,7 +43,7 @@ lfdr_mean_data <- numeric(p)
 ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
 ebmt_X_data <- matrix(0,nrow=times,ncol=p)
 
-## Confidence intervals inclusion probabilities 
+## Confidence intervals inclusion probabilities
 ci80_X_ref <- matrix(0,nrow=times,ncol=p)
 ci90_X_ref <- matrix(0,nrow=times,ncol=p)
 ci95_X_ref <- matrix(0,nrow=times,ncol=p)
@@ -51,7 +51,7 @@ ci80_X_data <- matrix(0,nrow=times,ncol=p)
 ci90_X_data <- matrix(0,nrow=times,ncol=p)
 ci95_X_data <- matrix(0,nrow=times,ncol=p)
 
-## Control of the Q-value 
+## Control of the Q-value
 rho_hat_seq <- c(0.05,0.1,0.2,0.3)
 q_avg_ref <- matrix(0,nrow=p,ncol=length(rho_hat_seq))
 q_avg_data  <- matrix(0,nrow=p,ncol=length(rho_hat_seq))
@@ -60,8 +60,8 @@ for(i in 1:times){
   data <- simulate_data()
   y <- dplyr::pull(data, var="y")
   x <- dplyr::select(data, -contains("y"))
-  
-  
+
+
   ## Fitting the reference model
   nc <- 5
   dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p, sup.only = T, verbose = F)
@@ -69,61 +69,61 @@ for(i in 1:times){
 
   model_data <- list(y = y,
                      X = z,
-                     p = nc,
+                     p = ncol(z),
[…]

### 2019-08-16 paper/ref_approach.tex
included new experiment minimal subset selection and iterative projection - still to update figures with final version

@@
   \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
-  \caption{Sample correlation plot of each feature (relevant in red, non-relevant in blue) with the target variable $y$ and the latent variable $f$ respectively on the x and y axis.
-Data are generated according to procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$, $k=100$, $p=1000$.\\}
+  \caption{Sample correlation plot of each feature (relevant in red, 
+  non-relevant in blue) with the target variable $y$ and the latent variable 
+  $f$ respectively on the x and y axis. Data are generated according to 
+  procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
+  $k=100$, $p=1000$.\\}
   \label{fig:correlation}
+\end{figure}
+
+\hypertarget{comparison-minimal-subset}{
+\section{A comparison for the minimal subset selection}\label{comparison-minimal-subset}}
+
+Addressing the problem of selecting the minimal subset of relevant/predictive features, 
+we compare with a simulation study the selection via projection predictive approach, 
+via stepwise forward selection with/without a reference model on top and a Bayesian 
+stepwise forward selection.
+\begin{itemize}
+\item projpred (ref model based): reference model is a linear regression over the first 
+five supervised principal components, search heuristics is forward search and the predictive 
+performance is estimated via 10-fold cross-validation.
+\item stepwise selection (data based): it's based on AIC comparison
+\item stepwise selection (ref model based): reference model is a linear regression 
+over the first five SPC. The reference model point predictions (posterior predictive means $\hat{y}$) 
+are used instead of the target variable values $y$. Based on AIC comparison
+\item Bayesian stepwise selection (data based): At each step the model fitted is a 
+linear regression using RHS prior and the feature excluded is the one with higher 
+Bayesian p-value, defined as:
+\begin{equation}
+\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
+\end{equation}
+The selection continues if the reduced model has an elpd score higher than the
+current fitted model.
+\end{itemize}
+
+We simulate data according to \eqref{eq:simulated_data} fixing the overall number of 
+features equal to $p=100$ with $k=20$ of them being predictive. In Figure \ref{fig:rmse_vs_fdr} 
+it is shown, for different values of $n$ and $\rho$, the predictive performance in terms of 
+root mean square error and the false discovery rate of the selected submodel, averaged after 100 data simulations.
+Figure \ref{fig:entropy} reports the entropy scores for the different methods compared. Lower entropy corresponds to
+a more stable selection. Highly correlated predictive features may happen to be alternately selected, making the measure of
+the stability of the selection a non-trivial task. Entropy suffers of such a problem, thus such a measure should be seen
+as one of different possible measurements of the actual stability. We note that the reference model approach slightly improves 
+with respect to the corresponding data based methods, whereas the projection predictive approach results to be far more stable
+than all the other ones.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr.pdf}
+  \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
+  \label{fig:rmse_vs_fdr}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/entropy.pdf}
+  \caption{Entropy score for the minimal subset of feature selection.\\}
+  \label{fig:entropy}
 \end{figure}
@@
 false discovery rate \citep{paper:efron, efron2012large}, the
-empirical Bayes median \citep{johnstone2004needles} and the selection
-by posterior credible intervals.  \
+empirical Bayes median \citep{johnstone2004needles}, the selection
+by posterior credible intervals and an adaptation of the projection 
+predictive approach that we name iterative projection.\
 
@@
 hyperparameter of the Laplace distribution and the mixing weight of
-the prior are estimated by marginal maximum likelihood.  The selection
+the prior are estimated by marginal maximum likelihood.
+
+The selection
 by 90\% posterior credible intervals is done using the regularised
@@
 
-Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on
+The iterative projection is a tentative to adapt the projection predictive 
+approach to select the whole set of relevant features. Applying the straightforward 
+implementation of projpred, we are able to select a minimal subset of features, which
+yield to a model with a predictive performance comparable to the full model one.
+The iterative projection repeats the projpred selection for different iterations, at each time
+excluding from the search path the features selected in the previous steps. At each iteration
+the selected submodel size corresponds to the one having a predictive performance close enough
+to the baseline model, which in this iterative version is the submodel with the highest predictive
+score explored at the current iteration. The stopping rule that we adopted is the following:
+\begin{equation} 
+\label{eq:rule_of_thumb}
+\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
+\end{equation}
+where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
+at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
+the stopping rule.
+The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
+observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
+number of observations or not very predictive features. 
+In our experiments we chose the default value used in the \texttt{projpred} 
+\texttt{R}-package that corresponds to $\alpha=0.16$.
+\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
+I did in the thesis}
+
+Figure \ref{fig:sensitivity_vs_fdr_iterated} reports the average sensitivity on
 the vertical axis versus the average false discovery rate on the
@@
 the reference model are smaller since the raw data already provide
-enough information to identify the relevant covariates.
+enough information to identify the relevant covariates. The iterative
+projection performs fairly well if the number of observations and the correlation level
+are not too small. In those cases it mainly results to be too conservative, resulting in a low
+sensitivity, but good false discovery rate. Tuning $\alpha$ might lead to improved selection, yet
+the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
+utility score for misspecified models with cross-validation \hl{(maybe add some references?)}.
 
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr.pdf}
+  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
   \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
-  \label{fig:sensitivity_vs_fdr}
+  \label{fig:sensitivity_vs_fdr_iterated}
 \end{figure}
 
-Figure \ref{fig:stability} shows the estimates of the stability
+%\begin{figure}[tp]
+%  \centering
+%  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr.pdf}
+%  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
+%  \label{fig:sensitivity_vs_fdr}
+%\end{figure}
+
+Figure \ref{fig:stability_iterated} shows the estimates of the stability
 measure proposed by \cite{paper:stability} with 0.95 confidence
@@
 which can be still connected to the overall stability of the
-procedure.
+procedure. As in Figure \ref{fig:sensitivity_vs_fdr_iterated}, the iterative
+projection does not perform well in the hardest scenarios.
 
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
+  \includegraphics[width=0.98\textwidth]{graphics/stability_iterated.pdf}
   \caption{Stability estimates with 95\% intervals based on 100 data simulations.\\}
-  \label{fig:stability}
+  \label{fig:stability_iterated}
 \end{figure}

### 2019-08-30 paper/ref_approach.tex
less lines in table
modified abstract

@@
 A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism.
-Using the reference model predictions in the model selection reduces tha variability and improves stability leading to improved model selection performance.
-The simplest reference model approach can be used in combination of common feature selection methods .
-In several numerical experiments, we show how this translates into better and more stable feature selection independently of the specific selection procedure.
+Using the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance.
+Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach.
+The reference model can be used also ad-hoc in combination of common feature selection methods.
+In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure.
 % These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
@@
 \begin{tabular}{l|l|l|l}
-  \hline
- Method & Alias & Type & Quantities of interest \\ 
+ Method & Abbreviation & Type & Quantities of interest \\ 
   \hline
@@
  Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
- \hline
 \end{tabular}

### 2019-09-22 code/plots.R
added plots for minimal subset with parallelization data

@@ -686,3 +686,108 @@ plot2 <- ggplot(data.plot, aes(x=entropy,y=method, color=approach)) +
     labs(x='Entropy',y='',color='Approach')
 
 ggsave('../paper/graphics/entropy.pdf',plot2,width=10,height=3)
+
+
+##++++++++++++++++++++++++++++++++++++++++++++++++#
+##++++++++++++++++++++++++++++++++++++++++++++++++#
+####### MINIMAL SUBSET SELECTION PARALLEL #########
+##++++++++++++++++++++++++++++++++++++++++++++++++#
+##++++++++++++++++++++++++++++++++++++++++++++++++#
+
+data.plot <- tibble(n = numeric(),
+                    rho = numeric(),
+                    method = character(),
+                    fdr = numeric(),
+                    rmse = numeric(),
+                    entropy = numeric())
+
+library(entropy)
+
+intervals <- matrix(1:100,nrow=25,ncol=4)
+
+for(nn in c(80,100,150)){
+    for(rr in c(0.3,0.5)){
+        X.projpred.tot <- numeric()
+        X.step.data.tot <- numeric()
+        X.step.ref.tot <- numeric()
+        X.bayes.step.data.tot <- numeric()
+        X.bayes.step.ref.tot <- numeric()
+        rmse.projpred.tot <- numeric()
+        rmse.step.data.tot <- numeric()
+        rmse.step.ref.tot <- numeric()
+        rmse.bayes.step.data.tot <- numeric()
+        rmse.bayes.step.ref.tot <- numeric()
+        for(ii in seq(1,25)){
+            load(paste('minimal_subset_parallel/minimal_subset_final_n',nn,'_rho',rr,'_inter',ii,'.RData',sep=''))
+            which.intervals <- intervals[ii,]
+            X.projpred.tot <- rbind(X.projpred.tot,
+                                    X.projpred[which.intervals,])
+            X.step.data.tot <- rbind(X.step.data.tot,
+                                     X.step.data[which.intervals,])
+            X.step.ref.tot <- rbind(X.step.ref.tot,
+                                    X.step.ref[which.intervals,])
+            X.bayes.step.data.tot <- rbind(X.bayes.step.data.tot,
+                                       X.bayes.step.data[which.intervals,])
+            X.bayes.step.ref.tot <- rbind(X.bayes.step.ref.tot,
+                                      X.bayes.step.ref[which.intervals,])
+            rmse.projpred.tot <- c(rmse.projpred.tot,
[…]

### 2019-09-22 paper/ref_approach.tex
added minimal subset analysis using parallelized data

@@
 current fitted model.
+\item Bayesian stepwise selection (ref model based): same as the data based, but instead of using the observed data values to fit the models at each step, it uses the observed covariate and the target values predicted by a reference model
 \end{itemize}
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr.pdf}
+  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
   \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
@@
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/entropy.pdf}
+  \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
   \caption{Entropy score for the minimal subset of feature selection.\\}

### 2019-10-15 paper/ref_approach.tex
rewriting and reordering

@@
 \newtheorem{example}{Example}
+\newcommand{\note}[1]{\textcolor{red}{#1}}
 
@@
   Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data.
-In this paper we discuss and demonstrate the benefits of using a reference model in model selection in general.
-A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism.
-Using the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance.
+In this paper we discuss and demonstrate the benefits of using a reference model in feature selection.
+A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
+Use of the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance.
 Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach.
-The reference model can be used also ad-hoc in combination of common feature selection methods.
+The reference model can be used also ad-hoc in combination with common feature selection methods.
 In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure.
@@
 $\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is we have
+\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
 constructed a model which reflects in the best way our beliefs about
@@
 To motivate the further discussion and experiments, we start by simple
-example comparing projection predictive approach (projpred,
+example comparing projection predictive approach (\emph{projpred},
 \citet{paper:projpred}) which uses a reference model and classic
@@
 and thicknes of skin and fat in different body locations). The
-covariates are are highly correlated whichs causes additional
-challenge in the model selection. In total, we have 251
+covariates are are highly correlated which causes additional
+challenge in the feature selection. In total, we have 251
 observations. The goal is to find the model which is able to predict
@@
 
-\cite{paper:bodyfat} report results using steplm with a significance
+\cite{paper:bodyfat} report results using \emph{steplm} with a significance
 level of 0.157 with AIC selection \citep{akaike1974new}, fixing
@@
 \citep{paper:psis_loo}.  We select the submodel as the one with the
-smallest size which has an elpd score higher (i.e., better) than the
-reference model score with probability of at least 5\%. See Appendix A
-for brief review of projection predictive approach and papers by
-\citet{paper:model_selection} and \citet{paper:projpred} for more
-details. projpred selection is made using the \texttt{projpred} package.
+smallest size which has an elpd score similar to the reference model
+when taking into account the uncertainty in estimating the predictive
+model performance. See Appendix A for brief review of projection
+predictive approach and papers by \citet{paper:model_selection} and
+\citet{paper:projpred} for more details. projpred selection is made
+using the \texttt{projpred} package.
 
@@
 \centering
-\begin{tabular}{l||l|r||l|r}
+\begin{tabular}{l|lr|lr}
+%  \hline
+M & projpred & Freq \% & steplm & Freq \%  \\ 
   \hline
-M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
-  \hline
-1 & abdomen, weight & 39 & abdomen, age, forearm, height, hip, neck, thigh, wrist & 4 \\
-2 & abdomen, wrist & 10 & abdomen, age, chest, forearm, height, neck, thigh, wrist & 4 \\
-3 & abdomen, height & 10 & abdomen, forearm, height, neck, wrist & 2 \\
-4 & abdomen, height, wrist & 9 & abdomen, forearm, neck, weight, wrist & 2 \\
-5 & abdomen, weight, wrist & 8 & abdomen, age, height, hip, thigh, wrist & 2 \\
-6 & abdomen, chest, height, wrist & 2 & abdomen, age, height, hip, neck, thigh, wrist & 2 \\
-7 & abdomen, biceps, weight, wrist & 2 & abdomen, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
-8 & abdomen, height, weight, wrist & 2 & abdomen, age, biceps, chest, height, neck, wrist & 2 \\
-9 & abdomen, age, wrist & 2 & abdomen, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
-10 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, age, ankle, biceps, weight, wrist & 2 \\
-   \hline
+1 & abdom, weight & 39 & abdom, age, forearm, height, hip, neck, thigh, wrist & 4 \\
+2 & abdom, wrist & 10 & abdom, age, chest, forearm, height, neck, thigh, wrist & 4 \\
+3 & abdom, height & 10 & abdom, forearm, height, neck, wrist & 2 \\
+4 & abdom, height, wrist & 9 & abdom, forearm, neck, weight, wrist & 2 \\
+5 & abdom, weight, wrist & 8 & abdom, age, height, hip, thigh, wrist & 2 \\
+6 & abdom, chest, height, wrist & 2 & abdom, age, height, hip, neck, thigh, wrist & 2 \\
+7 & abdom, biceps, weight, wrist & 2 & abdom, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
+8 & abdom, height, weight, wrist & 2 & abdom, age, biceps, chest, height, neck, wrist & 2 \\
+9 & abdom, age, wrist & 2 & abdom, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
+10 & abdom, age, height, neck, thigh, wrist & 2 & abdom, age, ankle, biceps, weight, wrist & 2 \\
+%   \hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{l|r|r|r|r}
+\begin{tabular}{ll|rrrr}
+%  \hline
+Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
   \hline
- & RMSE(Full) & RMSE(Sel) & Size(Sel) & SizeIr(Sel) \\ 
+original & projpred & 4.35 & 4.47 & 2 &   \\
+& steplm & 4.38 & 4.47 & 7 &  \\
 \hline
-projpred & 4.35 & 4.47 & 2 & -  \\
-steplm & 4.38 & 4.47 & 7 & - \\
-\hline
-\hline
-projpred & 4.58 & 4.54 & 2 & 0  \\
-steplm & 5.89 & 5.43 & 19 & 13 \\
-   \hline
++ noisy features & projpred & 4.58 & 4.54 & 2 & 0  \\
+& steplm & 5.89 & 5.43 & 19 & 13 \\
+%   \hline
 \end{tabular}
 \caption{Model predictive performances with original data (first two
-  rows) and adding noisy features (last two rows) estimated with
-  10-fold cross-validation. Abbreviations: Full = full model; Sel =
-  selected submodel; Size = total number of included covariates;
-  SizeIr = number of included irrelevant covariates.}
+  rows) and with extra noisy features (last two rows) estimated with
+  10-fold cross-validation. Abbreviations: Full = full model; Selected =
+  selected submodel; \# Selected = total number of features selected;
+  \# Selected noisy = number of extra noisy features selected.}
 \label{tab:model_performances}
@@
 uses Bayesian inference and steplm maximum likelihood, it is not
-decisive feature explaining the difference in the performance.  The
+here the decisive feature explaining the difference in the performance.  The
 main difference between the approaches is whether a reference model is
 used or not, and in the rest of the paper we look into more detail how
-the use of reference model helps and limitations of the approach.
+the benefits and limitations of the reference model approach.
 
@@
 higher the benefit of using a reference models as the basis for
-variable selection.
+feature selection.
 
@@
 \hypertarget{comparison-minimal-subset}{
-\section{A comparison for the minimal subset selection}\label{comparison-minimal-subset}}
-
-Addressing the problem of selecting the minimal subset of relevant/predictive features, 
-we compare with a simulation study the selection via projection predictive approach, 
-via stepwise forward selection with/without a reference model on top and a Bayesian 
-stepwise forward selection.
+\section{Minimal subset feature selection}\label{comparison-minimal-subset}}
+
+In the bodyfat example above we desired at the same time good
+predictive performance and selection of a smaller number of
+features. When the goal is to select a minimal subset of features
+which have similar predictive performance as the full model we call it
+\emph{minimal subset feature selection}. This minimal subset might
+exclude features which have some predictive information about the
+target, but given the minimal subset these features are nit able to
+provide such additional information which would improve predictive
+performance. The usual reason for this is that the relevant features
+not in the minimal subset highly correlate with features already in
+the minimal subset. We will later return to a problem of finding all
+the features with some predictive power.
+
+Using the data generating mechanism \eqref{eq:simulated_data}, we
+simulate data sets of different size with a relatively large number of
+features $p=100$ with with $k=20$ of them being predictive.
+We compare the minimal subset feature selection perfomance of
+projection predictive approach (with a reference model), a Bayesian
+stepwise forward selection (without a reference model), and stepwise
+forward selection with and without a reference model.
 \begin{itemize}
-\item projpred (ref model based): reference model is a linear regression over the first 
-five supervised principal components, search heuristics is forward search and the predictive 
-performance is estimated via 10-fold cross-validation.
-\item stepwise selection (data based): it's based on AIC comparison
-\item stepwise selection (ref model based): reference model is a linear regression 
-over the first five SPC. The reference model point predictions (posterior predictive means $\hat{y}$) 
-are used instead of the target variable values $y$. Based on AIC comparison
-\item Bayesian stepwise selection (data based): At each step the model fitted is a 
-linear regression using RHS prior and the feature excluded is the one with higher 
-Bayesian p-value, defined as:
+\item projpred: The reference model is a Bayesian linear regression
+  model (ie, the posterior predictive distributions are used) using
+  the first five supervised principal components. The search heuristic
+  is forward search, and the predictive performance is estimated via
+  10-fold cross-validation.
+\item steplm (data based): Stepwise selection using AIC as in the bodyfat example.
+\item steplm using a reference model: The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
+Same AIC selection is used in data based steplm.
+\item Bayesian stepwise selection (data based): At each step the model
+  fitted is a Bayesian linear regression using regularised horseshoe
+  prior and the feature excluded is the one with higher Bayesian
+  $p$-value, defined as:
 \begin{equation}
@@
 
-We simulate data according to \eqref{eq:simulated_data} fixing the overall number of 
-features equal to $p=100$ with $k=20$ of them being predictive. In Figure \ref{fig:rmse_vs_fdr} 
-it is shown, for different values of $n$ and $\rho$, the predictive performance in terms of 
-root mean square error and the false discovery rate of the selected submodel, averaged after 100 data simulations.
-Figure \ref{fig:entropy} reports the entropy scores for the different methods compared. Lower entropy corresponds to
-a more stable selection. Highly correlated predictive features may happen to be alternately selected, making the measure of
-the stability of the selection a non-trivial task. Entropy suffers of such a problem, thus such a measure should be seen
-as one of different possible measurements of the actual stability. We note that the reference model approach slightly improves 
-with respect to the corresponding data based methods, whereas the projection predictive approach results to be far more stable
-than all the other ones.
-
+In Figure \ref{fig:rmse_vs_fdr} it is shown, for different values of
+$n$ and $\rho$, the predictive performance in terms of root mean
+square error and the false discovery rate of the selected submodel,
+averaged after 100 data simulations. projpred has superior FDR and the
+smallest RMSE. Using a reference model improves steplm significantly,
+but the minimal subset feature selection stays unreliable. Stepwise
+Bayesian linear regression model without a reference model is better
+than steplm without a reference model, but the minimal subset feature
+selection is unreliable.
+
+Figure \ref{fig:entropy} reports the entropy scores for the different
+methods compared. Lower entropy corresponds to a more stable
+selection. Highly correlated predictive features may happen to be
+alternately selected, making the measure of the stability of the
+selection a non-trivial task. Entropy suffers of such a problem, thus
+such a measure should be seen as one of different possible
+measurements of the actual stability. The use of a reference model
+improves slightly stability of steplm in feature selection. The
+projection predictive approach results to be far more stable than all
+the other ones. This is likely due to as projpred is based on better
+decision theoretical formulation which 1) takes into account the full
+predictive distribution and not just point estimate and 2) projects
+the reference model posterior to the submodel instead of using a
+simple refit of submodels.
+
+% TODO: Bigger and more distinctive symbols in figures
+% label order: steplm, bayes.step, projpred
 \begin{figure}[tp]
@@
   \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
-  \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
+  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset feature selection.}
   \label{fig:rmse_vs_fdr}
@@
 
+% TODO: Bigger and more distinctive symbols in figures
+% TODO: order steplm, bayes.step, projpred
 \begin{figure}[tp]
@@
   \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
-  \caption{Entropy score for the minimal subset of feature selection.\\}
+  \caption{Entropy score in the minimal subset feature selection.}
   \label{fig:entropy}
@@
 
-\hypertarget{comparison}{%
-\section{A comparison in the normal means problem framework}\label{comparison}}
-
-In this section, we analyse in more detail the benefits of reference
-model approaches in combination of a few common variable selection
-approach.
-
-\subsection{Simulated data}
-
-The normal means problem consists of estimating the (usually
-sparse) vector of means of a vector of normally distributed
-observations. The dimensionality of the vector of means is denoted by
-$p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the
-random variables $\{Z_{j}\}_{j=1}^{p}$. The task is to estimate the
-latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model: \
-\begin{equation}\label{eq:normal_means_problem}
-Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}), \quad j=1,..,p.
-\end{equation}
-This is equivalent to a linear regression where the design matrix is
-the identity matrix with the number of features being equal to the
-number of observations. This formulation can be found in practice, for
-example, in the analysis of microarray data, where a large set of
-genes are tested in two groups of patients labeled as positive or
-negative to some disease \citep{paper:efron,efron2012large}. The
-objective of the analysis is to select the subset of genes
-statistically relevant to the disease. One common way to proceed is to
-compute the two-sample $t$-statistic for every gene separately.  After
-normalising these statistics, they then become the data, $Z$, in the
-normal means problem \eqref{eq:normal_means_problem}. For further
-details see the examples in \cite{paper:efron, efron2012large}.
-
-In our experiments, we retrieve the normal means problem from the
-sample correlations between the target and the covariates using the
-Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
-continuous target random variable $Y$, a set of $p$ continuous
-covariates $\{X_{j}\}_{j=1}^{p}$, and denote
-$\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$
-statistical units and define $r_{j}$ the sample correlation between
-the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
-$j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
-Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
-$T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate
-normally distributed, the corresponding transformed correlations are
-approximately normally distributed with known variance: \
-\begin{equation} \label{eq:fisher_transformation}
-T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p.
-\end{equation}
-Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and
-denoting the results as $z_{j}$, we have the formulation
-\eqref{eq:normal_means_problem} of the normal means problem, this time
-with unit variance: \
-\begin{equation} \label{eq:normal_means_problem2}
-Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p.
-\end{equation}
-Now the quantities of interest $\theta_{j}$ are equal to
-$\sqrt{n-3}\,T_{F}(\rho_{j})$.
-
-We use different levels of correlation $\rho\in\{0.3,0.5\}$ and number
-observation $n\in\{50,70,100\}$. The total number of covariates $p$
-and the number of relevant covariates $k$ are fixed to $p = 1000$ and
-$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the selection.
-
-\subsection{Model selection approach to be compared}
-
-The Bayesian estimation methods we use to solve the normal means
-problem have in common that first a Bayesian regression model is
-fitted using some sparsifying prior on the regression coefficients,
-for example, as discussed in \cite{paper:dirichlet_laplace},
-\cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.  In our
-experiments, we include the Dirichlet-Laplace
-\cite[DL;][]{paper:dirichlet_laplace} prior and the regularised
-horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better
-to higher number of covariates as compared to other horseshoe-like
-priors.
+% \hypertarget{comparison}{%
+%   \section{A comparison in the normal means problem framework}\label{comparison}}
+\section{Complete feature selection}
+
+Alternative to minimal subset feature selection is \emph{complete
+  feature selection}, in which the goal is to find all relevant
+features which have some predictive information about the target. In
+complete feature selection it is possible that there are theoretically
+relevant features, but given finite noisy data we are not able infer
+these effects.
+
+The projection predictive approach was designed for the minimal subset
+feature selection, but here examine its performance also in complete
+feature selection. In addition, we analyse the benefits of reference
+model approach in combination of a few common complete feature
+selection approaches.
+
+\subsection{Complete feature selection approaches to be compared}
+
+Many Bayesian approaches for complete feature selection first fit a
+Bayesian regression model using some sparsifying prior on the
+regression coefficients, for example, as discussed in
+\cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
+\cite{johnstone2004needles}.  In our experiments, we include the
+Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} prior and the
+regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think
+scales better to higher number of covariates as compared to other
+horseshoe-like priors.
+\note{Aki: How this paragraph connects to the next paragraph?}
 
@@
 selection procedure using their prior. We refer to this method as
-EB.med. Further, we use a method to control for the local false
-discovery rate (loc.fdr) as described in \cite{paper:efron,
+\emph{EB.med}. Further, we use a method to control for the local false
+discovery rate (\emph{loc.fdr}) as described in \cite{paper:efron,
   efron2012large}. Finally, we device a simple selection procedure
@@
 prior in which we select covariates whose 90\% credible intervals
-excludes zero (ci.90). All of these methods provide a complete
-selection procedure and we compare their performance with and without
-using a reference model on top of them. As criteria of selection
-performance, we evaluate the average false discovery rate (i.e., the
-ratio of the number of non-relevant selected features over the number
-of selected features) and the average sensitivity (i.e., the ratio of
-the number of relevant selected features over the total number of
-relevant features). We also provide a comparison of the stability of
-the selection by means of a stability measure proposed by
-\cite{paper:stability}. Table \ref{tab:comparison} summarises the
-methods used in the numerical experiments.
+excludes zero (\emph{ci.90}) \note{Reference for this?}.
+
+All of these methods provide a complete selection procedure and we
+compare their performance with and without using a reference model.
+\note{Aki: Explain here how the reference mdoels are used for these. Point
+  estimates replace data?}
+
+As criteria of selection performance, we evaluate the average false
+discovery rate (i.e., the ratio of the number of non-relevant selected
+features over the number of selected features) and the average
+sensitivity (i.e., the ratio of the number of relevant selected
+features over the total number of relevant features). We also provide
+a comparison of the stability of the selection by means of a stability
+measure proposed by \cite{paper:stability}. Table \ref{tab:comparison}
+summarises the methods used in the numerical experiments.
+
+\note{Aki: ``Type: Complete selection'' doesn't make sense in the table. Maybe we need to discuss when to use the term complete selection and what is the alternative title for this section.}
 
@@
 \end{table}
+
+\hypertarget{complete-selection}{%
+\subsection{Details of methods?}\label{complete-selection}}
+
+\note{Should this be combined with previous subsection?}
+
+As complete selection procedures we consider the control of the local
+false discovery rate \citep{paper:efron, efron2012large}, the
+empirical Bayes median \citep{johnstone2004needles}, the selection
+by posterior credible intervals and an adaptation of the projection 
+predictive approach that we name iterative projection.\
+
+The control of the local false discovery rate is applied through the
+\texttt{R}-package \texttt{locfdr}. It consists of testing the
+z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the
+theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
+meaning no relevance) against the alternative hypothesis distribution
+$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
+distribution (see expression \eqref{eq:normal_means_problem2}). The
+quantity of interest is the local false discovery rate (loc.fdr)
+defined as: \
+\begin{equation}
+\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
+\end{equation}
+where $\pi_{0}$ is the prior probability of $H_0$ and
+$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
+distribution of the z-values. The latter is estimated using splines
+with 7 degrees of freedom. We select features with local false
+discovery rate below $0.2$, which is suggested by
+\citet{efron2012large} as it corresponds to a Bayes factor larger than
+36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
+sensitive to the specific value. We use the default setting to
+estimate $\pi_{0}$ from the data provided by the package.
+
+The empirical Bayes median procedure is given by the
+\texttt{R}-package \texttt{EbayesThresh} and consists of fitting a
+Bayesian model with a prior composed by a mixture of a delta in zero
+and a heavy-tailed distribution. As suggested by
+\cite{johnstone2004needles}, we use a Laplace distribution resulting
+in a thresholding property, that is, there exists a threshold value
+such that all the data under that threshold have posterior median
+equal to zero. Therefore the selection is done by selecting only those
+parameters whose posterior median is different from zero. The
+hyperparameter of the Laplace distribution and the mixing weight of
+the prior are estimated by marginal maximum likelihood.
+
+The selection
+by 90\% posterior credible intervals is done using the regularised
+horseshoe prior and selecting those features whose posterior
+distribution does not include zero in the interval between the 5\% and
+the 95\% quantiles. \note{Reference?}
+
+We can use the projection predictive approach for complete feature
+selection by using it iteratively.  Applying the straightforward
+implementation of projpred, we are able to select a minimal subset of
+features, which yield to a model with a predictive performance
+comparable to the full model one.  The iterative projection repeats
+the projpred selection for different iterations, at each time
+excluding from the search the features selected in the previous
+iterations. At each iteration the selected submodel size corresponds to the
+one having a predictive performance close enough to the baseline
+model, which in this iterative version is the submodel with the
+highest predictive score explored at the current iteration. The
+stopping rule that we adopted is the following:
+\begin{equation} 
+\label{eq:rule_of_thumb}
+\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
+\end{equation}
+where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
+at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
+the stopping rule.
+The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
+observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
+number of observations or not very predictive features. 
+In our experiments we chose the default value used in the \texttt{projpred} 
+\texttt{R}-package that corresponds to $\alpha=0.16$.
+\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
+I did in the thesis}
+
+\subsection{Simulated data}
+
+\note{Aki: Why two subsections on simulated data? Combine this with next one, or did I understand their contents wrong?}
+
+The normal means problem consists of estimating the (usually
+sparse) vector of means of a vector of normally distributed
+observations. The dimensionality of the vector of means is denoted by
+$p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the
+random variables $\{Z_{j}\}_{j=1}^{p}$. The task is to estimate the
+latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model: \
+\begin{equation}\label{eq:normal_means_problem}
+Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}), \quad j=1,..,p.
+\end{equation}
+This is equivalent to a linear regression where the design matrix is
+the identity matrix with the number of features being equal to the
+number of observations. This formulation can be found in practice, for
+example, in the analysis of microarray data, where a large set of
+genes are tested in two groups of patients labeled as positive or
+negative to some disease \citep{paper:efron,efron2012large}. The
+objective of the analysis is to select the subset of genes
+statistically relevant to the disease. One common way to proceed is to
+compute the two-sample $t$-statistic for every gene separately.  After
+normalising these statistics, they then become the data, $Z$, in the
+normal means problem \eqref{eq:normal_means_problem}. For further
+details see the examples in \cite{paper:efron, efron2012large}.
+
+In our experiments, we retrieve the normal means problem from the
+sample correlations between the target and the covariates using the
+Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
+continuous target random variable $Y$, a set of $p$ continuous
+covariates $\{X_{j}\}_{j=1}^{p}$, and denote
+$\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$
+statistical units and define $r_{j}$ the sample correlation between
+the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
+$j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
+Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
+$T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate
+normally distributed, the corresponding transformed correlations are
+approximately normally distributed with known variance: \
+\begin{equation} \label{eq:fisher_transformation}
+T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p.
+\end{equation}
+Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and
+denoting the results as $z_{j}$, we have the formulation
+\eqref{eq:normal_means_problem} of the normal means problem, this time
+with unit variance: \
+\begin{equation} \label{eq:normal_means_problem2}
+Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p.
+\end{equation}
+Now the quantities of interest $\theta_{j}$ are equal to
+$\sqrt{n-3}\,T_{F}(\rho_{j})$.
+
+We use different levels of correlation $\rho\in\{0.3,0.5\}$ and number
+observation $n\in\{50,70,100\}$. The total number of covariates $p$
+and the number of relevant covariates $k$ are fixed to $p = 1000$ and
+$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
+more challenging the selection.
 
@@
 
-\hypertarget{complete-selection}{%
-\subsubsection{Complete selection analysis}\label{complete-selection}}
-As complete selection procedures we consider the control of the local
-false discovery rate \citep{paper:efron, efron2012large}, the
-empirical Bayes median \citep{johnstone2004needles}, the selection
-by posterior credible intervals and an adaptation of the projection 
-predictive approach that we name iterative projection.\
-
-The control of the local false discovery rate is applied through the
-\texttt{R}-package \texttt{locfdr}. It consists of testing the
-z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the
-theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
-meaning no relevance) against the alternative hypothesis distribution
-$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
-distribution (see expression \eqref{eq:normal_means_problem2}). The
-quantity of interest is the local false discovery rate (loc.fdr)
-defined as: \
-\begin{equation}
-\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
-\end{equation}
-where $\pi_{0}$ is the prior probability of $H_0$ and
-$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
-distribution of the z-values. The latter is estimated using splines
-with 7 degrees of freedom. We select features with local false
-discovery rate below $0.2$, which is suggested by
-\citet{efron2012large} as it corresponds to a Bayes factor larger than
-36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
-sensitive to the specific value. We use the default setting to
-estimate $\pi_{0}$ from the data provided by the package.
-
-The empirical Bayes median procedure is given by the
-\texttt{R}-package \texttt{EbayesThresh} and consists of fitting a
-Bayesian model with a prior composed by a mixture of a delta in zero
-and a heavy-tailed distribution. As suggested by
-\cite{johnstone2004needles}, we use a Laplace distribution resulting
-in a thresholding property, that is, there exists a threshold value
-such that all the data under that threshold have posterior median
-equal to zero. Therefore the selection is done by selecting only those
-parameters whose posterior median is different from zero. The
-hyperparameter of the Laplace distribution and the mixing weight of
-the prior are estimated by marginal maximum likelihood.
-
-The selection
-by 90\% posterior credible intervals is done using the regularised
-horseshoe prior and selecting those features whose posterior
-distribution does not include zero in the interval between the 5\% and
-the 95\% quantiles.
-
-The iterative projection is a tentative to adapt the projection predictive 
-approach to select the whole set of relevant features. Applying the straightforward 
-implementation of projpred, we are able to select a minimal subset of features, which
-yield to a model with a predictive performance comparable to the full model one.
-The iterative projection repeats the projpred selection for different iterations, at each time
-excluding from the search path the features selected in the previous steps. At each iteration
-the selected submodel size corresponds to the one having a predictive performance close enough
-to the baseline model, which in this iterative version is the submodel with the highest predictive
-score explored at the current iteration. The stopping rule that we adopted is the following:
-\begin{equation} 
-\label{eq:rule_of_thumb}
-\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
-\end{equation}
-where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
-at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
-the stopping rule.
-The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
-observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
-number of observations or not very predictive features. 
-In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package that corresponds to $\alpha=0.16$.
-\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
-I did in the thesis}
+\subsection{Simulation results of complete feature selection}
 
@@
 \subsection{The body fat data: A real world example}\label{real-world-data}}
+
+\note{Aki: Is this only complete feature selection or also more results for the minimal subset feature selection?}
 

### 2019-10-17 paper/ref_approach.tex
clean up sections 1 to 3

@@
 \begin{abstract}
-  Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data.
+  Feature selection, or more generally, model reduction is an important aspect of the statistical workflow aiming to provide insights from data.
 In this paper we discuss and demonstrate the benefits of using a reference model in feature selection.
 A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
-Use of the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance.
-Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach.
-The reference model can be used also ad-hoc in combination with common feature selection methods.
+As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability leading to improved model selection performance.
+Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive variable selection approach.
+Alternatively, reference models may also be used in an ad-hoc manner in combination with common feature selection methods.
 In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure.
@@
 \citep{book:bernardo_smith,vehtari2012survey}, that is, we have
-constructed a model which reflects in the best way our beliefs about
-the future data and which has passed model checking and criticism
+constructed a model which reflects our beliefs about
+the future data in the best possible way and which has passed model checking and criticism
 \citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
-has been used for long time in Bayesian statistics since the seminal
+has been used for a long time in Bayesian statistics since the seminal
 work of \citet{paper:reference_lindley}. For more historical
-references, see papers by \citet{vehtari2012survey} and
+references, see the papers by \citet{vehtari2012survey} and
 \citet{paper:model_selection}, and for most recent methodological
@@
 backward search is used), and the predictive utility is the expected
-log-predictive density (elpd) estimated using PSIS-LOO
-\citep{paper:psis_loo}.  We select the submodel as the one with the
-smallest size which has an elpd score similar to the reference model
+log-predictive density (elpd) estimated using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
+\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.  We select the smallest  submodel with an elpd score similar to the reference model
 when taking into account the uncertainty in estimating the predictive
 model performance. See Appendix A for brief review of projection
-predictive approach and papers by \citet{paper:model_selection} and
-\citet{paper:projpred} for more details. projpred selection is made
-using the \texttt{projpred} package.
+predictive approach and \citet{paper:model_selection} and
+\citet{paper:projpred} for more details. The complete projpred procedure is implemented in the \texttt{projpred} R package.
 
@@
 
-First two rows of Table \ref{tab:model_performances} report the
+In the first two rows of Table \ref{tab:model_performances}, we report the
 predictive performances, in terms of cross-validated root mean square
@@
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy features. Last two rows of Table
-\ref{tab:model_performances} report cross-validated RMSE, the size of
+unrelated noisy features. In the last two rows of Table
+\ref{tab:model_performances}, we report the cross-validated RMSE, the size of
 the selected model and the number of selected noisy features using
@@
 forward or backward search, which can lead to selection induced
-overfitting, but even with 100 covariates projpred is able to select a
-submodel with similar performance as the full model. Although projpred
-uses Bayesian inference and steplm maximum likelihood, it is not
-here the decisive feature explaining the difference in the performance.  The
-main difference between the approaches is whether a reference model is
-used or not, and in the rest of the paper we look into more detail how
-the benefits and limitations of the reference model approach.
-
-\subsection{Benefits and cost of using a reference model}
+overfitting, but even with 100 covariates, projpred is able to select a
+submodel with similar performance as the full model. In this example, the two
+ compared methods also differ in other aspects than the usage of a reference 
+ model, such as that projpred
+uses Bayesian inference and steplm uses maximum likelihood estimation. 
+However, as we show in the present paper, one of the primary difference 
+with respect to quality of the variable selection is indeed whether or 
+not a reference model approach is applied.
+
+\subsection{Benefits and costs of using a reference model}
 
@@
 exclude features which have some predictive information about the
-target, but given the minimal subset these features are nit able to
+target but given the minimal subset, these features are not able to
 provide such additional information which would improve predictive
@@
 \begin{itemize}
-\item projpred: The reference model is a Bayesian linear regression
-  model (ie, the posterior predictive distributions are used) using
-  the first five supervised principal components. The search heuristic
-  is forward search, and the predictive performance is estimated via
-  10-fold cross-validation.
+\item projpred: The Projective prediction approach is used. 
+  The reference model is a Bayesian linear regression
+  model using the first five supervised principal components as predictors
+  and the full posterior predictive distribution as the basis of the projection.   
+  The search heuristic  is forward search and the predictive performance 
+  is estimated via 10-fold cross-validation.
+
 \item steplm (data based): Stepwise selection using AIC as in the bodyfat example.
-\item steplm using a reference model: The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
-Same AIC selection is used in data based steplm.
-\item Bayesian stepwise selection (data based): At each step the model
-  fitted is a Bayesian linear regression using regularised horseshoe
-  prior and the feature excluded is the one with higher Bayesian
-  $p$-value, defined as:
+
+\item steplm (reference model based): The reference model is the same as for
+ projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
+ are used to replace the target variable $y$. The same AIC selection strategy 
+ as in the data based steplm is used.
+
+\item Bayesian stepwise selection (data based): At each step, the fitted model
+ is a Bayesian linear regression using the regularised horseshoe
+  prior and the feature excluded is the one with the highest Bayesian
+  $p$-value defined as:
 \begin{equation}
-\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
+\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}
 \end{equation}
-The selection continues if the reduced model has an elpd score higher than the
-current fitted model.
-\item Bayesian stepwise selection (ref model based): same as the data based, but instead of using the observed data values to fit the models at each step, it uses the observed covariate and the target values predicted by a reference model
+The selection continues if the reduced model has an elpd score higher 
+(i.e., better) than the current model.
+
+\item Bayesian stepwise selection (reference model based): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
+The same Bayesian
+  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.
+
+%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
 \end{itemize}
 
-In Figure \ref{fig:rmse_vs_fdr} it is shown, for different values of
-$n$ and $\rho$, the predictive performance in terms of root mean
-square error and the false discovery rate of the selected submodel,
-averaged after 100 data simulations. projpred has superior FDR and the
+In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
+for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR) of the selected submodel,
+averaged after 100 data simulations. We see that projpred has superior FDR and the
 smallest RMSE. Using a reference model improves steplm significantly,
@@
 such a measure should be seen as one of different possible
-measurements of the actual stability. The use of a reference model
+measurements of the actual stability. 
+[TODO: please clarify the above sentences about entropy.] 
+The use of a reference model
 improves slightly stability of steplm in feature selection. The
 projection predictive approach results to be far more stable than all
-the other ones. This is likely due to as projpred is based on better
+other approaches. This is likely due to projpred being based on better
 decision theoretical formulation which 1) takes into account the full
@@
 %   \section{A comparison in the normal means problem framework}\label{comparison}}
-\section{Complete feature selection}
+\section{Complete feature selection}\label{comparison}
 

### 2019-10-19 paper/ref_approach.tex
rewrite Section 4 and 5

@@
 \subsection{Example of model selection with or without reference model}
+\label{intro-example}
 
@@
 model, its benefits with examples and how it can be used as a filter
-on data in a simple way. In Section \ref{comparison}, we show the
-benefits of a reference model approach, regardless of what specific
-procedure is applied, using the normal means estimation problem as a
-benchmark. Finally, we end with a conclusion in Section
-\ref{conclusion}.
+on data in a simple way. In Section \ref{comparison-minimal-subset} and 
+Section \ref{comparison-complete-subset}, we show the
+benefits of a reference model approaches for minimal and complete 
+feature selection, respectively, before we illustrate the use 
+of a reference model in a detailed case study of the 'body fat' data.
+Finally, we end with a conclusion in Section \ref{conclusion}.
 
@@
 predictive means of model \eqref{eq:ref_mod}; see Section
-\ref{simulated-data}). Looking at the marginal distributions, we see
+\ref{simulations}). Looking at the marginal distributions, we see
 that using a reference model to filter out noise in the data, the two
@@
 %   \section{A comparison in the normal means problem framework}\label{comparison}}
-\section{Complete feature selection}\label{comparison}
-
-Alternative to minimal subset feature selection is \emph{complete
-  feature selection}, in which the goal is to find all relevant
-features which have some predictive information about the target. In
+\section{Complete feature selection}\label{comparison-complete-subset}
+\label{complete-selection}
+
+An alternative to minimal subset feature selection is \emph{complete
+  feature selection} in which the goal is to find all relevant
+features that have some predictive information about the target. In
 complete feature selection it is possible that there are theoretically
-relevant features, but given finite noisy data we are not able infer
-these effects.
-
-The projection predictive approach was designed for the minimal subset
-feature selection, but here examine its performance also in complete
-feature selection. In addition, we analyse the benefits of reference
-model approach in combination of a few common complete feature
+relevant features, but given finite noisy data we are not able infer their relevance.
+The projection predictive approach was originally designed for the minimal subset
+feature selection but we will generalized it for the complete
+feature selection case. In addition, we analyse the benefits of the reference
+model approach in combination with three other complete feature
 selection approaches.
 
-\subsection{Complete feature selection approaches to be compared}
-
-Many Bayesian approaches for complete feature selection first fit a
-Bayesian regression model using some sparsifying prior on the
-regression coefficients, for example, as discussed in
-\cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
-\cite{johnstone2004needles}.  In our experiments, we include the
-Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} prior and the
-regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think
-scales better to higher number of covariates as compared to other
-horseshoe-like priors.
-\note{Aki: How this paragraph connects to the next paragraph?}
+As criteria of selection performance, we evaluate the average false
+discovery rate (i.e., the ratio of the number of non-relevant selected
+features over the number of selected features) and the average
+sensitivity (i.e., the ratio of the number of relevant selected
+features over the total number of relevant features). We also provide
+a comparison of the stability of the selection by means of a stability
+measure proposed by \cite{paper:stability}.
+
+%Table \ref{tab:comparison} summarises the methods used in the numerical experiments.
+
+\subsection{Iterative projections}
+
+We can use the projection predictive approach for complete feature
+selection by using it iteratively.  Applying the straightforward
+implementation of projpred, we are able to select a minimal subset of
+features, which yield to a model with a predictive performance
+comparable to the full model one.  The iterative projection repeats
+the projpred selection for different iterations, at each time
+excluding from the search the features selected in the previous
+iterations. At each iteration the selected submodel size corresponds to the
+one having a predictive performance close enough to the baseline
+model, which in this iterative version is the submodel with the
+highest predictive score explored at the current iteration. The
+stopping rule that we adopted is the following:
+\begin{equation} 
+\label{eq:rule_of_thumb}
+\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
+\end{equation}
+where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
+at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
+the stopping rule.
+The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
+observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
+number of observations or not very predictive features. 
+In our experiments we chose the default value used in the \texttt{projpred} 
+\texttt{R}-package that corresponds to $\alpha=0.16$.
+\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
+I did in the thesis}
+TODO: add the pseudo code here
+
+\subsection{Alternative complete feature selection approaches}
+
+% Many Bayesian approaches for complete feature selection first fit a
+% Bayesian regression model using some sparsifying prior on the
+% regression coefficients, for example, as discussed in
+% \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
+% \cite{johnstone2004needles}.  In our experiments, we include the
+% Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} prior and the
+% regularised horseshoe (RHS) prior \citep{paper:rhs}, which in our experience
+% scales better to higher number of covariates as compared to other
+% horseshoe-like priors.
+% \note{Aki: How this paragraph connects to the next paragraph?}
 
@@
 
-Within the set of complete selection procedures, we consider three
-Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
-type prior given by a mixture of a delta distribution in zero and a
-heavy-tailed distribution \cite[see
-also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
-distribution, they show an interesting thresholding property of the
-median estimator and, based on this observation, present a complete
-selection procedure using their prior. We refer to this method as
-\emph{EB.med}. Further, we use a method to control for the local false
-discovery rate (\emph{loc.fdr}) as described in \cite{paper:efron,
-  efron2012large}. Finally, we device a simple selection procedure
-based on posterior credible intervals using the regularised horseshoe
-prior in which we select covariates whose 90\% credible intervals
-excludes zero (\emph{ci.90}) \note{Reference for this?}.
-
-All of these methods provide a complete selection procedure and we
-compare their performance with and without using a reference model.
-\note{Aki: Explain here how the reference mdoels are used for these. Point
-  estimates replace data?}
-
-As criteria of selection performance, we evaluate the average false
-discovery rate (i.e., the ratio of the number of non-relevant selected
-features over the number of selected features) and the average
-sensitivity (i.e., the ratio of the number of relevant selected
-features over the total number of relevant features). We also provide
-a comparison of the stability of the selection by means of a stability
-measure proposed by \cite{paper:stability}. Table \ref{tab:comparison}
-summarises the methods used in the numerical experiments.
-
-\note{Aki: ``Type: Complete selection'' doesn't make sense in the table. Maybe we need to discuss when to use the term complete selection and what is the alternative title for this section.}
-
-\begin{table}[tp]
-\scriptsize
-\centering
-\begin{tabular}{l|l|l|l}
- Method & Abbreviation & Type & Quantities of interest \\ 
-  \hline
- Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
- Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
- Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
- Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
- Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
-\end{tabular}
-\caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
-\label{tab:comparison}
-\end{table}
-
-\hypertarget{complete-selection}{%
-\subsection{Details of methods?}\label{complete-selection}}
-
-\note{Should this be combined with previous subsection?}
-
-As complete selection procedures we consider the control of the local
+%Within the set of complete selection procedures, we consider three
+%Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
+%type prior given by a mixture of a delta distribution in zero and a
+%heavy-tailed distribution \cite[see
+%also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
+%distribution, they show an interesting thresholding property of the
+%median estimator and, based on this observation, present a complete
+%selection procedure using their prior. We refer to this method as
+%\emph{EB.med}. Further, we use a method to control for the local false
+%discovery rate (\emph{loc.fdr}) as described in \cite{paper:efron,
+%  efron2012large}. Finally, we device a simple selection procedure
+%based on posterior credible intervals using the regularised horseshoe
+%prior in which we select covariates whose 90\% credible intervals
+%excludes zero (\emph{ci.90}) \note{Reference for this?}.
+
+We consider three alternative complete selection procedures,
+ the control of the local
 false discovery rate \citep{paper:efron, efron2012large}, the
-empirical Bayes median \citep{johnstone2004needles}, the selection
-by posterior credible intervals and an adaptation of the projection 
-predictive approach that we name iterative projection.\
-
-The control of the local false discovery rate is applied through the
-\texttt{R}-package \texttt{locfdr}. It consists of testing the
+empirical Bayes median \citep{johnstone2004needles}, and the selection
+by posterior credible intervals.
+
+The control of the local false discovery rate consists of testing the
 z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the
@@
 sensitive to the specific value. We use the default setting to
-estimate $\pi_{0}$ from the data provided by the package.
-
-The empirical Bayes median procedure is given by the
-\texttt{R}-package \texttt{EbayesThresh} and consists of fitting a
+estimate $\pi_{0}$ from the data provided by the \texttt{R}-package
+\texttt{locfdr} (cite), which implements the method.
+
+The empirical Bayes median procedure consists of fitting a
 Bayesian model with a prior composed by a mixture of a delta in zero
-and a heavy-tailed distribution. As suggested by
+and a heavy-tailed distribution. It is implemented in the
+\texttt{R}-package \texttt{EbayesThresh} (cite). As suggested by
 \cite{johnstone2004needles}, we use a Laplace distribution resulting
@@
 distribution does not include zero in the interval between the 5\% and
-the 95\% quantiles. \note{Reference?}
-
-We can use the projection predictive approach for complete feature
-selection by using it iteratively.  Applying the straightforward
-implementation of projpred, we are able to select a minimal subset of
-features, which yield to a model with a predictive performance
-comparable to the full model one.  The iterative projection repeats
-the projpred selection for different iterations, at each time
-excluding from the search the features selected in the previous
-iterations. At each iteration the selected submodel size corresponds to the
-one having a predictive performance close enough to the baseline
-model, which in this iterative version is the submodel with the
-highest predictive score explored at the current iteration. The
-stopping rule that we adopted is the following:
-\begin{equation} 
-\label{eq:rule_of_thumb}
-\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
-\end{equation}
-where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
-at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
-the stopping rule.
-The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
-observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
-number of observations or not very predictive features. 
-In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package that corresponds to $\alpha=0.16$.
-\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
-I did in the thesis}
-
-\subsection{Simulated data}
-
-\note{Aki: Why two subsections on simulated data? Combine this with next one, or did I understand their contents wrong?}
-
+the 95\% quantiles (cite).
+
+All of these methods provide a complete selection procedure and we
+compare their performance with and without using a reference model.
+That is, in the data condition, we apply the method on the original
+data $y$ while, in the referece model condition, we replace $y$ by
+their mean predictions $\hat{y}$ based on the reference model.
+
+%\note{Aki: ``Type: Complete selection'' doesn't make sense in the table. Maybe we need to discuss when to use the term complete selection and what is the alternative title for this section.}
+
+% \begin{table}[tp]
+% \scriptsize
+% \centering
+% \begin{tabular}{l|l|l|l}
+% Method & Abbreviation & Type & Quantities of interest \\ 
+%  \hline
+% Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
+% Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
+% Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
+% Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
+% Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
+% \end{tabular}
+% \caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
+% \label{tab:comparison}
+% \end{table}
+
+\subsection{Simulations}
+\label{simulations}
+
+To investigate the performance of the four complete selection procedures,
+we are going to use simulations based on the normal means problem.
 The normal means problem consists of estimating the (usually
@@
 \end{equation}
-Now the quantities of interest $\theta_{j}$ are equal to
+In our situation, the quantities of interest $\theta_{j}$ are equal to
 $\sqrt{n-3}\,T_{F}(\rho_{j})$.
@@
 We use different levels of correlation $\rho\in\{0.3,0.5\}$ and number
-observation $n\in\{50,70,100\}$. The total number of covariates $p$
-and the number of relevant covariates $k$ are fixed to $p = 1000$ and
-$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the selection.
-
-\hypertarget{simulated-data}{%
-\subsection{Simulated data}\label{simulated-data}}
-
-Here we use simulated data in order to control the difficulty of the
-selection problem. We rely on the scheme \eqref{eq:simulated_data}
-using different levels of correlation $\rho\in\{0.3,0.5\}$ and number
 observation $n\in\{50,70,100\}$. The total number of covariates $p$
@@
 
-The normal means problem formulation is obtained as explained in
-Section \ref{comparison} by applying the Fisher-z-transformation to
-the empirical correlations. We label the reference approach as
-``ref'', which consists of using the reference model on top of the
-computation of the z-values, and the standard approach based on the
-observed data simply as ``data''. In Section \ref{shrinkage-signal},
-we analyse the different shrinkage and signal estimates in the context
-of the full Bayes estimation methods by comparing the ref and data
-approach. In Section \ref{complete-selection}, we present results for
-the complete selection procedures.
+% The normal means problem formulation is obtained as explained in
+% Section \ref{comparison} by applying the Fisher-z-transformation to
+% the empirical correlations. We label the reference approach as
+% ``ref'', which consists of using the reference model on top of the
+% computation of the z-values, and the standard approach based on the
+% observed data simply as ``data''. In Section \ref{shrinkage-signal},
+% we analyse the different shrinkage and signal estimates in the context
+% of the full Bayes estimation methods by comparing the ref and data
+% approach. In Section \ref{complete-selection}, we present results for
+% the complete selection procedures.
 
@@
 
-\subsection{Simulation results of complete feature selection}
-
 Figure \ref{fig:sensitivity_vs_fdr_iterated} reports the average sensitivity on
@@
 \hypertarget{real-world-data}{%
-\subsection{The body fat data: A real world example}\label{real-world-data}}
-
-\note{Aki: Is this only complete feature selection or also more results for the minimal subset feature selection?}
+\section{Case study: Body fat data}\label{real-world-data}}
 
@@
 comparing the projection predictive approach and the stepwise
-regression in Section \ref{projection}. We carry out two different
+regression in Section \ref{intro-example}. We carry out two different
 analyses: one using the normal means problem framework and another one
@@
 In the second analysis, we repeat the selection of Section
-\ref{projection} via stepwise backward regression. In this case, the
+\ref{intro-example} via stepwise backward regression. In this case, the
 overall number of covariates (original plus noisy) is 100, as it was
-in the last part of Section \ref{projection}. We compare results with
+in the last part of Section \ref{intro-example}. We compare results with
 and without using a reference model on top of the procedure following
@@
 regression achieves outstanding improvements considering its
-simplicity, yet it does not reach the goodness of more thoughtful
-implementations, for instance, the projective prediction approach (see
-results of Section \ref{projection}).
+simplicity, yet it does not reach the goodness of the much
+more sophisticated projective prediction approach (see
+results of Section \ref{intro-example}).
 
@@
 In this paper, we demonstrated the benefits of using a reference model
-to improve feature selection, or more generally, model reduction. The
-goal of this paper is not to provide a specific procedure to carry out
-the selection, but rather to explain and motivate the general benefits
-of a reference model.  We have seen how the reference model acts as an
+to improve feature selection, or more generally, model reduction. 
+We have motivated and explained the general benefits
+of a reference model regardless of the method it is applied in combination
+with. Specifically, we have seen how the reference model acts as an
 approximation of the data generation mechanism through its predictive
@@
 other. Some of these approaches have been present in the literature
-for several years \cite[e.g. see][]{vehtari2012survey,paper:projpred}
+for several years \cite[e.g., see][]{vehtari2012survey,paper:projpred}
 but often without a clear explanation of \emph{why} they are actually
@@
 \cite{gabry2019visualization}.
-\\
+
+Another main result of this paper is that the projective
+prediction approach shows superior performance compared to alternative methods whether or not
+these methods make use of a reference model. That is, while the reference 
+model is certainly one important aspect the projective
+prediction approach, it is not the only reason for its superior performance.
+Rather, by incoporating the full uncertainty of the posterior predictive distribution into the feature selection procedure (instead of just using
+point estimates) and using principled cross-validation method, projective
+predictions combine several desirable features into a single procedure \citep{paper:projpred}.
+In summary, we would strongly recommend using projective predictions for
+feature selection if possible and feasible. However, if this is not an option
+in a given situation, we would in any case recommend using a reference model
+on top of the chosen feature selection method.
 
@@
 using the same selection procedures. Other kinds of comparisons, as
-the one presented in Section \ref{projection}, work well as
+the one presented in Section \ref{intro-example}, work well as
 motivational examples but lack in terms of generality since the

### 2019-11-05 paper/ref_approach.tex
revised

@@
-\documentclass[american,]{article}
-\usepackage{lmodern}
+\documentclass[a4]{article}
+
 \usepackage{amssymb,amsmath,amsthm}
+\usepackage{newtxtext}
+\usepackage{newtxmath}
 \usepackage{ifxetex,ifluatex}
@@
 \usepackage{graphicx,grffile,subcaption}
+\textwidth 6.0 true in
 \makeatletter
@@
 \usepackage{mathtools}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
 \usepackage{textcomp}
@@
 \newtheorem{example}{Example}
+\DeclareMathOperator{\Cor}{Cor}
+\DeclareMathOperator{\N}{N}
 \newcommand{\note}[1]{\textcolor{red}{#1}}
@@
   Paul-Christian B\"{u}rkner
-  and Aki Vehtari \footnote{Helsinki Institute for Information Technology HIIT,
-  Department of Computer Science, Aalto University, Finland.}
+  and Aki Vehtari \footnote{Department of Computer Science, Aalto University, Finland.}
   }
@@
 the future data in the best possible way and which has passed model checking and criticism
-\citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
-has been used for a long time in Bayesian statistics since the seminal
+\citep[see, e.g.][]{gelman2013bayesian,gabry2019visualization}.  The reference model approach
+has been used in Bayesian statistics at least since the seminal
 work of \citet{paper:reference_lindley}. For more historical
@@
 To motivate the further discussion and experiments, we start by simple
-example comparing projection predictive approach (\emph{projpred},
-\citet{paper:projpred}) which uses a reference model and classic
-stepwise backward regression (steplm).  using the body fat data
-\citep{johnson1996fitting}\footnote{The analysis is based on
-  \texttt{R}-notebook by Vehtari available at
-  \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.  The
-experiments are implemented in \texttt{R} \citep{Rcore2018}.
+variable selection example using body fat data by \citet{johnson1996fitting}.
+We compare projection predictive approach (\emph{projpred},
+\citet{paper:projpred}) which uses a reference model, and classic
+stepwise backward regression (steplm).
+% \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
+%   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
+The experiments are implemented in \texttt{R} \citep{Rcore2018}.
 
@@
 observations. The goal is to find the model which is able to predict
-the amount of fat sufficiently well while requiring least amount of
+the amount of fat well while requiring least amount of
 measurements for a new person.
@@
 comparison we don't fix any of the variables.  The steplm approach is
-carried out combining the \texttt{step} and \texttt{lm} functions
+carried out combining the \texttt{step} and \texttt{lm} functions.
 
 For the selection via projpred, the Bayesian reference model includes
-all the covariates using a regularised horseshoe prior on the
-covariate coefficients \citep{paper:rhs}. Submodels are explored using
+all the covariates using a regularised horseshoe prior~\citep{paper:rhs} on the
+covariate coefficients. Submodels are explored using
 forward search (the results are not sensitive to whether forward or
@@
 \begin{alignat}{2} \label{eq:simulated_data}
-     &f\sim N(0,1) && \nonumber \\ 
-     Y|&f\sim N(f,1) && \\
-     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
-     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
+     &f\sim \N(0,1) && \nonumber \\ 
+     Y|&f\sim \N(f,1) && \\
+     X_{j}|&f \overset{iid}{\sim} \N(\sqrt{\rho}f,1-\rho) \quad &&j=1,\ldots,k \nonumber \\
+     X_{j}|&f \overset{iid}{\sim} \N(0,1) &&j=k+1,\ldots,p \nonumber,
 \end{alignat}
@@
 
-In the bodyfat example above we desired at the same time good
+In the bodyfat example above, we desired at the same time good
 predictive performance and selection of a smaller number of
-features. When the goal is to select a minimal subset of features
-which have similar predictive performance as the full model we call it
+features. When the goal is to select a minimal subset of features,
+which have similar predictive performance as the full model, we call it
 \emph{minimal subset feature selection}. This minimal subset might
 exclude features which have some predictive information about the
-target but given the minimal subset, these features are not able to
-provide such additional information which would improve predictive
+target, but given the minimal subset these features are not able to
+provide such additional information that would improve predictive
 performance. The usual reason for this is that the relevant features
-not in the minimal subset highly correlate with features already in
-the minimal subset. We will later return to a problem of finding all
-the features with some predictive power.
+not in the minimal are subset highly correlated with features already in
+the minimal subset. We will return to a problem of finding all
+the features with some predictive power in Section~\ref{complete-selection}.
 
 Using the data generating mechanism \eqref{eq:simulated_data}, we
-simulate data sets of different size with a relatively large number of
-features $p=100$ with with $k=20$ of them being predictive.
-We compare the minimal subset feature selection perfomance of
-projection predictive approach (with a reference model), a Bayesian
-stepwise forward selection (without a reference model), and stepwise
-forward selection with and without a reference model.
+simulate data sets of different sizes with a relatively large number
+of features $p=100$ with $k=20$ of them being predictive.  We compare
+the minimal subset feature selection perfomance of projection
+predictive approach (with a reference model), a Bayesian stepwise
+forward selection with and without a reference model, and maximum
+likelihood stepwise forward selection with and without a reference
+model:
 \begin{itemize}
-\item projpred: The Projective prediction approach is used. 
+\item projpred: The projective prediction approach is used. 
   The reference model is a Bayesian linear regression
-  model using the first five supervised principal components as predictors
+  model using the first five supervised principal components \citep{piironen2018} as predictors
   and the full posterior predictive distribution as the basis of the projection.   
@@
 
-\item steplm (data based): Stepwise selection using AIC as in the bodyfat example.
-
-\item steplm (reference model based): The reference model is the same as for
+\item Bayesian stepwise selection (without a reference model): At each step, the fitted model
+ is a Bayesian linear regression using the regularised horseshoe
+  prior and the feature excluded is the one with the highest Bayesian
+  $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$.
+The selection continues if the reduced model has an elpd score higher 
+(i.e., better) than the current model.
+
+\item Bayesian stepwise selection (with a reference model): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
+The same Bayesian
+  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.
+
+%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
+\item steplm (without a reference model): Stepwise selection using AIC as in the bodyfat example.
+
+\item steplm (with a reference model): The reference model is the same as for
  projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
@@
 
-\item Bayesian stepwise selection (data based): At each step, the fitted model
- is a Bayesian linear regression using the regularised horseshoe
-  prior and the feature excluded is the one with the highest Bayesian
-  $p$-value defined as:
-\begin{equation}
-\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}
-\end{equation}
-The selection continues if the reduced model has an elpd score higher 
-(i.e., better) than the current model.
-
-\item Bayesian stepwise selection (reference model based): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
-The same Bayesian
-  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.
-
-%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
 \end{itemize}
@@
 In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
-for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR) of the selected submodel,
+for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR, the ratio of the number of non-relevant selected
+features over the number of selected features) of the selected submodel,
 averaged after 100 data simulations. We see that projpred has superior FDR and the
@@
 
+When the variable selection is repeated with different simulated data
+sets, there is some variability in which variables are selected. We
+measure the stability of variable selection by computing the entropy
+of observed distribution over different models. The smallest entropy
+would be obtained if the approach selectes always the same set of
+variables, and the largest entropy would be observed if the approach
+would always select different set of variables.
 Figure \ref{fig:entropy} reports the entropy scores for the different
-methods compared. Lower entropy corresponds to a more stable
-selection. Highly correlated predictive features may happen to be
-alternately selected, making the measure of the stability of the
-selection a non-trivial task. Entropy suffers of such a problem, thus
-such a measure should be seen as one of different possible
-measurements of the actual stability. 
-[TODO: please clarify the above sentences about entropy.] 
+methods compared.  
 The use of a reference model
-improves slightly stability of steplm in feature selection. The
+improves slightly the stability of steplm in feature selection. The
 projection predictive approach results to be far more stable than all
@@
 features that have some predictive information about the target. In
-complete feature selection it is possible that there are theoretically
+complete feature selection, it is possible that there are theoretically
 relevant features, but given finite noisy data we are not able infer their relevance.
 The projection predictive approach was originally designed for the minimal subset
-feature selection but we will generalized it for the complete
+feature selection, but we generalize it here for the complete
 feature selection case. In addition, we analyse the benefits of the reference
@@
 As criteria of selection performance, we evaluate the average false
-discovery rate (i.e., the ratio of the number of non-relevant selected
-features over the number of selected features) and the average
+discovery rate and the average
 sensitivity (i.e., the ratio of the number of relevant selected
@@
 a comparison of the stability of the selection by means of a stability
-measure proposed by \cite{paper:stability}.
+measure proposed by \citet{paper:stability}.
 
@@
 \label{eq:rule_of_thumb}
-\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
+\text{min} \{i\in \{0,\ldots,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \},
 \end{equation}
@@
 % \text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
-% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}], \label{eq:SESE}
+% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},\ldots,z_{p})d\theta_{j} \\
+% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},\ldots,z_{p}], \label{eq:SESE}
 % \end{align}
@@
 % \begin{align}
-% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
+% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,\ldots,p \\
 % &\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
@@
 36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
-sensitive to the specific value. We use the default setting to
-estimate $\pi_{0}$ from the data provided by the \texttt{R}-package
-\texttt{locfdr} (cite), which implements the method.
-
-The empirical Bayes median procedure consists of fitting a
-Bayesian model with a prior composed by a mixture of a delta in zero
-and a heavy-tailed distribution. It is implemented in the
-\texttt{R}-package \texttt{EbayesThresh} (cite). As suggested by
+sensitive to the specific value. To estimate $\pi_{0}$ from the data,
+we use the default setting provided by the \texttt{R}-package
+\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr}.
+
+The empirical Bayes median procedure consists of fitting a Bayesian
+model with a prior composed by a mixture of a delta spike in zero and
+a heavy-tailed distribution. We use the implementation in the
+\texttt{R}-package \texttt{EbayesThresh}
+\citep{Silverman+etal:2017:EbayesThresh}. As suggested by
 \cite{johnstone2004needles}, we use a Laplace distribution resulting
@@
 \begin{equation}\label{eq:normal_means_problem}
-Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}N(\theta_{j},\sigma^{2}), \quad j=1,..,p.
+Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}\N(\theta_{j},\sigma^{2}), \quad j=1,\ldots,p.
 \end{equation}
@@
 compute the two-sample $t$-statistic for every gene separately.  After
-normalising these statistics, they then become the data, $Z$, in the
+normalising these statistics, they then become the data $Z$ in the
 normal means problem \eqref{eq:normal_means_problem}. For further
-details see the examples in \cite{paper:efron, efron2012large}.
+details see the examples by \cite{paper:efron, efron2012large}.
 
@@
 Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
-continuous target random variable $Y$, a set of $p$ continuous
+continuous target random variable $Y,$ a set of $p$ continuous
 covariates $\{X_{j}\}_{j=1}^{p}$, and denote
-$\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$
+$\rho_{j}=\Cor(Y,X_{j})$. Further, suppose we have observed $n$
 statistical units and define $r_{j}$ the sample correlation between
@@
 \begin{equation} \label{eq:fisher_transformation}
-T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p.
+T_{F}(r_{j})\overset{ind}{\sim} \N(T_{F}(\rho_{j}),\frac{1}{n-3}), \quad j=1,\ldots,p.
 \end{equation}
@@
 \begin{equation} \label{eq:normal_means_problem2}
-Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p.
+Z_{j}|\theta_{j}\overset{ind}{\sim}\N(\theta_{j},1), \quad j=1,\ldots,p.
 \end{equation}
-In our situation, the quantities of interest $\theta_{j}$ are equal to
+In this case, the quantities of interest $\theta_{j}$ are equal to
 $\sqrt{n-3}\,T_{F}(\rho_{j})$.
 
-We use different levels of correlation $\rho\in\{0.3,0.5\}$ and number
-observation $n\in\{50,70,100\}$. The total number of covariates $p$
+We use different levels of correlation $\rho\in\{0.3,0.5\}$ and numbers of
+observations $n\in\{50,70,100\}$. The total number of covariates $p$
 and the number of relevant covariates $k$ are fixed to $p = 1000$ and
 $k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the selection. As mentioned, this data generation
-mechanism was originally proposed by \cite{paper:projpred} who also
-devise a reference model performing sufficiently well in this
-situation. It consists of a linear regression using the first five
-supervised principal components (SPCs) \citep{bair2006prediction,
-  piironen2018} as covariates and imposing an hierarchical prior on
-their coefficients: \
+more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
+use a reference model which a Bayesian linear regression using the first five
+supervised principal components (SPC) as covariates and imposing an hierarchical prior on
+their coefficients:
 \begin{equation}
@@
 \begin{aligned}
-    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,..,n \\
-    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} N(0,\tau^{2})\\
+    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} \N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,\ldots,n \\
+    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} \N(0,\tau^{2})\\
     &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
-    \end{aligned} &j=1,..,5 \\ 
+    \end{aligned} &j=1,\ldots,5 \\ 
     &\sigma \sim t_{3}^{+}(0,10). \\
@@
 observation $i$, and $s_{max}$ denotes the sample standard deviation
-of the largest SPC.  The SPCs are computed through the
+of the largest SPC.  The SPCs are computed using the
 \texttt{R}-package \texttt{dimreduce} setting the screening threshold
-parameter at $0.6s_{max}$.  In our experiments the results are not
-sensible to such a choice of the screening threshold, yet a more
+parameter at $0.6s_{max}$.  In our experiments, the results are not
+sensitive to the specific choice of the screening threshold, yet a more
 principled approach would be to use cross-validation to select the
@@
 
-Figure \ref{fig:sensitivity_vs_fdr_iterated} reports the average sensitivity on
-the vertical axis versus the average false discovery rate on the
+Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
+the vertical axis and the average false discovery rate on the
 horizontal axis based on 100 data simulations for the different
-combinations of $n$ and $\rho$. For each method (different colours)
-the squares and the circles correspond to using the reference and
-approach respectively. The best selection performance is on the
+combinations of $n$ and $\rho$. The best selection performance is on the
 top-left corner of each plot, as it implies the lowest false discovery
@@
 applied selection method, the use of a reference model improves the
-selection performance as it reduces the false discovery rate (shifting
+selection performance, as it reduces the false discovery rate (shifting
 to the left) or increases the sensitivity (shifting upwards). In
-accordance with what can be expected, the larger number of
-observations and the higher the true correlations, the easier the
+accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
 selection is. Thus, for easier selection scenarios, the benefits of
@@
 enough information to identify the relevant covariates. The iterative
-projection performs fairly well if the number of observations and the correlation level
-are not too small. In those cases it mainly results to be too conservative, resulting in a low
-sensitivity, but good false discovery rate. Tuning $\alpha$ might lead to improved selection, yet
+projection predictive approach has good false discovery rate in all cases, and the sensitivity is good except when the number of observations and the correlation level
+are small. Tuning $\alpha$ might lead to improved selection, yet
 the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
@@
 
-We conclude our  experiments using the real world `body fat' dataset
-one more time, which was already described in the motivational example
-comparing the projection predictive approach and the stepwise
-regression in Section \ref{intro-example}. We carry out two different
-analyses: one using the normal means problem framework and another one
-using selection via stepwise backward regression. In the former, we
-add noisy uncorrelated covariates to the original data up to a total
-of 1000 features. These covariates are normally distributed and scaled
-as the original covariates. We compute correlations between each
-variable and the target variable, that is the amount of fat, and
-transform them by Fisher-Z-transformation. The original assumption in
-order for \eqref{eq:fisher_transformation} to hold is that the
-variables are jointly normally distributed. In our experience the
-normal approximation in \eqref{eq:fisher_transformation} is still
-reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the
-variance to be one, and instead estimate it from the data. The methods
-we compare are those used in Section \ref{complete-selection}: the
-control of the local false discovery rate (loc.fdr), the empirical
-Bayes median (EB.med) and the selection by posterior credible
-intervals at level 90\% (ci.90).  In order to vary the difficulty of
-the selection, we bootstrap subsamples of different sizes, going from
-$n=50$ up to $n=251$ (i.e., the full size of the data). For each
-condition, results are averaged over 100 bootstrap samples of the
-respective size.
+We conclude our experiments using the body fat dataset one
+more time, which was already described in Section \ref{intro-example}. We
+carry out two different analyses: one using the normal means problem
+framework and another one using selection via stepwise backward
+regression. In the former, we add noisy uncorrelated covariates to the
+original data up to a total of 1000 features. These covariates are
+normally distributed and scaled as the original covariates. We compute
+correlations between each variable and the target variable, that is
+the amount of fat, and transform them by Fisher-Z-transformation. The
+original assumption in order for \eqref{eq:fisher_transformation} to
+hold is that the variables are jointly normally distributed. In our
+experience the normal approximation in
+\eqref{eq:fisher_transformation} is still reasonable, but after
+rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
+instead estimate it from the data. The methods we compare are those
+used in Section \ref{complete-selection}: the control of the local
+false discovery rate (loc.fdr), the empirical Bayes median (EB.med)
+and the selection by posterior credible intervals at level 90\%
+(ci.90).  In order to vary the difficulty of the selection, we
+bootstrap subsamples of different sizes, going from $n=50$ up to
+$n=251$ (i.e., the full size of the data). For each condition, results
+are averaged over 100 bootstrap samples of the respective size.
 
@@
 available with regard the original covariates of the data, we believe
-it is reasonable to consider all of them relevant, at least at some
+it is reasonable to consider all of them relevant, at least to some
 degree. The artificially added features are naturally irrelevant by
-construction. In almost all the bootstrapped subsamples, the reference
+construction. In almost all of the bootstrapped subsamples, the reference
 model improves the selection both in terms of sensitivity and false
-discovery rate. When $n=50$, we observe a worsening in terms of false
-discovery rate, yet by a lower amount compared to the gain in
+discovery rate. When $n=50$, we observe worse false
+discovery rates, yet by a lower amount compared to the gain in
 sensitivity. Again, we observe that the benefits are more evident as
@@
 observations). Figure \ref{fig:bodyfat_stability} shows the stability
-results, still using the measure provided by
+results using the measure by
 \cite{paper:stability}. The benefits of the reference model are here
@@
 
-In this example, we have still used the reference model defined as a
-linear regression over some supervised principal components, because
-of its fairly good predictive performance and efficient estimation. We
-do not argue that this is always a good choice and more sophisticated
-models can lead to even better results. Since, in our case, the sake
-of the analysis was only to motivate the use of reference models in
-general, and since we needed to average results over a lot of
-repetitions per simulation condition, we preferred to stick to such a
-comparably simple reference model.
+In this example, we have used the reference model defined as a linear
+regression over some supervised principal components, because it is
+natural for a large number of correlating variables, has fairly good
+predictive performance and is computationally efficient. We do not
+argue that this is always the best choice and more sophisticated
+models can lead to even better results. Here the purpose of the
+experiments were to motivate the use of reference models in general,
+and as we needed to average results over a lot of repetitions per
+simulation condition, we preferred such a comparably simple and
+computationally fast reference model.
 
@@
 other. Some of these approaches have been present in the literature
-for several years \cite[e.g., see][]{vehtari2012survey,paper:projpred}
-but often without a clear explanation of \emph{why} they are actually
+\cite[e.g., see references in][]{vehtari2012survey,paper:projpred}
+but often without a clear explanation of {why} they are actually
 favourable and how they connect to other related approaches. We hope
@@
 real world application will consist in devising a sensible reference
-model itself and assessing its predictive performance. We did provide
-a generic way to build simple reference models, but those may not
-necessarily be appropriate in all situations. If more sophisticated
-reference models are required, which are more specifically tuned to
-the data and problem at hand, we recommend them to be developed using
-a robust (Bayesian) modelling workflow, for instance, as outlined in
-\cite{gabry2019visualization}.
-
-Another main result of this paper is that the projective
-prediction approach shows superior performance compared to alternative methods whether or not
-these methods make use of a reference model. That is, while the reference 
-model is certainly one important aspect the projective
-prediction approach, it is not the only reason for its superior performance.
-Rather, by incoporating the full uncertainty of the posterior predictive distribution into the feature selection procedure (instead of just using
-point estimates) and using principled cross-validation method, projective
-predictions combine several desirable features into a single procedure \citep{paper:projpred}.
-In summary, we would strongly recommend using projective predictions for
-feature selection if possible and feasible. However, if this is not an option
-in a given situation, we would in any case recommend using a reference model
-on top of the chosen feature selection method.
+model itself and assessing its predictive performance.
+% We did provide
+% a generic way to build simple reference models, but those may not
+% necessarily be appropriate in all situations.
+To build good predictive reference models, which are specifically
+tuned to the data and problem at hand, we recommend them to be
+developed using a robust Bayesian modelling workflow, for instance, as
+outlined by \citet{gelman2013bayesian} and \citet{gabry2019visualization}.
+
+Another main result of this paper is that the projective prediction
+approach shows superior performance in minimal subset feature
+selection compared to alternative methods whether or not these methods
+make use of a reference model. That is, while the reference model is
+certainly one important aspect the projective prediction approach, it
+is not the only reason for its superior performance.  Rather, by
+incoporating the full uncertainty of the posterior predictive
+distribution into the feature selection procedure (instead of just
+using point estimates) and using principled cross-validation method,
+projective predictions combine several desirable features into a
+single procedure \citep{paper:projpred}.  In summary, we would
+strongly recommend using projective predictions for feature selection
+if possible and feasible. However, if this is not an option in a given
+situation, we would in any case recommend using a reference model on
+top of the chosen feature selection method.
+
+While the projective prediction approach was not designed for the
+complete feature selection, the iterative version retains the
+excellent false discovery rate property. The iterative projection
+predictive approach had lower sensitivity than the other methods, and
+it is left for future resarch whether it is possible to improve
+sensitivity without sacrifying the good false discovery rate.
 
@@
 
-%\appendix
+\appendix
 
@@
 %\end{figure}
+
+\section*{Appendix}
 
@@
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,..,S \,,
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,\ldots,S \,,
 \end{equation}

### 2019-11-08 code/plots.R
updated plot scripts

@@ -6,6 +6,7 @@ theme_set(theme_light() +
           theme(strip.background = element_rect(color='black',fill='white'),
                 strip.text.x = element_text(color='black'),
                 strip.text.y = element_text(color='black')))
+shapes <- c('ref'=8, 'data'=20)
 library(latex2exp)
 source("getStability.R")
 
@@ -120,7 +121,7 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
   geom_point(aes(shape=approach),size=2.5) +
  # geom_errorbar(aes(ymin=sensitivity-sensitivity.sd, ymax=sensitivity+sensitivity.sd)) +
  # geom_errorbarh(aes(xmin=fdr-fdr.sd, xmax=fdr+fdr.sd)) +
-  scale_shape_manual(values = c(16,15)) +
+  scale_shape_manual(values = shapes) +
   geom_line(aes(col=method)) +
   labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
 #  theme_light()
@@ -467,8 +468,8 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
     ##geom_abline(intercept=0, slope=1, linetype='dashed') +
     scale_x_continuous(limits=c(0,0.6)) +
     scale_y_continuous(limits=c(0.3,0.9)) +
-    geom_point(aes(shape=approach),size=2.5) +
-    scale_shape_manual(values = c(16,15)) +
+    geom_point(aes(shape=approach), size=2) +
+    scale_shape_manual(values = shapes) +
     geom_line(aes(col=method)) +
     labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
    # theme_light() +
@@ -482,7 +483,7 @@ ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=
 ## Stability plot
 plot2 <- ggplot(data.plot,aes(y=stab.mean,x=method,col=approach)) +
   facet_grid(~n, labeller=facet.labels) +
-  geom_point(size=2.5) +
+  geom_point(size=1.5) +
   geom_linerange(aes(ymin=stab.low,ymax=stab.up)) +
   coord_flip() +
   labs(x="",y="Stability", col="Approach") +
[…]

### 2019-11-08 code/plots_iterated.R

@@ -4,6 +4,7 @@ theme_set(theme_light() +
           theme(strip.background = element_rect(color='black',fill='white'),
                 strip.text.x = element_text(color='black'),
                 strip.text.y = element_text(color='black')))
+shapes <- c('ref'=8, 'data'=20)
 library(latex2exp)
 source("getStability.R")
 
@@ -172,7 +173,7 @@ plot1 <- ggplot(data.plot.clean,aes(x=fdr,y=sensitivity,col=method)) +
     ##                 segment.size = 0.2,
     ##                 size = 3,
     ##                 alpha = 0.6) +
-    scale_shape_manual(values = c(16,15)) +
+    scale_shape_manual(values = shapes) +
     scale_colour_manual(values = colors) +
     geom_line(data=filter(data.plot.clean,method!='iter.cv'),aes(col=method)) +
     guides(label=FALSE) +
@@ -182,15 +183,13 @@ ggsave(filename='../paper/graphics/sensitivity_vs_fdr_iterated.pdf',plot1,width=
 
 plot2 <- ggplot(data.plot.clean,aes(y=stab.mean,x=method,col=approach)) +
   facet_grid(rho~n, labeller=facet.labels) +
-  geom_point(size=2.5) +
+  geom_point() +
   geom_linerange(aes(ymin=stab.low,ymax=stab.up)) +
   coord_flip() +
   labs(x="",y="Stability", col="Approach") +
   scale_color_manual(values=c("#819FF7","#FAAC58"))
 
 ggsave(filename='../paper/graphics/stability_iterated.pdf',plot2, width=10,height=3)
-
-
 
 ## #### Test vs K10 ####
 

### 2019-11-08 paper/ref_approach.tex
fixed TODO and plots

--- 2019-10-19 paper/ref_approach.tex
@@
 \usepackage{fixltx2e} % provides \textsubscript
+\usepackage{algorithm2e}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
 
-\item Bayesian stepwise selection (reference model based): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
-The same Bayesian
-  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.
+\item Bayesian stepwise selection (reference model based): The reference model is 
+the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
+are used to replace the target variable $y$. The same Bayesian $p$-value selection
+ strategy as in the data based Bayesian stepwise selection is used.
 
@@
 In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
-for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR) of the selected submodel,
+for different values of $n$ and $\rho$ in terms of RMSE and the false
+ discovery rate (FDR) of the selected submodel,
 averaged after 100 data simulations. We see that projpred has superior FDR and the
@@
 alternately selected, making the measure of the stability of the
-selection a non-trivial task. Entropy suffers of such a problem, thus
-such a measure should be seen as one of different possible
-measurements of the actual stability. 
-[TODO: please clarify the above sentences about entropy.] 
+selection a non-trivial task. Entropy can not distinguish the interchangeability 
+due to correlation from instability, thus such a measure should be 
+consider as relative indicator and not as an absolute measure of stability.
+\hl{TODO: The above sentence should be clearer now}
 The use of a reference model
@@
 at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
-the stopping rule.
+the stopping rule (see Algorithm \ref{alg:iterated_proj}).
 The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
@@
 \texttt{R}-package that corresponds to $\alpha=0.16$.
-\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
-I did in the thesis}
-TODO: add the pseudo code here
+
+\begin{center}
+\begin{algorithm}[H]
+\SetAlgoLined
+\KwResult{$R:=\{\text{selected features}\}$}
+ $F:=\{\text{set of features}\}$ \;
+ $R=\{\emptyset\}$ \;
+ Fit reference model\;
+ \While{$F\neq\{\emptyset\}$}{
+   projection.HeuristicSearch \;
+   projection.elpdEstimate() \;
+%:
+   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;
+
+  \eIf{$S=\{\emptyset\}$}{
+   break \;
+   }{
+   $R=R\cup S$\;
+   $F=F\setminus S$\;
+  }
+ }
+ \caption{Automated iterative projections}
+ \label{alg:iterated_proj}
+\end{algorithm}
+\end{center}
 
@@
 the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
-utility score for misspecified models with cross-validation \hl{(maybe add some references?)}.
+utility score for misspecified models with cross-validation \hl{(maybe add some references? The last sentence 
+refers to the problem when comparing misspecified models using CV. Tuomas did a talk about this problem.
+Maybe Aki can check the content and add some references - not sure Tuomas' work is already available)}.
 

### 2019-11-08 paper/ref_approach.tex

--- 2019-11-05 paper/ref_approach.tex
@@
 Figure \ref{fig:entropy} reports the entropy scores for the different
-methods compared.  
+methods compared. Lower entropy corresponds to a more stable
+selection. Highly correlated predictive features may happen to be
+alternately selected, making the measure of the stability of the
+selection a non-trivial task. Entropy can not distinguish the interchangeability 
+due to correlation from instability, thus such a measure should be 
+consider as relative indicator and not as an absolute measure of stability.
+\hl{TODO: The above sentence should be clearer now}
 The use of a reference model

### 2019-11-09 code/plots_in_the_paper.R
clean version of the script for final plots in the paper

@@ -1,0 +1,661 @@
+##########################################
+### Script for the plots of the paper ####
+##########################################
+library(tidyverse)
+library(ggrepel)
+theme_set(theme_light() +
+          theme(strip.background = element_rect(color='black',fill='white'),
+                strip.text.x = element_text(color='black'),
+                strip.text.y = element_text(color='black')))
+shapes <- c('ref'=8, 'data'=20)
+library(latex2exp)
+source("getStability.R")
+
+p <- 1000
+k <- 100
+
+avg.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+sd.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(sd(tmp, na.rm = TRUE))
+}
+
+avg.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+sd.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(sd(tmp, na.rm = TRUE))
+}
+
+data.plot <- tibble(n = numeric(),
+                    rho = numeric(),
+                    method = character(),
+                    approach = character(),
+                    sensitivity = numeric(),
+                    sensitivity.sd = numeric(),
+                    fdr = numeric(),
+                    fdr.sd = numeric(),
+                    stab.low = numeric(),
+                    stab.mean = numeric(),
+                    stab.up = numeric())
+
+for(nn in c(50,70,100)){
+  for(rr in c(0.3,0.5)){
+    load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
+
+    data.plot <- data.plot %>%
+      # Credibility intervals inclusion probabilities with regularized horseshoe prior
+      bind_rows(tibble(n = rep(n,2),
+              rho = rep(rho,2),
+              method = rep("ci.90",2),
+              approach = c("ref","data"),
+              sensitivity = c(avg.sensitivity(ci90_X_ref),
+                              avg.sensitivity(ci90_X_data)),
+              sensitivity.sd = c(sd.sensitivity(ci90_X_ref),
[…]

### 2019-11-25 paper/ref_approach.tex
slightly bigger font size for tables
update graphics

@@
 \begin{table}[tp]
-\scriptsize
+\footnotesize
 \centering
@@
 of observed distribution over different models. The smallest entropy
-would be obtained if the approach selectes always the same set of
+would be obtained if the approach always selects the same set of
 variables, and the largest entropy would be observed if the approach
 would always select different set of variables.
-Figure \ref{fig:entropy} reports the entropy scores for the different
-methods compared. Lower entropy corresponds to a more stable
+Figure \ref{fig:entropy} reports the entropy scores for the different compared
+methods. Lower entropy corresponds to a more stable
 selection. Highly correlated predictive features may happen to be
 alternately selected, making the measure of the stability of the
-selection a non-trivial task. Entropy can not distinguish the interchangeability 
-due to correlation from instability, thus such a measure should be 
-consider as relative indicator and not as an absolute measure of stability.
-\hl{TODO: The above sentence should be clearer now}
+selection a non-trivial task. Entropy cannot distinguish the interchangeability 
+due to correlation from instability. Thus, such a measure should be 
+considerd as a relative and not as an absolute measure of stability.
 The use of a reference model

### 2019-11-28 paper/ref_approach.tex
add a ref

@@
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
 \usepackage{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
 \usepackage[margin=1in]{geometry}
@@
 \hypersetup{unicode=true,
-            pdftitle={The reference model approach in feature selection problems},
+            pdftitle={The reference model approach in feature selection},
             pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
@@
 
-\title{Using reference models in feature selection problems 
+\title{Using reference models in feature selection 
 	\vspace{.1in}}
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
+  \vspace{-5mm}
+  \includegraphics[width=0.4\textwidth]{graphics/correlation.pdf}
   \caption{Sample correlation plot of each feature (relevant in red, 
@@
 the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
-utility score for misspecified models with cross-validation \hl{(maybe add some references? The last sentence 
-refers to the problem when comparing misspecified models using CV. Tuomas did a talk about this problem.
-Maybe Aki can check the content and add some references - not sure Tuomas' work is already available)}.
+utility score for misspecified models with cross-validation \citep{bengio2004no}.
 
@@
 presence or absence of a reference model is not the only aspect
-differentiating the two procedures. We will come back to the more
-general comparison in Section \ref{comparison}.
+differentiating the two procedures.
+% We will come back to the more
+% general comparison in Section \ref{comparison}.
 

### 2019-12-03 code/plots_in_the_paper.R
updated plots for last bodyfat experiment with iterative proj

@@ -330,9 +330,24 @@ for(nn in c(50,70,100,251)){
                                    getStability(ebmt_X_data)$stability),
                      stab.up = c(getStability(ebmt_X_ref)$upper,
                                  getStability(ebmt_X_data)$upper)))
+
+  load(paste("bodyfat_type1_varyN_iteratedproj_n",nn,".Rdata",sep=""))
+## Iterative projection
+  data.plot <- data.plot %>%
+      bind_rows(tibble(n = n,
+                       method = "projpred.iter",
+                       approach = "ref",
+                       sensitivity =  avg.sensitivity(projpred_X),
+                       fdr = avg.fdr(projpred_X),
+                       stab.low = getStability(projpred_X)$lower,
+                       stab.mean = getStability(projpred_X)$stability,
+                       stab.up = getStability(projpred_X)$upper))
 }
 
-
+colors <- c('projpred.iter' = '#2E2E2E',
+            'loc.fdr' = '#819FF7',
+            'EB.med' = '#298A08',
+            'ci.90' = '#F78181')
 
 facet.labels <- labeller(n = function(x){paste("n=",x,sep="")})
 
@@ -341,9 +356,10 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
     facet_grid(~n, labeller=facet.labels) +
     ##geom_abline(intercept=0, slope=1, linetype='dashed') +
     scale_x_continuous(limits=c(0,0.6)) +
-    scale_y_continuous(limits=c(0.3,0.9)) +
+    scale_y_continuous(limits=c(0.3,0.99)) +
     geom_point(aes(shape=approach), size=2) +
     scale_shape_manual(values = shapes) +
+    scale_colour_manual(values = colors) +
     geom_line(aes(col=method)) +
     labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
    # theme_light() +
@@ -352,7 +368,7 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
    #       strip.text.y = element_text(color='black'))
 
 
-ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.1)
+ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.5)
 
 ## Stability plot
 plot2 <- ggplot(data.plot,aes(y=stab.mean,x=method,col=approach)) +

### 2019-12-03 code/iterated_projection.R
fixed code in order not to fail bc less spc than requested components

@@ -60,7 +60,7 @@ for(aaa in alpha_vec){
                   chains = 1, iter = 2000, seed = 4345342+k,refresh=0)
         draws <- as.matrix(fit_k) # posterior draws
         sigma <- draws[,'sigma'] # noise std
-        beta <- draws[,2:(nc+1)] # regression coefficients
+        beta <- draws[,2:(ncol(zz)+1)] # regression coefficients
         alpha <- draws[,'intercept'] # intercept
 
         predfun <- function(zt){

### 2019-12-03 code/bodyfat_comparison_varying_n_iteratedproj.R
script for iterative proj in bodyfat experiment

@@ -1,0 +1,109 @@
+## BODYFAT COMPARISON ##
+rm(list=ls())
+args = commandArgs(trailingOnly=TRUE)
+library(rstan)
+library(rstanarm)
+library(projpred)
+library(dimreduce)
+set.seed(3428954)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n_full <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p <- 1000
+n <- as.numeric(args[1])
+times <- 100
+
+projpred_X <- matrix(0,nrow=times,ncol=p)
+alpha_lev <- 0.16
+## Stan model
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
+dfr<-cbind(df,noise=noise)
+formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+pred2 <- c(pred,colnames(dfr[,15:(p+1)]))
+
+for(i in 1:times){
+    print(paste('ITERATION NUMBER: ',i))
+    sel  <- sample(1:n_full,n,replace = T)
+    x <- dfr[sel,-1]
+    y <- dfr[sel,1]
+    nc <- 5
+    dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p,
+               sup.only = T, verbose = F)
+    z <- predict(dr, x)
+  ## fit the model
+    cvfun <- function(folds) {
+      lapply(1:max(folds), function (k) {
+        w <- which(folds!=k)
+        dr <- spca(x[w,],y[w], nctot=nc, screenthresh = 0.6, window=p,
+                   sup.only = T, verbose = F) # screenthresh = 0.6, sup.only=T
+        zz <- predict(dr, x[w,])
+        # fit the model
+        model_data <- list(y=y[w],X=zz,p=ncol(zz),n=length(w),s_max=dr$sdev[1])
[…]

### 2019-12-03 code/plots_in_the_paper_new.R
Create plots_in_the_paper_new.R

@@ -1,0 +1,714 @@
+##########################################
+### Script for the plots of the paper ####
+##########################################
+library(tidyverse)
+library(ggrepel)
+theme_set(theme_light() +
+          theme(strip.background = element_rect(color='black',fill='white'),
+                strip.text.x = element_text(color='black'),
+                strip.text.y = element_text(color='black')))
+shapes <- c('ref'=8, 'data'=20)
+library(latex2exp)
+source("getStability.R")
+
+p <- 1000
+k <- 100
+
+avg.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+sd.sensitivity <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+  return(sd(tmp, na.rm = TRUE))
+}
+
+avg.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(mean(tmp, na.rm = TRUE))
+}
+
+sd.fdr <- function(X){
+  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+  return(sd(tmp, na.rm = TRUE))
+}
+
+colors <- c(
+  'projpred.iter' = '#2E2E2E',
+  'loc.fdr' = '#619CFF',
+  'ci.90' = '#F8766D',
+  'EB.med' = '#00BA38'
+)
+
+data.plot <- tibble(n = numeric(),
+                    rho = numeric(),
+                    method = character(),
+                    approach = character(),
+                    sensitivity = numeric(),
+                    sensitivity.sd = numeric(),
+                    fdr = numeric(),
+                    fdr.sd = numeric(),
+                    stab.low = numeric(),
+                    stab.mean = numeric(),
+                    stab.up = numeric())
+
+for(nn in c(50,70,100)){
+  for(rr in c(0.3,0.5)){
+    load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
+
+    data.plot <- data.plot %>%
+      # Credibility intervals inclusion probabilities with regularized horseshoe prior
+      bind_rows(tibble(n = rep(n,2),
+              rho = rep(rho,2),
+              method = rep("ci.90",2),
+              approach = c("ref","data"),
+              sensitivity = c(avg.sensitivity(ci90_X_ref),
[…]

### 2019-12-04 code/plots_in_the_paper_new.R
updated with iter proj for figure 8-9 + saved only plot data

@@ -41,83 +41,93 @@ colors <- c(
   'EB.med' = '#00BA38'
 )
 
-data.plot <- tibble(n = numeric(),
-                    rho = numeric(),
-                    method = character(),
-                    approach = character(),
-                    sensitivity = numeric(),
-                    sensitivity.sd = numeric(),
-                    fdr = numeric(),
-                    fdr.sd = numeric(),
-                    stab.low = numeric(),
-                    stab.mean = numeric(),
-                    stab.up = numeric())
+## If you want to run the script to create the data object
+## set TRUE, otherwise set FALSE to load the data.
+saveMode <- FALSE
 
-for(nn in c(50,70,100)){
-  for(rr in c(0.3,0.5)){
-    load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
+######################################################
+###### COMPLETE SELECTION (OLD VERSION) ##############
+######################################################
 
-    data.plot <- data.plot %>%
-      # Credibility intervals inclusion probabilities with regularized horseshoe prior
-      bind_rows(tibble(n = rep(n,2),
-              rho = rep(rho,2),
-              method = rep("ci.90",2),
-              approach = c("ref","data"),
-              sensitivity = c(avg.sensitivity(ci90_X_ref),
-                              avg.sensitivity(ci90_X_data)),
-              sensitivity.sd = c(sd.sensitivity(ci90_X_ref),
-                                 sd.sensitivity(ci90_X_data)),
-              fdr = c(avg.fdr(ci90_X_ref),
-                      avg.fdr(ci90_X_data)),
-              fdr.sd = c(sd.fdr(ci90_X_ref),
-                         sd.fdr(ci90_X_data)),
-              stab.low = c(getStability(ci90_X_ref)$lower,
-                           getStability(ci90_X_data)$lower),
-              stab.mean = c(getStability(ci90_X_ref)$stability,
-                            getStability(ci90_X_data)$stability),
-              stab.up = c(getStability(ci90_X_ref)$upper,
-                          getStability(ci90_X_data)$upper))) %>%
-      # Control of the local false discovery rate
-      bind_rows(tibble(n = rep(n,2),
-              rho = rep(rho,2),
-              method = rep("loc.fdr",2),
-              approach = c("ref","data"),
-              sensitivity = c(avg.sensitivity(lfdr_X_ref),
-                              avg.sensitivity(lfdr_X_data)),
[…]

### 2019-12-04 paper/ref_approach.tex
re-arranged some sections

@@
 
+\section{Reference models in feature selection}
+\label{intro-example}
+
+Blah blah
+
 \subsection{Example of model selection with or without reference model}
@@
 \hypertarget{reference-model-approach}{%
-\section{Why the reference model helps}\label{reference-model-approach}}
+\subsection{Why the reference model helps}\label{reference-model-approach}}
 
@@
 
+\subsection{Simulation study}
+
 Using the data generating mechanism \eqref{eq:simulated_data}, we
@@
 \end{figure}
+
+\hypertarget{real-world-data}{%
+\subsection{Body fat example part 2}\label{real-world-data}}
+
+Here we repeat the selection of Section \ref{intro-example} via
+stepwise backward regression. In this case, the overall number of
+covariates (original plus noisy) is 100, as it was in the last part of
+Section \ref{intro-example}. We compare results with and without using
+a reference model on top of the procedure following our simple
+reference model approach outlined in \eqref{eq:ref_mod}. Figure
+\ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant
+features included in the final model and the out-of-sample root mean
+square error (RMSE). Results are based on 100 bootstrap samples on the
+whole dataset, and the predictive performance is tested on the
+observations excluded at each bootstrap sample. We observe that the
+reference model reduces the number of irrelevant features included in
+the final model. This leads to less overfitting and thus to improved
+out-of-sample predictive performance in terms of RMSE. The reference
+model approach applied to the stepwise backward regression achieves
+outstanding improvements considering its simplicity, yet it does not
+reach the goodness of the much more sophisticated projective
+prediction approach (see results of Section \ref{intro-example}).
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
+  \caption{Stepwise backward selection with and without using a reference model.
+The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
+  \label{fig:bodyfat_step_refvsdata}
+\end{figure}
+
+In this example, we have used the reference model defined as a linear
+regression over some supervised principal components, because it is
+natural for a large number of correlating variables, has fairly good
+predictive performance and is computationally efficient. We do not
+argue that this is always the best choice and more sophisticated
+models can lead to even better results. Here the purpose of the
+experiments were to motivate the use of reference models in general,
+and as we needed to average results over a lot of repetitions per
+simulation condition, we preferred such a comparably simple and
+computationally fast reference model.
 
@@
 
-\subsection{Simulations}
+\subsection{Simulation study}
 \label{simulations}
@@
 \hypertarget{real-world-data}{%
-\section{Case study: Body fat data}\label{real-world-data}}
-
-We conclude our experiments using the body fat dataset one
+\subsection{Body fat example part 3}\label{real-world-data}}
+
+We conclude our complete selection experiments using the body fat dataset one
 more time, which was already described in Section \ref{intro-example}. We
@@
 marginal with only small improvements.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
-  \caption{Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
-  \label{fig:bodyfat_step_refvsdata}
-\end{figure}
-
-In the second analysis, we repeat the selection of Section
-\ref{intro-example} via stepwise backward regression. In this case, the
-overall number of covariates (original plus noisy) is 100, as it was
-in the last part of Section \ref{intro-example}. We compare results with
-and without using a reference model on top of the procedure following
-our simple reference model approach outlined in
-\eqref{eq:ref_mod}. Figure \ref{fig:bodyfat_step_refvsdata} shows the
-number of irrelevant features included in the final model and the
-out-of-sample root mean square error (RMSE). Results are based on 100
-bootstrap samples on the whole dataset, and the predictive performance
-is tested on the observations excluded at each bootstrap sample. We
-observe that the reference model reduces the number of irrelevant
-features included in the final model. This leads to less overfitting
-and thus to improved out-of-sample predictive performance in terms of
-RMSE. The reference model approach applied to the stepwise backward
-regression achieves outstanding improvements considering its
-simplicity, yet it does not reach the goodness of the much
-more sophisticated projective prediction approach (see
-results of Section \ref{intro-example}).
-
-In this example, we have used the reference model defined as a linear
-regression over some supervised principal components, because it is
-natural for a large number of correlating variables, has fairly good
-predictive performance and is computationally efficient. We do not
-argue that this is always the best choice and more sophisticated
-models can lead to even better results. Here the purpose of the
-experiments were to motivate the use of reference models in general,
-and as we needed to average results over a lot of repetitions per
-simulation condition, we preferred such a comparably simple and
-computationally fast reference model.
 

### 2019-12-04 code/plots_in_the_paper_new.R
update graphics

@@ -126,8 +126,9 @@ if(saveMode){
         }
     }
     save(data.plot, file='complete_selection_old_plot.RData')
-} else
+} else {
     load('complete_selection_old_plot.RData')
+}
 
 data.plot <- data.plot %>%
   mutate(method = factor(method, levels = names(colors)))
@@ -379,8 +380,9 @@ if(saveMode){
                              stab.up = getStability(projpred_X)$upper))
     }
     save(data.plot, file='bodyfat_complete_selection_plot.RData')
-} else
+} else {
     load('bodyfat_complete_selection_plot.RData')
+}
 
 ## colors <- c('loc.fdr' = '#819FF7',
 ##             'ci.90' = '#F78181',
@@ -411,7 +413,7 @@ plot1 <- data.plot %>%
    #       strip.text.y = element_text(color='black'))
 
 
-ggsave("graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.1)
+ggsave("graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.5)
 
 ## Stability plot
 plot2 <- data.plot %>%
@@ -545,8 +547,9 @@ if(saveMode){
         }
     }
     save(data.plot,file='minimal_subset_selection_parallel_plot.RData')
-} else
+} else {
     load('minimal_subset_selection_parallel_plot.RData')
+}
 
 facet.labels <- labeller(n = function(x){paste("n=",x,sep="")},
                          rho=function(x){paste("rho=",x,sep="")})
@@ -698,9 +701,10 @@ if(saveMode){
         }
     }
     save(data.plot, file='complete_selection_plot.RData')
-} else
+} else {
     load('complete_selection_plot.RData')
-
+}
+  
 facet.labels <- labeller(n = function(x){paste("n=",x,sep="")},
                          rho=function(x){paste("rho=",x,sep="")})
 

### 2019-12-04 paper/ref_approach.tex
minor cleaning

@@
 reference model instead of the observed responses $y$.
+Whatever the terminology or applied statistical framework, reference
+models offer a powerful approach to improving feature selection as we
+will demonstrate in the present paper.
 
@@
 
-Blah blah
-
-\subsection{Example of model selection with or without reference model}
+In this section, we will provide an initial motivation and intuition 
+for the use of reference models to improve feature selection procedures.
+We will start with a case study that is repeatedly used throughout
+the paper to illustrate the benefits of reference models before we dive deeper
+into the theoretical reasons why reference models help in feature selection.
+
+\subsection{Bodyfat example: Part 1}
 \label{intro-example}
@@
 \hypertarget{real-world-data}{%
-\subsection{Body fat example part 2}\label{real-world-data}}
+\subsection{Body fat example: Part 2}\label{real-world-data}}
 
@@
 \hypertarget{real-world-data}{%
-\subsection{Body fat example part 3}\label{real-world-data}}
+\subsection{Body fat example: Part 3}\label{real-world-data}}
 

### 2019-12-04 paper/ref_approach.tex
move a paragraph to a later section

@@
 Section \ref{intro-example}. We compare results with and without using
-a reference model on top of the procedure following our simple
-reference model approach outlined in \eqref{eq:ref_mod}. Figure
+a reference model on top of the procedure following a simple
+reference model approach outlined in Equation \eqref{eq:ref_mod} 
+of Section \ref{simulations}. Figure
 \ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant
@@
 \end{figure}
-
-In this example, we have used the reference model defined as a linear
-regression over some supervised principal components, because it is
-natural for a large number of correlating variables, has fairly good
-predictive performance and is computationally efficient. We do not
-argue that this is always the best choice and more sophisticated
-models can lead to even better results. Here the purpose of the
-experiments were to motivate the use of reference models in general,
-and as we needed to average results over a lot of repetitions per
-simulation condition, we preferred such a comparably simple and
-computationally fast reference model.
 
@@
 We conclude our complete selection experiments using the body fat dataset one
-more time, which was already described in Section \ref{intro-example}. We
+more time, which was initially described in Section \ref{intro-example}. We
 carry out two different analyses: one using the normal means problem
@@
 marginal with only small improvements.
+
+In this example, we have used the reference model defined as a linear
+regression over some supervised principal components, because it is
+natural for a large number of correlating variables, has fairly good
+predictive performance and is computationally efficient. We do not
+argue that this is always the best choice and more sophisticated
+models can lead to even better results. Here the purpose of the
+experiments were to motivate the use of reference models in general,
+and as we needed to average results over a lot of repetitions per
+simulation condition, we preferred such a comparably simple and
+computationally fast reference model.
 

### 2019-12-04 paper/ref_approach.tex
clean up Appendix A

@@
 
-As an another example, let us consider a candidate submodel in a
-feature selection process and let us refer to the parameter
-distribution of the submodel by $\pi$ and to the induced predictive
+\subsection*{Appendix A: Projective Predictions}
+
+The projective prediction (projpred) approach was developed and is thoroughly
+ described in \cite{paper:projpred}. In this appendix, we provide a high level
+  description of the method so that readers do not need to study \cite{paper:projpred} in detail
+in order to understand the main ideas behind projpred.
+
+ Let us refer to the parameter
+distribution of a given candidate submodel by $\pi$ and to the induced predictive
 distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
@@
 data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
-elpd using the reference model predictive distribution is equivalent
+elpd using the reference model's predictive distribution is equivalent
 to the minimisation of the Kullback-Leibler (KL) divergence from the
@@
 \begin{equation} \label{proj_as_filter}
-\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
+\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)
+\, \text{d} \tilde{y} 
+\quad \Leftrightarrow \quad 
+\underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D) \; || \; q_{\pi}(\tilde{y})] 
 \end{equation}
@@
 distribution, which is the general idea behind the projection
-predictive approach \cite[see][]{paper:projpred}. Again the reference
-model is acting as a filter, or substitute, on data.
-
-Relying on the idea of the reference model as a noise-filter, a
-generic reference model approach, which can be used on top of any
-feature selection procedure, consists of simply substituting the
-target observations with corresponding point predictions of the
-reference model, for instance, the posterior predictive
-means. Afterwards, any method for feature selection can be used. We do
-not argue that such a reference model approach should necessarily be
-used as is for feature selection in real applications. There are
-several more sophisticated reference model approaches available in the
-literature \cite[see,
-e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
-which are likely to yield even better results. Rather, the reason for
-focusing on this simple version is to enable a fair comparison between
-a reference model and a purely data based approach when otherwise
-using the same selection procedures. Other kinds of comparisons, as
-the one presented in Section \ref{intro-example}, work well as
-motivational examples but lack in terms of generality since the
-presence or absence of a reference model is not the only aspect
-differentiating the two procedures.
-% We will come back to the more
-% general comparison in Section \ref{comparison}.
-
-As a motivational example to the implications of using a reference
-model in feature selection problems, we show its application in the
-form of the projection predictive approach, which uses the reference
-model to project the posterior draws to the submodels
-\citep{paper:original_proj}. The \texttt{R}-package \texttt{projpred}
-(available at \url{https://CRAN.R-project.org/package=projpred})
-implements the projection in case of submodels in the family of the
-generalised linear models and, additionally, it provides a framework
-to choose the optimal submodel size through a predictive utility
-comparison between the submodels and the reference model.
-
+predictive approach \cite[see][]{paper:projpred}. 
 We now summarise the workflow of the projection predictive approach in
@@
 \begin{enumerate}
-\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
+\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model's posterior.
 \item Rank the covariates according to their relevance using some
@@
   preserve this order, starting from including only the highest ranked
-  covariate (the submodels are then naturally identified by their
-  model size). This is not strictly necessary but reduces the number
-  of submodels to consider in the following steps.
-\item For each submodel, project the reference model posterior draws as follows:
+  covariate. The submodels are then naturally identified by their
+  model size. This step is not strictly necessary but reduces the number
+  of submodels to considered in the following steps and thus reduces computation time.
+\item For each submodel $\pi$ selected in Step 2, project each of the reference model's posterior draws $\boldsymbol{\theta}_{*}^{s}$ as follows:
 \begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,\ldots,S \,,
+\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left[ p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right],
 \end{equation}
@@
 values related to the statistical unit (identified by the subscript
-$i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
+$i$), whereas $q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
 predictive distribution of the submodel. The projected draws
@@
 for the submodel.
-\item For each submodel (size), test the predictive performance, for example, via cross-validation.
+\item For each submodel (size), test the predictive performance for a chosen predictive utility score, for example, via cross-validation.
 \item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
@@
 
-Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
-in general, but in the special case of submodels for the family of
-generalised linear models, \eqref{eq:draw_by_draw} reduces to a
-maximum likelihood estimation problem, which can be easily optimised
+In general, Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
+However, in the special case of the submodels being
+generalised linear models with a likelihood coming from the exponential family, \eqref{eq:draw_by_draw} reduces to a
+maximum likelihood estimation problem, which can be easily solved
 \citep{paper:original_proj}. For further details on the projective

### 2019-12-06 code/bodyfat_comparison_varying_n.R
updated script to run with p=100

@@ -1,6 +1,6 @@
 ## BODYFAT COMPARISON ##
 rm(list=ls())
-args = commandArgs(trailingOnly=TRUE) 
+args = commandArgs(trailingOnly=TRUE)
 library(rstan)
 library(rstanarm)
 library(locfdr)
@@ -13,14 +13,14 @@ df[,4:19] <- scale(df[,4:19])
 df <- as.data.frame(df)
 n_full <- nrow(df)
 colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
-pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip", 
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
           "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
 target <- "siri"
 formula <- paste("siri~", paste(pred, collapse = "+"))
 p <- length(pred)
 df <- df[,c(target,pred)]
 
-p <- 1000
+p <- 100
 n <- as.numeric(args[1])
 times <- 100
 
@@ -32,7 +32,7 @@ lfdr_X_data <- matrix(0,nrow=times,ncol=p)
 ebmt_X_ref <- matrix(0,nrow=times,ncol=p)
 ebmt_X_data <- matrix(0,nrow=times,ncol=p)
 
-## Confidence intervals inclusion probabilities 
+## Confidence intervals inclusion probabilities
 ci80_X_ref <- matrix(0,nrow=times,ncol=p)
 ci90_X_ref <- matrix(0,nrow=times,ncol=p)
 ci95_X_ref <- matrix(0,nrow=times,ncol=p)
@@ -53,64 +53,64 @@ pred2 <- c(pred,colnames(dfr[,15:(p+1)]))
 
 for(i in 1:times){
   sel  <- sample(1:n_full,n,replace = T)
-  
+
   x <- dfr[sel,-1]
   y <- dfr[sel,1]
 
   nc <- 5
   dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p, sup.only = T, verbose = F)
   z <- predict(dr, x)
-  
+
   # fit the model
   model_data <- list(y=y,X=z,p=ncol(z),n=n,s_max=dr$sdev[1])
-  fit <- sampling(fit_model, data = model_data, 
-                  chains = 1, iter = 2000, seed = 45342)  
+  fit <- sampling(fit_model, data = model_data,
+                  chains = 1, iter = 2000, seed = 45342)
   predfun <- function(zt){
[…]

### 2019-12-06 code/bodyfat_comparison_varying_n_iteratedproj.R

@@ -19,7 +19,7 @@ formula <- paste("siri~", paste(pred, collapse = "+"))
 p <- length(pred)
 df <- df[,c(target,pred)]
 
-p <- 1000
+p <- 100
 n <- as.numeric(args[1])
 times <- 100
 
@@ -106,4 +106,4 @@ for(i in 1:times){
 }
 
 
-save.image(file=paste("bodyfat_type1_varyN_iteratedproj_n",n,".Rdata",sep=""))
+save.image(file=paste("bodyfat_type1_varyN_p100_iteratedproj_n",n,".Rdata",sep=""))

### 2019-12-06 paper/ref_approach.tex
update bodyfat plots
edits

@@
 Alternatively, reference models may also be used in an ad-hoc manner in combination with common feature selection methods.
-In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure.
+In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection method.
 % These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
@@
 workflow is covariate or feature selection, which is a special case of
-model reduction. Variable selection may have multiple goals.  First,
+model reduction. Feature (variable) selection may have multiple goals.  First,
 if the covariates themselves are of interest, we can use variable
@@
 \citet{paper:model_selection}, and for most recent methodological
-development see \citet{paper:projpred}.
+development see a paper by \citet{paper:projpred}.
 
@@
 In this section, we will provide an initial motivation and intuition 
-for the use of reference models to improve feature selection procedures.
+for the use of reference models to improve feature selection methods.
 We will start with a case study that is repeatedly used throughout
@@
 covariates which are anthropometric measurements (e.g., height, weight
-and thicknes of skin and fat in different body locations). The
-covariates are are highly correlated which causes additional
+and circumference of different body parts). The
+covariates are highly correlated which causes additional
 challenge in the feature selection. In total, we have 251
 observations. The goal is to find the model which is able to predict
-the amount of fat well while requiring least amount of
+the amount of body fat well while requiring least amount of
 measurements for a new person.
@@
 model performance. See Appendix A for brief review of projection
-predictive approach and \citet{paper:model_selection} and
-\citet{paper:projpred} for more details. The complete projpred procedure is implemented in the \texttt{projpred} R package.
+predictive approach, and papers by \citet{paper:model_selection} and
+\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} R package.
 
 The inclusion frequencies of each feature in the final model given 100
-bootstrap samples are depicted in Figure
-\ref{fig:inclusion_frequencies}. The projpred approach has only two
-variables, `abdomen' and `weight', with inclusion frequencies above
-50\% (`abdomen' is the only one included always), the third most
-included is `wrist' at 44\%, and the fourth is `height' at 35\%, while
-steplm has seven features above 50\%. Such a higher variability and
-lower stability of steplm can be observed also in the bootstrap model
-selection frequencies reported in Table
-\ref{tab:model_frequencies}. For example, the first five selected
-models have a cumulative frequency of 76\% with projpred, but only of
-14\% with steplm. In addition, the size of the selected model is much
-smaller when using projpred.
+bootstrap samples are shown in Figure
+\ref{fig:inclusion_frequencies}. In case of projpred there are two
+variables, `abdomen' and `weight', which have inclusion frequencies
+above 50\% (`abdomen' is the only one included always), the third most
+frequently included is `wrist' at 44\%, and the fourth one is `height'
+at 35\%.  The steplm approach has seven features with inclusion
+frequencies above 50\%. Such a higher variability and lower stability
+of steplm can be observed also in the bootstrap model selection
+frequencies reported in Table \ref{tab:model_frequencies}. For
+example, the first five selected models have a cumulative frequency of
+76\% with projpred, but only of 14\% with steplm. In addition, the
+sizes of the selected models with projpred are much smaller with
+steplm.
 \begin{figure}[tp]
@@
   \hline
-1 & abdom, weight & 39 & abdom, age, forearm, height, hip, neck, thigh, wrist & 4 \\
-2 & abdom, wrist & 10 & abdom, age, chest, forearm, height, neck, thigh, wrist & 4 \\
-3 & abdom, height & 10 & abdom, forearm, height, neck, wrist & 2 \\
-4 & abdom, height, wrist & 9 & abdom, forearm, neck, weight, wrist & 2 \\
-5 & abdom, weight, wrist & 8 & abdom, age, height, hip, thigh, wrist & 2 \\
-6 & abdom, chest, height, wrist & 2 & abdom, age, height, hip, neck, thigh, wrist & 2 \\
-7 & abdom, biceps, weight, wrist & 2 & abdom, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
-8 & abdom, height, weight, wrist & 2 & abdom, age, biceps, chest, height, neck, wrist & 2 \\
-9 & abdom, age, wrist & 2 & abdom, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
-10 & abdom, age, height, neck, thigh, wrist & 2 & abdom, age, ankle, biceps, weight, wrist & 2 \\
+1 & abdom., weight & 39 & abdom., age, forearm, height, hip, neck, thigh, wrist & 4 \\
+2 & abdom., wrist & 10 & abdom., age, chest, forearm, height, neck, thigh, wrist & 4 \\
+3 & abdom., height & 10 & abdom., forearm, height, neck, wrist & 2 \\
+4 & abdom., height, wrist & 9 & abdom., forearm, neck, weight, wrist & 2 \\
+5 & abdom., weight, wrist & 8 & abdom., age, height, hip, thigh, wrist & 2 \\
+6 & abdom., chest, height, wrist & 2 & abdom., age, height, hip, neck, thigh, wrist & 2 \\
+7 & abdom., biceps, weight, wrist & 2 & abdom., age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
+8 & abdom., height, weight, wrist & 2 & abdom., age, biceps, chest, height, neck, wrist & 2 \\
+9 & abdom., age, wrist & 2 & abdom., age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
+10 & abdom., age, height, neck, thigh, wrist & 2 & abdom., age, ankle, biceps, weight, wrist & 2 \\
 %   \hline
@@
 
-In the first two rows of Table \ref{tab:model_performances}, we report the
+The first two rows of Table \ref{tab:model_performances} show the
 predictive performances, in terms of cross-validated root mean square
-error (RMSE), of the full model and the selected models using either
-the projection predictive approach or the stepwise backward
-elimination.  There is no difference in predictive performance of the
-selected models by different approaches even if there is difference in
-the selected features.
+error (RMSE), of the full model and the selected models using projpred
+or steplm.  There is no signfiant difference in predictive performance
+of the selected models by different approaches even if there is
+difference in the selected features. This can be explained by high
+correlation between the features and different combinations can
+provide similar predictive accuracy.
 
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy features. In the last two rows of Table
-\ref{tab:model_performances}, we report the cross-validated RMSE, the size of
-the selected model and the number of selected noisy features using
-either the projection predictive approach or the stepwise backward
-elimination.  The projection predictive approach has similar
-predictive performance and the same submodel size as in the first
-experiment, whereas the stepwise regression has worse predictive
-performance and selects a much larger submodel including a large
-number of irrelevant features.
+unrelated noisy features. The last two rows of Table
+\ref{tab:model_performances} show the cross-validated RMSE, the size
+of the selected model and the number of selected noisy features using
+projpred or steplm.  The projection predictive approach has similar
+predictive performance and the same number of selected features as
+with the original data, whereas the stepwise regression has worse
+predictive performance and the number of selected features is much
+higher and include a large number of irrelevant features.
 
@@
   \hline
-original & projpred & 4.35 & 4.47 & 2 &   \\
+bodyfat & projpred & 4.35 & 4.47 & 2 &   \\
 & steplm & 4.38 & 4.47 & 7 &  \\
@@
 \end{tabular}
-\caption{Model predictive performances with original data (first two
+\caption{Predictive performances with original bodyfat data (first two
   rows) and with extra noisy features (last two rows) estimated with
   10-fold cross-validation. Abbreviations: Full = full model; Selected =
-  selected submodel; \# Selected = total number of features selected;
-  \# Selected noisy = number of extra noisy features selected.}
+  selected submodel; \# Selected = selected number of features;
+  \# Selected noisy = selected number of extra noisy features.}
 \label{tab:model_performances}
@@
 reference model. Sometimes including all the available features in an
-elaborate model can often be computationally demanding.  In such a
+elaborate model can be computationally demanding.  In such a
 case, even simpler screening or dimensionality reduction techniques,
@@
 obscure the relevance of the covariates in relation to the target
-variable of interest. Let us consider the following simple
+variable of interest. We demonstrate with the following simple
 explanatory example taken from \cite{paper:projpred}. The data
@@
   $f$ respectively on the x and y axis. Data are generated according to 
-  procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
+  \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
   $k=100$, $p=1000$.\\}
@@
 provide such additional information that would improve predictive
-performance. The usual reason for this is that the relevant features
-not in the minimal are subset highly correlated with features already in
+performance significantly. The usual reason for this is that the relevant features
+which are not in the minimal subset are highly correlated with features already in
 the minimal subset. We will return to a problem of finding all
@@
 When the variable selection is repeated with different simulated data
-sets, there is some variability in which variables are selected. We
+sets, there is some variability in selected variables. We
 measure the stability of variable selection by computing the entropy
@@
 would always select different set of variables.
-Figure \ref{fig:entropy} reports the entropy scores for the different compared
+Figure \ref{fig:entropy} shows the entropy scores for the different compared
 methods. Lower entropy corresponds to a more stable
@@
 Section \ref{intro-example}. We compare results with and without using
-a reference model on top of the procedure following a simple
-reference model approach outlined in Equation \eqref{eq:ref_mod} 
-of Section \ref{simulations}. Figure
-\ref{fig:bodyfat_step_refvsdata} shows the number of irrelevant
-features included in the final model and the out-of-sample root mean
-square error (RMSE). Results are based on 100 bootstrap samples on the
-whole dataset, and the predictive performance is tested on the
-observations excluded at each bootstrap sample. We observe that the
-reference model reduces the number of irrelevant features included in
-the final model. This leads to less overfitting and thus to improved
-out-of-sample predictive performance in terms of RMSE. The reference
-model approach applied to the stepwise backward regression achieves
-outstanding improvements considering its simplicity, yet it does not
-reach the goodness of the much more sophisticated projective
+a simple reference model approach outlined in \eqref{eq:ref_mod} with
+steplm. Figure \ref{fig:bodyfat_step_refvsdata} shows the number of
+irrelevant features included in the final model and the out-of-sample
+root mean square error (RMSE). Results are based on 100 bootstrap
+samples on the whole dataset, and the predictive performance is tested
+on the observations excluded at each bootstrap sample. We observe that
+the reference model reduces the number of irrelevant features included
+in the final model. This leads to less overfitting and thus to
+improved out-of-sample predictive performance in terms of RMSE. The
+reference model approach applied to the stepwise backward regression
+achieves outstanding improvements considering its simplicity, yet it
+does not reach the goodness of the much more sophisticated projective
 prediction approach (see results of Section \ref{intro-example}).
@@
 The projection predictive approach was originally designed for the minimal subset
-feature selection, but we generalize it here for the complete
+feature selection, but we test here a simple iterative variant for the complete
 feature selection case. In addition, we analyse the benefits of the reference
-model approach in combination with three other complete feature
-selection approaches.
-
-As criteria of selection performance, we evaluate the average false
+model approach in combination with three other
+methods which have been originally designed for complete feature selection.
+
+As the criteria of selection performance, we evaluate the average false
 discovery rate and the average
@@
 
-We can use the projection predictive approach for complete feature
+We modify the projection predictive approach for complete feature
 selection by using it iteratively.  Applying the straightforward
@@
 the stopping rule (see Algorithm \ref{alg:iterated_proj}).
-The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
+The choice of the hyperparameter $\alpha$ is non-trivial, and we have 
 observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
@@
 
-\subsection{Alternative complete feature selection approaches}
+\subsection{Alternative complete feature selection methods}
 
@@
 
-We consider three alternative complete selection procedures,
+We consider three alternative complete selection methods,
  the control of the local
@@
 
-The empirical Bayes median procedure consists of fitting a Bayesian
+The empirical Bayes median approach consists of fitting a Bayesian
 model with a prior composed by a mixture of a delta spike in zero and
@@
 
-All of these methods provide a complete selection procedure and we
+All of these methods provide a complete selection approach and we
 compare their performance with and without using a reference model.
@@
 
-To investigate the performance of the four complete selection procedures,
+To investigate the performance of the four complete selection approaches,
 we are going to use simulations based on the normal means problem.
@@
 \begin{equation} \label{eq:fisher_transformation}
-T_{F}(r_{j})\overset{ind}{\sim} \N(T_{F}(\rho_{j}),\frac{1}{n-3}), \quad j=1,\ldots,p.
+T_{F}(r_{j})\overset{ind}{\sim} \N\left(T_{F}(\rho_{j}),\frac{1}{n-3}\right), \quad j=1,\ldots,p.
 \end{equation}
@@
 principled approach would be to use cross-validation to select the
-threshold as done in \cite{paper:projpred}.
+threshold as done by \citet{paper:projpred}.
 
@@
 enough information to identify the relevant covariates. The iterative
-projection predictive approach has good false discovery rate in all cases, and the sensitivity is good except when the number of observations and the correlation level
-are small. Tuning $\alpha$ might lead to improved selection, yet
-the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
-utility score for misspecified models with cross-validation \citep{bengio2004no}.
+projpred has good false discovery rate in all cases, and the
+sensitivity is good except when the number of observations and the
+correlation level are small. Tuning $\alpha$ might lead to improved
+selection, yet the main source of poor performance could well be the
+miscalibration of the uncertainty of the predictive utility score for
+misspecified models with cross-validation \citep{bengio2004no}.
 
@@
 
-We conclude our complete selection experiments using the body fat dataset one
-more time, which was initially described in Section \ref{intro-example}. We
-carry out two different analyses: one using the normal means problem
-framework and another one using selection via stepwise backward
-regression. In the former, we add noisy uncorrelated covariates to the
-original data up to a total of 1000 features. These covariates are
-normally distributed and scaled as the original covariates. We compute
+We conclude our complete selection experiments using the body fat
+dataset one more time. As earlier we add noisy uncorrelated covariates
+to the original data to get a total of 100 features.
+Since we do not have a ground truth available with regard the original
+covariates of the data, we assume it is reasonable to consider all of
+them relevant, at least to some degree. The artificially added
+features are naturally irrelevant by construction.
+We compute
 correlations between each variable and the target variable, that is
@@
 rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
-instead estimate it from the data. The methods we compare are those
-used in Section \ref{complete-selection}: the control of the local
+instead estimate it from the data. We compare the control of the local
 false discovery rate (loc.fdr), the empirical Bayes median (EB.med)
@@
 Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
-against the false discovery rate. Since we do not have a ground truth
-available with regard the original covariates of the data, we believe
-it is reasonable to consider all of them relevant, at least to some
-degree. The artificially added features are naturally irrelevant by
-construction. In almost all of the bootstrapped subsamples, the reference
+against the false discovery rate.  In almost all of the bootstrapped
+subsamples, the reference
 model improves the selection both in terms of sensitivity and false
@@
 the selection becomes more challenging (i.e., lower number of
-observations). Figure \ref{fig:bodyfat_stability} shows the stability
+observations).
+The great performance of projpred in minimal subset selection is not
+carried over for the complete feature selection with iterative
+projpred, and the methods designed for the complete feature selection
+perform better.
+Figure \ref{fig:bodyfat_stability} shows the stability
 results using the measure by
@@
 specific selection method. These benefits apply to a large family of
-different approaches all involving a reference model in one way or the
+different methods all involving a reference model in one way or the
 other. Some of these approaches have been present in the literature
@@
 
-While the projective prediction approach was not designed for the
-complete feature selection, the iterative version retains the
-excellent false discovery rate property. The iterative projection
-predictive approach had lower sensitivity than the other methods, and
-it is left for future resarch whether it is possible to improve
-sensitivity without sacrifying the good false discovery rate.
+The projective prediction approach was not designed for the complete
+feature selection. We tested a simple iterative version of projpred,
+with mixed results and the methds specifically designed for complete
+feature selection (especially loc.fdr) performed better in the
+experiments. It is left for future resarch whether it is possible to
+design a better projection predictive approach based complete feature
+selection method.
 
@@
 The projective prediction (projpred) approach was developed and is thoroughly
- described in \cite{paper:projpred}. In this appendix, we provide a high level
-  description of the method so that readers do not need to study \cite{paper:projpred} in detail
-in order to understand the main ideas behind projpred.
-
- Let us refer to the parameter
-distribution of a given candidate submodel by $\pi$ and to the induced predictive
+ described by \cite{paper:projpred}. In this appendix, we provide a high level
+  description of the method so that readers do not need to study paper by \cite{paper:projpred} in detail
+to understand the main ideas behind projpred.
+
+The parameter
+distribution of a given candidate submodel is denoted by $\pi$ and the induced predictive
 distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
@@
 \item For each submodel (size), test the predictive performance for a chosen predictive utility score, for example, via cross-validation.
+Fast cross-validation can be performed using using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
+\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.
 \item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
@@
 \citep{paper:original_proj}. For further details on the projective
-prediction workflow and implementation see \cite{paper:projpred}.
+prediction workflow and implementation see paper by \citet{paper:projpred}.
 

### 2019-12-07 paper/ref_approach.tex
next round of proofreading

@@
     \author{
-    Federico Pavone, 
-  Juho Piironen,
-  Paul-Christian B\"{u}rkner
-  and Aki Vehtari \footnote{Department of Computer Science, Aalto University, Finland.}
+    Federico Pavone \footnote{Department of Computer Science, Aalto University, Finland.} $\,$\footnote{Correspondence concerning this article should be addressed to TODO.}, 
+  Juho Piironen$^*$,
+  Paul-Christian B\"{u}rkner$^*$
+  and Aki Vehtari$^*$
   }
@@
 As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability leading to improved model selection performance.
-Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive variable selection approach.
+Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive feature selection approach.
 Alternatively, reference models may also be used in an ad-hoc manner in combination with common feature selection methods.
-In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection method.
+In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative feature selection methods with and without reference models.
+Our results indicate that the use of reference models generally translates into better and more stable feature selection.
+Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative feature selection methods independently of whether or not they use reference models.
 % These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
@@
 In statistical applications, one of the main steps in the modelling
-workflow is covariate or feature selection, which is a special case of
-model reduction. Feature (variable) selection may have multiple goals.  First,
-if the covariates themselves are of interest, we can use variable
-selection to infer which variables contain predictive information
+workflow is feature selection, which is a special case of
+model reduction. Feature selection (also known as variable or 
+covariate selection) may have multiple goals.  First,
+if the features themselves are of interest, we can use feature
+selection to infer which features contain predictive information
 about the target variable.  Second, as simpler models come with the
 advantages of reduced measurement costs and improved interpretability,
-we may be interested in finding the minimal subset of covariates which
+we may be interested in finding the minimal subset of features which
 still provides good predictive performance (or good balance between
@@
 of a reference model, which can be, for example, a full-encompassing
-model including all covariates.  The main assumption under any
+model including all features.  The main assumption under any
 reference model approach is that we operate in an
@@
 using neural networks, which typically perform very well in terms of
-prediction, but whose covariates are difficult to be understood in
+prediction, but whose features are difficult to be understood in
 terms of relevance.  \cite{paul2008preconditioning}, using the term
@@
 
+This paper is structured as follows. In Section
+\ref{ref-intro}, we review the concept of the reference
+model, its benefits with examples and how it can be used as a filter
+on data in a simple way. In Section \ref{comparison-minimal-subset} and 
+Section \ref{comparison-complete-subset}, we show the
+benefits of a reference model approaches for minimal and complete 
+feature selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
+
 \section{Reference models in feature selection}
-\label{intro-example}
+\label{ref-intro}
 
@@
 \subsection{Bodyfat example: Part 1}
-\label{intro-example}
+\label{bodyfat-1}
 
 To motivate the further discussion and experiments, we start by simple
-variable selection example using body fat data by \citet{johnson1996fitting}.
-We compare projection predictive approach (\emph{projpred},
+feature selection example using body fat data by \citet{johnson1996fitting}.
+We compare the projective prediction approach (\emph{projpred},
 \citet{paper:projpred}) which uses a reference model, and classic
@@
 expensive procedure. Additionally, we have information about 13
-covariates which are anthropometric measurements (e.g., height, weight
+features which are anthropometric measurements (e.g., height, weight
 and circumference of different body parts). The
-covariates are highly correlated which causes additional
+features are highly correlated which causes additional
 challenge in the feature selection. In total, we have 251
@@
 comparison we don't fix any of the variables.  The steplm approach is
-carried out combining the \texttt{step} and \texttt{lm} functions.
+carried out combining the \texttt{step} and \texttt{lm} functions in R.
 
 For the selection via projpred, the Bayesian reference model includes
-all the covariates using a regularised horseshoe prior~\citep{paper:rhs} on the
-covariate coefficients. Submodels are explored using
+all the features using a regularised horseshoe prior~\citep{paper:rhs} on the
+feature coefficients. Submodels are explored using
 forward search (the results are not sensitive to whether forward or
@@
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy features. The last two rows of Table
+unrelated noisy features so that there are 100 feature in total. 
+The last two rows of Table
 \ref{tab:model_performances} show the cross-validated RMSE, the size
 of the selected model and the number of selected noisy features using
-projpred or steplm.  The projection predictive approach has similar
+projpred or steplm. The results show that projpred has similar
 predictive performance and the same number of selected features as
@@
 forward or backward search, which can lead to selection induced
-overfitting, but even with 100 covariates, projpred is able to select a
+overfitting, but even with 100 features, projpred is able to select a
 submodel with similar performance as the full model. In this example, the two
@@
 However, as we show in the present paper, one of the primary difference 
-with respect to quality of the variable selection is indeed whether or 
-not a reference model approach is applied.
+with respect to quality of the feature selection is indeed whether or 
+not a reference model is applied.
 
@@
 used as a reference model, there is no additional cost of using a
-reference model. Sometimes including all the available features in an
+reference model as it was estimated as part of the analysis anyway.
+Sometimes including all the available features in an
 elaborate model can be computationally demanding.  In such a
@@
 
-The remainder of the paper is structured as follows. In Section
-\ref{reference-model-approach}, we review the concept of the reference
-model, its benefits with examples and how it can be used as a filter
-on data in a simple way. In Section \ref{comparison-minimal-subset} and 
-Section \ref{comparison-complete-subset}, we show the
-benefits of a reference model approaches for minimal and complete 
-feature selection, respectively, before we illustrate the use 
-of a reference model in a detailed case study of the 'body fat' data.
-Finally, we end with a conclusion in Section \ref{conclusion}.
-
 \hypertarget{reference-model-approach}{%
@@
 the data. The noise is the main source of the instability and tends to
-obscure the relevance of the covariates in relation to the target
+obscure the relevance of the features in relation to the target
 variable of interest. We demonstrate with the following simple
@@
 where $f$ is the latent variable of interest of which $Y$ is a noisy
-observation. The first $k$ covariates are strongly related to the
+observation. The first $k$ features are strongly related to the
 target variable $Y$ and correlated among themselves. Precisely, $\rho$
-is the correlation among any pair of the first $k$ covariates, whereas
+is the correlation among any pair of the first $k$ features, whereas
 $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
-any relevant covariate and, respectively, $f$ and $Y$. If we had an
+any relevant feature and, respectively, $f$ and $Y$. If we had an
 infinite amount of observations, the sample correlation would be equal
@@
 ideal asymptotic regime, this correlation would still remain a biased
-indicator of the true relevance of each covariate (represented by the
+indicator of the true relevance of each feature (represented by the
 correlation between $X_j$ and $f$) due to the intrinsic noisy nature
@@
 When using a reference model, we first obtain predictions for $f$
-using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account
+using all the features $\{X_{j}\}_{j=1}^{p}$ taking into account
 that we have only observed the noisy representation $Y$ of $f$. If our
@@
 which improves the accuracy in the estimation of the relevance of the
-covariates.  Figure \ref{fig:correlation} illustrates this process in
+features.  Figure \ref{fig:correlation} illustrates this process in
 the form of a scatter plot of (absolute) correlations of the
-covariates with $Y$ against the corresponding correlations with the
+features with $Y$ against the corresponding correlations with the
 predictions of a reference model (in this case the posterior
@@
 
-In the bodyfat example above, we desired at the same time good
-predictive performance and selection of a smaller number of
-features. When the goal is to select a minimal subset of features,
+In the bodyfat example above, our two simultaneous goals were to 
+obtain good predictive performance and to select a smaller number of features. 
+When the goal is to select a minimal subset of features,
 which have similar predictive performance as the full model, we call it
@@
 exclude features which have some predictive information about the
-target, but given the minimal subset these features are not able to
+target but, given the minimal subset, these features are not able to
 provide such additional information that would improve predictive
-performance significantly. The usual reason for this is that the relevant features
+performance in a substantial manner.
+The usual reason for this is that the relevant features
 which are not in the minimal subset are highly correlated with features already in
@@
 but the minimal subset feature selection stays unreliable. Stepwise
-Bayesian linear regression model without a reference model is better
-than steplm without a reference model, but the minimal subset feature
-selection is unreliable.
-
-When the variable selection is repeated with different simulated data
-sets, there is some variability in selected variables. We
-measure the stability of variable selection by computing the entropy
+Bayesian linear regression is better than steplm when comparing both methods with
+and without a reference model, respectively. However, the minimal subset feature
+selection of the Bayesian linear regression is still less reliable than projpred.
+
+When the feature selection is repeated with different simulated data
+sets, there is some variability in the selected features. We
+measure the stability of feature selection by computing the entropy
 of observed distribution over different models. The smallest entropy
-would be obtained if the approach always selects the same set of
-variables, and the largest entropy would be observed if the approach
-would always select different set of variables.
+would be obtained if the approach always selected the same set of
+features, and the largest entropy would be observed if the approach
+would always selected different sets of features.
 Figure \ref{fig:entropy} shows the entropy scores for the different compared
@@
 selection. Highly correlated predictive features may happen to be
-alternately selected, making the measure of the stability of the
+selected alternately, thus making stability estimation of the
 selection a non-trivial task. Entropy cannot distinguish the interchangeability 
@@
 The use of a reference model
-improves slightly the stability of steplm in feature selection. The
-projection predictive approach results to be far more stable than all
-other approaches. This is likely due to projpred being based on better
+improves the stability of steplm in feature selection slightly, while it makes
+little difference for the Bayesian linear regression. The
+projpred approach turns out to be far more stable than all
+other methods. This is likely due to projpred being based on better
 decision theoretical formulation which 1) takes into account the full
@@
 
-\hypertarget{real-world-data}{%
-\subsection{Body fat example: Part 2}\label{real-world-data}}
-
-Here we repeat the selection of Section \ref{intro-example} via
+\hypertarget{bodyfat-2}{%
+\subsection{Body fat example: Part 2}\label{bodyfat-2}}
+
+Here we repeat the selection of Section \ref{bodyfat-1} via
 stepwise backward regression. In this case, the overall number of
-covariates (original plus noisy) is 100, as it was in the last part of
-Section \ref{intro-example}. We compare results with and without using
+features (original plus noisy) is 100, as it was in the last part of
+Section \ref{bodyfat-1}. We compare results with and without using
 a simple reference model approach outlined in \eqref{eq:ref_mod} with
@@
 does not reach the goodness of the much more sophisticated projective
-prediction approach (see results of Section \ref{intro-example}).
+prediction approach (see results of Section \ref{bodyfat-1}).
 \begin{figure}[tp]
@@
 The projection predictive approach was originally designed for the minimal subset
-feature selection, but we test here a simple iterative variant for the complete
-feature selection case. In addition, we analyse the benefits of the reference
+feature selection but we will test a simple iterative variant for the complete
+feature selection case in the section.
+ In addition, we analyse the benefits of the reference
 model approach in combination with three other
-methods which have been originally designed for complete feature selection.
-
+methods which have been specifically designed for complete feature selection. 
 As the criteria of selection performance, we evaluate the average false
@@
 features, which yield to a model with a predictive performance
-comparable to the full model one.  The iterative projection repeats
+comparable to the full model's predictive performance. 
+ The iterative projection repeats
 the projpred selection for different iterations, at each time
-excluding from the search the features selected in the previous
-iterations. At each iteration the selected submodel size corresponds to the
+excluding the features selected in the previous
+iterations from the search.
+ At each iteration the selected submodel size corresponds to the
 one having a predictive performance close enough to the baseline
@@
 \end{equation}
-where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
+where $i$ indexes the submodel size and ``best'' stands for the best predictive explored submodel
 at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
@@
 In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package that corresponds to $\alpha=0.16$.
+\texttt{R}-package, that is, $\alpha=0.16$.
 
@@
 % regularised horseshoe (RHS) prior \citep{paper:rhs}, which in our experience
-% scales better to higher number of covariates as compared to other
+% scales better to higher number of features as compared to other
 % horseshoe-like priors.
@@
 %based on posterior credible intervals using the regularised horseshoe
-%prior in which we select covariates whose 90\% credible intervals
+%prior in which we select features whose 90\% credible intervals
 %excludes zero (\emph{ci.90}) \note{Reference for this?}.
@@
 by 90\% posterior credible intervals is done using the regularised
-horseshoe prior and selecting those features whose posterior
+horseshoe prior \Citep{paper:rhs} and selecting those features whose posterior
 distribution does not include zero in the interval between the 5\% and
-the 95\% quantiles (cite).
+the 95\% quantiles.
 
@@
 That is, in the data condition, we apply the method on the original
-data $y$ while, in the referece model condition, we replace $y$ by
+data $y$ while, in the reference model condition, we replace $y$ by
 their mean predictions $\hat{y}$ based on the reference model.
@@
 In our experiments, we retrieve the normal means problem from the
-sample correlations between the target and the covariates using the
+sample correlations between the target and the features using the
 Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
 continuous target random variable $Y,$ a set of $p$ continuous
-covariates $\{X_{j}\}_{j=1}^{p}$, and denote
+features $\{X_{j}\}_{j=1}^{p}$, and denote
 $\rho_{j}=\Cor(Y,X_{j})$. Further, suppose we have observed $n$
@@
 the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
-$j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
+$j$-th feature $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
 Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
@@
 
-We use different levels of correlation $\rho\in\{0.3,0.5\}$ and numbers of
-observations $n\in\{50,70,100\}$. The total number of covariates $p$
-and the number of relevant covariates $k$ are fixed to $p = 1000$ and
+In our simulations, we use different levels of correlation 
+$\rho\in\{0.3,0.5\}$ and numbers of
+observations $n\in\{50,70,100\}$. The total number of features $p$
+and the number of relevant features $k$ are fixed to $p = 1000$ and
 $k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
+more challenging the feature selection is. For this example, \citet{paper:projpred} proposed to
 use a reference model which a Bayesian linear regression using the first five
-supervised principal components (SPC) as covariates and imposing an hierarchical prior on
+supervised principal components (SPC) as features and imposing an hierarchical prior on
 their coefficients:
@@
 % \cite{paper:rhs} by setting the prior guess of the number of relevant
-% covariates to one in order to achieve the highest possible
+% features to one in order to achieve the highest possible
 % shrinkage. The results are not sensitive with respect to the specific
@@
 the reference model are smaller since the raw data already provide
-enough information to identify the relevant covariates. The iterative
+enough information to identify the relevant features. The iterative
 projpred has good false discovery rate in all cases, and the
@@
 
-\hypertarget{real-world-data}{%
-\subsection{Body fat example: Part 3}\label{real-world-data}}
+\hypertarget{bodyfat-2}{%
+\subsection{Body fat example: Part 3}\label{bodyfat-3}}
 
 We conclude our complete selection experiments using the body fat
-dataset one more time. As earlier we add noisy uncorrelated covariates
+dataset one more time. As earlier we add noisy uncorrelated features
 to the original data to get a total of 100 features.
 Since we do not have a ground truth available with regard the original
-covariates of the data, we assume it is reasonable to consider all of
+features of the data, we assume it is reasonable to consider all of
 them relevant, at least to some degree. The artificially added
@@
 rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
-instead estimate it from the data. We compare the control of the local
-false discovery rate (loc.fdr), the empirical Bayes median (EB.med)
+instead estimate it from the data. We compare iteration projections, 
+the control of the local false discovery rate (loc.fdr), 
+the empirical Bayes median (EB.med),
 and the selection by posterior credible intervals at level 90\%
@@
 carried over for the complete feature selection with iterative
-projpred, and the methods designed for the complete feature selection
-perform better.
+projpred, and the methods specifically designed for the complete 
+feature selection perform better.
 Figure \ref{fig:bodyfat_stability} shows the stability
@@
 filter on the observed target values on top of different widely used
-variable selection methods. Overall, using a reference model leads to
+feature selection methods. Overall, using a reference model leads to
 more accurate and stable selection results independently of the
@@
 different methods all involving a reference model in one way or the
-other. Some of these approaches have been present in the literature
+other. Some of these approaches have been present in the literature for some time
 \cite[e.g., see references in][]{vehtari2012survey,paper:projpred}
@@
 
-We argue that, whenever it is possible to come up with a reasonable
+We argue that, whenever it is possible to construct a reasonable
 reference model, it should be employed on top of the preferred
@@
 single procedure \citep{paper:projpred}.  In summary, we would
-strongly recommend using projective predictions for feature selection
-if possible and feasible. However, if this is not an option in a given
+strongly recommend using projective predictions for minimal subset
+ feature selection if possible and feasible. 
+ However, if this is not an option in a given
 situation, we would in any case recommend using a reference model on
@@
 feature selection. We tested a simple iterative version of projpred,
-with mixed results and the methds specifically designed for complete
-feature selection (especially loc.fdr) performed better in the
-experiments. It is left for future resarch whether it is possible to
-design a better projection predictive approach based complete feature
-selection method.
+with mixed results and the methods specifically designed for complete
+feature selection (especially loc.fdr) performed better in our
+experiments. It is left for future resarch to develop 
+a better projective prediction approach for complete feature
+selection problems.
 
@@
 with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
-covariates for which we want to obtain a minimally relevant
+features for which we want to obtain a minimally relevant
 subset. Than, the main steps are the following:
@@
 \item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model's posterior.
-\item Rank the covariates according to their relevance using some
+\item Rank the features according to their relevance using some
   heuristics and consider as candidate submodels only those which
   preserve this order, starting from including only the highest ranked
-  covariate. The submodels are then naturally identified by their
+  feature. The submodels are then naturally identified by their
   model size. This step is not strictly necessary but reduces the number
@@
 predictive distribution of the reference model with parameters fixed
-at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
+at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the feature
 values related to the statistical unit (identified by the subscript

### 2019-12-07 paper/ref_approach.tex
change 'feature' to 'variable'

@@
 \hypersetup{unicode=true,
-            pdftitle={The reference model approach in feature selection},
+            pdftitle={The reference model approach in variable selection},
             pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
@@
 
-\title{Using reference models in feature selection 
+\title{Using reference models in variable selection 
 	\vspace{.1in}}
@@
 \begin{abstract}
-  Feature selection, or more generally, model reduction is an important aspect of the statistical workflow aiming to provide insights from data.
-In this paper we discuss and demonstrate the benefits of using a reference model in feature selection.
+  Variable selection, or more generally, model reduction is an important aspect of the statistical workflow aiming to provide insights from data.
+In this paper we discuss and demonstrate the benefits of using a reference model in variable selection.
 A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
 As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability leading to improved model selection performance.
-Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive feature selection approach.
-Alternatively, reference models may also be used in an ad-hoc manner in combination with common feature selection methods.
-In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative feature selection methods with and without reference models.
-Our results indicate that the use of reference models generally translates into better and more stable feature selection.
-Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative feature selection methods independently of whether or not they use reference models.
+Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive variable selection approach.
+Alternatively, reference models may also be used in an ad-hoc manner in combination with common variable selection methods.
+In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative variable selection methods with and without reference models.
+Our results indicate that the use of reference models generally translates into better and more stable variable selection.
+Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods independently of whether or not they use reference models.
 % These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
@@
 In statistical applications, one of the main steps in the modelling
-workflow is feature selection, which is a special case of
-model reduction. Feature selection (also known as variable or 
+workflow is variable selection, which is a special case of
+model reduction. Variable selection (also known as feature or 
 covariate selection) may have multiple goals.  First,
-if the features themselves are of interest, we can use feature
-selection to infer which features contain predictive information
-about the target variable.  Second, as simpler models come with the
+if the variables themselves are of interest, we can use variable
+selection to infer which variables contain predictive information
+about the target. Second, as simpler models come with the
 advantages of reduced measurement costs and improved interpretability,
-we may be interested in finding the minimal subset of features which
+we may be interested in finding the minimal subset of variables which
 still provides good predictive performance (or good balance between
@@
 of a reference model, which can be, for example, a full-encompassing
-model including all features.  The main assumption under any
+model including all variables.  The main assumption under any
 reference model approach is that we operate in an
@@
 using neural networks, which typically perform very well in terms of
-prediction, but whose features are difficult to be understood in
+prediction, but whose variables are difficult to be understood in
 terms of relevance.  \cite{paul2008preconditioning}, using the term
@@
 Whatever the terminology or applied statistical framework, reference
-models offer a powerful approach to improving feature selection as we
+models offer a powerful approach to improving variable selection as we
 will demonstrate in the present paper.
@@
 benefits of a reference model approaches for minimal and complete 
-feature selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
-
-\section{Reference models in feature selection}
+variable selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
+
+\section{Reference models in variable selection}
 \label{ref-intro}
@@
 In this section, we will provide an initial motivation and intuition 
-for the use of reference models to improve feature selection methods.
+for the use of reference models to improve variable selection methods.
 We will start with a case study that is repeatedly used throughout
 the paper to illustrate the benefits of reference models before we dive deeper
-into the theoretical reasons why reference models help in feature selection.
+into the theoretical reasons why reference models help in variable selection.
 
@@
 To motivate the further discussion and experiments, we start by simple
-feature selection example using body fat data by \citet{johnson1996fitting}.
+variable selection example using body fat data by \citet{johnson1996fitting}.
 We compare the projective prediction approach (\emph{projpred},
@@
 expensive procedure. Additionally, we have information about 13
-features which are anthropometric measurements (e.g., height, weight
+variables which are anthropometric measurements (e.g., height, weight
 and circumference of different body parts). The
-features are highly correlated which causes additional
-challenge in the feature selection. In total, we have 251
+variables are highly correlated which causes additional
+challenge in the variable selection. In total, we have 251
 observations. The goal is to find the model which is able to predict
@@
 For the selection via projpred, the Bayesian reference model includes
-all the features using a regularised horseshoe prior~\citep{paper:rhs} on the
-feature coefficients. Submodels are explored using
+all the variables using a regularised horseshoe prior~\citep{paper:rhs} on the
+variable coefficients. Submodels are explored using
 forward search (the results are not sensitive to whether forward or
@@
 
-The inclusion frequencies of each feature in the final model given 100
+The inclusion frequencies of each variable in the final model given 100
 bootstrap samples are shown in Figure
@@
 frequently included is `wrist' at 44\%, and the fourth one is `height'
-at 35\%.  The steplm approach has seven features with inclusion
+at 35\%.  The steplm approach has seven variables with inclusion
 frequencies above 50\%. Such a higher variability and lower stability
@@
 of the selected models by different approaches even if there is
-difference in the selected features. This can be explained by high
-correlation between the features and different combinations can
+difference in the selected variables. This can be explained by high
+correlation between the variables and different combinations can
 provide similar predictive accuracy.
@@
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy features so that there are 100 feature in total. 
+unrelated noisy variables so that there are 100 variable in total. 
 The last two rows of Table
 \ref{tab:model_performances} show the cross-validated RMSE, the size
-of the selected model and the number of selected noisy features using
+of the selected model and the number of selected noisy variables using
 projpred or steplm. The results show that projpred has similar
-predictive performance and the same number of selected features as
+predictive performance and the same number of selected variables as
 with the original data, whereas the stepwise regression has worse
-predictive performance and the number of selected features is much
-higher and include a large number of irrelevant features.
+predictive performance and the number of selected variables is much
+higher and include a large number of irrelevant variables.
 
@@
 \hline
-+ noisy features & projpred & 4.58 & 4.54 & 2 & 0  \\
++ noisy variables & projpred & 4.58 & 4.54 & 2 & 0  \\
 & steplm & 5.89 & 5.43 & 19 & 13 \\
@@
 \caption{Predictive performances with original bodyfat data (first two
-  rows) and with extra noisy features (last two rows) estimated with
+  rows) and with extra noisy variables (last two rows) estimated with
   10-fold cross-validation. Abbreviations: Full = full model; Selected =
-  selected submodel; \# Selected = selected number of features;
-  \# Selected noisy = selected number of extra noisy features.}
+  selected submodel; \# Selected = selected number of variables;
+  \# Selected noisy = selected number of extra noisy variables.}
 \label{tab:model_performances}
@@
 forward or backward search, which can lead to selection induced
-overfitting, but even with 100 features, projpred is able to select a
+overfitting, but even with 100 variables, projpred is able to select a
 submodel with similar performance as the full model. In this example, the two
@@
 However, as we show in the present paper, one of the primary difference 
-with respect to quality of the feature selection is indeed whether or 
+with respect to quality of the variable selection is indeed whether or 
 not a reference model is applied.
@@
 higher the benefit of using a reference models as the basis for
-feature selection.
+variable selection.
 
@@
 reference model as it was estimated as part of the analysis anyway.
-Sometimes including all the available features in an
+Sometimes including all the available variables in an
 elaborate model can be computationally demanding.  In such a
@@
 the data. The noise is the main source of the instability and tends to
-obscure the relevance of the features in relation to the target
+obscure the relevance of the variables in relation to the target
 variable of interest. We demonstrate with the following simple
@@
 where $f$ is the latent variable of interest of which $Y$ is a noisy
-observation. The first $k$ features are strongly related to the
+observation. The first $k$ variables are strongly related to the
 target variable $Y$ and correlated among themselves. Precisely, $\rho$
-is the correlation among any pair of the first $k$ features, whereas
+is the correlation among any pair of the first $k$ variables, whereas
 $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
-any relevant feature and, respectively, $f$ and $Y$. If we had an
+any relevant variable and, respectively, $f$ and $Y$. If we had an
 infinite amount of observations, the sample correlation would be equal
@@
 ideal asymptotic regime, this correlation would still remain a biased
-indicator of the true relevance of each feature (represented by the
+indicator of the true relevance of each variable (represented by the
 correlation between $X_j$ and $f$) due to the intrinsic noisy nature
@@
 When using a reference model, we first obtain predictions for $f$
-using all the features $\{X_{j}\}_{j=1}^{p}$ taking into account
+using all the variables $\{X_{j}\}_{j=1}^{p}$ taking into account
 that we have only observed the noisy representation $Y$ of $f$. If our
@@
 which improves the accuracy in the estimation of the relevance of the
-features.  Figure \ref{fig:correlation} illustrates this process in
+variables.  Figure \ref{fig:correlation} illustrates this process in
 the form of a scatter plot of (absolute) correlations of the
-features with $Y$ against the corresponding correlations with the
+variables with $Y$ against the corresponding correlations with the
 predictions of a reference model (in this case the posterior
@@
 that using a reference model to filter out noise in the data, the two
-groups of features (relevant and non-relevant) can be distinguished
+groups of variables (relevant and non-relevant) can be distinguished
 much better than when the correlation is computed using the observed
@@
   \includegraphics[width=0.4\textwidth]{graphics/correlation.pdf}
-  \caption{Sample correlation plot of each feature (relevant in red, 
+  \caption{Sample correlation plot of each variable (relevant in red, 
   non-relevant in blue) with the target variable $y$ and the latent variable 
@@
 \hypertarget{comparison-minimal-subset}{
-\section{Minimal subset feature selection}\label{comparison-minimal-subset}}
+\section{Minimal subset variable selection}\label{comparison-minimal-subset}}
 
 In the bodyfat example above, our two simultaneous goals were to 
-obtain good predictive performance and to select a smaller number of features. 
-When the goal is to select a minimal subset of features,
+obtain good predictive performance and to select a smaller number of variables. 
+When the goal is to select a minimal subset of variables,
 which have similar predictive performance as the full model, we call it
-\emph{minimal subset feature selection}. This minimal subset might
-exclude features which have some predictive information about the
-target but, given the minimal subset, these features are not able to
+\emph{minimal subset variable selection}. This minimal subset might
+exclude variables which have some predictive information about the
+target but, given the minimal subset, these variables are not able to
 provide such additional information that would improve predictive
 performance in a substantial manner.
-The usual reason for this is that the relevant features
-which are not in the minimal subset are highly correlated with features already in
+The usual reason for this is that the relevant variables
+which are not in the minimal subset are highly correlated with variables already in
 the minimal subset. We will return to a problem of finding all
-the features with some predictive power in Section~\ref{complete-selection}.
+the variables with some predictive power in Section~\ref{complete-selection}.
 
@@
 simulate data sets of different sizes with a relatively large number
-of features $p=100$ with $k=20$ of them being predictive.  We compare
-the minimal subset feature selection perfomance of projection
+of variables $p=100$ with $k=20$ of them being predictive.  We compare
+the minimal subset variable selection perfomance of projection
 predictive approach (with a reference model), a Bayesian stepwise
@@
  is a Bayesian linear regression using the regularised horseshoe
-  prior and the feature excluded is the one with the highest Bayesian
+  prior and the variable excluded is the one with the highest Bayesian
   $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$.
@@
 for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR, the ratio of the number of non-relevant selected
-features over the number of selected features) of the selected submodel,
+variables over the number of selected variables) of the selected submodel,
 averaged after 100 data simulations. We see that projpred has superior FDR and the
 smallest RMSE. Using a reference model improves steplm significantly,
-but the minimal subset feature selection stays unreliable. Stepwise
+but the minimal subset variable selection stays unreliable. Stepwise
 Bayesian linear regression is better than steplm when comparing both methods with
-and without a reference model, respectively. However, the minimal subset feature
+and without a reference model, respectively. However, the minimal subset variable
 selection of the Bayesian linear regression is still less reliable than projpred.
 
-When the feature selection is repeated with different simulated data
-sets, there is some variability in the selected features. We
-measure the stability of feature selection by computing the entropy
+When the variable selection is repeated with different simulated data
+sets, there is some variability in the selected variables. We
+measure the stability of variable selection by computing the entropy
 of observed distribution over different models. The smallest entropy
 would be obtained if the approach always selected the same set of
-features, and the largest entropy would be observed if the approach
-would always selected different sets of features.
+variables, and the largest entropy would be observed if the approach
+would always selected different sets of variables.
 Figure \ref{fig:entropy} shows the entropy scores for the different compared
 methods. Lower entropy corresponds to a more stable
-selection. Highly correlated predictive features may happen to be
+selection. Highly correlated predictive variables may happen to be
 selected alternately, thus making stability estimation of the
@@
 The use of a reference model
-improves the stability of steplm in feature selection slightly, while it makes
+improves the stability of steplm in variable selection slightly, while it makes
 little difference for the Bayesian linear regression. The
@@
   \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
-  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset feature selection.}
+  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection.}
   \label{fig:rmse_vs_fdr}
@@
   \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
-  \caption{Entropy score in the minimal subset feature selection.}
+  \caption{Entropy score in the minimal subset variable selection.}
   \label{fig:entropy}
@@
 stepwise backward regression. In this case, the overall number of
-features (original plus noisy) is 100, as it was in the last part of
+variables (original plus noisy) is 100, as it was in the last part of
 Section \ref{bodyfat-1}. We compare results with and without using
@@
 steplm. Figure \ref{fig:bodyfat_step_refvsdata} shows the number of
-irrelevant features included in the final model and the out-of-sample
+irrelevant variables included in the final model and the out-of-sample
 root mean square error (RMSE). Results are based on 100 bootstrap
@@
 on the observations excluded at each bootstrap sample. We observe that
-the reference model reduces the number of irrelevant features included
+the reference model reduces the number of irrelevant variables included
 in the final model. This leads to less overfitting and thus to
@@
   \caption{Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelevant features on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
+The x-axis denotes the number of selected irrelevant variables on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
   \label{fig:bodyfat_step_refvsdata}
@@
 %   \section{A comparison in the normal means problem framework}\label{comparison}}
-\section{Complete feature selection}\label{comparison-complete-subset}
+\section{Complete variable selection}\label{comparison-complete-subset}
 \label{complete-selection}
 
-An alternative to minimal subset feature selection is \emph{complete
-  feature selection} in which the goal is to find all relevant
-features that have some predictive information about the target. In
-complete feature selection, it is possible that there are theoretically
-relevant features, but given finite noisy data we are not able infer their relevance.
+An alternative to minimal subset variable selection is \emph{complete
+  variable selection} in which the goal is to find all relevant
+variables that have some predictive information about the target. In
+complete variable selection, it is possible that there are theoretically
+relevant variables, but given finite noisy data we are not able infer their relevance.
 The projection predictive approach was originally designed for the minimal subset
-feature selection but we will test a simple iterative variant for the complete
-feature selection case in the section.
+variable selection but we will test a simple iterative variant for the complete
+variable selection case in the section.
  In addition, we analyse the benefits of the reference
 model approach in combination with three other
-methods which have been specifically designed for complete feature selection. 
+methods which have been specifically designed for complete variable selection. 
 As the criteria of selection performance, we evaluate the average false
@@
 sensitivity (i.e., the ratio of the number of relevant selected
-features over the total number of relevant features). We also provide
+variables over the total number of relevant variables). We also provide
 a comparison of the stability of the selection by means of a stability
@@
 
-We modify the projection predictive approach for complete feature
+We modify the projection predictive approach for complete variable
 selection by using it iteratively.  Applying the straightforward
 implementation of projpred, we are able to select a minimal subset of
-features, which yield to a model with a predictive performance
+variables, which yield to a model with a predictive performance
 comparable to the full model's predictive performance. 
@@
 the projpred selection for different iterations, at each time
-excluding the features selected in the previous
+excluding the variables selected in the previous
 iterations from the search.
@@
 observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
-number of observations or not very predictive features. 
+number of observations or not very predictive variables. 
 In our experiments we chose the default value used in the \texttt{projpred} 
@@
 \SetAlgoLined
-\KwResult{$R:=\{\text{selected features}\}$}
- $F:=\{\text{set of features}\}$ \;
+\KwResult{$R:=\{\text{selected variables}\}$}
+ $F:=\{\text{set of variables}\}$ \;
  $R=\{\emptyset\}$ \;
@@
 
-\subsection{Alternative complete feature selection methods}
-
-% Many Bayesian approaches for complete feature selection first fit a
+\subsection{Alternative complete variable selection methods}
+
+% Many Bayesian approaches for complete variable selection first fit a
 % Bayesian regression model using some sparsifying prior on the
@@
 % regularised horseshoe (RHS) prior \citep{paper:rhs}, which in our experience
-% scales better to higher number of features as compared to other
+% scales better to higher number of variables as compared to other
 % horseshoe-like priors.
@@
 % For shrinkage priors, one central aspect is the amount of shrinkage
-% they actually impose on the relevant and irrelevant features. Ideally,
-% the irrelevant features should be completely shrunk to zero while the
-% relevant features should not be shrunk at all. The amount of shrinkage
+% they actually impose on the relevant and irrelevant variables. Ideally,
+% the irrelevant variables should be completely shrunk to zero while the
+% relevant variables should not be shrunk at all. The amount of shrinkage
 % can be quantified by the shrinkage factor $\kappa_{j}$ for each
@@
 %based on posterior credible intervals using the regularised horseshoe
-%prior in which we select features whose 90\% credible intervals
+%prior in which we select variables whose 90\% credible intervals
 %excludes zero (\emph{ci.90}) \note{Reference for this?}.
@@
 distribution of the z-values. The latter is estimated using splines
-with 7 degrees of freedom. We select features with local false
+with 7 degrees of freedom. We select variables with local false
 discovery rate below $0.2$, which is suggested by
@@
 by 90\% posterior credible intervals is done using the regularised
-horseshoe prior \Citep{paper:rhs} and selecting those features whose posterior
+horseshoe prior \Citep{paper:rhs} and selecting those variables whose posterior
 distribution does not include zero in the interval between the 5\% and
@@
 This is equivalent to a linear regression where the design matrix is
-the identity matrix with the number of features being equal to the
+the identity matrix with the number of variables being equal to the
 number of observations. This formulation can be found in practice, for
@@
 In our experiments, we retrieve the normal means problem from the
-sample correlations between the target and the features using the
+sample correlations between the target and the variables using the
 Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
 continuous target random variable $Y,$ a set of $p$ continuous
-features $\{X_{j}\}_{j=1}^{p}$, and denote
+variables $\{X_{j}\}_{j=1}^{p}$, and denote
 $\rho_{j}=\Cor(Y,X_{j})$. Further, suppose we have observed $n$
@@
 the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
-$j$-th feature $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
+$j$-th variable $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
 Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
@@
 $\rho\in\{0.3,0.5\}$ and numbers of
-observations $n\in\{50,70,100\}$. The total number of features $p$
-and the number of relevant features $k$ are fixed to $p = 1000$ and
+observations $n\in\{50,70,100\}$. The total number of variables $p$
+and the number of relevant variables $k$ are fixed to $p = 1000$ and
 $k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the feature selection is. For this example, \citet{paper:projpred} proposed to
+more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
 use a reference model which a Bayesian linear regression using the first five
-supervised principal components (SPC) as features and imposing an hierarchical prior on
+supervised principal components (SPC) as variables and imposing an hierarchical prior on
 their coefficients:
@@
 % \cite{paper:rhs} by setting the prior guess of the number of relevant
-% features to one in order to achieve the highest possible
+% variables to one in order to achieve the highest possible
 % shrinkage. The results are not sensitive with respect to the specific
@@
 %     prior. Posterior means and one standard deviation intervals are
-%     depicted. Relevant and non-relevant features are displayed in red
+%     depicted. Relevant and non-relevant variables are displayed in red
 %     and in blue respectively. Horizontal dashed lines corresponds to
-%     the true value of the mean for the relevant features.\\}
+%     the true value of the mean for the relevant variables.\\}
 %   \label{fig:posterior_intervals}
@@
 % less biased estimates and clearer separation between relevant and
-% irrelevant features. This is quantified in Figure \ref{fig:SESE_SSE}
+% irrelevant variables. This is quantified in Figure \ref{fig:SESE_SSE}
 % where average SESE and SSE are depicted based on 100 simulations. We
@@
 % of each parameter using the regularised horseshoe prior, averaged over
-% 100 data simulations. Relevant and non-relevant features are
+% 100 data simulations. Relevant and non-relevant variables are
 % highlighted in red and blue respectively. The ideal shrinkage would be
@@
 % reference model did not make any difference, we would expect the
-% points to lie on the diagonal. For the non-relevant features points
+% points to lie on the diagonal. For the non-relevant variables points
 % are on the diagonal on average for all the simulated scenarios, which
 % implies that their shrinkage was not improved by the reference
-% approach. For the relevant features, the points are always located
+% approach. For the relevant variables, the points are always located
 % under the diagonal, which means that the reference model helps and
@@
 % lower correlations and a smaller number of observations. The perfect
-% distinction of the two clusters of features (relevant and
+% distinction of the two clusters of variables (relevant and
 % non-relevant) observable on both the marginal distributions of the
@@
 the reference model are smaller since the raw data already provide
-enough information to identify the relevant features. The iterative
+enough information to identify the relevant variables. The iterative
 projpred has good false discovery rate in all cases, and the
@@
 intervals based on 100 simulations. Such a measure takes in account
-the variability of the subset of the selected features at each
+the variability of the subset of the selected variables at each
 simulation (originally at each bootstrap sample), modelling the
@@
 We conclude our complete selection experiments using the body fat
-dataset one more time. As earlier we add noisy uncorrelated features
-to the original data to get a total of 100 features.
+dataset one more time. As earlier we add noisy uncorrelated variables
+to the original data to get a total of 100 variables.
 Since we do not have a ground truth available with regard the original
-features of the data, we assume it is reasonable to consider all of
+variables of the data, we assume it is reasonable to consider all of
 them relevant, at least to some degree. The artificially added
-features are naturally irrelevant by construction.
+variables are naturally irrelevant by construction.
 We compute
@@
 The great performance of projpred in minimal subset selection is not
-carried over for the complete feature selection with iterative
+carried over for the complete variable selection with iterative
 projpred, and the methods specifically designed for the complete 
-feature selection perform better.
+variable selection perform better.
 Figure \ref{fig:bodyfat_stability} shows the stability
@@
 In this paper, we demonstrated the benefits of using a reference model
-to improve feature selection, or more generally, model reduction. 
+to improve variable selection, or more generally, model reduction. 
 We have motivated and explained the general benefits
@@
 filter on the observed target values on top of different widely used
-feature selection methods. Overall, using a reference model leads to
+variable selection methods. Overall, using a reference model leads to
 more accurate and stable selection results independently of the
@@
 Another main result of this paper is that the projective prediction
-approach shows superior performance in minimal subset feature
+approach shows superior performance in minimal subset variable
 selection compared to alternative methods whether or not these methods
@@
 incoporating the full uncertainty of the posterior predictive
-distribution into the feature selection procedure (instead of just
+distribution into the variable selection procedure (instead of just
 using point estimates) and using principled cross-validation method,
-projective predictions combine several desirable features into a
+projective predictions combine several desirable variables into a
 single procedure \citep{paper:projpred}.  In summary, we would
 strongly recommend using projective predictions for minimal subset
- feature selection if possible and feasible. 
+ variable selection if possible and feasible. 
  However, if this is not an option in a given
 situation, we would in any case recommend using a reference model on
-top of the chosen feature selection method.
+top of the chosen variable selection method.
 
 The projective prediction approach was not designed for the complete
-feature selection. We tested a simple iterative version of projpred,
+variable selection. We tested a simple iterative version of projpred,
 with mixed results and the methods specifically designed for complete
-feature selection (especially loc.fdr) performed better in our
+variable selection (especially loc.fdr) performed better in our
 experiments. It is left for future resarch to develop 
-a better projective prediction approach for complete feature
+a better projective prediction approach for complete variable
 selection problems.
@@
 with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
-features for which we want to obtain a minimally relevant
+variables for which we want to obtain a minimally relevant
 subset. Than, the main steps are the following:
@@
 \item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model's posterior.
-\item Rank the features according to their relevance using some
+\item Rank the variables according to their relevance using some
   heuristics and consider as candidate submodels only those which
   preserve this order, starting from including only the highest ranked
-  feature. The submodels are then naturally identified by their
+  variable. The submodels are then naturally identified by their
   model size. This step is not strictly necessary but reduces the number
@@
 predictive distribution of the reference model with parameters fixed
-at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the feature
+at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the variable
 values related to the statistical unit (identified by the subscript

### 2019-12-16 code/test.R
comparison reference model RHS and SCPA

@@ -1,0 +1,52 @@
+rm(list=ls())
+library(rstan)
+library(rstanarm)
+library(loo)
+library(projpred)
+library(dimreduce)
+set.seed(3428954)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n_full <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+p <- 100
+n <- 251
+noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
+dfr<-cbind(df,noise=noise)
+formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+pred2 <- c(pred,colnames(dfr[,15:(p+1)]))
+fit_model <- stan_model("model.stan", model_name = "reference_model",
+                        auto_write = rstan_options("auto_write"=TRUE))
+
+##########################
+## SPCA reference model ##
+x <- dfr[,-1]
+y <- dfr[,1]
+nc <- 5
+dr <- spca(x,y, nctot=nc, screenthresh = 0.6, window=p,
+           sup.only = T, verbose = F)
+z <- predict(dr, x)
+model_data <- list(y=y,X=z,p=ncol(z),n=n,s_max=dr$sdev[1])
+fit_SPCA <- sampling(fit_model, data = model_data,
+                chains = 1, iter = 2000, seed = 45342)
+loglik_SPCA <- extract_log_lik(fit_SPCA)
+loo_SPCA <- loo(loglik_SPCA)
+  
+#########################
+## RHS reference model ##
+p0 <- 5 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+hs_prior <- hs(global_scale=tau0)
+fit_RHS <- stan_glm(formula2, data = dfr[sel,], prior = hs_prior,
+                    seed=34523, refresh=0)
+loo_RHS <- loo(fit_RHS)
+
+compare(loo_SPCA,loo_RHS) # elpd_diff 53.0 (14.5 se), SPCA is better

### 2019-12-17 code/plots_in_the_paper_new.R
added table with numerical values of stepwise w/ and w/out ref model

@@ -436,28 +436,30 @@ ggsave("graphics/bodyfat_stability.pdf",plot2,width=10,height=2)
 #################################################
 
 
-# TODO: add new data to the plot
-# load('bodyfat_step.Rdata')
-#
-# data.plot <- data.frame(stat=c(noisy_ref,noisy_data,rmse_ref,rmse_data),
-#                         method=rep(c(rep('ref',100),rep('data',100)),2),
-#                         type=c(rep('noisy',200),rep('rmse',200)))
-#
-# facet.labels <- labeller(type=function(x){ifelse(x=='noisy','Noisy features selected','RMSE')})
-#
-# plot1 <- ggplot(data.plot,aes(x=stat,fill=method,color=method)) +
-#     facet_grid(~type, scales='free', labeller=facet.labels) +
-#     geom_histogram(position = "identity", alpha=0.7, bins=30) +
-#     labs(x='',y='',fill='Approach') +
-#     guides(color=FALSE) +
-#     scale_fill_manual(values=c("#819FF7","#FAAC58")) +
-#     scale_color_manual(values=c("#819FF7","#FAAC58")) +
-#     theme(axis.text.y = element_blank(),
-#           axis.ticks.y = element_blank())
-# #    theme_light()
-#
-# ggsave("graphics/bodyfat_step_refvsdata.pdf",plot1,width=10,height=2)
+load('bodyfat_step.Rdata')
 
+data.plot <- data.frame(stat=c(noisy_ref,noisy_data,rmse_ref,rmse_data),
+                        method=rep(c(rep('ref',100),rep('data',100)),2),
+                        type=c(rep('noisy',200),rep('rmse',200)))
+
+facet.labels <- labeller(type=function(x){ifelse(x=='noisy','Noisy features selected','RMSE')})
+
+plot1 <- ggplot(data.plot,aes(x=stat,fill=method,color=method)) +
+    facet_grid(~type, scales='free', labeller=facet.labels) +
+    geom_histogram(position = "identity", alpha=0.7, bins=30) +
+    labs(x='',y='',fill='Approach') +
+    guides(color=FALSE) +
+    scale_fill_manual(values=c("#819FF7","#FAAC58")) +
+    scale_color_manual(values=c("#819FF7","#FAAC58")) +
+    theme(axis.text.y = element_blank(),
+          axis.ticks.y = element_blank())
+
[…]

### 2019-12-18 paper/ref_approach.tex
added table with numerical values of stepwise w/ and w/out ref model
minor stylistic edit

@@
 \citet{paper:projpred}) which uses a reference model, and classic
-stepwise backward regression (steplm).
+stepwise backward regression (\emph{steplm}).
 % \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
@@
 observations. The goal is to find the model which is able to predict
-the amount of body fat well while requiring least amount of
+the amount of body fat well while requiring the least amount of
 measurements for a new person.
 
-\cite{paper:bodyfat} report results using \emph{steplm} with a significance
+\cite{paper:bodyfat} report results using steplm with a significance
 level of 0.157 with AIC selection \citep{akaike1974new}, fixing
@@
 \end{figure}
+
+\begin{table}[tp]
+\footnotesize
+\centering
+\begin{tabular}{l|r|r}
+%  \hline
+Method & RMSE & Selected noisy \\ 
+  \hline
+Stepwise selection & 6.92 (0.68) & 48.1 (7.46)    \\
+Reference model + Stepwise selection & 4.71 (0.45) & 25.1 (6.89)   \\
+\end{tabular}
+\caption{Mean and standard deviation (between brackets) values of Figure \ref{fig:bodyfat_step_refvsdata}}
+\label{tab:step_refvsdata}
+\end{table}
 

### 2019-12-19 paper/ref_approach.tex
added sentence about RHS ref model for iterative proj

@@
 carried over for the complete variable selection with iterative
-projpred, and the methods specifically designed for the complete 
-variable selection perform better.
+projpred (even when changing the reference model into an full encompassing 
+linear regression with regularised horseshoe prior), and the methods 
+specifically designed for the complete variable selection perform better. 
 Figure \ref{fig:bodyfat_stability} shows the stability

### 2019-12-20 paper/ref_approach.tex
edited begin Section 4.3

@@
 
-To investigate the performance of the four complete selection approaches,
+The iterative projection applies straightforwardly to data, whereas
+to investigate the performance of the three alternative complete selection approaches,
 we are going to use simulations based on the normal means problem.

### 2019-12-22 paper/ref_approach.tex
minor edits

@@
     \author{
-    Federico Pavone \footnote{Department of Computer Science, Aalto University, Finland.} $\,$\footnote{Correspondence concerning this article should be addressed to TODO.}, 
+    Federico Pavone \footnote{Department of Computer Science, Aalto University, Finland.} $\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
+E-mail: federicopavone01@gmail.com.},
   Juho Piironen$^*$,
@@
 abdomen and height to be always included in the model. For better
-comparison we don't fix any of the variables.  The steplm approach is
+comparison we do not fix any of the variables.  The steplm approach is
 carried out combining the \texttt{step} and \texttt{lm} functions in R.
@@
 76\% with projpred, but only of 14\% with steplm. In addition, the
-sizes of the selected models with projpred are much smaller with
-steplm.
+sizes of the selected models with projpred are much smaller than the ones 
+selected with steplm.
 \begin{figure}[tp]
@@
 carried over for the complete variable selection with iterative
-projpred (even when changing the reference model into an full encompassing 
+projpred (even changing the reference model with a full encompassing 
 linear regression with regularised horseshoe prior), and the methods 
@@
 variable selection (especially loc.fdr) performed better in our
-experiments. It is left for future resarch to develop 
+experiments. It is left for future research to develop 
 a better projective prediction approach for complete variable

### 2019-12-27 code/plots_in_the_paper_new.R
added projpred without ref model in simulated data experiment

@@ -153,7 +153,7 @@ plot1 <- ggplot(data.plot,aes(x=fdr,y=sensitivity,col=method)) +
   labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
 #  theme_light()
 
-ggsave("graphics/sensitivity_vs_fdr.pdf",plot1,width=10,height=3)
+ggsave("../paper/graphics/sensitivity_vs_fdr.pdf",plot1,width=10,height=3)
 
 ## Stability plot
 plot2 <- ggplot(data.plot,aes(y=stab.mean,x=method,col=approach)) +
@@ -165,7 +165,7 @@ plot2 <- ggplot(data.plot,aes(y=stab.mean,x=method,col=approach)) +
   scale_color_manual(values=c("#819FF7","#FAAC58"))
 #  theme_light()
 
-ggsave("graphics/stability.pdf",plot2,width=10,height=3)
+ggsave("../paper/graphics/stability.pdf",plot2,width=10,height=3)
 
 
 
@@ -190,7 +190,7 @@ inc_prob <- boot_inclusion %>%
   scale_fill_manual(values=c('steplm'="#819FF7",'projpred'="#FAAC58"))
 #  theme_light()
 
-ggsave("graphics/inc_prob.pdf",inc_prob,width=10,height=3)
+ggsave("../paper/graphics/inc_prob.pdf",inc_prob,width=10,height=3)
 
 
 # Model selection frequencies
@@ -293,7 +293,7 @@ cor_plot_final <- ggExtra::ggMarginal(cor_plot,
                                       type = 'density',
                                       xparams = list(size=0.5),
                                       yparams = list(size=0.5))
-ggsave("graphics/correlation.pdf",cor_plot_final, width=4, height=4)
+ggsave("../paper/graphics/correlation.pdf",cor_plot_final, width=4, height=4)
 
 
 ##################################################
@@ -413,7 +413,7 @@ plot1 <- data.plot %>%
    #       strip.text.y = element_text(color='black'))
 
 
-ggsave("graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.5)
+ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.5)
 
 ## Stability plot
 plot2 <- data.plot %>%
@@ -427,7 +427,7 @@ plot2 <- data.plot %>%
[…]

### 2019-12-27 paper/ref_approach.tex
fixed few things from Juho comments + added iterative proj without a ref model in simulated experiment

@@
 a comparison of the stability of the selection by means of a stability
-measure proposed by \citet{paper:stability}.
+measure proposed by \citet{paper:stability}, which goes from 0 to 1 and a higher value 
+means a more stable selection.
 
@@
 of the largest SPC.  The SPCs are computed using the
-\texttt{R}-package \texttt{dimreduce} setting the screening threshold
+\texttt{R}-package \texttt{dimreduce} (\url{https://github.com/jpiironen/dimreduce}) setting the screening threshold
 parameter at $0.6s_{max}$.  In our experiments, the results are not

### 2020-02-03 code/plots_in_the_paper_new.R
modified plot for iterative lasso: different point shape and dashed connecting line

@@ -624,7 +624,7 @@ if(saveMode){
                                  method = c('test.iter',
                                             'test.iter',
                                             'projpred.iter',
-                                            'projpred.iter'),
+                                            'lasso.iter'),
                                  approach = rep(c('ref','data'),2),
                                  sensitivity = c(avg.sensitivity(X_ref_test),
                                                  avg.sensitivity(X_data_test),
@@ -706,14 +706,20 @@ if(saveMode){
 } else {
     load('complete_selection_plot.RData')
 }
-  
+
+
+colors <- c(
+  'projpred.iter' = '#2E2E2E',
+  'lasso.iter' = '#2E2E2E',
+  'loc.fdr' = '#619CFF',
+  'ci.90' = '#F8766D',
+  'EB.med' = '#00BA38'
+)
+
+shapes <- c('ref'=8, 'data'=20, 'data.lasso'=9)
+
 facet.labels <- labeller(n = function(x){paste("n=",x,sep="")},
                          rho=function(x){paste("rho=",x,sep="")})
-
-# colors <- c('projpred.iter' = '#2E2E2E',
-#             'loc.fdr' = '#819FF7',
-#             'ci.90' = '#F78181',
-#             'EB.med' = '#298A08')
 
 ## Sensitivity vs False discovery rate plot
 data.plot.clean <- data.plot %>%
@@ -721,8 +727,12 @@ data.plot.clean <- data.plot %>%
   #filter(!(method=='projpred.iter' & approach=='data')) %>%
   mutate(method = factor(method, levels = names(colors)))
 
+## Specific approach label for iterative lasso
+data.plot.clean.plot1 <- data.plot.clean
+data.plot.clean.plot1[data.plot.clean.plot1$method=='lasso.iter',]$approach <- 'data.lasso'
 
-plot1 <- ggplot(data.plot.clean,aes(x=fdr,y=sensitivity,col=method)) +
+
+plot1 <- ggplot(data.plot.clean.plot1,aes(x=fdr,y=sensitivity,col=method)) +
     facet_grid(rho~n, labeller=facet.labels) +
     geom_point(aes(shape=approach),size=2) +
     ## geom_label_repel(data=filter(data.plot.clean,!is.na(alpha)),
@@ -738,6 +748,8 @@ plot1 <- ggplot(data.plot.clean,aes(x=fdr,y=sensitivity,col=method)) +
     ) +
[…]

### 2020-02-04 code/bodyfat_comparison_varying_n_iteratedlasso.R
bodyfat experiment iterative lasso

@@ -1,0 +1,67 @@
+## BODYFAT COMPARISON ##
+rm(list=ls())
+args = commandArgs(trailingOnly=TRUE)
+library(rstan)
+library(rstanarm)
+library(projpred)
+library(dimreduce)
+set.seed(3428954)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n_full <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p <- 100
+n <- as.numeric(args[1])
+times <- 100
+
+lasso_X <- matrix(0,nrow=times,ncol=p)
+alpha_lev <- 0.16
+
+noise <- array(rnorm((p-13)*n_full), c(n_full,(p-13)))
+dfr<-cbind(df,noise=noise)
+formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+pred2 <- c(pred,colnames(dfr[,15:(p+1)]))
+
+for(i in 1:times){
+  print(paste('ITERATION NUMBER: ',i))
+  sel  <- sample(1:n_full,n,replace = T)
+  x <- dfr[sel,-1]
+  y <- dfr[sel,1]
+  
+  ## Iterative lasso
+  ref_lasso <- init_refmodel(z=as.matrix(x), y, gaussian() ,x=as.matrix(x))
+  vs_lasso <- list()
+  suggested_lasso <- numeric()
+  relevants_lasso <- NULL
+  costs_lasso <- rep(1,p)
+  
+  j <- 0
+  while(length(relevants_lasso)<p){
+    j <- j + 1
+    vs_lasso[[j]] <- cv_varsel(ref_lasso, method = 'l1',
+                               penalty = costs_lasso,
+                               cv_method = 'kfold',
+                               K = 15,
+                               seed = 589435)
+    
+    suggested_lasso[j] <- suggest_size(vs_lasso[[j]],stat="rmse",alpha=alpha_lev,baseline='best')
[…]

### 2020-02-04 code/plots_in_the_paper_new.R
updated plots: included iterative lasso in bodyfat experiment and changed label

@@ -301,29 +301,29 @@ ggsave("../paper/graphics/correlation.pdf",cor_plot_final, width=4, height=4)
 ##################################################
 k <- 13
 
-avg.sensitivity <- function(X){
-  tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
-  return(mean(tmp, na.rm = TRUE))
-}
-
-avg.fdr <- function(X){
-  tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
-  return(mean(tmp, na.rm = TRUE))
-}
+# avg.sensitivity <- function(X){
+#   tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
+#   return(mean(tmp, na.rm = TRUE))
+# }
+# 
+# avg.fdr <- function(X){
+#   tmp <- apply(X,1,function(x){sum(which(x==1)>k)/sum(x)})
+#   return(mean(tmp, na.rm = TRUE))
+# }
 
 if(saveMode){
     data.plot <- tibble(n = numeric(),
                         rho = numeric(),
                         method = character(),
                         approach = character(),
-                        recall = numeric(),
+                        sensitivity = numeric(),
                         fdr = numeric(),
                         stab.low = numeric(),
                         stab.mean = numeric(),
                         stab.up = numeric())
 
     for(nn in c(50,70,100,251)){
-        load(paste("bodyfat_type1_varyN_n",nn,".Rdata",sep=""))
+        load(paste("bodyfat_type1_varyN_p100_n",nn,".Rdata",sep=""))
         data.plot <- data.plot %>%
             ## Credibility intervals inclusion probabilities
             ## with regularized horseshoe prior
@@ -368,7 +368,7 @@ if(saveMode){
                              stab.up = c(getStability(ebmt_X_ref)$upper,
                                          getStability(ebmt_X_data)$upper)))
         ## Iterative projection
-        load(paste("bodyfat_type1_varyN_iteratedproj_n",nn,".Rdata",sep=""))
+        load(paste("bodyfat_type1_varyN_p100_iteratedproj_n",nn,".Rdata",sep=""))
         data.plot <- data.plot %>%
             bind_rows(tibble(n = n,
                              method = "projpred.iter",
@@ -378,30 +378,53 @@ if(saveMode){
                              stab.low = getStability(projpred_X)$lower,
                              stab.mean = getStability(projpred_X)$stability,
[…]

### 2020-02-04 paper/ref_approach.tex
minor edits about iterative lasso

@@
 
+In the experiments in the next Sections we include a method which we refer to as iterative lasso.
+It consists in the same algorithm of the iterative projection, expect for not using any reference model.
+Given the implementation of projpred in the R-package, it means that the predictions of the reference model consist simply on the observed target values.
+Iterative lasso is therefore used as the free-reference-model comparison baseline of the iterative projection.
+
 \subsection{Alternative complete variable selection methods}
@@
 sensitivity is good except when the number of observations and the
-correlation level are small. Tuning $\alpha$ might lead to improved
+correlation level are small. It performs better than the iterative lasso 
+selection in any of the simulated scenarios. Tuning $\alpha$ might lead to improved
 selection, yet the main source of poor performance could well be the
@@
 specifically designed for the complete variable selection perform better. 
+However we still observe a better selection with respect to iterative lasso
+in any of the examined scenarios, mainly in terms of false discovery rate.
 Figure \ref{fig:bodyfat_stability} shows the stability

### 2020-02-06 code/plots_in_the_paper_new.R
included error 1-sd error bars in plots

@@ -49,123 +49,123 @@ saveMode <- FALSE
 ###### COMPLETE SELECTION (OLD VERSION) ##############
 ######################################################
 
-if(saveMode){
-    data.plot <- tibble(n = numeric(),
-                        rho = numeric(),
-                        method = character(),
-                        approach = character(),
-                        sensitivity = numeric(),
-                        sensitivity.sd = numeric(),
-                        fdr = numeric(),
-                        fdr.sd = numeric(),
-                        stab.low = numeric(),
-                        stab.mean = numeric(),
-                        stab.up = numeric())
-    for(nn in c(50,70,100)){
-        for(rr in c(0.3,0.5)){
-            load(paste("ref_approach_n",nn,"rho",rr,".Rdata",sep=""))
-            data.plot <- data.plot %>%
-                ## Credibility intervals inclusion probabilities
-                ## with regularized horseshoe prior
-                bind_rows(tibble(n = rep(n,2),
-                                 rho = rep(rho,2),
-                                 method = rep("ci.90",2),
-                                 approach = c("ref","data"),
-                                 sensitivity = c(avg.sensitivity(ci90_X_ref),
-                                                 avg.sensitivity(ci90_X_data)),
-                                 sensitivity.sd = c(sd.sensitivity(ci90_X_ref),
-                                                    sd.sensitivity(ci90_X_data)),
-                                 fdr = c(avg.fdr(ci90_X_ref),
-                                         avg.fdr(ci90_X_data)),
-                                 fdr.sd = c(sd.fdr(ci90_X_ref),
-                                            sd.fdr(ci90_X_data)),
-                                 stab.low = c(getStability(ci90_X_ref)$lower,
-                                              getStability(ci90_X_data)$lower),
-                                 stab.mean = c(getStability(ci90_X_ref)$stability,
-                                               getStability(ci90_X_data)$stability),
-                                 stab.up = c(getStability(ci90_X_ref)$upper,
-                                             getStability(ci90_X_data)$upper))) %>%
-                ## Control of the local false discovery rate
-                bind_rows(tibble(n = rep(n,2),
-                                 rho = rep(rho,2),
-                                 method = rep("loc.fdr",2),
-                                 approach = c("ref","data"),
[…]

### 2020-02-08 code/plots_in_the_paper_new.R
new labels and minor improvements in the plots

@@ -7,12 +7,8 @@ theme_set(theme_light() +
           theme(strip.background = element_rect(color='black',fill='white'),
                 strip.text.x = element_text(color='black'),
                 strip.text.y = element_text(color='black')))
-shapes <- c('ref'=8, 'data'=20)
 library(latex2exp)
 source("getStability.R")
-
-p <- 1000
-k <- 100
 
 avg.sensitivity <- function(X){
   tmp <- apply(X,1,function(x){sum(which(x==1)<=k)/k})
@@ -35,11 +31,15 @@ sd.fdr <- function(X){
 }
 
 colors <- c(
+  'lasso.iter' = '#2E2E2E',
   'projpred.iter' = '#2E2E2E',
   'loc.fdr' = '#619CFF',
   'ci.90' = '#F8766D',
   'EB.med' = '#00BA38'
 )
+shapes <- c('ref'=18, 'data'=1, 'data.lasso'=20)
+facet.labels <- labeller(n = function(x){paste("n=",x,sep="")},
+                         rho=function(x){paste("rho=",x,sep="")})
 
 ## If you want to run the script to create the data object
 ## set TRUE, otherwise set FALSE to load the data.
@@ -299,8 +299,6 @@ ggsave("../paper/graphics/correlation.pdf",cor_plot_final, width=4, height=4)
 ##################################################
 ########## BODYFAT VARIABLE SELECTION ############
 ##################################################
-k <- 13
-
 if(saveMode){
     data.plot <- tibble(n = numeric(),
                         rho = numeric(),
@@ -404,18 +402,6 @@ if(saveMode){
     load('bodyfat_complete_selection_plot.RData')
 }
 
-colors <- c(
-  'projpred.iter' = '#2E2E2E',
-  'lasso.iter' = '#2E2E2E',
-  'loc.fdr' = '#619CFF',
-  'ci.90' = '#F8766D',
-  'EB.med' = '#00BA38'
-)
-
-shapes <- c('ref'=8, 'data'=20, 'data.lasso'=9)
-
-facet.labels <- labeller(n = function(x){paste("n=",x,sep="")})
-
 ## Sensitivity vs False discovery rate plot
 data.plot.fixed <- data.plot
 data.plot.fixed[data.plot.fixed$method=='lasso.iter',]$approach <- 'data.lasso'
[…]

### 2020-02-08 code/plots_in_the_paper_new.R
minor edits

@@ -429,7 +429,7 @@ plot1 <- ggplot(data.plot.fixed, aes(x=fdr,y=sensitivity,col=method)) +
     labs(x="False discovery rate",y="Sensitivity", shape="Approach", col="Method")
 
 
-ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.5)
+ggsave("../paper/graphics/bodyfat_sensitivity_vs_fdr.pdf",plot1,width=10,height=2.8)
 
 ## Stability plot
 plot2 <- data.plot %>%

### 2020-02-08 paper/ref_approach.tex

--- 2019-12-27 paper/ref_approach.tex
@@
  \While{$F\neq\{\emptyset\}$}{
-   projection.HeuristicSearch \;
+   projection.HeuristicSearch() \;
    projection.elpdEstimate() \;
@@
 \end{center}
+
+In the experiments shown in the next sections, we include an additional iterative
+method which we refer to as 'iterative lasso'. It consists of the same iterative
+algorithm as iterative projpred expect for not using any reference model but
+the lasso method for variable selection, instead.
+That is, it uses the observed target values instead of predictions of the reference model.
+Iterative lasso can help to distangle the effects
+of the iterative procedure and the usage of a reference model in complete feature selection.
 

### 2020-02-08 paper/ref_approach.tex
added one sd error bar in figure caption

@@
   \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
-  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection.}
+  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.}
   \label{fig:rmse_vs_fdr}
@@
 In the experiments shown in the next sections, we include an additional iterative
-method which we refer to as 'iterative lasso'. It consists of the same iterative
+method which we refer to as `iterative lasso'. It consists of the same iterative
 algorithm as iterative projpred expect for not using any reference model but
@@
   \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
-  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
+  \caption{Sensitivity against false discovery rate based on 100 data simulations with one standard deviation error bars.\\}
   \label{fig:sensitivity_vs_fdr_iterated}
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples.\\}
+  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples with one standard deviation error bars.\\}
   \label{fig:bodyfat_sensitivity_vs_fdr}

### 2020-02-08 code/plots_in_the_paper_new.R
fixed Approach labels and iter.lasso plots

@@ -31,13 +31,13 @@ sd.fdr <- function(X){
 }
 
 colors <- c(
-  'lasso.iter' = '#2E2E2E',
+  'lasso.iter' = '#A4A4A4',
   'projpred.iter' = '#2E2E2E',
   'loc.fdr' = '#619CFF',
   'ci.90' = '#F8766D',
   'EB.med' = '#00BA38'
 )
-shapes <- c('ref'=18, 'data'=1, 'data.lasso'=20)
+shapes <- c('ref'=5, 'data'=19)
 facet.labels <- labeller(n = function(x){paste("n=",x,sep="")},
                          rho=function(x){paste("rho=",x,sep="")})
 
@@ -404,7 +404,6 @@ if(saveMode){
 
 ## Sensitivity vs False discovery rate plot
 data.plot.fixed <- data.plot
-data.plot.fixed[data.plot.fixed$method=='lasso.iter',]$approach <- 'data.lasso'
 data.plot.fixed <- data.plot.fixed %>%
     mutate(method = factor(method, levels = names(colors)))
 
@@ -413,21 +412,20 @@ plot1 <- ggplot(data.plot.fixed, aes(x=fdr,y=sensitivity,col=method)) +
     ##geom_abline(intercept=0, slope=1, linetype='dashed') +
     #scale_x_continuous(limits=c(0,0.65)) +
     #scale_y_continuous(limits=c(0.3,0.99)) +
-    geom_point(aes(shape=approach), size=3) +
     geom_errorbar(aes(ymin=sensitivity-sensitivity.sd,ymax=sensitivity+sensitivity.sd),alpha=0.6) +
     geom_errorbarh(aes(xmin=fdr-fdr.sd,xmax=fdr+fdr.sd),alpha=0.6) + 
+    geom_point(aes(shape=approach), size=2.3) +
     scale_shape_manual(values = shapes) +
     scale_color_manual(values = colors) +
     #geom_line(aes(col=method)) +
     geom_line(data=data.plot.fixed,aes(col=method)) +
     geom_line(data=filter(data.plot.fixed,method%in%c('projpred.iter','lasso.iter')),
-            aes(group=1), linetype='dashed') +
+            aes(group=1), linetype='dashed',color='#A4A4A4') +
     guides(
       shape = guide_legend(order = 1),
       colour = guide_legend(order = 2)
     ) +
[…]

### 2020-04-22 code/minimal_subset.R
fixed value of p=80

@@ -12,7 +12,7 @@ args = commandArgs(trailingOnly=TRUE) # n rho
 ## Simulation parameters
 n <- as.numeric(args[1])  # number of observations
 rho <- as.numeric(args[2])  # correlation level
-p <- 100   # total number of features
+p <- 80   # total number of features
 k <- 20    # number of relevant features
 
 times <- 100

### 2020-04-22 code/minimal_subset.R
fix p=70

@@ -12,7 +12,7 @@ args = commandArgs(trailingOnly=TRUE) # n rho
 ## Simulation parameters
 n <- as.numeric(args[1])  # number of observations
 rho <- as.numeric(args[2])  # correlation level
-p <- 80   # total number of features
+p <- 70   # total number of features
 k <- 20    # number of relevant features
 
 times <- 100

### 2020-04-22 paper/ref_approach.tex

@@
   The search heuristic  is forward search and the predictive performance 
-  is estimated via 10-fold cross-validation.
+  is estimated via 10-fold cross-validation. The selection continues
+  until the predictive performance is close to the predictive
+  performance of the reference model. See more details in Appendix A.
 
@@
 \item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
+The results in this paper were not sensitive to the specific choice of how ``sufficiently close'' is defined, and we used the same definition as \citet{paper:projpred}.
 \end{enumerate}
@@
 \citep{paper:original_proj}. For further details on the projective
-prediction workflow and implementation see paper by \citet{paper:projpred}.
+prediction workflow and implementation see the paper by \citet{paper:projpred}.
 

### 2020-04-22 code/bodyfat_notebook_RMSE.R
minor edits

@@ -75,12 +75,16 @@ for (k in 1:K) {
 lmmus<-unlist(lmmuss)[order(as.integer(names(unlist(lmmuss))))]
 lmvsnlmus<-unlist(lmvsnlmuss)[order(as.integer(names(unlist(lmvsnlmuss))))]
 lmvsnlnvs <- unlist(lmvsnlnvss)
+mean(lmvsnlnvs)
+sd(lmvsnlnvs)
 rmse_lmfull <- sqrt(mean((df$siri-lmmus)^2))
 rmse_lmselnl <- sqrt(mean((df$siri-lmvsnlmus)^2))
 ## Reference model + projpred
 mus<-unlist(muss)[order(as.integer(names(unlist(muss))))]
 vsmus<-unlist(vsmuss)[order(as.integer(names(unlist(vsmuss))))]
 vsnvs <- unlist(vsnvss)
+mean(vsnvs)
+sd(vsnvs)
 rmse_full <- sqrt(mean((df$siri-mus)^2))
 rmse_proj <- sqrt(mean((df$siri-vsmus)^2))
 
@@ -145,12 +149,16 @@ for (k in 1:K) {
 lmmus2 <- unlist(lmmuss2)[order(as.integer(names(unlist(lmmuss2))))]
 lmvsnlmus2 <- unlist(lmvsnlmuss2)[order(as.integer(names(unlist(lmvsnlmuss2))))]
 lmvsnlnvs2 <- unlist(lmvsnlnvss2)
+mean(lmvsnlnvs2)
+sd(lmvsnlnvs2)
 rmse_lmfull2 <- sqrt(mean((dfr$siri-lmmus2)^2))
 rmse_lmselnl2 <- sqrt(mean((dfr$siri-lmvsnlmus2)^2))
 ## Reference model + projpred
 mus2 <- unlist(muss2)[order(as.integer(names(unlist(muss2))))]
 vsmus2 <- unlist(vsmuss2)[order(as.integer(names(unlist(vsmuss2))))]
 vsnvs2 <- unlist(vsnvss2)
+mean(vsnvs2)
+sd(vsnvs2)
 rmse_full2 <- sqrt(mean((dfr$siri-mus2)^2))
 rmse_proj2 <- sqrt(mean((dfr$siri-vsmus2)^2))
 

### 2020-04-22 paper/ref_approach.tex
fixed p=70 minimal selection, added avg and sd in Table bodyfat, fixed references

@@
 %  \hline
-Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
+Data  & Method & RMSE Full & RMSE Selected & \# Selected (avg, sd) & \# Selected noisy \\ 
   \hline
-bodyfat & projpred & 4.35 & 4.47 & 2 &   \\
-& steplm & 4.38 & 4.47 & 7 &  \\
+bodyfat & projpred & 4.36 & 4.45 & 2 (2.3, 0.48) &   \\
+& steplm & 4.38 & 4.46 & 7 (6, 0.94) &  \\
 \hline
-+ noisy variables & projpred & 4.58 & 4.54 & 2 & 0  \\
-& steplm & 5.89 & 5.43 & 19 & 13 \\
++ noisy variables & projpred & 4.58 & 4.54 & 2 (2, 0)& 0  \\
+& steplm & 5.89 & 5.43 & 23 (26.2, 4.54) & 15 \\
 %   \hline
@@
   selected submodel; \# Selected = selected number of variables;
-  \# Selected noisy = selected number of extra noisy variables.}
+  \# Selected noisy = selected number of extra noisy variables. 
+  Between brackets average number of selected features and one standard deviation
+  values over the 10-fold cross-validation.}
 \label{tab:model_performances}
@@
 simulate data sets of different sizes with a relatively large number
-of variables $p=100$ with $k=20$ of them being predictive.  We compare
+of variables $p=70$ with $k=20$ of them being predictive.  We compare
 the minimal subset variable selection perfomance of projection
@@
 we use the default setting provided by the \texttt{R}-package
-\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr}.
+\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr, Rlocfdr}.
 
@@
 \texttt{R}-package \texttt{EbayesThresh}
-\citep{Silverman+etal:2017:EbayesThresh}. As suggested by
+\citep{Silverman+etal:2017:EbayesThresh, REbayesThresh}. As suggested by
 \cite{johnstone2004needles}, we use a Laplace distribution resulting

### 2020-04-23 paper/ref_approach.tex
added reference R package projpred
further references + language edits

@@
 work of \citet{paper:reference_lindley}. For more historical
-references, see the papers by \citet{vehtari2012survey} and
+references, see \citet{vehtari2012survey} and
 \citet{paper:model_selection}, and for most recent methodological
-development see a paper by \citet{paper:projpred}.
-
-Reference models have been also used in non-Bayesian contexts, where
+developments see \citet{paper:projpred}.
+
+Reference models have been also used in non-Bayesian contexts, in which
 \cite{harrell2015regression} describes them as full models that can be
@@
 
-To motivate the further discussion and experiments, we start by simple
+To motivate the further discussion and experiments, we start by a simple
 variable selection example using body fat data by \citet{johnson1996fitting}.
@@
 The target variable of interest is the amount of body fat, which is
-measured by immersing a person in water tank which is a complex and
-expensive procedure. Additionally, we have information about 13
+obtained by a complex and expensive procedure consisting in immersing a 
+person in a water tank and carrying out different measuraments and computations. 
+Additionally, we have information about 13
 variables which are anthropometric measurements (e.g., height, weight
@@
 predictive approach, and papers by \citet{paper:model_selection} and
-\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} R package.
+\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} R package \citep{Rprojpred}.
 
@@
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy variables so that there are 100 variable in total. 
+unrelated noisy variables so that there are 100 variables in total. 
 The last two rows of Table
@@
 A properly designed reference model is able to filter parts of the
-noise present in the data, and hence provide an improved and more
+noise present in the data, and hence to provide an improved and more
 stable selection process. This holds even if the reference model does
@@
 itself, rather than the specific way of using it.  In general, the
-less data we have and the more complex the estimated models, the
-higher the benefit of using a reference models as the basis for
+less data we have and the more complex the estimated models are, the
+higher is the benefit of using a reference models as the basis for
 variable selection.
 
-If one of the models to be compared is the full model which can be
+If one of the models to be compared is the full model, which can be
 used as a reference model, there is no additional cost of using a
@@
 A good predictive model is able to filter part of the noise present in
-the data. The noise is the main source of the instability and tends to
+the data. The noise is the main source of the instability in the selection
+and tends to
 obscure the relevance of the variables in relation to the target
-variable of interest. We demonstrate with the following simple
+variable of interest. We demonstrate it with the following simple
 explanatory example taken from \cite{paper:projpred}. The data
@@
 simulate data sets of different sizes with a relatively large number
-of variables $p=70$ with $k=20$ of them being predictive.  We compare
-the minimal subset variable selection perfomance of projection
-predictive approach (with a reference model), a Bayesian stepwise
+of variables $p=70$, with $k=20$ of them being predictive.  We compare
+the minimal subset variable selection performance of the projection
+predictive approach (which uses a reference model and it is referred to as projpred), 
+a Bayesian stepwise
 forward selection with and without a reference model, and maximum
 likelihood stepwise forward selection with and without a reference
-model:
+model (steplm). The following is a summary of the implementation of the compared methods:
 \begin{itemize}
@@
   prior and the variable excluded is the one with the highest Bayesian
-  $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$.
+  $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$,
+  where $D$ stays for the observed data.
 The selection continues if the reduced model has an elpd score higher 
@@
 measure the stability of variable selection by computing the entropy
-of observed distribution over different models. The smallest entropy
+of the observed distribution of the included variables over different models. The smallest entropy
 would be obtained if the approach always selected the same set of
 variables, and the largest entropy would be observed if the approach
-would always selected different sets of variables.
+would always selected different sets of variables. Therefore, lower entropy 
+corresponds to a more stable selection. Highly correlated predictive variables may happen to be
+selected alternately, thus making stability estimation of the
+selection a non-trivial task. Entropy can not distinguish the interchangeability 
+due to correlation from instability. Thus, such a measure should be 
+considered as a relative, and not as an absolute, measure of stability.
 Figure \ref{fig:entropy} shows the entropy scores for the different compared
-methods. Lower entropy corresponds to a more stable
-selection. Highly correlated predictive variables may happen to be
-selected alternately, thus making stability estimation of the
-selection a non-trivial task. Entropy cannot distinguish the interchangeability 
-due to correlation from instability. Thus, such a measure should be 
-considerd as a relative and not as an absolute measure of stability.
-The use of a reference model
+methods. The use of a reference model
 improves the stability of steplm in variable selection slightly, while it makes
@@
 complete variable selection, it is possible that there are theoretically
-relevant variables, but given finite noisy data we are not able infer their relevance.
+relevant variables, but given finite noisy data we are not able to infer their relevance.
 The projection predictive approach was originally designed for the minimal subset
 variable selection but we will test a simple iterative variant for the complete
-variable selection case in the section.
+variable selection case in this Section.
  In addition, we analyse the benefits of the reference
@@
 model, which in this iterative version is the submodel with the
-highest predictive score explored at the current iteration. The
-stopping rule that we adopted is the following:
+highest predictive score explored at the current iteration. This translates
+in the following stopping rule at each iteration:
 \begin{equation} 
@@
 The choice of the hyperparameter $\alpha$ is non-trivial, and we have 
-observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
+observed sensitivity of the selection to such a choice, mainly when using cross-validation with a small
 number of observations or not very predictive variables. 
@@
 method which we refer to as `iterative lasso'. It consists of the same iterative
-algorithm as iterative projpred expect for not using any reference model but
+algorithm as iterative projpred expect for not using any reference model, but
 the lasso method for variable selection, instead.
 That is, it uses the observed target values instead of predictions of the reference model.
-Iterative lasso can help to distangle the effects
+The comparison with iterative lasso can help to disentangle the effects
 of the iterative procedure and the usage of a reference model in complete feature selection.
@@
 
-We consider three alternative complete selection methods,
+We consider three alternative complete selection methods:
  the control of the local
@@
 The control of the local false discovery rate consists of testing the
-z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the
+z-values $\{z_{j}\}_{j=1}^{p}$ of a normal mean problem (explained in Section \ref{simulations}) 
+on whether they belong to the
 theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
@@
 available in \cite{paper:stability}. The reference model helps in
-improving the stability of the selection: Again, the benefits are
+improving the stability of the selection: again, the benefits are
 bigger when the problem is more difficult (small $n$ and $\rho$). In
@@
 rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
-instead estimate it from the data. We compare iteration projections, 
+instead estimate it from the data. We compare the iterative projection, 
 the control of the local false discovery rate (loc.fdr), 
-the empirical Bayes median (EB.med),
+the empirical Bayes median (EB.med)
 and the selection by posterior credible intervals at level 90\%
@@
 regression over some supervised principal components, because it is
-natural for a large number of correlating variables, has fairly good
-predictive performance and is computationally efficient. We do not
+natural for a large number of correlating variables, and has fairly good
+predictive performance plus it is computationally efficient. We do not
 argue that this is always the best choice and more sophisticated
@@
 
-All Bayesian models used in the this paper have been implemented in
+All Bayesian models in this paper have been implemented in
 the probabilistic programming language \texttt{Stan}
 \citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo
-\citep{hoffman2014no,betancourt2017conceptual}. The code to run all
+\citep{hoffman2014no,betancourt2017conceptual}, through the R-packages 
+\texttt{rstan} \citep{Rrstan} and \texttt{rstanarm} \citep{Rrstanarm}.
+Graphics elaborations have been done using \texttt{ggplot2} \citep{Rggplot2}
+and the \texttt{tidyverse} framework \citep{Rtidyverse}.
+The code to run all
 the experiments is available on GitHub

### 2020-04-24 paper/ref_approach.tex
improve table 2

@@
 %  \hline
-Data  & Method & RMSE Full & RMSE Selected & \# Selected (avg, sd) & \# Selected noisy \\ 
+Data  & Method & RMSE Full & RMSE Sel & \# Sel (CPL, AVG, SD) & \# Sel noisy (CPL, AVG, SD) \\ 
   \hline
-bodyfat & projpred & 4.36 & 4.45 & 2 (2.3, 0.48) &   \\
-& steplm & 4.38 & 4.46 & 7 (6, 0.94) &  \\
+bodyfat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
+& steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
 \hline
-+ noisy variables & projpred & 4.58 & 4.54 & 2 (2, 0)& 0  \\
-& steplm & 5.89 & 5.43 & 23 (26.2, 4.54) & 15 \\
++ noisy variables & projpred & 4.58 & 4.54 & (2, 2, 0)& 0  \\
+& steplm & 5.89 & 5.43 & (23, 26.2, 4.54) & 15 \\
 %   \hline
@@
   rows) and with extra noisy variables (last two rows) estimated with
-  10-fold cross-validation. Abbreviations: Full = full model; Selected =
-  selected submodel; \# Selected = selected number of variables;
-  \# Selected noisy = selected number of extra noisy variables. 
-  Between brackets average number of selected features and one standard deviation
-  values over the 10-fold cross-validation.}
+  10-fold cross-validation. Abbreviations: RMSE = root mean squared error;
+  Full = full model; Sel = selected submodel; 
+  \# Sel = total number of selected variables;
+  \# Sel noisy = number of selected noisy variables. 
+  CPL = results for the complete data (not using cross-validation).
+  AVG = average over the 10-fold cross-validation. SD = standard deviation
+  over the 10-fold cross-validation.}
 \label{tab:model_performances}

### 2020-04-24 code/bodyfat_notebook_RMSE.R
added avg and sd noisy selected

@@ -94,6 +94,7 @@ p <- 100
 noise <- array(rnorm((p-13)*n), c(n,p-13))
 dfr<-cbind(df,noise=noise)
 formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+noisy_names <- colnames(dfr[,15:(p+1)])
 
 sel2 <- step(lm(formula2, data = dfr,  x=T,y=T),
                 direction = "backward",
@@ -118,6 +119,8 @@ lmvsnlnvss2 <- list()
 muss2 <- list()
 vsmuss2 <- list()
 vsnvss2 <- list()
+step_selected_noisy <- list()
+proj_selected_noisy <- list()
 for (k in 1:K) {
     message("Fitting model ", k, " out of ", K)
     omitted <- which(bin == k)
@@ -127,6 +130,7 @@ for (k in 1:K) {
     selnl_k2 <- step(lm(formula2, data = dfr[-omitted,, drop=FALSE],  x=T,y=T),
                     direction = "backward",
                     trace = 0)
+    step_selected_noisy[[k]] <- coef(selnl_k2)
     lmvsnlmuss2[[k]] <- predict(selnl_k2, newdata = dfr[omitted, , drop = FALSE])
     lmvsnlnvss2[[k]] <- length(coef(selnl_k2))-1
     ## Reference model + projpred
@@ -139,6 +143,7 @@ for (k in 1:K) {
     fit_cvvs_k2 <- cv_varsel(fit_k2, method='forward', cv_method='LOO',
                             nloo=nrow(dfr[-omitted,, drop=FALSE]))
     nvk2 <- suggest_size(fit_cvvs_k2,alpha=0.1)
+    proj_selected_noisy[[k]] <- fit_cvvs_k2$vind[1:nvk2]
     vsnvss2[[k]] <- nvk2
     proj_k2 <- project(fit_cvvs_k2, nv = nvk2, ns = 4000)
     muss2[[k]] <- colMeans(posterior_linpred(fit_k2,
@@ -151,6 +156,9 @@ lmvsnlmus2 <- unlist(lmvsnlmuss2)[order(as.integer(names(unlist(lmvsnlmuss2))))]
 lmvsnlnvs2 <- unlist(lmvsnlnvss2)
 mean(lmvsnlnvs2)
[…]

### 2020-04-26 paper/ref_approach.tex
fixed table 2 with avg and sd values
added Acknowledgments

--- 2020-04-22 paper/ref_approach.tex
@@
 %  \hline
-Data  & Method & RMSE Full & RMSE Selected & \# Selected (avg, sd) & \# Selected noisy \\ 
+Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
   \hline
-bodyfat & projpred & 4.36 & 4.45 & 2 (2.3, 0.48) &   \\
-& steplm & 4.38 & 4.46 & 7 (6, 0.94) &  \\
+bodyfat & projpred & 4.35 & 4.47 & 2 &   \\
+& steplm & 4.38 & 4.47 & 7 &  \\
 \hline
-+ noisy variables & projpred & 4.58 & 4.54 & 2 (2, 0)& 0  \\
-& steplm & 5.89 & 5.43 & 23 (26.2, 4.54) & 15 \\
++ noisy variables & projpred & 4.58 & 4.54 & 2 & 0  \\
+& steplm & 5.89 & 5.43 & 19 & 13 \\
 %   \hline
@@
   selected submodel; \# Selected = selected number of variables;
-  \# Selected noisy = selected number of extra noisy variables. 
-  Between brackets average number of selected features and one standard deviation
-  values over the 10-fold cross-validation.}
+  \# Selected noisy = selected number of extra noisy variables.}
 \label{tab:model_performances}
@@
 simulate data sets of different sizes with a relatively large number
-of variables $p=70$ with $k=20$ of them being predictive.  We compare
+of variables $p=100$ with $k=20$ of them being predictive.  We compare
 the minimal subset variable selection perfomance of projection
@@
 we use the default setting provided by the \texttt{R}-package
-\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr, Rlocfdr}.
+\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr}.
 
@@
 \texttt{R}-package \texttt{EbayesThresh}
-\citep{Silverman+etal:2017:EbayesThresh, REbayesThresh}. As suggested by
+\citep{Silverman+etal:2017:EbayesThresh}. As suggested by
 \cite{johnstone2004needles}, we use a Laplace distribution resulting
@@
 (\url{https://github.com/fpavone/ref-approach-paper}).
+
+\section*{Acknowledgments}
+
+We thank Alejandro Catalina Feliu for help with experiments, and
+Academy of Finland (grants 298742, and 313122), Finnish Center for
+Artificial Intelligence and Technology Industries of Finland
+Centennial Foundation (grant 70007503; Artificial Intelligence for
+Research and Development) for partial support of this research. We
+also acknowledge the computational resources provided by the Aalto
+Science-IT project.
 

### 2020-04-26 paper/ref_approach.tex

--- 2020-04-24 paper/ref_approach.tex
@@
 \hline
-+ noisy variables & projpred & 4.58 & 4.54 & (2, 2, 0)& 0  \\
-& steplm & 5.89 & 5.43 & (23, 26.2, 4.54) & 15 \\
++ noisy variables & projpred & 4.48 & 4.46 & (2, 2, 0)&  (0, 0, 0)  \\
+& steplm & 5.74 & 5.13 & (23, 26.2, 4.54) & (15, 18.9, 4.01) \\
 %   \hline

### 2020-04-26 paper/ref_approach.tex
spell check

@@
 
-\subsection{Bodyfat example: Part 1}
+\subsection{Body fat example: Part 1}
 \label{bodyfat-1}
@@
 obtained by a complex and expensive procedure consisting in immersing a 
-person in a water tank and carrying out different measuraments and computations. 
+person in a water tank and carrying out different measurements and computations. 
 Additionally, we have information about 13
@@
 error (RMSE), of the full model and the selected models using projpred
-or steplm.  There is no signfiant difference in predictive performance
+or steplm.  There is no significant difference in predictive performance
 of the selected models by different approaches even if there is
@@
 is not the only reason for its superior performance.  Rather, by
-incoporating the full uncertainty of the posterior predictive
+incorporating the full uncertainty of the posterior predictive
 distribution into the variable selection procedure (instead of just

### 2020-04-26 paper/ref_approach.tex
fixed locfdr ref
bodyfat -> body fat

@@
   \hline
-bodyfat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
+body fat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
 & steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
@@
 \end{tabular}
-\caption{Predictive performances with original bodyfat data (first two
+\caption{Predictive performances with original body fat data (first two
   rows) and with extra noisy variables (last two rows) estimated with
@@
 
-In the bodyfat example above, our two simultaneous goals were to 
+In the body fat example above, our two simultaneous goals were to 
 obtain good predictive performance and to select a smaller number of variables. 
@@
 %Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
-\item steplm (without a reference model): Stepwise selection using AIC as in the bodyfat example.
+\item steplm (without a reference model): Stepwise selection using AIC as in the body fat example.
 

### 2020-04-26 paper/ref_approach.tex
fixed EbayesThresh ref
slight adjustment of fonts
more flexible float placement
fix affiliations

@@
 \usepackage{amssymb,amsmath,amsthm}
-\usepackage{newtxtext}
-\usepackage{newtxmath}
+\usepackage{newtxtext} % times
+\usepackage[scaled=.95]{cabin} % sans serif
+\usepackage[varqu,varl]{inconsolata} % typewriter
+\usepackage{amsmath}
+\usepackage[varg]{newtxmath}
 \usepackage{ifxetex,ifluatex}
@@
 
+\renewcommand{\textfraction}{0.07}
+\renewcommand{\topfraction}{0.8}
+\renewcommand{\bottomfraction}{0.8}
+\renewcommand{\floatpagefraction}{0.8}
+
 \title{Using reference models in variable selection 
@@
     \author{
-    Federico Pavone \footnote{Department of Computer Science, Aalto University, Finland.} $\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
-E-mail: federicopavone01@gmail.com.},
-  Juho Piironen$^*$,
+      Federico Pavone\footnote{Department of Computer Science, Aalto University, Finland.}\, \footnote{Department of Decision Sciences, Bocconi University, Italy.}%$\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
+E-mail: federicopavone01@gmail.com.}
+      \,,\,
+  Juho Piironen$^*$,\,
   Paul-Christian B\"{u}rkner$^*$

### 2020-04-26 paper/ref_approach.tex
improved tables, captions and float placements

@@
   \includegraphics[width=0.98\textwidth]{graphics/inc_prob.pdf}
-  \caption{Bootstrap inclusion frequencies after 100 bootstrap samples.}
+  \vspace{-0.7\baselineskip}
+  \caption{Body fat example: Bootstrap inclusion frequencies calculated from 100 bootstrap samples. The projpred approach has less variability on which variables are selected.}
   \label{fig:inclusion_frequencies}
@@
 \end{tabular}
-\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
+\caption{Body fat example: Bootstrap model selection frequencies from 100 bootstrap samples.  The projpred approach has less variability on which variable combinations are selected.}
 \label{tab:model_frequencies}
@@
 of the selected models by different approaches even if there is
-difference in the selected variables. This can be explained by high
+clear difference in the number of selected variables. This can be explained by high
 correlation between the variables and different combinations can
@@
 %  \hline
-Data  & Method & RMSE Full & RMSE Sel & \# Sel (CPL, AVG, SD) & \# Sel noisy (CPL, AVG, SD) \\ 
+Data  & Method & RMSE Full & RMSE Sel & \# Sel (10-CV avg, sd) & \# Sel noisy (10-CV avg, sd) \\ 
   \hline
-body fat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
-& steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
+body fat & projpred & 4.4 & 4.5 &  2\, (2.3, 0.5) &   \\
+& steplm & 4.4 & 4.5 & 7\, (6.0, 0.9) &  \\
 \hline
-+ noisy variables & projpred & 4.48 & 4.46 & (2, 2, 0)&  (0, 0, 0)  \\
-& steplm & 5.74 & 5.13 & (23, 26.2, 4.54) & (15, 18.9, 4.01) \\
++ noisy variables & projpred & 4.5 & 4.5 &  2\, (2.0, 0.0)&  0\,\; (0,\, 0)  \\
+& steplm & 5.7 & 5.1 & 23\, (26,\; 4.5) &  15\, (19, 4) \\
 %   \hline
 \end{tabular}
-\caption{Predictive performances with original body fat data (first two
+\caption{Body fat example: Predictive performances with original data (first two
   rows) and with extra noisy variables (last two rows) estimated with
@@
   \# Sel noisy = number of selected noisy variables. 
-  CPL = results for the complete data (not using cross-validation).
-  AVG = average over the 10-fold cross-validation. SD = standard deviation
-  over the 10-fold cross-validation.}
+  10-CV avg = average over the 10 folds in cross-validation. 10-CV sd = standard deviation
+  over the 10 folds in cross-validation.}
 \label{tab:model_performances}
@@
 noisy data directly.
-
 \begin{figure}[tp]
@@
   \vspace{-5mm}
-  \includegraphics[width=0.4\textwidth]{graphics/correlation.pdf}
+  \includegraphics[width=0.35\textwidth]{graphics/correlation.pdf}
+  \vspace{-0.5\baselineskip}
   \caption{Sample correlation plot of each variable (relevant in red, 
   non-relevant in blue) with the target variable $y$ and the latent variable 
-  $f$ respectively on the x and y axis. Data are generated according to 
+  $f$ respectively on the x and y axis. Simulated data are generated according to 
   \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
-  $k=100$, $p=1000$.\\}
+  $k=100$, $p=1000$.}
   \label{fig:correlation}
@@
 
-\subsection{Simulation study}
+\subsection{Simulation study 1}
 
@@
 simple refit of submodels.
-
 % TODO: Bigger and more distinctive symbols in figures
@@
   \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
-  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.}
+  \vspace{-0.3\baselineskip}
+  \caption{Simulation study 1: Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.
+The projpred approach has the smallest RMSE and false discovery ratio.}
   \label{fig:rmse_vs_fdr}
 \end{figure}
-
 % TODO: Bigger and more distinctive symbols in figures
@@
   \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
-  \caption{Entropy score in the minimal subset variable selection.}
+  \vspace{-0.3\baselineskip}
+  \caption{Simulation study 1: Entropy score in the minimal subset variable selection.  The projpred approach has much smaller entropy score than the other approaches.}
   \label{fig:entropy}
@@
   \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
-  \caption{Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelevant variables on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.\\}
+  \vspace{-0.7\baselineskip}
+  \caption{Body fat example: Stepwise backward selection with and without using a reference model.
+The x-axis denotes the number of selected irrelevant variables on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.
+The reference approach reduces the number of noisy variables selected and the out-of-sample RMSE.}
   \label{fig:bodyfat_step_refvsdata}
 \end{figure}
-
 \begin{table}[tp]
@@
 \centering
-\begin{tabular}{l|r|r}
+\begin{tabular}{l|rr}
 %  \hline
@@
   \hline
-Stepwise selection & 6.92 (0.68) & 48.1 (7.46)    \\
-Reference model + Stepwise selection & 4.71 (0.45) & 25.1 (6.89)   \\
+Stepwise selection & 6.9 (0.7) & 48 (7)    \\
+Reference model + Stepwise selection & 4.7 (0.5) & 25 (7)   \\
 \end{tabular}
-\caption{Mean and standard deviation (between brackets) values of Figure \ref{fig:bodyfat_step_refvsdata}}
+\caption{Body fat example: Mean and standard deviation (between brackets) values of Figure \ref{fig:bodyfat_step_refvsdata}.}
 \label{tab:step_refvsdata}
@@
 
-\subsection{Simulation study}
+\subsection{Simulation study 2}
 \label{simulations}
@@
 % \end{figure}
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
+  \vspace{-0.3\baselineskip}
+  \caption{Simulation study 2: Complete variable selection sensitivity against false discovery rate based on 100 data simulations with one standard deviation error bars.
+The reference approach improves sensitivity and reduces false discovery rate for all methods.}
+  \label{fig:sensitivity_vs_fdr_iterated}
+\end{figure}
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/stability_iterated.pdf}
+  \vspace{-0.3\baselineskip}
+  \caption{Simulation study 2: Complete variable selection stability estimates with 95\% intervals based on 100 data simulations. The reference approach improves stability for all methods.}
+  \label{fig:stability_iterated}
+\end{figure}
 
@@
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
-  \caption{Sensitivity against false discovery rate based on 100 data simulations with one standard deviation error bars.\\}
-  \label{fig:sensitivity_vs_fdr_iterated}
-\end{figure}
-
 %\begin{figure}[tp]
@@
 
+\hypertarget{bodyfat-2}{%
+\subsection{Body fat example: Part 3}\label{bodyfat-3}}
+
 \begin{figure}[tp]
   \centering
-  \includegraphics[width=0.98\textwidth]{graphics/stability_iterated.pdf}
-  \caption{Stability estimates with 95\% intervals based on 100 data simulations.\\}
-  \label{fig:stability_iterated}
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
+  \vspace{-0.3\baselineskip}
+  \caption{Body fat example with noisy variables: Complete variable selection sensitivity against false discovery rate based on 100 bootstrap samples with one standard deviation error bars.
+The improvement from using the reference approach is small (except that the projpred is much better than lasso).}
+  \label{fig:bodyfat_sensitivity_vs_fdr}
 \end{figure}
-
-\hypertarget{bodyfat-2}{%
-\subsection{Body fat example: Part 3}\label{bodyfat-3}}
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
+  \vspace{-0.3\baselineskip}
+  \caption{Body fat example with noisy variables: Complete variable selection stability estimates with 0.95 confidence intervals based on 100 bootstrap samples.
+The improvement from using the reference approach is small (except that the projpred is much better than lasso).}
+  \label{fig:bodyfat_stability}
+\end{figure}
 
@@
 are averaged over 100 bootstrap samples of the respective size.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
-  \caption{Sensitivity against false discovery rate based on 100 bootstrap samples with one standard deviation error bars.\\}
-  \label{fig:bodyfat_sensitivity_vs_fdr}
-\end{figure}
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
-  \caption{Stability estimates with 0.95 confidence intervals based on 100 bootstrap samples.\\}
-  \label{fig:bodyfat_stability}
-\end{figure}
 

### 2020-04-27 paper/ref_approach.tex
minor cleaning

@@
   Variable selection, or more generally, model reduction is an important aspect of the statistical workflow aiming to provide insights from data.
-In this paper we discuss and demonstrate the benefits of using a reference model in variable selection.
+In this paper, we discuss and demonstrate the benefits of using a reference model in variable selection.
 A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
@@
 
-In data based approaches, such as Lasso selection
+In data-based approaches, such as Lasso selection
 \citep{tibshirani1996regression} or stepwise backward/forward
@@
 \end{tabular}
-\caption{Body fat example: Mean and standard deviation (between brackets) values of Figure \ref{fig:bodyfat_step_refvsdata}.}
+\caption{Body fat example: Means and standard deviations (between brackets) of the results shown in Figure \ref{fig:bodyfat_step_refvsdata}.}
 \label{tab:step_refvsdata}

### 2020-04-27 paper/ref_approach.tex
minor edits

@@
 Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods independently of whether or not they use reference models.
-% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
 \end{abstract}
@@
 stepwise backward regression (\emph{steplm}).
-% \footnote{The analysis is based on \texttt{R}-notebook by Vehtari available at
-%   \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.
 The experiments are implemented in \texttt{R} \citep{Rcore2018}.
@@
 comparison we do not fix any of the variables.  The steplm approach is
-carried out combining the \texttt{step} and \texttt{lm} functions in R.
+carried out combining the \texttt{step} and \texttt{lm} functions in \texttt{R}.
 
@@
 predictive approach, and papers by \citet{paper:model_selection} and
-\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} R package \citep{Rprojpred}.
+\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} \texttt{R} package \citep{Rprojpred}.
 
@@
 \begin{tabular}{l|lr|lr}
-%  \hline
 M & projpred & Freq \% & steplm & Freq \%  \\ 
@@
 10 & abdom., age, height, neck, thigh, wrist & 2 & abdom., age, ankle, biceps, weight, wrist & 2 \\
-%   \hline
 \end{tabular}
@@
 We repeat the experiment with a modified data set by adding 84
-unrelated noisy variables so that there are 100 variables in total. 
+unrelated noisy variables, resulting in 100 variables in total. 
 The last two rows of Table
@@
 \begin{tabular}{ll|rrrr}
-%  \hline
 Data  & Method & RMSE Full & RMSE Sel & \# Sel (10-CV avg, sd) & \# Sel noisy (10-CV avg, sd) \\ 
@@
 & steplm & 5.7 & 5.1 & 23\, (26,\; 4.5) &  15\, (19, 4) \\
-%   \hline
 \end{tabular}
@@
 
-\hypertarget{reference-model-approach}{%
+\hypertarget{reference-model-approach}{
 \subsection{Why the reference model helps}\label{reference-model-approach}}
@@
 \begin{itemize}
-\item projpred: The projective prediction approach is used. 
+\item \textbf{projpred}: the projective prediction approach is used. 
   The reference model is a Bayesian linear regression
@@
 
-\item Bayesian stepwise selection (without a reference model): At each step, the fitted model
+\item \textbf{Bayesian stepwise selection (without a reference model)}: at each step, the fitted model
  is a Bayesian linear regression using the regularised horseshoe
@@
 
-\item Bayesian stepwise selection (with a reference model): The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
+\item \textbf{Bayesian stepwise selection (with a reference model)}: the reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
 The same Bayesian
@@
 
-%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
-\item steplm (without a reference model): Stepwise selection using AIC as in the body fat example.
-
-\item steplm (with a reference model): The reference model is the same as for
+\item \textbf{steplm (without a reference model)}: stepwise selection using AIC as in the body fat example.
+
+\item \textbf{steplm (with a reference model)}: the reference model is the same as for
  projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
@@
 simple refit of submodels.
-% TODO: Bigger and more distinctive symbols in figures
-% label order: steplm, bayes.step, projpred
+
 \begin{figure}[tp]
@@
 \end{figure}
-% TODO: Bigger and more distinctive symbols in figures
-% TODO: order steplm, bayes.step, projpred
+
 \begin{figure}[tp]
@@
 
-\hypertarget{bodyfat-2}{%
+\hypertarget{bodyfat-2}{
 \subsection{Body fat example: Part 2}\label{bodyfat-2}}
@@
 \begin{tabular}{l|rr}
-%  \hline
 Method & RMSE & Selected noisy \\ 
@@
 
-% \hypertarget{comparison}{%
-%   \section{A comparison in the normal means problem framework}\label{comparison}}
 \section{Complete variable selection}\label{comparison-complete-subset}
@@
 means a more stable selection.
-
-%Table \ref{tab:comparison} summarises the methods used in the numerical experiments.
 
@@
    projection.elpdEstimate() \;
-%:
    $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;
@@
 \subsection{Alternative complete variable selection methods}
-
-% Many Bayesian approaches for complete variable selection first fit a
-% Bayesian regression model using some sparsifying prior on the
-% regression coefficients, for example, as discussed in
-% \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
-% \cite{johnstone2004needles}.  In our experiments, we include the
-% Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} prior and the
-% regularised horseshoe (RHS) prior \citep{paper:rhs}, which in our experience
-% scales better to higher number of variables as compared to other
-% horseshoe-like priors.
-% \note{Aki: How this paragraph connects to the next paragraph?}
-
-% If these priors have continuous support, as is the case for the DL and
-% horseshoe-like priors \citep{paper:hs,bhadra2017horseshoe+,paper:rhs},
-% there is no canonical way to complete the selection since the
-% posterior probability of an exactly zero signal is always
-% zero. Whereas \cite{paper:dirichlet_laplace} used k-means clustering
-% over the posterior samples to perform the actual selection,
-% \cite{bhadra2017horseshoe+} just focused their analysis on the
-% obtained shrinkage and the correct estimation of the sparse signals
-% without any actual selection.
-
-% For the Bayesian regression
-% models with these priors, we compare the posterior shrinkage and the
-% correct estimation of the sparse signals with and without using a
-% reference model as a noise filter. For this purpose, we consider the
-% average SSE (sum of square errors) and the average SESE (sum of
-% expected square errors) as quantities measuring estimation
-% accuracy. They are defined as \
-% \begin{align}
-% \text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
-% \text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},\ldots,z_{p})d\theta_{j} \\
-% &=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},\ldots,z_{p}], \label{eq:SESE}
-% \end{align}
-% where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value,
-% $\hat{\theta}_{j}$ is the posterior median of each parameter
-% $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities
-% independent of the number of statistical units.  The SESE takes the
-% posterior uncertainty in account and thus also the shrinkage of the
-% posterior distributions, whereas the SSE only measures the bias in the
-% point estimates.  Any (sensible) point estimate could be used to
-% compute the SSE but here we follow \cite{paper:dirichlet_laplace} and
-% use the posterior median. The results that we show later on in Section
-% \ref{shrinkage-signal} are not sensitive to the choice of this point
-% estimate.
-
-% For shrinkage priors, one central aspect is the amount of shrinkage
-% they actually impose on the relevant and irrelevant variables. Ideally,
-% the irrelevant variables should be completely shrunk to zero while the
-% relevant variables should not be shrunk at all. The amount of shrinkage
-% can be quantified by the shrinkage factor $\kappa_{j}$ for each
-% parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$
-% (complete shrinkage). For model \eqref{eq:normal_means_problem2} with
-% a hierarchical shrinkage prior of the type
-% \begin{align}
-% Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,\ldots,p \\
-% &\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
-% \end{align}
-% the shrinkage factor $\kappa_{j}$ is defined as
-% \begin{equation}
-% \kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
-% \end{equation}
-% \
-% For RHS and DL priors we have
-% \begin{equation}
-% \kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}.
-% \end{equation}
-% In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent
-% the global and local shrinkage parameters of the regularised horseshoe
-% prior \cite[for further details see][]{paper:rhs}, whereas on the
-% right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of
-% the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the
-% notation of \cite{paper:dirichlet_laplace}. We use the posterior mean
-% of $\kappa_{j}$ as a point estimate.
-
-%Within the set of complete selection procedures, we consider three
-%Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
-%type prior given by a mixture of a delta distribution in zero and a
-%heavy-tailed distribution \cite[see
-%also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
-%distribution, they show an interesting thresholding property of the
-%median estimator and, based on this observation, present a complete
-%selection procedure using their prior. We refer to this method as
-%\emph{EB.med}. Further, we use a method to control for the local false
-%discovery rate (\emph{loc.fdr}) as described in \cite{paper:efron,
-%  efron2012large}. Finally, we device a simple selection procedure
-%based on posterior credible intervals using the regularised horseshoe
-%prior in which we select variables whose 90\% credible intervals
-%excludes zero (\emph{ci.90}) \note{Reference for this?}.
 
@@
 their mean predictions $\hat{y}$ based on the reference model.
-
-%\note{Aki: ``Type: Complete selection'' doesn't make sense in the table. Maybe we need to discuss when to use the term complete selection and what is the alternative title for this section.}
-
-% \begin{table}[tp]
-% \scriptsize
-% \centering
-% \begin{tabular}{l|l|l|l}
-% Method & Abbreviation & Type & Quantities of interest \\ 
-%  \hline
-% Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
-% Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
-% Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
-% Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
-% Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
-% \end{tabular}
-% \caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
-% \label{tab:comparison}
-% \end{table}
 
@@
 
-% The normal means problem formulation is obtained as explained in
-% Section \ref{comparison} by applying the Fisher-z-transformation to
-% the empirical correlations. We label the reference approach as
-% ``ref'', which consists of using the reference model on top of the
-% computation of the z-values, and the standard approach based on the
-% observed data simply as ``data''. In Section \ref{shrinkage-signal},
-% we analyse the different shrinkage and signal estimates in the context
-% of the full Bayes estimation methods by comparing the ref and data
-% approach. In Section \ref{complete-selection}, we present results for
-% the complete selection procedures.
-
-% \hypertarget{shrinkage-signal}{%
-% \subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
-% In the framework of fully Bayesian estimation methods, we analyse the
-% effect of the reference model using two continuous hierarchical
-% shrinkage priors: the Dirichlet-Laplace
-% \citep{paper:dirichlet_laplace} and the regularised horseshoe prior
-% \citep{paper:rhs}.
-% %
-% For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we
-% use an uniform prior on the interval $(1/p,1/2)$. For the regularised
-% horseshoe prior, we follow the recommendations provided in
-% \cite{paper:rhs} by setting the prior guess of the number of relevant
-% variables to one in order to achieve the highest possible
-% shrinkage. The results are not sensitive with respect to the specific
-% choice.  \ Since, as explained at the start of Section
-% \ref{comparison}, continuous priors usually do not provide an
-% automatic selection procedure, we study the amount of shrinkage and
-% the bias of the posterior medians looking at the SESE and the SSE (see
-% definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the
-% posterior mean of the shrinkage factors.
-
-% \begin{figure}[tp]
-%   \centering
-%   \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
-%   \caption{Posterior intervals for the parameters of the normal means
-%     problem ($n=50$, $\rho=0.3$) using the regularised horseshoe
-%     prior. Posterior means and one standard deviation intervals are
-%     depicted. Relevant and non-relevant variables are displayed in red
-%     and in blue respectively. Horizontal dashed lines corresponds to
-%     the true value of the mean for the relevant variables.\\}
-%   \label{fig:posterior_intervals}
-% \end{figure}
-
-% Figure \ref{fig:posterior_intervals} shows an example of posterior
-% distributions for the model \eqref{eq:normal_means_problem2} using the
-% regularised horseshoe prior with the data approach on the left and the
-% ref approach on the right-hand side. It is evident how the reference
-% model helps in tearing apart the signal from the noise, resulting in
-% less biased estimates and clearer separation between relevant and
-% irrelevant variables. This is quantified in Figure \ref{fig:SESE_SSE}
-% where average SESE and SSE are depicted based on 100 simulations. We
-% observe that the reference approach (in orange) has a clearly lower
-% estimate for both the SESE and the SSE. As $n$ and $\rho$ increase,
-% the amount of error diminishes, as expected, due to a larger amount of
-% information of the relevance of each variable provided by the
-% data. The two priors (RHS and DL) seem to achieve similar results
-% under all conditions.
-
-% \begin{figure}[tp]
-%   \centering
-%   \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
-%   \caption{Average SESE and SSE with one standard deviation intervals based on 100 simulations.\\}
-%   \label{fig:SESE_SSE}
-% \end{figure}
-
-% Figure \ref{fig:k} shows the posterior means for the shrinkage factors
-% of each parameter using the regularised horseshoe prior, averaged over
-% 100 data simulations. Relevant and non-relevant variables are
-% highlighted in red and blue respectively. The ideal shrinkage would be
-% $\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is
-% noise. The shrinkage factors using the data and reference approach are
-% depicted on the y-axis and on the x-axis respectively. If the
-% reference model did not make any difference, we would expect the
-% points to lie on the diagonal. For the non-relevant variables points
-% are on the diagonal on average for all the simulated scenarios, which
-% implies that their shrinkage was not improved by the reference
-% approach. For the relevant variables, the points are always located
-% under the diagonal, which means that the reference model helps and
-% true signals are shrunk less. This benefit is roughly proportional to
-% the difficulty of the problem, that is, the benefit increases with
-% lower correlations and a smaller number of observations. The perfect
-% distinction of the two clusters of variables (relevant and
-% non-relevant) observable on both the marginal distributions of the
-% shrinkage factors is due to the averaging over the 100 data
-% simulations. In a single data realisation, there is more noise and the
-% cluster are closer and overlapping. The results for the
-% Dirichlet-Laplace prior are very similar.
-
-% \begin{figure}[tp]
-%   \centering
-%   \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
-%   \caption{Average posterior mean values for the shrinkage factors
-%     using the regularised horseshoe prior based on 100
-%     simulations. Relevant and non-relevant variables are displayed in
-%     red and blue respectively.\\}
-%   \label{fig:k}
-% \end{figure}
 \begin{figure}[tp]
@@
 misspecified models with cross-validation \citep{bengio2004no}.
-
-%\begin{figure}[tp]
-%  \centering
-%  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr.pdf}
-%  \caption{Sensitivity against false discovery rate based on 100 data simulations.\\}
-%  \label{fig:sensitivity_vs_fdr}
-%\end{figure}
 
@@
 
-\hypertarget{conclusion}{%
+\hypertarget{conclusion}{
 \section{Conclusion}\label{conclusion}}
@@
 model itself and assessing its predictive performance.
-% We did provide
-% a generic way to build simple reference models, but those may not
-% necessarily be appropriate in all situations.
 To build good predictive reference models, which are specifically
@@
 \citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo
-\citep{hoffman2014no,betancourt2017conceptual}, through the R-packages 
+\citep{hoffman2014no,betancourt2017conceptual}, through the \texttt{R}-packages 
 \texttt{rstan} \citep{Rrstan} and \texttt{rstanarm} \citep{Rrstanarm}.
@@
 \appendix
-
-%\hypertarget{ap:shrinkage_signal}{%
-%\section{Appendix: Shrinkage factors with Dirichlet-Laplace prior}\label{ap:shrinkage_signal}}
-%Figure \ref{fig:k_DL} shows the posterior mean shrinkage factors using the Dirichlet-Laplace prior for the normal means problem in the simulated data study of Section \ref{comparison}.
-The result is qualitatively equal to the regularised horseshoe prior's one (see Figure \ref{fig:k}).
-
-%\begin{figure}[tp]
-%  \centering
-%  \includegraphics[width=0.98\textwidth]{graphics/k_DL.pdf}
-%  \caption{Average posterior mean values for the shrinkage factors using the Dirichlet-Laplace prior based on 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
-%  \label{fig:k_DL}
-%\end{figure}
 

### 2020-05-02 paper/ref_approach.tex
modified first page for submission

@@
 
+\vspace{2cm}
+
+\textbf{Keywords}: variable selection, projection predictive approach, reference model
+
+\textbf{Corresponding author}: Federico Pavone (\texttt{federicopavone01@gmail.com})
+
+\textbf{Declarations}:
+\begin{itemize}
+\item \textbf{Funding}: Academy of Finland (grants 298742, and 313122), Finnish Center for Artificial Intelligence and Technology Industries of Finland Centennial Foundation (grant 70007503; Artificial Intelligence for Research and Development)
+
+\item \textbf{Conflicts of interest/Competing interests}: no conflicts of interest
+
+\item \textbf{Availability of data and material}: data and material available at \url{https://github.com/fpavone/ref-approach-paper}
+
+\item \textbf{Code availability}: code available at \url{https://github.com/fpavone/ref-approach-paper}
+\end{itemize}
+
+\newpage
+
 \hypertarget{introduction}{%

### 2020-07-03 paper/titlepage.tex
title page for subsmission

--- 2020-05-02 paper/ref_approach.tex
@@
 
-\newpage
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-In statistical applications, one of the main steps in the modelling
-workflow is variable selection, which is a special case of
-model reduction. Variable selection (also known as feature or 
-covariate selection) may have multiple goals.  First,
-if the variables themselves are of interest, we can use variable
-selection to infer which variables contain predictive information
-about the target. Second, as simpler models come with the
-advantages of reduced measurement costs and improved interpretability,
-we may be interested in finding the minimal subset of variables which
-still provides good predictive performance (or good balance between
-simplicity and predictive performance).  When the predictive
-capability is guiding the selection, the true data generation
-mechanism of future data can be approximated either by using the
-observed data directly or alternatively by using predictions from a
-\emph{reference model} \citep{vehtari2012survey}.
-
-In data-based approaches, such as Lasso selection
-\citep{tibshirani1996regression} or stepwise backward/forward
-regression \citep{venables2013modern,harrell2015regression}, the
-observed empirical data distribution is utilised as a proxy of future
-data usually in combination with cross-validation or information
-criteria to provide estimates for out-of-sample predictive
-performance.  In contrast, reference model based methods approximate
-the future data generation mechanism using the predictive distribution
-of a reference model, which can be, for example, a full-encompassing
-model including all variables.  The main assumption under any
-reference model approach is that we operate in an
-$\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
-constructed a model which reflects our beliefs about
-the future data in the best possible way and which has passed model checking and criticism
-\citep[see, e.g.][]{gelman2013bayesian,gabry2019visualization}.  The reference model approach
-has been used in Bayesian statistics at least since the seminal
-work of \citet{paper:reference_lindley}. For more historical
-references, see \citet{vehtari2012survey} and
-\citet{paper:model_selection}, and for most recent methodological
-developments see \citet{paper:projpred}.
-
-Reference models have been also used in non-Bayesian contexts, in which
-\cite{harrell2015regression} describes them as full models that can be
-thought of as a ``gold standard'' (for a given application).  For
-example, \cite{faraggi2001understanding} deal with the necessity of
-identifying interpretable risk groups in the context of survival data
-using neural networks, which typically perform very well in terms of
-prediction, but whose variables are difficult to be understood in
-terms of relevance.  \cite{paul2008preconditioning}, using the term
-preconditioning, explore approximating models fitting Lasso or
-stepwise regression against consistent estimates $\hat{y}$ of a
-reference model instead of the observed responses $y$.
-Whatever the terminology or applied statistical framework, reference
-models offer a powerful approach to improving variable selection as we
-will demonstrate in the present paper.
-
-This paper is structured as follows. In Section
-\ref{ref-intro}, we review the concept of the reference
-model, its benefits with examples and how it can be used as a filter
-on data in a simple way. In Section \ref{comparison-minimal-subset} and 
-Section \ref{comparison-complete-subset}, we show the
-benefits of a reference model approaches for minimal and complete 
-variable selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
-
-\section{Reference models in variable selection}
-\label{ref-intro}
-
-In this section, we will provide an initial motivation and intuition 
-for the use of reference models to improve variable selection methods.
-We will start with a case study that is repeatedly used throughout
-the paper to illustrate the benefits of reference models before we dive deeper
-into the theoretical reasons why reference models help in variable selection.
-
-\subsection{Body fat example: Part 1}
-\label{bodyfat-1}
-
-To motivate the further discussion and experiments, we start by a simple
-variable selection example using body fat data by \citet{johnson1996fitting}.
-We compare the projective prediction approach (\emph{projpred},
-\citet{paper:projpred}) which uses a reference model, and classic
-stepwise backward regression (\emph{steplm}).
-The experiments are implemented in \texttt{R} \citep{Rcore2018}.
-
-The target variable of interest is the amount of body fat, which is
-obtained by a complex and expensive procedure consisting in immersing a 
-person in a water tank and carrying out different measurements and computations. 
-Additionally, we have information about 13
-variables which are anthropometric measurements (e.g., height, weight
-and circumference of different body parts). The
-variables are highly correlated which causes additional
-challenge in the variable selection. In total, we have 251
-observations. The goal is to find the model which is able to predict
-the amount of body fat well while requiring the least amount of
-measurements for a new person.
-
-\cite{paper:bodyfat} report results using steplm with a significance
-level of 0.157 with AIC selection \citep{akaike1974new}, fixing
-abdomen and height to be always included in the model. For better
-comparison we do not fix any of the variables.  The steplm approach is
-carried out combining the \texttt{step} and \texttt{lm} functions in \texttt{R}.
-
-For the selection via projpred, the Bayesian reference model includes
-all the variables using a regularised horseshoe prior~\citep{paper:rhs} on the
-variable coefficients. Submodels are explored using
-forward search (the results are not sensitive to whether forward or
-backward search is used), and the predictive utility is the expected
-log-predictive density (elpd) estimated using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
-\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.  We select the smallest  submodel with an elpd score similar to the reference model
-when taking into account the uncertainty in estimating the predictive
-model performance. See Appendix A for brief review of projection
-predictive approach, and papers by \citet{paper:model_selection} and
-\citet{paper:projpred} for more details. The complete projpred approach is implemented in the \texttt{projpred} \texttt{R} package \citep{Rprojpred}.
-
-The inclusion frequencies of each variable in the final model given 100
-bootstrap samples are shown in Figure
-\ref{fig:inclusion_frequencies}. In case of projpred there are two
-variables, `abdomen' and `weight', which have inclusion frequencies
-above 50\% (`abdomen' is the only one included always), the third most
-frequently included is `wrist' at 44\%, and the fourth one is `height'
-at 35\%.  The steplm approach has seven variables with inclusion
-frequencies above 50\%. Such a higher variability and lower stability
-of steplm can be observed also in the bootstrap model selection
-frequencies reported in Table \ref{tab:model_frequencies}. For
-example, the first five selected models have a cumulative frequency of
-76\% with projpred, but only of 14\% with steplm. In addition, the
-sizes of the selected models with projpred are much smaller than the ones 
-selected with steplm.
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/inc_prob.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{Body fat example: Bootstrap inclusion frequencies calculated from 100 bootstrap samples. The projpred approach has less variability on which variables are selected.}
-  \label{fig:inclusion_frequencies}
-\end{figure}
-
-\begin{table}[tp]
-\footnotesize
-\centering
-\begin{tabular}{l|lr|lr}
-M & projpred & Freq \% & steplm & Freq \%  \\ 
-  \hline
-1 & abdom., weight & 39 & abdom., age, forearm, height, hip, neck, thigh, wrist & 4 \\
-2 & abdom., wrist & 10 & abdom., age, chest, forearm, height, neck, thigh, wrist & 4 \\
-3 & abdom., height & 10 & abdom., forearm, height, neck, wrist & 2 \\
-4 & abdom., height, wrist & 9 & abdom., forearm, neck, weight, wrist & 2 \\
-5 & abdom., weight, wrist & 8 & abdom., age, height, hip, thigh, wrist & 2 \\
-6 & abdom., chest, height, wrist & 2 & abdom., age, height, hip, neck, thigh, wrist & 2 \\
-7 & abdom., biceps, weight, wrist & 2 & abdom., age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
-8 & abdom., height, weight, wrist & 2 & abdom., age, biceps, chest, height, neck, wrist & 2 \\
-9 & abdom., age, wrist & 2 & abdom., age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
-10 & abdom., age, height, neck, thigh, wrist & 2 & abdom., age, ankle, biceps, weight, wrist & 2 \\
-\end{tabular}
-\caption{Body fat example: Bootstrap model selection frequencies from 100 bootstrap samples.  The projpred approach has less variability on which variable combinations are selected.}
-\label{tab:model_frequencies}
-\end{table}
-
-The first two rows of Table \ref{tab:model_performances} show the
-predictive performances, in terms of cross-validated root mean square
-error (RMSE), of the full model and the selected models using projpred
-or steplm.  There is no significant difference in predictive performance
-of the selected models by different approaches even if there is
-clear difference in the number of selected variables. This can be explained by high
-correlation between the variables and different combinations can
-provide similar predictive accuracy.
-
-We repeat the experiment with a modified data set by adding 84
-unrelated noisy variables, resulting in 100 variables in total. 
-The last two rows of Table
-\ref{tab:model_performances} show the cross-validated RMSE, the size
-of the selected model and the number of selected noisy variables using
-projpred or steplm. The results show that projpred has similar
-predictive performance and the same number of selected variables as
-with the original data, whereas the stepwise regression has worse
-predictive performance and the number of selected variables is much
-higher and include a large number of irrelevant variables.
-
-\begin{table}[tp]
-\footnotesize
-\centering
-\begin{tabular}{ll|rrrr}
-Data  & Method & RMSE Full & RMSE Sel & \# Sel (10-CV avg, sd) & \# Sel noisy (10-CV avg, sd) \\ 
-  \hline
-body fat & projpred & 4.4 & 4.5 &  2\, (2.3, 0.5) &   \\
-& steplm & 4.4 & 4.5 & 7\, (6.0, 0.9) &  \\
-\hline
-+ noisy variables & projpred & 4.5 & 4.5 &  2\, (2.0, 0.0)&  0\,\; (0,\, 0)  \\
-& steplm & 5.7 & 5.1 & 23\, (26,\; 4.5) &  15\, (19, 4) \\
-\end{tabular}
-\caption{Body fat example: Predictive performances with original data (first two
-  rows) and with extra noisy variables (last two rows) estimated with
-  10-fold cross-validation. Abbreviations: RMSE = root mean squared error;
-  Full = full model; Sel = selected submodel; 
-  \# Sel = total number of selected variables;
-  \# Sel noisy = number of selected noisy variables. 
-  10-CV avg = average over the 10 folds in cross-validation. 10-CV sd = standard deviation
-  over the 10 folds in cross-validation.}
-\label{tab:model_performances}
-\end{table}
-
-Both projpred and steplm compare a large number of models using either
-forward or backward search, which can lead to selection induced
-overfitting, but even with 100 variables, projpred is able to select a
-submodel with similar performance as the full model. In this example, the two
- compared methods also differ in other aspects than the usage of a reference 
- model, such as that projpred
-uses Bayesian inference and steplm uses maximum likelihood estimation. 
-However, as we show in the present paper, one of the primary difference 
-with respect to quality of the variable selection is indeed whether or 
-not a reference model is applied.
-
-\subsection{Benefits and costs of using a reference model}
-
-A properly designed reference model is able to filter parts of the
-noise present in the data, and hence to provide an improved and more
-stable selection process. This holds even if the reference model does
-not perfectly resemble the true data generating process. Moreover, our
-analyses indicate that the substantial reduction of variance
-attributable to noise is usually more important than small potential
-bias due to model misspecification.  We argue that, regardless of how
-the reference model is set up and used in the inference procedure, it
-can be always seen as acting as a filter on the observed
-data. Furthermore, regardless of what specific model selection method
-is used, a reference model can be used instead of raw data during the
-selection process to improve the stability and selection
-performance. Our results indicate that the core reason why the
-reference model based methods perform well is the reference model
-itself, rather than the specific way of using it.  In general, the
-less data we have and the more complex the estimated models are, the
-higher is the benefit of using a reference models as the basis for
-variable selection.
-
-If one of the models to be compared is the full model, which can be
-used as a reference model, there is no additional cost of using a
-reference model as it was estimated as part of the analysis anyway.
-Sometimes including all the available variables in an
-elaborate model can be computationally demanding.  In such a
-case, even simpler screening or dimensionality reduction techniques,
-as for example the supervised principal components
-\citep{bair2006prediction,piironen2018} can produce useful reference
-models.
-
-\hypertarget{reference-model-approach}{
-\subsection{Why the reference model helps}\label{reference-model-approach}}
-
-A good predictive model is able to filter part of the noise present in
-the data. The noise is the main source of the instability in the selection
-and tends to
-obscure the relevance of the variables in relation to the target
-variable of interest. We demonstrate it with the following simple
-explanatory example taken from \cite{paper:projpred}. The data
-generation mechanism is
-\begin{alignat}{2} \label{eq:simulated_data}
-     &f\sim \N(0,1) && \nonumber \\ 
-     Y|&f\sim \N(f,1) && \\
-     X_{j}|&f \overset{iid}{\sim} \N(\sqrt{\rho}f,1-\rho) \quad &&j=1,\ldots,k \nonumber \\
-     X_{j}|&f \overset{iid}{\sim} \N(0,1) &&j=k+1,\ldots,p \nonumber,
-\end{alignat}
-where $f$ is the latent variable of interest of which $Y$ is a noisy
-observation. The first $k$ variables are strongly related to the
-target variable $Y$ and correlated among themselves. Precisely, $\rho$
-is the correlation among any pair of the first $k$ variables, whereas
-$\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between
-any relevant variable and, respectively, $f$ and $Y$. If we had an
-infinite amount of observations, the sample correlation would be equal
-to the true correlation between $X_j$ and $Y$. However, even in this
-ideal asymptotic regime, this correlation would still remain a biased
-indicator of the true relevance of each variable (represented by the
-correlation between $X_j$ and $f$) due to the intrinsic noisy nature
-of $Y$.
-
-When using a reference model, we first obtain predictions for $f$
-using all the variables $\{X_{j}\}_{j=1}^{p}$ taking into account
-that we have only observed the noisy representation $Y$ of $f$. If our
-model is good, we are able to describe $f$ better than $Y$ itself can,
-which improves the accuracy in the estimation of the relevance of the
-variables.  Figure \ref{fig:correlation} illustrates this process in
-the form of a scatter plot of (absolute) correlations of the
-variables with $Y$ against the corresponding correlations with the
-predictions of a reference model (in this case the posterior
-predictive means of model \eqref{eq:ref_mod}; see Section
-\ref{simulations}). Looking at the marginal distributions, we see
-that using a reference model to filter out noise in the data, the two
-groups of variables (relevant and non-relevant) can be distinguished
-much better than when the correlation is computed using the observed
-noisy data directly.
-\begin{figure}[tp]
-  \centering
-  \vspace{-5mm}
-  \includegraphics[width=0.35\textwidth]{graphics/correlation.pdf}
-  \vspace{-0.5\baselineskip}
-  \caption{Sample correlation plot of each variable (relevant in red, 
-  non-relevant in blue) with the target variable $y$ and the latent variable 
-  $f$ respectively on the x and y axis. Simulated data are generated according to 
-  \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
-  $k=100$, $p=1000$.}
-  \label{fig:correlation}
-\end{figure}
-
-\hypertarget{comparison-minimal-subset}{
-\section{Minimal subset variable selection}\label{comparison-minimal-subset}}
-
-In the body fat example above, our two simultaneous goals were to 
-obtain good predictive performance and to select a smaller number of variables. 
-When the goal is to select a minimal subset of variables,
-which have similar predictive performance as the full model, we call it
-\emph{minimal subset variable selection}. This minimal subset might
-exclude variables which have some predictive information about the
-target but, given the minimal subset, these variables are not able to
-provide such additional information that would improve predictive
-performance in a substantial manner.
-The usual reason for this is that the relevant variables
-which are not in the minimal subset are highly correlated with variables already in
-the minimal subset. We will return to a problem of finding all
-the variables with some predictive power in Section~\ref{complete-selection}.
-
-\subsection{Simulation study 1}
-
-Using the data generating mechanism \eqref{eq:simulated_data}, we
-simulate data sets of different sizes with a relatively large number
-of variables $p=70$, with $k=20$ of them being predictive.  We compare
-the minimal subset variable selection performance of the projection
-predictive approach (which uses a reference model and it is referred to as projpred), 
-a Bayesian stepwise
-forward selection with and without a reference model, and maximum
-likelihood stepwise forward selection with and without a reference
-model (steplm). The following is a summary of the implementation of the compared methods:
-\begin{itemize}
-\item \textbf{projpred}: the projective prediction approach is used. 
-  The reference model is a Bayesian linear regression
-  model using the first five supervised principal components \citep{piironen2018} as predictors
-  and the full posterior predictive distribution as the basis of the projection.   
-  The search heuristic  is forward search and the predictive performance 
-  is estimated via 10-fold cross-validation. The selection continues
-  until the predictive performance is close to the predictive
-  performance of the reference model. See more details in Appendix A.
-
-\item \textbf{Bayesian stepwise selection (without a reference model)}: at each step, the fitted model
- is a Bayesian linear regression using the regularised horseshoe
-  prior and the variable excluded is the one with the highest Bayesian
-  $p$-value defined as $\text{min}\{P(\theta\leq0 \; | \; D),P(\theta>0 \; | \; D)\}$,
-  where $D$ stays for the observed data.
-The selection continues if the reduced model has an elpd score higher 
-(i.e., better) than the current model.
-
-\item \textbf{Bayesian stepwise selection (with a reference model)}: the reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$.
-The same Bayesian
-  $p$-value selection strategy as in the data based Bayesian stepwise selection is used.
-
-\item \textbf{steplm (without a reference model)}: stepwise selection using AIC as in the body fat example.
-
-\item \textbf{steplm (with a reference model)}: the reference model is the same as for
- projpred, but only point predictions (posterior predictive means) $\hat{y}$ 
- are used to replace the target variable $y$. The same AIC selection strategy 
- as in the data based steplm is used.
-
-\end{itemize}
-
-In Figure \ref{fig:rmse_vs_fdr}, the predictive performance is shown
-for different values of $n$ and $\rho$ in terms of RMSE and the false discovery rate (FDR, the ratio of the number of non-relevant selected
-variables over the number of selected variables) of the selected submodel,
-averaged after 100 data simulations. We see that projpred has superior FDR and the
-smallest RMSE. Using a reference model improves steplm significantly,
-but the minimal subset variable selection stays unreliable. Stepwise
-Bayesian linear regression is better than steplm when comparing both methods with
-and without a reference model, respectively. However, the minimal subset variable
-selection of the Bayesian linear regression is still less reliable than projpred.
-
-When the variable selection is repeated with different simulated data
-sets, there is some variability in the selected variables. We
-measure the stability of variable selection by computing the entropy
-of the observed distribution of the included variables over different models. The smallest entropy
-would be obtained if the approach always selected the same set of
-variables, and the largest entropy would be observed if the approach
-would always selected different sets of variables. Therefore, lower entropy 
-corresponds to a more stable selection. Highly correlated predictive variables may happen to be
-selected alternately, thus making stability estimation of the
-selection a non-trivial task. Entropy can not distinguish the interchangeability 
-due to correlation from instability. Thus, such a measure should be 
-considered as a relative, and not as an absolute, measure of stability.
-Figure \ref{fig:entropy} shows the entropy scores for the different compared
-methods. The use of a reference model
-improves the stability of steplm in variable selection slightly, while it makes
-little difference for the Bayesian linear regression. The
-projpred approach turns out to be far more stable than all
-other methods. This is likely due to projpred being based on better
-decision theoretical formulation which 1) takes into account the full
-predictive distribution and not just point estimate and 2) projects
-the reference model posterior to the submodel instead of using a
-simple refit of submodels.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Simulation study 1: Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.
-The projpred approach has the smallest RMSE and false discovery ratio.}
-  \label{fig:rmse_vs_fdr}
-\end{figure}
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Simulation study 1: Entropy score in the minimal subset variable selection.  The projpred approach has much smaller entropy score than the other approaches.}
-  \label{fig:entropy}
-\end{figure}
-
-\hypertarget{bodyfat-2}{
-\subsection{Body fat example: Part 2}\label{bodyfat-2}}
-
-Here we repeat the selection of Section \ref{bodyfat-1} via
-stepwise backward regression. In this case, the overall number of
-variables (original plus noisy) is 100, as it was in the last part of
-Section \ref{bodyfat-1}. We compare results with and without using
-a simple reference model approach outlined in \eqref{eq:ref_mod} with
-steplm. Figure \ref{fig:bodyfat_step_refvsdata} shows the number of
-irrelevant variables included in the final model and the out-of-sample
-root mean square error (RMSE). Results are based on 100 bootstrap
-samples on the whole dataset, and the predictive performance is tested
-on the observations excluded at each bootstrap sample. We observe that
-the reference model reduces the number of irrelevant variables included
-in the final model. This leads to less overfitting and thus to
-improved out-of-sample predictive performance in terms of RMSE. The
-reference model approach applied to the stepwise backward regression
-achieves outstanding improvements considering its simplicity, yet it
-does not reach the goodness of the much more sophisticated projective
-prediction approach (see results of Section \ref{bodyfat-1}).
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
-  \vspace{-0.7\baselineskip}
-  \caption{Body fat example: Stepwise backward selection with and without using a reference model.
-The x-axis denotes the number of selected irrelevant variables on the left and the out-of-sample RMSE on the right-hand side based on 100 bootstrap samples.
-The reference approach reduces the number of noisy variables selected and the out-of-sample RMSE.}
-  \label{fig:bodyfat_step_refvsdata}
-\end{figure}
-\begin{table}[tp]
-\footnotesize
-\centering
-\begin{tabular}{l|rr}
-Method & RMSE & Selected noisy \\ 
-  \hline
-Stepwise selection & 6.9 (0.7) & 48 (7)    \\
-Reference model + Stepwise selection & 4.7 (0.5) & 25 (7)   \\
-\end{tabular}
-\caption{Body fat example: Means and standard deviations (between brackets) of the results shown in Figure \ref{fig:bodyfat_step_refvsdata}.}
-\label{tab:step_refvsdata}
-\end{table}
-
-\section{Complete variable selection}\label{comparison-complete-subset}
-\label{complete-selection}
-
-An alternative to minimal subset variable selection is \emph{complete
-  variable selection} in which the goal is to find all relevant
-variables that have some predictive information about the target. In
-complete variable selection, it is possible that there are theoretically
-relevant variables, but given finite noisy data we are not able to infer their relevance.
-The projection predictive approach was originally designed for the minimal subset
-variable selection but we will test a simple iterative variant for the complete
-variable selection case in this Section.
- In addition, we analyse the benefits of the reference
-model approach in combination with three other
-methods which have been specifically designed for complete variable selection. 
-As the criteria of selection performance, we evaluate the average false
-discovery rate and the average
-sensitivity (i.e., the ratio of the number of relevant selected
-variables over the total number of relevant variables). We also provide
-a comparison of the stability of the selection by means of a stability
-measure proposed by \citet{paper:stability}, which goes from 0 to 1 and a higher value 
-means a more stable selection.
-
-\subsection{Iterative projections}
-
-We modify the projection predictive approach for complete variable
-selection by using it iteratively.  Applying the straightforward
-implementation of projpred, we are able to select a minimal subset of
-variables, which yield to a model with a predictive performance
-comparable to the full model's predictive performance. 
- The iterative projection repeats
-the projpred selection for different iterations, at each time
-excluding the variables selected in the previous
-iterations from the search.
- At each iteration the selected submodel size corresponds to the
-one having a predictive performance close enough to the baseline
-model, which in this iterative version is the submodel with the
-highest predictive score explored at the current iteration. This translates
-in the following stopping rule at each iteration:
-\begin{equation} 
-\label{eq:rule_of_thumb}
-\text{min} \{i\in \{0,\ldots,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \},
-\end{equation}
-where $i$ indexes the submodel size and ``best'' stands for the best predictive explored submodel
-at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
-the stopping rule (see Algorithm \ref{alg:iterated_proj}).
-The choice of the hyperparameter $\alpha$ is non-trivial, and we have 
-observed sensitivity of the selection to such a choice, mainly when using cross-validation with a small
-number of observations or not very predictive variables. 
-In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package, that is, $\alpha=0.16$.
-
-\begin{center}
-\begin{algorithm}[H]
-\SetAlgoLined
-\KwResult{$R:=\{\text{selected variables}\}$}
- $F:=\{\text{set of variables}\}$ \;
- $R=\{\emptyset\}$ \;
- Fit reference model\;
- \While{$F\neq\{\emptyset\}$}{
-   projection.HeuristicSearch() \;
-   projection.elpdEstimate() \;
-   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;
-
-  \eIf{$S=\{\emptyset\}$}{
-   break \;
-   }{
-   $R=R\cup S$\;
-   $F=F\setminus S$\;
-  }
- }
- \caption{Automated iterative projections}
- \label{alg:iterated_proj}
-\end{algorithm}
-\end{center}
-
-In the experiments shown in the next sections, we include an additional iterative
-method which we refer to as `iterative lasso'. It consists of the same iterative
-algorithm as iterative projpred expect for not using any reference model, but
-the lasso method for variable selection, instead.
-That is, it uses the observed target values instead of predictions of the reference model.
-The comparison with iterative lasso can help to disentangle the effects
-of the iterative procedure and the usage of a reference model in complete feature selection.
-
-\subsection{Alternative complete variable selection methods}
-
-We consider three alternative complete selection methods:
- the control of the local
-false discovery rate \citep{paper:efron, efron2012large}, the
-empirical Bayes median \citep{johnstone2004needles}, and the selection
-by posterior credible intervals.
-
-The control of the local false discovery rate consists of testing the
-z-values $\{z_{j}\}_{j=1}^{p}$ of a normal mean problem (explained in Section \ref{simulations}) 
-on whether they belong to the
-theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
-meaning no relevance) against the alternative hypothesis distribution
-$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
-distribution (see expression \eqref{eq:normal_means_problem2}). The
-quantity of interest is the local false discovery rate (loc.fdr)
-defined as: \
-\begin{equation}
-\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
-\end{equation}
-where $\pi_{0}$ is the prior probability of $H_0$ and
-$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
-distribution of the z-values. The latter is estimated using splines
-with 7 degrees of freedom. We select variables with local false
-discovery rate below $0.2$, which is suggested by
-\citet{efron2012large} as it corresponds to a Bayes factor larger than
-36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
-sensitive to the specific value. To estimate $\pi_{0}$ from the data,
-we use the default setting provided by the \texttt{R}-package
-\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr}.
-
-The empirical Bayes median approach consists of fitting a Bayesian
-model with a prior composed by a mixture of a delta spike in zero and
-a heavy-tailed distribution. We use the implementation in the
-\texttt{R}-package \texttt{EbayesThresh}
-\citep{Silverman+etal:2017:EbayesThresh}. As suggested by
-\cite{johnstone2004needles}, we use a Laplace distribution resulting
-in a thresholding property, that is, there exists a threshold value
-such that all the data under that threshold have posterior median
-equal to zero. Therefore the selection is done by selecting only those
-parameters whose posterior median is different from zero. The
-hyperparameter of the Laplace distribution and the mixing weight of
-the prior are estimated by marginal maximum likelihood.
-
-The selection
-by 90\% posterior credible intervals is done using the regularised
-horseshoe prior \Citep{paper:rhs} and selecting those variables whose posterior
-distribution does not include zero in the interval between the 5\% and
-the 95\% quantiles.
-
-All of these methods provide a complete selection approach and we
-compare their performance with and without using a reference model.
-That is, in the data condition, we apply the method on the original
-data $y$ while, in the reference model condition, we replace $y$ by
-their mean predictions $\hat{y}$ based on the reference model.
-
-\subsection{Simulation study 2}
-\label{simulations}
-
-The iterative projection applies straightforwardly to data, whereas
-to investigate the performance of the three alternative complete selection approaches,
-we are going to use simulations based on the normal means problem.
-The normal means problem consists of estimating the (usually
-sparse) vector of means of a vector of normally distributed
-observations. The dimensionality of the vector of means is denoted by
-$p$ and $\{z_{j}\}_{j=1}^{p}$ is the vector of observations of the
-random variables $\{Z_{j}\}_{j=1}^{p}$. The task is to estimate the
-latent variables $\{\theta_{j}\}_{j=1}^{p}$ of the following model: \
-\begin{equation}\label{eq:normal_means_problem}
-Z_{j}|\theta_{j},\sigma\overset{ind}{\sim}\N(\theta_{j},\sigma^{2}), \quad j=1,\ldots,p.
-\end{equation}
-This is equivalent to a linear regression where the design matrix is
-the identity matrix with the number of variables being equal to the
-number of observations. This formulation can be found in practice, for
-example, in the analysis of microarray data, where a large set of
-genes are tested in two groups of patients labeled as positive or
-negative to some disease \citep{paper:efron,efron2012large}. The
-objective of the analysis is to select the subset of genes
-statistically relevant to the disease. One common way to proceed is to
-compute the two-sample $t$-statistic for every gene separately.  After
-normalising these statistics, they then become the data $Z$ in the
-normal means problem \eqref{eq:normal_means_problem}. For further
-details see the examples by \cite{paper:efron, efron2012large}.
-
-In our experiments, we retrieve the normal means problem from the
-sample correlations between the target and the variables using the
-Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a
-continuous target random variable $Y,$ a set of $p$ continuous
-variables $\{X_{j}\}_{j=1}^{p}$, and denote
-$\rho_{j}=\Cor(Y,X_{j})$. Further, suppose we have observed $n$
-statistical units and define $r_{j}$ the sample correlation between
-the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the
-$j$-th variable $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the
-Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as
-$T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate
-normally distributed, the corresponding transformed correlations are
-approximately normally distributed with known variance: \
-\begin{equation} \label{eq:fisher_transformation}
-T_{F}(r_{j})\overset{ind}{\sim} \N\left(T_{F}(\rho_{j}),\frac{1}{n-3}\right), \quad j=1,\ldots,p.
-\end{equation}
-Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and
-denoting the results as $z_{j}$, we have the formulation
-\eqref{eq:normal_means_problem} of the normal means problem, this time
-with unit variance: \
-\begin{equation} \label{eq:normal_means_problem2}
-Z_{j}|\theta_{j}\overset{ind}{\sim}\N(\theta_{j},1), \quad j=1,\ldots,p.
-\end{equation}
-In this case, the quantities of interest $\theta_{j}$ are equal to
-$\sqrt{n-3}\,T_{F}(\rho_{j})$.
-
-In our simulations, we use different levels of correlation 
-$\rho\in\{0.3,0.5\}$ and numbers of
-observations $n\in\{50,70,100\}$. The total number of variables $p$
-and the number of relevant variables $k$ are fixed to $p = 1000$ and
-$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
-more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
-use a reference model which a Bayesian linear regression using the first five
-supervised principal components (SPC) as variables and imposing an hierarchical prior on
-their coefficients:
-\begin{equation}
-\label{eq:ref_mod}
-\begin{aligned}
-    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} \N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,\ldots,n \\
-    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} \N(0,\tau^{2})\\
-    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
-    \end{aligned} &j=1,\ldots,5 \\ 
-    &\sigma \sim t_{3}^{+}(0,10). \\
-\end{aligned}
-\end{equation}
-In the above, $u_{ij}$ represents the $j$-th SPC evaluated at
-observation $i$, and $s_{max}$ denotes the sample standard deviation
-of the largest SPC.  The SPCs are computed using the
-\texttt{R}-package \texttt{dimreduce} (\url{https://github.com/jpiironen/dimreduce}) setting the screening threshold
-parameter at $0.6s_{max}$.  In our experiments, the results are not
-sensitive to the specific choice of the screening threshold, yet a more
-principled approach would be to use cross-validation to select the
-threshold as done by \citet{paper:projpred}.
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/sensitivity_vs_fdr_iterated.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Simulation study 2: Complete variable selection sensitivity against false discovery rate based on 100 data simulations with one standard deviation error bars.
-The reference approach improves sensitivity and reduces false discovery rate for all methods.}
-  \label{fig:sensitivity_vs_fdr_iterated}
-\end{figure}
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/stability_iterated.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Simulation study 2: Complete variable selection stability estimates with 95\% intervals based on 100 data simulations. The reference approach improves stability for all methods.}
-  \label{fig:stability_iterated}
-\end{figure}
-
-Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
-the vertical axis and the average false discovery rate on the
-horizontal axis based on 100 data simulations for the different
-combinations of $n$ and $\rho$. The best selection performance is on the
-top-left corner of each plot, as it implies the lowest false discovery
-rate and the highest sensitivity. We see that regardless of the
-applied selection method, the use of a reference model improves the
-selection performance, as it reduces the false discovery rate (shifting
-to the left) or increases the sensitivity (shifting upwards). In
-accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
-selection is. Thus, for easier selection scenarios, the benefits of
-the reference model are smaller since the raw data already provide
-enough information to identify the relevant variables. The iterative
-projpred has good false discovery rate in all cases, and the
-sensitivity is good except when the number of observations and the
-correlation level are small. It performs better than the iterative lasso 
-selection in any of the simulated scenarios. Tuning $\alpha$ might lead to improved
-selection, yet the main source of poor performance could well be the
-miscalibration of the uncertainty of the predictive utility score for
-misspecified models with cross-validation \citep{bengio2004no}.
-
-Figure \ref{fig:stability_iterated} shows the estimates of the stability
-measure proposed by \cite{paper:stability} with 0.95 confidence
-intervals based on 100 simulations. Such a measure takes in account
-the variability of the subset of the selected variables at each
-simulation (originally at each bootstrap sample), modelling the
-selection of each variable as a Bernoulli process. Further details are
-available in \cite{paper:stability}. The reference model helps in
-improving the stability of the selection: again, the benefits are
-bigger when the problem is more difficult (small $n$ and $\rho$). In
-addition, we observe less uncertainty in the stability estimates for
-the reference approach (i.e., smaller width of the 95\% intervals),
-which can be still connected to the overall stability of the
-procedure. As in Figure \ref{fig:sensitivity_vs_fdr_iterated}, the iterative
-projection does not perform well in the hardest scenarios.
-
-\hypertarget{bodyfat-2}{%
-\subsection{Body fat example: Part 3}\label{bodyfat-3}}
-
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_sensitivity_vs_fdr.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Body fat example with noisy variables: Complete variable selection sensitivity against false discovery rate based on 100 bootstrap samples with one standard deviation error bars.
-The improvement from using the reference approach is small (except that the projpred is much better than lasso).}
-  \label{fig:bodyfat_sensitivity_vs_fdr}
-\end{figure}
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_stability.pdf}
-  \vspace{-0.3\baselineskip}
-  \caption{Body fat example with noisy variables: Complete variable selection stability estimates with 0.95 confidence intervals based on 100 bootstrap samples.
-The improvement from using the reference approach is small (except that the projpred is much better than lasso).}
-  \label{fig:bodyfat_stability}
-\end{figure}
-
-We conclude our complete selection experiments using the body fat
-dataset one more time. As earlier we add noisy uncorrelated variables
-to the original data to get a total of 100 variables.
-Since we do not have a ground truth available with regard the original
-variables of the data, we assume it is reasonable to consider all of
-them relevant, at least to some degree. The artificially added
-variables are naturally irrelevant by construction.
-We compute
-correlations between each variable and the target variable, that is
-the amount of fat, and transform them by Fisher-Z-transformation. The
-original assumption in order for \eqref{eq:fisher_transformation} to
-hold is that the variables are jointly normally distributed. In our
-experience the normal approximation in
-\eqref{eq:fisher_transformation} is still reasonable, but after
-rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, and
-instead estimate it from the data. We compare the iterative projection, 
-the control of the local false discovery rate (loc.fdr), 
-the empirical Bayes median (EB.med)
-and the selection by posterior credible intervals at level 90\%
-(ci.90).  In order to vary the difficulty of the selection, we
-bootstrap subsamples of different sizes, going from $n=50$ up to
-$n=251$ (i.e., the full size of the data). For each condition, results
-are averaged over 100 bootstrap samples of the respective size.
-
-Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
-against the false discovery rate.  In almost all of the bootstrapped
-subsamples, the reference
-model improves the selection both in terms of sensitivity and false
-discovery rate. When $n=50$, we observe worse false
-discovery rates, yet by a lower amount compared to the gain in
-sensitivity. Again, we observe that the benefits are more evident as
-the selection becomes more challenging (i.e., lower number of
-observations).
-The great performance of projpred in minimal subset selection is not
-carried over for the complete variable selection with iterative
-projpred (even changing the reference model with a full encompassing 
-linear regression with regularised horseshoe prior), and the methods 
-specifically designed for the complete variable selection perform better. 
-However we still observe a better selection with respect to iterative lasso
-in any of the examined scenarios, mainly in terms of false discovery rate.
-Figure \ref{fig:bodyfat_stability} shows the stability
-results using the measure by
-\cite{paper:stability}. The benefits of the reference model are here
-marginal with only small improvements.
-
-In this example, we have used the reference model defined as a linear
-regression over some supervised principal components, because it is
-natural for a large number of correlating variables, and has fairly good
-predictive performance plus it is computationally efficient. We do not
-argue that this is always the best choice and more sophisticated
-models can lead to even better results. Here the purpose of the
-experiments were to motivate the use of reference models in general,
-and as we needed to average results over a lot of repetitions per
-simulation condition, we preferred such a comparably simple and
-computationally fast reference model.
-
-\hypertarget{conclusion}{
-\section{Conclusion}\label{conclusion}}
-
-In this paper, we demonstrated the benefits of using a reference model
-to improve variable selection, or more generally, model reduction. 
-We have motivated and explained the general benefits
-of a reference model regardless of the method it is applied in combination
-with. Specifically, we have seen how the reference model acts as an
-approximation of the data generation mechanism through its predictive
-distribution. Such approximation is generally less noisy than the
-sample estimation available purely from the observed data, leading to
-the main benefits of the reference model approach. In our comparisons,
-we have analysed the effect of a reference model in the form of a
-filter on the observed target values on top of different widely used
-variable selection methods. Overall, using a reference model leads to
-more accurate and stable selection results independently of the
-specific selection method. These benefits apply to a large family of
-different methods all involving a reference model in one way or the
-other. Some of these approaches have been present in the literature for some time
-\cite[e.g., see references in][]{vehtari2012survey,paper:projpred}
-but often without a clear explanation of {why} they are actually
-favourable and how they connect to other related approaches. We hope
-that the present paper can fill some of these gaps by providing a
-unifying framework and understanding of reference models.
-
-We argue that, whenever it is possible to construct a reasonable
-reference model, it should be employed on top of the preferred
-selection procedure or as an integral part of more complex methods,
-for example, the projective prediction approach
-\citep{paper:projpred}. Note that one of the main challenges in many
-real world application will consist in devising a sensible reference
-model itself and assessing its predictive performance.
-To build good predictive reference models, which are specifically
-tuned to the data and problem at hand, we recommend them to be
-developed using a robust Bayesian modelling workflow, for instance, as
-outlined by \citet{gelman2013bayesian} and \citet{gabry2019visualization}.
-
-Another main result of this paper is that the projective prediction
-approach shows superior performance in minimal subset variable
-selection compared to alternative methods whether or not these methods
-make use of a reference model. That is, while the reference model is
-certainly one important aspect the projective prediction approach, it
-is not the only reason for its superior performance.  Rather, by
-incorporating the full uncertainty of the posterior predictive
-distribution into the variable selection procedure (instead of just
-using point estimates) and using principled cross-validation method,
-projective predictions combine several desirable variables into a
-single procedure \citep{paper:projpred}.  In summary, we would
-strongly recommend using projective predictions for minimal subset
- variable selection if possible and feasible. 
- However, if this is not an option in a given
-situation, we would in any case recommend using a reference model on
-top of the chosen variable selection method.
-
-The projective prediction approach was not designed for the complete
-variable selection. We tested a simple iterative version of projpred,
-with mixed results and the methods specifically designed for complete
-variable selection (especially loc.fdr) performed better in our
-experiments. It is left for future research to develop 
-a better projective prediction approach for complete variable
-selection problems.
-
-All Bayesian models in this paper have been implemented in
-the probabilistic programming language \texttt{Stan}
-\citep{paper:stan} and fit via dynamic Hamiltonian Monte Carlo
-\citep{hoffman2014no,betancourt2017conceptual}, through the \texttt{R}-packages 
-\texttt{rstan} \citep{Rrstan} and \texttt{rstanarm} \citep{Rrstanarm}.
-Graphics elaborations have been done using \texttt{ggplot2} \citep{Rggplot2}
-and the \texttt{tidyverse} framework \citep{Rtidyverse}.
-The code to run all
-the experiments is available on GitHub
-(\url{https://github.com/fpavone/ref-approach-paper}).
-
-\section*{Acknowledgments}
-
-We thank Alejandro Catalina Feliu for help with experiments, and
-Academy of Finland (grants 298742, and 313122), Finnish Center for
-Artificial Intelligence and Technology Industries of Finland
-Centennial Foundation (grant 70007503; Artificial Intelligence for
-Research and Development) for partial support of this research. We
-also acknowledge the computational resources provided by the Aalto
-Science-IT project.
-
-\bibliography{ref_approach}
-
-\appendix
-
-\section*{Appendix}
-
-\subsection*{Appendix A: Projective Predictions}
-
-The projective prediction (projpred) approach was developed and is thoroughly
- described by \cite{paper:projpred}. In this appendix, we provide a high level
-  description of the method so that readers do not need to study paper by \cite{paper:projpred} in detail
-to understand the main ideas behind projpred.
-
-The parameter
-distribution of a given candidate submodel is denoted by $\pi$ and the induced predictive
-distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
-that $q_{\pi}(\tilde{y})$ maximises some predictive performance
-utility, for example, the expected log-predictive density (elpd)
-defined as: \
-\begin{equation}\label{eq:elpd}
-\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
-\end{equation}
-where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
-mechanism of future data $\tilde{y}$. If we refer to the posterior
-predictive distribution of a reference model with $p(\tilde{y}|D)$,
-where $D$ stands for the data on which we conditioned on, we can
-approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
-data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
-elpd using the reference model's predictive distribution is equivalent
-to the minimisation of the Kullback-Leibler (KL) divergence from the
-reference model's predictive distribution to the submodel's predictive
-distribution: \
-\begin{equation} \label{proj_as_filter}
-\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)
-\, \text{d} \tilde{y} 
-\quad \Leftrightarrow \quad 
-\underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D) \; || \; q_{\pi}(\tilde{y})] 
-\end{equation}
-The term on the right-hand side of Equation \eqref{proj_as_filter}
-describes what is referred to as the projection of the predictive
-distribution, which is the general idea behind the projection
-predictive approach \cite[see][]{paper:projpred}. 
-We now summarise the workflow of the projection predictive approach in
-the particular case of the draw-by-draw projection \cite[original
-formulation by][]{paper:original_proj}, following
-\cite{paper:projpred}. Suppose we have observed $n$ statistical units
-with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
-variables for which we want to obtain a minimally relevant
-subset. Than, the main steps are the following:
-\begin{enumerate}
-\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model's posterior.
-\item Rank the variables according to their relevance using some
-  heuristics and consider as candidate submodels only those which
-  preserve this order, starting from including only the highest ranked
-  variable. The submodels are then naturally identified by their
-  model size. This step is not strictly necessary but reduces the number
-  of submodels to considered in the following steps and thus reduces computation time.
-\item For each submodel $\pi$ selected in Step 2, project each of the reference model's posterior draws $\boldsymbol{\theta}_{*}^{s}$ as follows:
-\begin{equation}\label{eq:draw_by_draw}
-\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left[ p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right],
-\end{equation}
-where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
-predictive distribution of the reference model with parameters fixed
-at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the variable
-values related to the statistical unit (identified by the subscript
-$i$), whereas $q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
-predictive distribution of the submodel. The projected draws
-$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
-for the submodel.
-\item For each submodel (size), test the predictive performance for a chosen predictive utility score, for example, via cross-validation.
-Fast cross-validation can be performed using using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
-\citep[PSIS-LOO-CV; ][]{paper:psis_loo}.
-\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
-The results in this paper were not sensitive to the specific choice of how ``sufficiently close'' is defined, and we used the same definition as \citet{paper:projpred}.
-\end{enumerate}
-
-In general, Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
-However, in the special case of the submodels being
-generalised linear models with a likelihood coming from the exponential family, \eqref{eq:draw_by_draw} reduces to a
-maximum likelihood estimation problem, which can be easily solved
-\citep{paper:original_proj}. For further details on the projective
-prediction workflow and implementation see the paper by \citet{paper:projpred}.
-
 \end{document}

### 2020-07-03 paper/ref_approach.tex
added bullet point list of contributions

--- 2020-04-27 paper/ref_approach.tex
@@
 
-This paper is structured as follows. In Section
+The main contributions of our work are:
+
+\begin{itemize}
+\item to show a simple and basic way to frame any variable selection method in the reference model approach,
+\item to do a structured comparison for variable selection methods using or not a reference model, both for the the complete and the minimal subset selection,
+\item to bring evidence in supporting the projection predictive approach as a principled way to use the reference model.
+\end{itemize}
+
+The paper is structured as follows. In Section
 \ref{ref-intro}, we review the concept of the reference

### 2020-07-06 paper/ref_approach.tex
minor edit of contributions

--- 2020-04-27 paper/ref_approach.tex
@@
 
-This paper is structured as follows. In Section
+The main contributions of our work are:
+
+\begin{itemize}
+\item we show a simple and basic way to frame any variable selection method in the reference model approach,
+\item we make a structured comparison for variable selection methods with or without using a reference model, both for the the complete and the minimal subset selection,
+\item and we provide evidence in supporting the projection predictive approach as a principled way to use the reference model.
+\end{itemize}
+
+The paper is structured as follows. In Section
 \ref{ref-intro}, we review the concept of the reference

### 2020-07-06 paper/ref_approach.tex
update contributions

--- 2020-07-03 paper/ref_approach.tex
@@
 \begin{itemize}
-\item to show a simple and basic way to frame any variable selection method in the reference model approach,
-\item to do a structured comparison for variable selection methods using or not a reference model, both for the the complete and the minimal subset selection,
-\item to bring evidence in supporting the projection predictive approach as a principled way to use the reference model.
+\item We show a simple and intuitive way to combine any variable selection method with the reference model approach.
+\item We perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection.
+\item We provide evidence supporting the projection predictive approach as a principled way to use reference models.
 \end{itemize}

### 2020-07-10 paper/ref_approach_blinded.tex
blinded version

--- 2020-07-06 paper/ref_approach.tex
@@
             pdftitle={The reference model approach in variable selection},
-            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
+            %pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
             pdfkeywords={keywords},
@@
   \posttitle{\par}
-  \author{Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner and Aki Vehtari}
-
-    \author{
-      Federico Pavone\footnote{Department of Computer Science, Aalto University, Finland.}\, \footnote{Department of Decision Sciences, Bocconi University, Italy.}%$\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
+  %\author{Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner and Aki Vehtari}
+
+%    \author{
+%      Federico Pavone\footnote{Department of Computer Science, Aalto University, Finland.}\, \footnote{Department of Decision Sciences, Bocconi University, Italy.}%$\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
 E-mail: federicopavone01@gmail.com.}
-      \,,\,
-  Juho Piironen$^*$,\,
-  Paul-Christian B\"{u}rkner$^*$
-  and Aki Vehtari$^*$
-  }
+%      \,,\,
+%  Juho Piironen$^*$,\,
+%  Paul-Christian B\"{u}rkner$^*$
+%  and Aki Vehtari$^*$
+%  }
 

### 2021-09-23 reviews/rebuttal.tex
add a rebuttal template

% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.
% See https://creativecommons.org/licenses/by-sa/3.0/
% and https://stackoverflow.blog/2009/06/25/attribution-required/

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{xcolor}
\usepackage{hyperref}

% import Eq and Section references from the main manuscript where needed
% \usepackage{xr}
% \externaldocument{manuscript}

% package needed for optional arguments
\usepackage{xifthen}
% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }

\newenvironment{reply}
   {\medskip \noindent \begin{sf}\textbf{Reply}:\  }
   {\medskip \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\newcommand{\todo}{\subsection*{\textcolor{red}{To do (comment out when done)}:}}

\newcommand{\mm}[1]{\textcolor{red}{[M\aa ns: #1]}}
\newcommand{\av}[1]{\textcolor{blue}{[Aki: #1]}}
\newcommand{\ami}[1]{\textcolor{brown}{[Alonzo: #1]}}
\newcommand{\ts}[1]{\textcolor{purple}{[Tuomas: #1]}}

\begin{document}

\section*{Response to the reviewers}
% General intro text goes here
We thank the editor and the reviewers for careful review of the paper and the many useful comments.
\bigskip 
\hrule
\medskip 
\section*{Editor}

\paragraph{Editor comment}
I regret to inform you that the reviewers have raised serious concerns, and therefore your paper cannot be accepted for publication in Communications in Statistics – Theory and Methods. However since the reviewers do find some merit in the paper, I would be willing to reconsider if you wish to undertake major revisions and re-submit, addressing the referees' concerns.

\paragraph{Reply}

We thank the editor and the reviewer for the careful review of the paper and many valuable comments. We have addressed the discussed concerns and made changes to the manuscript accordingly. In particular, we have discussed the paper's practical implications and highlighted both the problem setting and the main contributions.

%\todo
%\begin{description}
%    \item [Mans] Nothing
%\end{description}

% Let's start point-by-point with Reviewer 1
\reviewersection

% Point one description 
\begin{point}
English language needs careful editing.
\end{point}

\begin{reply}
Thank you for the feedback. We have addressed now gone through the text multiple times and used automatic spell and grammar checkers. We are not native speakers, so please feel free to point out if you find further problems with the text.
\end{reply}

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
The specific case considered in the article needs to be elaborated on in terms of its practical meaning and importance. Giving a solution for a specific case can be useful if that case has some practical importance. Otherwise, anyone can create solutions for many different cases.
\end{point}

\begin{reply}
We realise that the motivation of the work may be unclear. We aim to show one feasible (albeit simple) problem setting to show that it is possible to derive an unbiased variance estimator for the popular way of analysing the uncertainty in LOO-CV. Previous literature (e.g. Bengio and Grandvalet, 2004) indicates that this is not possible in general. To the best of our knowledge, we do not know anyone who has shown that it is possible to derive an unbiased estimator if one also considers the actual problem setting and model. This is an important advancement in the study for understanding the uncertainty in LOO-CV estimation in practice and can further encourage new work on variance estimation in Bayesian LOO-CV.

We now see that this has not been clear enough in the paper. We have clarified this both in the introduction and the discussion.
\end{reply}

\begin{point}
It is noted that there is no need for the observations to be identically distributed. We should see the impact of this on the likelihood in Eq. (6).
\end{point}

\begin{reply}
We see that the analysis description may be a bit misleading considering the two-level perspective on the variable $y$: the model level and the true data generating process level. In the latter, we apply only weak assumption on the distribution $p_\text{true}(y)$, and in particular, do not need to assume identically distributed observations. At the model level, the Bayesian normal model does make this assumption. Equation (6) defines the likelihood of the model. Based on the feedback, we clarified this in the text.
\end{reply}

\begin{point}
You have a normal hyper-prior on the mean $\theta$, $\sigma_{m}^{2}$ and $\sigma_{0}^{2}$ are fixed. Specification of these variances needs elaboration.
\end{point}

\begin{reply}
Thank you for this suggestion. We are a little unsure about what the reviewer asks for here. We added the following descriptive explanation on the effects of the parameters:

"The fixed data variance parameter $\sigma_\mathrm{m}^2$ reflects how the model considers the magnitude of the variability of the data. A fixed $\sigma_\mathrm{m}^2$ is mainly chosen to simplify derivations. The fixed prior variance parameter $\sigma_0^2$ reflects the prior belief of the magnitude of the variability of the unknown mean parameter. The fixed model parameters $\sigma_\mathrm{m}^2$ and $\sigma_0^2$ can be chosen freely."

In addition, we emphasise that the model may be miss-specified so that it represents the true data generating mechanism poorly.
\end{reply}

\begin{point}
The settings in the numerical example need further explanation. Why are those specific numbers selected? The example runs are too specific and cannot be generalised. This makes the article too focused on some specific cases. Then, the importance of dealing with these specific cases have to be articulated clearly.
\end{point}

\begin{reply}
Thank you for the relevant comment. We understand that the motivation of the experiments can be a bit confusing. The simulation experiment has two purposes. First, illustrating that the theory is correct and, second, show the naive estimator can be both upward and negatively biased.

The experiments apply three problem settings covering different, but feasible, scenarios including both well-fitting and bad-fitting data. We have now clarified the selection of the problem settings in the text. It is clear that, as the true data generating mechanism is quite unrestricted, there are arbitrarily many possible experiment setups. We believe that these applied setups are sufficient for illustrative purposes.

We believe that your comment calls for this to be written out more clearly in the paper. We have tried to clarify this further in the paper.
\end{reply}
\end{document}

### 2021-09-23 reviews/rebuttal_draft.txt
added reviews and initial responses

***Federico's quick comments:***

Reviewer 1: I think they misunderstood some of our results regarding the use of a reference model and not the specific implementation of projpred. Also about the complete selection case, our focus was on how the other methods improve with a reference model rather than the new projpred-based algorithm.  Apart from this inconvenient, I think that the other comments they report are interesting as the ones on reference model misspecification and prior sensitivity. I believe we have already addressed some of those, but maybe not that explicitly.

Reviewer 3: they don’t address major problems with the works, but mostly minor changes.

Associate Editor: also here, I think there has been a misunderstanding of the purpose of the complete selection section.

I didn’t receive any report by Reviewer 2.

What do you suggest to do next? I think that addressing the reviewers’s concerns would require to work mainly in two directions: we need to 
clarify that the purpose of the simulations is to show the effect of the reference model (and not a specific implementation) and than to answer questions 1)-5) by Reviewers 1. The latter requires a bit of thinking: I think we could mostly answer to those question in a discursive way, but would it be enough? Setting up experiments to study the reference model misspecification and the prior sensitivity problem might require some thinking!
To start, I could go in details through the reviews and the paper and try to write down for each question if we have already answered somewhere in the paper or what we should do. What do you think? I wait for your advice!

The deadline for the possible resubmission is the 23/02/22.

***Aki's quick comments***

Quick comments that need to be processed to be polite answers (I wrote these before looking at Federico's comments)

Reviewer #1 (PDF reviewer?)

The reviewer has mistaken that we would be proposing a new method. The main purpose is as stated in the abstract:
"In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative variable selection methods with and without reference models. Our results indicate that the use of reference models generally translates into better and more stable variable selection."

We need to clarify this point. We knew that projpred works well for the minimal set variable selection, but we didn't know whether that is due to the use of reference model or due to the projection that make better inference after the selection. In this paper we show that the use of a reference model helps also other approaches and thus it canät be the projection alone that is producing the good results. Other point we make is that projpred was specifically designed for the minimal set variable selection and we show that it is not good for complete set selection, which is useful information, too. Showing a failure mode of existing algorithm is useful even without being able to develop a solutin for that failure.

We should clarify these issues and resbumit without better approach. I would assume the second round decision would be quicker.

For the last comment I would answer that, of course the performance of the variable selection depends on the quality of the reference model. If the reference model is, e.g., without any covariates, there is no useful information to learn. Stability of Bayesian inference wrt priors have been extensively studied elsewhere and the prior sensitivity checking is natural part of the workflow for building a reference model (cite Bayesian workflow, priorsense paper, and something else)

Reviewer #3

They also comment that " the motivation of the study in relation to
the literature is missing in the Introduction. " and we need to
clarify the poimt I mentioned above. They helpfully point out that
"Full motivation is given in Section 2. However, it needs to be
briefly mentioned in the Introduction as well to motivate the reader
to keep reading. In addition, instead of pointing to the references,
please give a brief critique of them." so we need to just copy stuff
from there.

> 2. Please include the computational cost of compared approaches in Section 2.1.

Sensible suggestion.

> 3. Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.

Sensible suggestion.

> 4. Please mention the availability of the R codes to reporoduce the results under each section as well.

Sensible suggestion.

AE

> Associate Editor: Please note the strong concerns of the
> reviewers. If you cannot implement a better projective prediction
> approach for complete variable selection problems, then at the very
> least, I would expect you to motivate why it's worth knowing about
> this approach; you show that it doesn't work very well.

I think the above answers cover this, too.

Overall the reviewer #3 seems to be positive, and also helpfully hints
why reviewer #1 may be confused.

I agree with Federico's analysis of the situation

 - Clarify as suggested by reviewer #3
 - Transform the comments about reviewr #1 to polite explanation how we have improved the paper and clarified the main points.
 - we can be more straight that iterative projpred is not that good

***Juho's quick comments***

I generally agree with Aki's comments, in particular that we should
not try to come up with a better algorithm for complete variable
selection, but try to articulate why this study still contains useful
findings (negative results are also useful, it's sad how often they
are overlooked).

A few comments to the points raised by reviewer 1 (should be
reformulated to be polite answers):

"... you can have use standard inverted gamma priors on sigma2 and
tau2 by determining the parameters of the prior in order to the prior
mixture gives reasonable results about the data using the prior
mixture. How can you study the robustness of your results to this
important aspect?"
- I have to admit that I did not understand what the reviewer is
trying to say here.

"Perhaps a solution to the previous problem would be to determine the
reference model using frequentist MLE procedures that avoid the
construction of prior distributions and use a single point prediction
or, alternatively, to use the sampling distribution of MLE as a
posterior distribution and take this “Bayesian” model as reference
model. Do you have any experience in this line?"
- I don't really have experience about this, but I don't quite see how
a frequentist reference model would solve the issue of having to
choose the prior for the reference model; afterall you need to choose
how you regularize your frequentist model, which is kinda equivalent
to choosing the prior (but you lose the extra regularizing effect
which comes from integrating over the posterior uncertainty in a
Bayesian model).

"What if the true generator process is a mixture model, in such a way
that there is not a unique solution to the minimal subset variable
selection problem? In fact, how can you assure that the minimal subset
variable selection problems have only one selection?"
- I don't think we have stated anywhere that we assume there is a
unique solution? Nor do we attempt to find such unique solution. We
attempt to find _a_ model with smallest number of variables without
substantial loss in predictive accuracy compared to the reference or
any other candidate model.

"In most of real situations, we have an M-open problem (particularly
in big data problems) where the true generator mechanism is too
complex and it is not included in the family of considered models.
What would be the performance of your methodology if the reference
model is far from the true generator process? How can you detect these
situations?"
- Not sure what we should answer here, but it feels to me that
answering this sort of question would require a paper (or two) on its
own. We can write e.g. that this is beyond the scope of this paper,
and we feel it's not quite fair to require such a major issue to be
solved in the present paper.

"Section 4.1: It is no clear how the value of alpha should be chosen.
alpha = 0.16 is a magic number and a more thoroughly discussion of the
influence of this value should be provided."
- It is purely heuristic, yes, but the 'magic' number comes from the
fact that if each tail has 16% mass, then the central interval has 68%
mass which corresponds to plus minus one std assuming normal
distribution (i.e. alpha=0.16 corresponds to one std away from mean,
thus it's not that magical).

### 2021-09-23 reviews/rebuttal_draft.txt
more comments

@@
 Stability of Bayesian inference wrt priors have been extensively studied elsewhere and the prior sensitivity checking is natural part of the workflow for building a reference model (cite Bayesian workflow, priorsense paper, and something else)
+
+Related to point 1)
+
+The reference model doesn't need to be Bayesian.
+The results are better with better model.
+The sensitivity of the Bayesian models to choice of priors is well studied and there exists well developed workflows for doing prior sensitivity analysis and other model checking (see, e.g.
+Gelman et al, 2020).
+In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be imporvef by relacing the data with filtered prediction from the reference model.
+We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
 
@@
 thus it's not that magical).
+
+***23 September 2021***
+
+We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
+A sensible reference model doesn't need to be Bayesian.
+The results are better with better reference models.
+The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking (see, e.g.
+Gelman et al, 2020).
+In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
+The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues.
+As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
+
+MLE is more unstable than Bayesian approach.
+The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors.
+We have added references that discuss merits of Bayesian approach compared to MLE.
+Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it’s a good predictive model, it will be a useful reference model.
+
+The projection predictive variable selection and its properties have been extensively discussed in Piironen & Vehtari, and Piironen, Paasiniemi & Vehtari, and we refer to them for the detailed discussion on the uncertainty related to search paths.
+Paasinemi (2018) https://aaltodoc.aalto.fi/handle/123456789/33657 provides illustrations how this uncertainty can be communicated to the users.
+When there are correlating variables that have exactly the same amount of information, the minimal set is not unique.
+In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in Paasinemi (2018) to analyse alternative possible variable sets.
+
+We assume that all models are wrong.
+Analysing model misspecification is well studied in Bayesian literature and there are plenty of methods available for model checking (see, e.g.
+Gelman et al, 2020).
+The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building (Gelman et al, 2020).
+Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved.
+
+See Piironen, Paasiniemi & Vehtari,
+
+The usual Bayesian workflow (Gelman et al, 2020) states that if there is uncertainty about which model then we integrate over the model space or create a continuous super model that includes the alternative models as special cases.
+
+We used AIC because reference X was using AIC.
+The goal of the paper was not to compare all possible information criteria.
+We made choices to keep the paper within reasonable length.
+Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model.
+
+> M Complete approach, it is usually consistent.
+
+It seems your definition of M-complete doesn’t match with definition of Bernardo & Smith (1994) we are using.

### 2021-11-02 reviews/rebuttal.tex
updated rebuttal: minor changes addressed

@@
 \usepackage{hyperref}
+\usepackage{amsmath}
+\usepackage[authoryear,round]{natbib}
 
@@
 
-\newcommand{\mm}[1]{\textcolor{red}{[M\aa ns: #1]}}
-\newcommand{\av}[1]{\textcolor{blue}{[Aki: #1]}}
-\newcommand{\ami}[1]{\textcolor{brown}{[Alonzo: #1]}}
-\newcommand{\ts}[1]{\textcolor{purple}{[Tuomas: #1]}}
+\newcommand{\fede}[1]{\textcolor{red}{[Fede: #1]}}
+%\newcommand{\av}[1]{\textcolor{blue}{[Aki: #1]}}
+%\newcommand{\ami}[1]{\textcolor{brown}{[Alonzo: #1]}}
+%\newcommand{\ts}[1]{\textcolor{purple}{[Tuomas: #1]}}
 
@@
 \medskip 
-\section*{Editor}
+\section*{Associated Editor}
 
-\paragraph{Editor comment}
-I regret to inform you that the reviewers have raised serious concerns, and therefore your paper cannot be accepted for publication in Communications in Statistics – Theory and Methods.
-However since the reviewers do find some merit in the paper, I would be willing to reconsider if you wish to undertake major revisions and re-submit, addressing the referees' concerns.
+\paragraph{Associated Editor comment}
+Please note the strong concerns of the reviewers.
+If you cannot implement a better projective prediction approach for complete variable selection problems, then at the very least, I would expect you to motivate why it's worth knowing about this approach; you show that it doesn't work very well.
 
 \paragraph{Reply}
-
-We thank the editor and the reviewer for the careful review of the paper and many valuable comments.
-We have addressed the discussed concerns and made changes to the manuscript accordingly.
-In particular, we have discussed the paper's practical implications and highlighted both the problem setting and the main contributions.
+todo
 
@@
 \begin{point}
-English language needs careful editing.
+My main concern with respect to the projective predictive approach is the robustness of the results to the reference model.
+Apparently, you can build very different references models to the same data set: have you study the sensitivity of the results with different reference models?.
+You use Bayesian models as reference models and, in these cases, the determination of prior distribution is not very clear.
+You can build hundreds and hundreds of prior distribution: for instance in (7) you can have use standard inverted gamma priors on $\tau^2$ and $\sigma^2$ by determining the parameters of the prior in order to the prior mixture gives reasonable results about the data using the prior mixture.
+How can you study the robustness of your results to this important aspect?
 \end{point}
@@
 \begin{reply}
-Thank you for the feedback.
-We have addressed now gone through the text multiple times and used automatic spell and grammar checkers.
-We are not native speakers, so please feel free to point out if you find further problems with the text.
+We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
+A sensible reference model doesn't need to be Bayesian. The results are better with better reference models.
+
+The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}.
+In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
+The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues.
+As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
 \end{reply}
@@
 \begin{point}
-The specific case considered in the article needs to be elaborated on in terms of its practical meaning and importance.
-Giving a solution for a specific case can be useful if that case has some practical importance.
-Otherwise, anyone can create solutions for many different cases.
+Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model.
+Do you have any experience in this line?
 \end{point}
@@
 \begin{reply}
-We realise that the motivation of the work may be unclear.
-We aim to show one feasible (albeit simple) problem setting to show that it is possible to derive an unbiased variance estimator for the popular way of analysing the uncertainty in LOO-CV.
-Previous literature (e.g.
-Bengio and Grandvalet, 2004) indicates that this is not possible in general.
-To the best of our knowledge, we do not know anyone who has shown that it is possible to derive an unbiased estimator if one also considers the actual problem setting and model.
-This is an important advancement in the study for understanding the uncertainty in LOO-CV estimation in practice and can further encourage new work on variance estimation in Bayesian LOO-CV.
-
-We now see that this has not been clear enough in the paper. We have clarified this both in the introduction and the discussion.
+MLE is more unstable than Bayesian approach.
+The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors.
+We have added references that discuss merits of Bayesian approach compared to MLE.
+Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
 \end{reply}
@@
 \begin{point}
-It is noted that there is no need for the observations to be identically distributed. We should see the impact of this on the likelihood in Eq. (6).
+What if the true generator process is a mixture model, in such a way that there is not a unique solution to the minimal subset variable selection problem?
+In fact, how can you assure that the minimal subset variable selection problems have only one selection?
+I think that the algorithm described in appendix A should take into account this possibility, and the step 5 not to choose the smallest (model) that is sufficient close to the reference model's predictive utility score but to use, for instance, an Occam window, that reflects more adequately the uncertainty associated with the model selection process something that, apparently, your methodology does not consider.
+In fact, and even though in your examples your results in the paper were not sensitive to the specific choice of how “sufficiently close” is defined, I guess that there can be situations where this statement is not true, and more of one solution to the minimal subset variable selection problem and to the complete variable selection problem could exist.
 \end{point}
@@
 \begin{reply}
-We see that the analysis description may be a bit misleading considering the two-level perspective on the variable $y$: the model level and the true data generating process level.
-In the latter, we apply only weak assumption on the distribution $p_\text{true}(y)$, and in particular, do not need to assume identically distributed observations.
-At the model level, the Bayesian normal model does make this assumption.
-Equation (6) defines the likelihood of the model.
-Based on the feedback, we clarified this in the text.
+The projection predictive variable selection and its properties have been extensively discussed in \citet{piironen2017comparison} and \citet{piironen2020projective}, and we refer to them for the detailed discussion on the uncertainty related to search paths.
+\citet{paasiniemi2018} provides illustrations how this uncertainty can be communicated to the users.
+When there are correlating variables that have exactly the same amount of information, the minimal set is not unique.
+In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in \citet{paasiniemi2018} to analyse alternative possible variable sets.
 \end{reply}
@@
 \begin{point}
-You have a normal hyper-prior on the mean $\theta$, $\sigma_{m}^{2}$ and $\sigma_{0}^{2}$ are fixed. Specification of these variances needs elaboration.
+In most of real situations, we have an M-open problem (particularly in big data problems) where the true generator mechanism is too complex and it is not included in the family of considered models.
+What would be the performance of your methodology if the reference model is far from the true generator process?
+How can you detect these situations?
 \end{point}
@@
 \begin{reply}
-Thank you for this suggestion. We are a little unsure about what the reviewer asks for here. We added the following descriptive explanation on the effects of the parameters:
+We assume that all models are wrong.
+Analysing model misspecification is well studied in Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}.
+The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}.
+Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved.
+\end{reply}
 
-"The fixed data variance parameter $\sigma_\mathrm{m}^2$ reflects how the model considers the magnitude of the variability of the data.
-A fixed $\sigma_\mathrm{m}^2$ is mainly chosen to simplify derivations.
-The fixed prior variance parameter $\sigma_0^2$ reflects the prior belief of the magnitude of the variability of the unknown mean parameter.
-The fixed model parameters $\sigma_\mathrm{m}^2$ and $\sigma_0^2$ can be chosen freely."
+\begin{point} \label{q5}
+In big data problems with n << p and the explanatory variables are weakly related (in such a way that the number of significant principal components is large), how do you build a reference model?
+Is it possible?
+\end{point}
 
-In addition, we emphasise that the model may be miss-specified so that it represents the true data generating mechanism poorly.
+\begin{reply}
+See \citet{piironen2020projective}.
 \end{reply}
@@
 \begin{point}
-The settings in the numerical example need further explanation.
-Why are those specific numbers selected?
-The example runs are too specific and cannot be generalised.
-This makes the article too focused on some specific cases.
-Then, the importance of dealing with these specific cases have to be articulated clearly.
+The same question that \ref{q5} but if n is small and your data have not power to discriminate between two alternative reference models.
 \end{point}
@@
 \begin{reply}
-Thank you for the relevant comment.
-We understand that the motivation of the experiments can be a bit confusing.
-The simulation experiment has two purposes.
-First, illustrating that the theory is correct and, second, show the naive estimator can be both upward and negatively biased.
+The usual Bayesian workflow \citep{gelman2020bayesian} states that if there is uncertainty about which model then we integrate over the model space or create a continuous super model that includes the alternative models as special cases.
+\end{reply}
 
-The experiments apply three problem settings covering different, but feasible, scenarios including both well-fitting and bad-fitting data.
-We have now clarified the selection of the problem settings in the text.
-It is clear that, as the true data generating mechanism is quite unrestricted, there are arbitrarily many possible experiment setups.
-We believe that these applied setups are sufficient for illustrative purposes.
+%%% SOME OF THE MINOR REQUEST
+\section*{Reviewer 1 - Minor comments}
 
-We believe that your comment calls for this to be written out more clearly in the paper. We have tried to clarify this further in the paper.
+\begin{point}
+Section 3.1: you say that in this simulation you use a Bayesian stepwise forward selection procedure. Is this really the case? In your description of the procedure in page
+6 you exclude (and not include variables) in this step of the algorithm. In my view, this procedure is a Bayesian stepwise backward selection procedure.
+\end{point}
+
+\begin{reply}
+Thanks for pointing out the typo. We fixed it in the new version of the paper.
 \end{reply}
+
+\begin{point}
+In the Bayesian stepwise selection procedures of section 3.1 you use posterior pvalues to exclude variables, and you exclude the variable with the highest Bayesian p- value.
+Shouldn't you take into account whether the value of the pvalue is large or small?
+Shouldn't you calibrate these pvalues?
+\end{point}
+
+\begin{reply}
+\fede{There is not need of calibration of the pvalues since they are used only to select the "worse" predictor.
+Then the variable is excluded or not looking at the predictive performance of the reduced model compared to the not-reduced one.
+In such a way, the posterior pvalues matter only for their ordering and not for their magnitude.}
+\end{reply}
+
+\begin{point}
+Section 3.1 steplm procedure: Why have you chosen the AIC criterion which, as it is well-known tend to select non-parsimonious models?
+Have you tried to use the BIC criterion instead?
+In my experience, this criterion tend to select more parsimonious models and in a M Complete approach, it is usually consistent.
+\end{point}
+
+\begin{reply}
+We used AIC because reference X was using AIC.
+The goal of the paper was not to compare all possible information criteria.
+We made choices to keep the paper within reasonable length.
+Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model.
+\end{reply}
+
+\begin{point}
+Section 4.1, page 8, line 38: $\text{elpd}_\text{base}$ should be $\text{elpd}_\text{best}$
+\end{point}
+
+\begin{reply}
+Thanks for pointing out the typo. We fixed it in the new version of the paper.
+\end{reply}
+
+\begin{point}
+How is calculated the probability used in the stopping rule (2)? Using the reference model?
+\end{point}
+
+\begin{reply}\label{reply:stopping}
+\fede{At each iteration, the best model is selected via the default stopping rule implemented the \texttt{R}-package \texttt{projpred}.
+For details, see \citet{piironen2020projective} for details.
+In few words, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
+The obtained lpd samples are used to estimate that probability under normality assumption.}
+\end{reply}
+
+\begin{point}
+It is not very exigent in (2) to impose that $\text{elpd}_i-\text{elpd}_\text{best}>0$?
+Perhaps you should consider other limits similar to those used in Bayes factors (Kass and Raftery, 1995) and not to choose only on solution but to explore other possible solutions in the spirit of Occam’s window
+\end{point}
+
+\begin{reply}
+\fede{The above condition comes from the implementation of the projection predictive approach \citet{piironen2020projective} in the \texttt{R}-package \texttt{projpred}.
+The fact that the algorithm is based on the probability of that condition and not on the condition itself make it not that exigent.}
+\end{reply}
+
+\begin{point}
+Section 4.1: It is no clear how the value of $\alpha$ should be chosen. $\alpha= 0.16$ is a magic number and a more thoroughly discussion of the influence of this value should be provided.
+\end{point}
+
+\begin{reply}
+\fede{The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
+One possible standard way to proceed, but not guaranteed to be the best in any case, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.
+For further details see \ref{reply:stopping} and \citet{piironen2020projective}.}
+\end{reply}
+
+\begin{point}
+Section 4.1, line 50 “expect” should be “except”
+\end{point}
+
+\begin{reply}
+Thanks for pointing out the typo. We fixed it in the new version of the paper.
+\end{reply}
+
+\reviewersection
+
+No comments provided.
+
+\reviewersection
+
+\begin{point}
+Although main articles related to the use of the reference model approach in the model selection are mentioned, the motivation of the study in relation to the literature is missing in the Introduction.
+The given discussion of the existing literature supports the idea that the reference models have been used in Bayesian and non-Bayesian contexts.
+However, why do we need the proposed approach in the article is missing.
+Full motivation is given in Section 2.
+However, it needs to be briefly mentioned in the Introduction as well to motivate the reader to keep reading.
+In addition, instead of pointing to the references, please give a brief critique of them.
+\end{point}
+
+\begin{reply}
+todo
+\end{reply}
+
+\begin{point}
+Please include the computational cost of compared approaches in Section 2.1. 
+\end{point}
+
+\begin{reply}
+todo
+\end{reply}
+
+\begin{point}
+Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
+\end{point}
+
+\begin{reply}
+todo
+\end{reply}
+
+\begin{point}
+Please mention the availability of the R codes to reproduce the results under each section as well.
+\end{point}
+
+\begin{reply}
+Thank you for the feedback, we mentioned the availability of the R codes under each section in the new version of the paper.
+\end{reply}
+
+\bibliographystyle{abbrvnat}
+\bibliography{rebuttal}
+
 \end{document}

### 2021-11-02 paper/ref_approach.tex
minor changes from the reviewers comments: typos and availability of repo

@@
 into the theoretical reasons why reference models help in variable selection.
+\\
+The code to run all
+the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 the variables with some predictive power in Section~\ref{complete-selection}.
+\\
+The code to run all
+the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 a Bayesian stepwise
-forward selection with and without a reference model, and maximum
-likelihood stepwise forward selection with and without a reference
+backward selection with and without a reference model, and maximum
+likelihood stepwise backward selection with and without a reference
 model (steplm). The following is a summary of the implementation of the compared methods:
@@
 means a more stable selection. 
+\\
+The code to run all
+the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
    projection.elpdEstimate() \;
-   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{base}}>0)\geq\alpha)$\} \;
+   $S=\text{min}\{\text{sub}: P(\text{elpd}_{\text{sub}}-\text{elpd}_{\text{best}}>0)\geq\alpha)$\} \;
 
@@
 method which we refer to as `iterative lasso'. It consists of the same iterative
-algorithm as iterative projpred expect for not using any reference model, but
+algorithm as iterative projpred except for not using any reference model, but
 the lasso method for variable selection, instead.

### 2022-01-03 reviews/rebuttal.tex
completed first draft answers

@@
 \paragraph{Reply}
-todo
+\fede{We have elaborated a better version of our paper following many of the reviewers' comments and suggestions.
+However, we believe that there has been a misunderstanding on the purpose of our work by Reviewer 1.
+The projective prediction approach for complete variable selection is not the aim of this work.
+The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
+Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection.
+We do not exclude that better projective prediction method for complete selection can be designed in the future.
+\\
+Reviewer 3 gave precious comments on how to clarify the real intentions of our work, which is the study of the effect of reference models when used to guide the selection process, regardless of the selection method.
+We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.}
 
@@
 The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}.
-In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
+In this paper the point is not the Bayesian workflow, but to analyse given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
 The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues.
@@
 \begin{point} \label{q5}
-In big data problems with n << p and the explanatory variables are weakly related (in such a way that the number of significant principal components is large), how do you build a reference model?
+In big data problems with $n<<p$ and the explanatory variables are weakly related (in such a way that the number of significant principal components is large), how do you build a reference model?
 Is it possible?
@@
 \begin{reply}
-See \citet{piironen2020projective}.
+Please, see \citet{piironen2020projective} for further information.
 \end{reply}
@@
 \begin{reply}
-\fede{There is not need of calibration of the pvalues since they are used only to select the "worse" predictor.
-Then the variable is excluded or not looking at the predictive performance of the reduced model compared to the not-reduced one.
+\fede{There is no need of calibration of the pvalues, since they are used only to select the "worse" predictor.
+Such predictor is then excluded or not, looking at the predictive performance of the reduced model and of the not-reduced one.
 In such a way, the posterior pvalues matter only for their ordering and not for their magnitude.}
@@
 \begin{reply}
-We used AIC because reference X was using AIC.
+We used AIC because reference \citet{heinze2018variable} was using AIC.
 The goal of the paper was not to compare all possible information criteria.
@@
 \begin{reply}\label{reply:stopping}
-\fede{At each iteration, the best model is selected via the default stopping rule implemented the \texttt{R}-package \texttt{projpred}.
-For details, see \citet{piironen2020projective} for details.
+\fede{At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}.
+For details, see \citet{piironen2020projective}.
 In few words, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
-The obtained lpd samples are used to estimate that probability under normality assumption.}
+The obtained lpd samples are used to estimate that probability.}
 \end{reply}
@@
 \begin{reply}
-\fede{The above condition comes from the implementation of the projection predictive approach \citet{piironen2020projective} in the \texttt{R}-package \texttt{projpred}.
-The fact that the algorithm is based on the probability of that condition and not on the condition itself make it not that exigent.}
+\fede{The above condition derives from the original criteria to choose the model size in \citet{piironen2020projective} for the use of the projection predictive approach in the minimal subset scenario.
+In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model.
+Here we decided to compare the submodel of size $i$ with the ``best'' size, at the given iteration, due to the natural loss of explanatory power of the remaining covariates as the iterations increase.
+\\
+In general, notice that the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself.}
 \end{reply}
@@
 \fede{The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
-One possible standard way to proceed, but not guaranteed to be the best in any case, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.
-For further details see \ref{reply:stopping} and \citet{piironen2020projective}.}
+One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.}
 \end{reply}
@@
 \begin{reply}
-todo
+\fede{Thank you for the feedback. We renovated Section 1 and Section 2, improving the paper according to your suggestions.}
 \end{reply}
@@
 \begin{reply}
-todo
+\fede{We touch the computational aspects in Section 2.2.
+The reference model approach has in general the additional cost of fitting a reference model.
+However, this is usually available when building up a model via robust workflows \citep{gelman2020bayesian}.
+Therefore, in these cases there is not additional cost.
+In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.}
 \end{reply}
@@
 \begin{reply}
-todo
+\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3.}
 \end{reply}

### 2022-01-03 paper/ref_approach.tex
modified paper according to review answers

@@
 
+\newcommand{\fede}[1]{\textcolor{red}{#1}}
+
 \title{Using reference models in variable selection 
@@
 reference model instead of the observed responses $y$.
+
+\fede{All these methods can be framed into the family of reference model approaches. 
+The common denominator is the use of the reference model posterior predictive information 
+instead of simply observed data to guide the selection.}
 Whatever the terminology or applied statistical framework, reference
 models offer a powerful approach to improving variable selection as we
-will demonstrate in the present paper.
-
-The main contributions of our work are:
-
-\begin{itemize}
-\item We show a simple and intuitive way to combine any variable selection method with the reference model approach.
-\item We perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection.
-\item We provide evidence supporting the projection predictive approach as a principled way to use reference models.
+will demonstrate in the present paper. \\
+\fede{The goal of our work is to study the impact of reference model approaches
+disentangling the benefit of the usage of a reference model from the specific selection algorithm.
+Specifically, we:}
+% The main contributions of our work are:
+
+\fede
+{\begin{itemize}
+\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach.
+This allows us to build up a comparison independent of the specific variable selection method;
+% We show a simple and intuitive way to combine any variable selection method with the reference model approach.
+\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
+\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.
 \end{itemize}
+}
 
@@
 
+\fede{Clearly, the reference model approach require a sensible model.
+The construcion of such a model should follow proper modelling workflow including model assessment and validation \citep[see, e.g.][]{gelman2020bayesian}.
+Better predictive models imply better selection results.}
+
 \hypertarget{comparison-minimal-subset}{
@@
 
-\subsection{Simulation study 1}
+\subsection{Simulation study 1}\label{minimal-simulated}
 
@@
 \end{table}
+
+\subsection{Reference model's effect and the projection predictive approach}
+\fede{The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case. \\
+The simulation study based on artificial data of Section \ref{minimal-simulated} shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied.
+These results are confirmed also in the real word data example with the body fat dataset.
+The stepwise selection achieves far better selection with the reference model approach (see Figure \ref{fig:bodyfat_step_refvsdata} and Table \ref{tab:step_refvsdata}).
+However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.
+Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}
 

### 2022-01-04 reviews/rebuttal.tex
minor edits
expanded answers including paper edits

@@
 	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }
+
+\newenvironment{comment}
+{\medskip \noindent \begin{sf}\textbf{Reviewer~comment}:\  }
+	{\medskip \end{sf}}
 
@@
 \reviewersection
+\begin{comment}
+The paper is well written and organized an the topic analyzed is very relevant and practice.
+However, in my view, the goals of the paper, described in the introduction section, have already been reached in the excellent paper of Pironen et al.
+(2020) and, in this sense, the contributions of the current paper is very marginal.
+The framework of Pironen et al.
+(2020) is more general (they consider exponential family models and generalized linear models) and provide some theoretical results that, as they said “...
+help us to understand when the reference model could be helpful for parameter learning in linear submodels” (section 8 of Piironen et al., 2020).
+The only innovation that I can appreciate in the current paper is the proposal of an algorithm to solve a complete variable selection problem that, unfortunately, does not work very well as the authors explicitly recognize: “The great performance of projpred in minimal subset selection is not carried out over for the complete variable selection with iterative projpred ..., and the methods specifically designed for the complete variable selection perform better” (page 12, lines 24-27), even though they observe a better selection to iterative lasso.
+In my view, this is due to that the algorithm is too simple (as the authors explicitly recognize in the conclusions) and that the projective prediction approach was not designed for the complete variable selection.
+You should modify this algorithm in such a way that a more exhaustive exploration of the space of models was carried out, perhaps using Bayesian variable selection procedures based on the use of Occam’s window or something similar.
+\end{comment}
+
+\begin{reply}
+	\fede{Thank you for your comments.
+We believe that in the first version of the paper the purpouse of our work was not clear and subject to possible misunderstanding.
+Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal.
+We studied what is the action of the reference model itself, disentangled from the specific variable selection algorithm.
+	We made it clearer in Section 1, where we now write}
+
+	\vspace{0.5cm}
+
+	\textit{``The goal of our work is to study the impact of reference model approaches disentangling the benefit of the usage of a reference model from the specific selection algorithm.
+Specifically, we:
+		\begin{itemize}
+			\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach.
+This allows us to build up a comparison independent of the specific variable selection method;
+			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
+			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.''
+		\end{itemize}}
+
+		\vspace{0.5cm}
+
+		\fede{Moreover, the projective prediction approach for complete variable selection is not the aim of this work.
+The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
+Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection.
+We do not exclude that better projective prediction method for complete selection can be designed in the future.}
+\end{reply}
 
@@
 \begin{reply}
-We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
-A sensible reference model doesn't need to be Bayesian. The results are better with better reference models.
+Thank you for your comments. We have added clarification at the end of Section 2.3 regarding the reference model, in particular we write that
+
+\vspace{0.5cm}
+\textit{
+``Clearly, the reference model approach requires a sensible model.
+The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}.
+Better predictive models imply better selection results.
+The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
+In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.''
+}
+\vspace{0.5cm}
+
+So that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
 
@@
 In this paper the point is not the Bayesian workflow, but to analyse given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
+
 The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues.
@@
 The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors.
-We have added references that discuss merits of Bayesian approach compared to MLE.
+We have added references that discuss merits of Bayesian approach compared to MLE \fede{not yet added!}.
 Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
@@
 \reviewersection
+%%%% REVIEWER 3
 
@@
 \begin{reply}
-\fede{Thank you for the feedback. We renovated Section 1 and Section 2, improving the paper according to your suggestions.}
+\fede{Thank you for the feedback.
+We renovated Section 1, improving the paper according to your suggestions.
+In particolar, we clarified what is the motivation of our work and, thus, what is the purpouse of the reference model approach used in our experiments.
+In the new version of the paper we write
+}
+\vspace{0.5cm}
+
+\textit{``The goal of our work is to study the impact of reference model approaches disentangling the benefit of the usage of a reference model from the specific selection algorithm. Specifically, we:
+	\begin{itemize}
+		\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach.
+This allows us to build up a comparison independent of the specific variable selection method;
+		\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
+		\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.''
+	\end{itemize}}
+
+	\vspace{0.5cm}
+
 \end{reply}
@@
 \begin{reply}
-\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3.}
+\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:
+}
+
+\vspace{0.5cm}
+\textit{
+The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
+The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied.
+These results are confirmed also in the real word data example with the body fat dataset.
+The stepwise selection achieves far better selection with the reference model approach (see Figure 5 and Table 3).
+However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.
+Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
+}
+\vspace{0.5cm}
 \end{reply}

### 2022-01-04 paper/ref_approach.tex
expanded answers including paper edits

@@
 
-\fede{Clearly, the reference model approach require a sensible model.
-The construcion of such a model should follow proper modelling workflow including model assessment and validation \citep[see, e.g.][]{gelman2020bayesian}.
-Better predictive models imply better selection results.}
+\fede{Clearly, the reference model approach requires a sensible model.
+The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}.
+Better predictive models imply better selection results.
+The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
+In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.}
 

### 2022-01-05 reviews/rebuttal.tex
extended answers to reviewers

@@
 \begin{reply}
-Thank you for your comments. We have added clarification at the end of Section 2.3 regarding the reference model, in particular we write that
+Thank you for your comments. We have added clarification at the end of Section 2.2 regarding the reference model, in particular we write that
 
@@
 The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
-In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.''
+[...] In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.''
 }
@@
 \begin{reply}
-MLE is more unstable than Bayesian approach.
+Thank you for the interesting question.
+It is known that MLE is more unstable than Bayesian approach.
 The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors.
-We have added references that discuss merits of Bayesian approach compared to MLE \fede{not yet added!}.
+We have added references that discuss merits of Bayesian approach compared to MLE.
 Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
+
+Inspired by your question, we added a discussion of this in the new version of the paper. In Section 2.2 we write
+
+\vspace{0.5cm}
+
+\textit{``In general, there is not restriction on the type of model the reference models 
+	should be and a sensible reference model does not need to be Bayesian.
+	However, Bayesian methods can help in some of those situations
+	where MLE procedures struggle. 
+	It is known that as the number of parameters in the model increases, the MLE
+	estimator is dominated by shrunk estimators 
+	\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
+	The use of a prior in Bayesian inference automatically incorporates 
+	some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
+	For the sake of our study, we rely on simple data structure which can be well described 
+	by linear regression models.
+However, more complex data can arise from applications, for example including hierarchical structures.
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.''}
+
+\vspace{0.5cm}
+
 \end{reply}
@@
 \textit{
-The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
+``The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
 The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied.
@@
 Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
-Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.''
 }

### 2022-01-05 paper/ref_approach.tex
extended answers to reviewers

@@
 stable selection process. This holds even if the reference model does
-not perfectly resemble the true data generating process. Moreover, our
-analyses indicate that the substantial reduction of variance
-attributable to noise is usually more important than small potential
-bias due to model misspecification.  We argue that, regardless of how
+not perfectly resemble the true data generating process. 
+\fede{Clearly, the reference model approach requires a sensible model. 
+The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. 
+The goodness of a reference model comes from its predictive ability which should be 
+assessed via proper validation methods.} Our analyses indicate that the substantial 
+reduction of variance attributable to noise is usually more important than small potential
+bias due to model misspecification.
+\fede{When the goal is ranking the variables for importance to
+perform variable selection, it is known that variance is
+generally more harmful then bias \citep{piironen2017comparison}.}
+
+\fede{In general, there is not restriction on the type of model the reference models 
+should be and a sensible reference model does not need to be Bayesian.
+However, Bayesian methods can help in some of those situations
+where MLE procedures struggle. 
+It is known that as the number of parameters in the model increases, the MLE
+estimator is dominated by shrunk estimators 
+\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
+The use of a prior in Bayesian inference automatically incorporates 
+some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
+For the sake of our study, we rely on simple data structure which can be well described 
+by linear regression models.
+However, more complex data can arise from applications, for example including hierarchical structures.
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.}
+
+We argue that, regardless of how
 the reference model is set up and used in the inference procedure, it
@@
 \end{figure}
-
-\fede{Clearly, the reference model approach requires a sensible model.
-The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}.
-Better predictive models imply better selection results.
-The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
-In general, there is not restriction on the type of model the reference models should be and a sensible reference model does not need to be Bayesian.}
 

### 2022-01-07 reviews/rebuttal.tex
edit response to comments for clarity and politeness

--- 2022-01-03 reviews/rebuttal.tex
@@
 
+\newenvironment{comment}
+{\medskip \noindent \begin{sf}\textbf{Reviewer~comment}:\  }
+	{\medskip \end{sf}}
+
 \newenvironment{reply}
@@
 \paragraph{Reply}
-\fede{We have elaborated a better version of our paper following many of the reviewers' comments and suggestions.
-However, we believe that there has been a misunderstanding on the purpose of our work by Reviewer 1.
-The projective prediction approach for complete variable selection is not the aim of this work.
-The method has been included for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
-Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection.
-We do not exclude that better projective prediction method for complete selection can be designed in the future.
-\\
+Based on the reviewers' comments and suggestions, we have substantially improved our paper.
+In particular, we hope that we now better explain the purpose of our work, which was a source of confusion in our original version.
+
+We hope that this specifically clarifies one misunderstanding on the purpose of our work highlighted by Reviewer 1 as we now better explain that the projective prediction approach for complete variable selection is not the main aim of the paper.
+This method has been included solely for the sake of a more exhaustive comparison, because of the good performances of the projective prediction method (projpred) for minimal variable selection.
+Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it not trivial to extend for the complete selection.
+We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in scope of this paper.
+
 Reviewer 3 gave precious comments on how to clarify the real intentions of our work, which is the study of the effect of reference models when used to guide the selection process, regardless of the selection method.
-We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.}
+We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.
 
@@
 \reviewersection
+\begin{comment}
+The paper is well written and organized an the topic analyzed is very relevant and practice.
+However, in my view, the goals of the paper, described in the introduction section, have already been reached in the excellent paper of Pironen et al.
+(2020) and, in this sense, the contributions of the current paper is very marginal.
+The framework of Pironen et al.
+(2020) is more general (they consider exponential family models and generalized linear models) and provide some theoretical results that, as they said “...
+help us to understand when the reference model could be helpful for parameter learning in linear submodels” (section 8 of Piironen et al., 2020).
+The only innovation that I can appreciate in the current paper is the proposal of an algorithm to solve a complete variable selection problem that, unfortunately, does not work very well as the authors explicitly recognize: “The great performance of projpred in minimal subset selection is not carried out over for the complete variable selection with iterative projpred ..., and the methods specifically designed for the complete variable selection perform better” (page 12, lines 24-27), even though they observe a better selection to iterative lasso.
+In my view, this is due to that the algorithm is too simple (as the authors explicitly recognize in the conclusions) and that the projective prediction approach was not designed for the complete variable selection.
+You should modify this algorithm in such a way that a more exhaustive exploration of the space of models was carried out, perhaps using Bayesian variable selection procedures based on the use of Occam’s window or something similar.
+\end{comment}
+
+\begin{reply}
+	Thank you very much for your comments.
+We believe that in the first version of the paper, the purpouse of our work was not clear and subject to possible misunderstandings.
+Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm
+	We now make our goals explicit already in Section 1, where we now write
+
+	\vspace{0.5cm}
+
+	\textit{``The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+In particular, we:
+		\begin{itemize}
+			\item propose a simple and intuitive approach to combine any variable selection method with the reference model approach.
+This allows us to investigate the benefit of using reference models independent of the specific variable selection method;
+			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
+			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimial subset variable selection.''
+		\end{itemize}}
+
+		\vspace{0.5cm}
+
+		Moreover, we clarified that the projective prediction approach for complete variable selection is not the main aim of this work.
+The method has been included solely for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
+Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection.
+We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in scope of this paper.
+\end{reply}
 
@@
 \begin{reply}
-We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
-A sensible reference model doesn't need to be Bayesian. The results are better with better reference models.
+Thank you for this comment. We have added some clarifications at the end of Section 2.2 with regard to building the reference model, where we write
+
+\vspace{0.5cm}
+\textit{
+``Clearly, the reference model approach requires a sensible reference model.
+The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}.
+Better predictive models imply better selection results.
+The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
+[...] In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.''
+}
+\vspace{0.5cm}
+
+As such, for example, a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
 
@@
 In this paper the point is not the Bayesian workflow, but to analyse given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
-The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues.
+
+The reference models used in the examples are using widely accepted weakly informative priors and there are no prior sensitivity issues for them.
 As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
@@
 \begin{reply}
-MLE is more unstable than Bayesian approach.
-The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors.
-We have added references that discuss merits of Bayesian approach compared to MLE.
-Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
+This is an interesting question.
+The way we see it is that MLE tends to be more unstable than comparable Bayesian approaches, as the latter get improved stability both from integration over the parameter space (instead of using only a point estimate) and can further be improved by using even just weakly informative priors (rather than improper flat priors).
+We have added references that discuss the merits of Bayesian approaches compared to MLE.
+Although we think Bayesian reference models are a better choice in most cases, we also assume that in large $n$, small $p$ cases there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model too.
+
+Inspired by your question, we added a discussion of this in the new version of the paper. In Section 2.2 we write
+
+\vspace{0.5cm}
+
+\textit{``In general, there is no restriction on the type of model the reference models 
+	should be and a sensible reference model does not even need to be Bayesian.
+	However, Bayesian methods can help in some of those situations
+	where MLE procedures struggle. 
+	It is known that, as the number of parameters in the model increases, the MLE
+	estimator is dominated by shrunk estimators 
+	\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
+	The use of a prior in Bayesian inference automatically incorporates 
+	some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
+	For the sake of our study, we rely on simple data structure which can be well be described 
+	by linear regression models.
+However, more complex data can arise in practice, for example, including hierarchical structures.
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.''}
+
+\vspace{0.5cm}
+
 \end{reply}
@@
 In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in \citet{paasiniemi2018} to analyse alternative possible variable sets.
+TODO: clarify this in the paper in 1 or 2 sentences?
 \end{reply}
@@
 We assume that all models are wrong.
-Analysing model misspecification is well studied in Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}.
+Analysing model misspecification is well studied in the Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}.
 The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}.
-Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved.
+Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved via an improved bias-variance tradeoff.
+TODO: clarify this in the paper 
 \end{reply}
@@
 \begin{reply}
-Please, see \citet{piironen2020projective} for further information.
+This situation was studied in \citet{piironen2020projective} and we now reference it in the paper by writing: 
+TODO: please add a clarifying sentence
 \end{reply}
@@
 \begin{reply}
-The usual Bayesian workflow \citep{gelman2020bayesian} states that if there is uncertainty about which model then we integrate over the model space or create a continuous super model that includes the alternative models as special cases.
+Following current best practices in the Bayesian workflow \citep{gelman2020bayesian}, if there is uncertainty about which model is best, then we recommend integrating over the model space or creating a continuous super model that includes the alternative models as special cases.
 \end{reply}
@@
 \begin{reply}
-\fede{There is no need of calibration of the pvalues, since they are used only to select the "worse" predictor.
-Such predictor is then excluded or not, looking at the predictive performance of the reduced model and of the not-reduced one.
-In such a way, the posterior pvalues matter only for their ordering and not for their magnitude.}
+There is no need of calibrating these pvalues, since they are used only to pre-select predictors for potential exclusion.
+Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and of the not-reduced model including the predictor.
+In such a way, the posterior pvalues matter only in terms of their ordering and not in terms of their magnitude.
 \end{reply}
@@
 \begin{reply}
-We used AIC because reference \citet{heinze2018variable} was using AIC.
-The goal of the paper was not to compare all possible information criteria.
-We made choices to keep the paper within reasonable length.
+We used AIC because \citet{heinze2018variable} was using AIC in the steplm procedure.
+The goal of our paper was not to compare all possible information criteria but to investigate whether using reference models helps variable selection methods.
+We made some choices to keep the paper within reasonable length and complexity.
 Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model.
@@
 \begin{reply}\label{reply:stopping}
-\fede{At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}.
+At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}.
 For details, see \citet{piironen2020projective}.
-In few words, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
-The obtained lpd samples are used to estimate that probability.}
+Explained shortly, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
+The obtained lpd samples form a distribution than can be used to estimate said probability.
+TODO: is it worth adding at least half of a sentence for this?
 \end{reply}
@@
 \begin{reply}
-\fede{The above condition derives from the original criteria to choose the model size in \citet{piironen2020projective} for the use of the projection predictive approach in the minimal subset scenario.
+The above condition is derived from the original criteria to choose the model size in \citet{piironen2020projective} for the use of the projection predictive approach in the minimal subset scenario.
 In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model.
@@
 \\
-In general, notice that the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself.}
+In general, notice that the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself.
+We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account.
+However, since this was not the main aim of this paper, we cannot reasonably address it here but will leave it for future research.
+TODO: is it worth adding a small sentence in the manuscropt about this?
 \end{reply}
@@
 \begin{reply}
-\fede{The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
-One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.}
+The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
+One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.
+TODO: clarify this in the paper
 \end{reply}
@@
 \begin{reply}
-\fede{Thank you for the feedback. We renovated Section 1 and Section 2, improving the paper according to your suggestions.}
+Thank you for your very helpful feedback.
+We have updated Section 1 following your suggestions.
+In particular, we clarified the motivation of our work and, thus, the purpouse of the reference model approach used in our experiments.
+In the revised version of the paper we write
+
+\vspace{0.5cm}
+
+\textit{``The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+In particular, we:
+		\begin{itemize}
+			\item propose a simple and intuitive approach to combine any variable selection method with the reference model approach.
+This allows us to investigate the benefit of using reference models independent of the specific variable selection method;
+			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
+			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimial subset variable selection.''
+		\end{itemize}}
+
+	\vspace{0.5cm}
+
 \end{reply}
@@
 \begin{reply}
-\fede{We touch the computational aspects in Section 2.2.
-The reference model approach has in general the additional cost of fitting a reference model.
-However, this is usually available when building up a model via robust workflows \citep{gelman2020bayesian}.
-Therefore, in these cases there is not additional cost.
-In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.}
+We discuss the computational aspects in Section 2.2.
+In general, the reference model approach has the additional cost of fitting the reference model before performing selection.
+However, this reference models is usually available anyway when building up a model via robust workflows \citep{gelman2020bayesian}.
+Therefore, in these cases there is no additional cost.
+In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
+TODO: does the reviewer only mean the reference model or also the selection methods themselves?
+Can we say something (vaguely) about the computational cost of the selection methods?
+Right now, I think this answer to the reviewer will not be percevied as fully satisfying.
 \end{reply}
@@
 \begin{reply}
-\fede{We added a new Section 3.3 which summarises and elaborate the results of Section 3.}
+This is a good idea. We added a new Section 3.3 which summarises and elaborate the results of Section 3. In particular, we write:
+
+\vspace{0.5cm}
+\textit{
+``The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
+The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied.
+These results are confirmed also in the real word data example with the body fat dataset.
+The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 3).
+However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.
+Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.''
+}
+\vspace{0.5cm}
 \end{reply}

### 2022-01-13 reviews/rebuttal.tex
rebuttal edits

@@
 \usepackage{xcolor}
-\usepackage{hyperref}
+\usepackage[pdftex,colorlinks=true,citecolor=black,pagecolor=black,linkcolor=black,menucolor=black, urlcolor=black]{hyperref}
 \usepackage{amsmath}
@@
 \newenvironment{point}
-   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ }
-   {\par }
+   {\refstepcounter{point} \bigskip \noindent \begin{sf}{\textbf{Reviewer~Point~\thepoint} } ---\ }
+   {\par \end{sf}}
 
 \newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
-	{\textbf{Reviewer~Point~\thepoint} } ---~#1\par }
+	{\begin{sf}\textbf{Reviewer~Point~\thepoint} } ---~#1\par \end{sf}}
 
@@
 
+\newenvironment{aecomment}
+{\medskip \noindent \begin{sf}\textbf{Associate Editor comment}:\  }
+	{\medskip \end{sf}}
+
 \newenvironment{reply}
-   {\medskip \noindent \begin{sf}\textbf{Reply}:\  }
-   {\medskip \end{sf}}
+   {\medskip \noindent \textbf{Reply}:\  }
+   {\medskip}
 
@@
 \medskip 
-\section*{Associated Editor}
+\section*{Associate Editor}
 
-\paragraph{Associated Editor comment}
+\begin{aecomment}
 Please note the strong concerns of the reviewers.
 If you cannot implement a better projective prediction approach for complete variable selection problems, then at the very least, I would expect you to motivate why it's worth knowing about this approach; you show that it doesn't work very well.
+\end{aecomment}
 
-\paragraph{Reply}
+\begin{reply}
 Based on the reviewers' comments and suggestions, we have substantially improved our paper.
@@
 We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.
+\end{reply}
 
@@
 We believe that in the first version of the paper, the purpouse of our work was not clear and subject to possible misunderstandings.
-Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm
+Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm.
 	We now make our goals explicit already in Section 1, where we now write
@@
 	It is known that, as the number of parameters in the model increases, the MLE
-	estimator is dominated by shrunk estimators 
+	estimator is dominated by shrinkage estimators 
 	\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
@@
 \begin{reply}
-There is no need of calibrating these pvalues, since they are used only to pre-select predictors for potential exclusion.
+There is no need of calibrating these $p$-values, since they are used only to pre-select predictors for potential exclusion.
 Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and of the not-reduced model including the predictor.
-In such a way, the posterior pvalues matter only in terms of their ordering and not in terms of their magnitude.
+In such a way, the posterior $p$-values matter only in terms of their ordering and not in terms of their magnitude.
 \end{reply}
@@
 \begin{reply}
-We used AIC because \citet{heinze2018variable} was using AIC in the steplm procedure.
+We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure.
 The goal of our paper was not to compare all possible information criteria but to investigate whether using reference models helps variable selection methods.
@@
 \\
-In general, notice that the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself.
+In general, the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself.
 We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account.

### 2022-01-16 reviews/rebuttal.tex
Add a few tiny grammatical edits

@@
 This method has been included solely for the sake of a more exhaustive comparison, because of the good performances of the projective prediction method (projpred) for minimal variable selection.
-Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it not trivial to extend for the complete selection.
-We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in scope of this paper.
+Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it non-trivial to extend for the complete selection.
+We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in the scope of this paper.
 
@@
 The method has been included solely for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
-Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it not trivial to extend for the complete selection.
-We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in scope of this paper.
+Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it non-trivial to extend for the complete selection.
+We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in the scope of this paper.
 \end{reply}

### 2022-01-17 reviews/rebuttal.tex
fixed some TODO

@@
 In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in \citet{paasiniemi2018} to analyse alternative possible variable sets.
-TODO: clarify this in the paper in 1 or 2 sentences?
+
+\fede{We clarified this point in the paper in Section 3, writing:}
+
+\vspace{0.5cm}
+
+\textit{``Such nature of the minimal subset makes the solution
+	not unique, except in the particular case of completely orthogonal predictors. 
+	The non-uniqueness of the solution is not a problem per se, as different samples of the data
+	are expected to give possible different minimal subsets but with same predictive power. 
+	However, it makes it difficult to define a proper
+	concept of stability of the selection.''}
 \end{reply}
@@
 \begin{reply}
-The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
-One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.
 TODO: clarify this in the paper
+\fede{We clarified the choice of $\alpha$ by writing in Section 4.1:}
+
+\vspace{0.5cm}
+
+\textit{``The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
+One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.''}
+
 \end{reply}

### 2022-01-17 paper/ref_approach.tex
fixed some TODO

@@
 which are not in the minimal subset are highly correlated with variables already in
-the minimal subset. We will return to a problem of finding all
+the minimal subset. \fede{Such nature of the minimal subset makes the solution
+not unique, except in the particular case of completely orthogonal predictors. 
+The non-uniqueness of the solution is not a problem per se, as different samples of the data
+are expected to give possible different minimal subsets but with same predictive power. 
+However, it makes it difficult to define a proper
+concept of stability of the selection.} \\
+We will return to a problem of finding all
 the variables with some predictive power in Section~\ref{complete-selection}.
@@
 In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package, that is, $\alpha=0.16$.
+\texttt{R}-package, that is, $\alpha=0.16$. \fede{The choice of $\alpha$ to determine 
+the submodel size is discussed in \cite{paper:projpred}. One possible way to proceed, 
+but just as rule of thumb, is to choose $\alpha = 0.16$, which correspond to requiring 
+that the submodel predictive score is at most at one standard deviation distance 
+from the best submodel predictive score.}
 

### 2022-01-18 reviews/rebuttal.tex
computational time for bodyfat example

@@
 \begin{reply}
-TODO: clarify this in the paper
 \fede{We clarified the choice of $\alpha$ by writing in Section 4.1:}
@@
 \begin{reply}
+Thanks for the suggestion.
 We discuss the computational aspects in Section 2.2.
@@
 In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
-TODO: does the reviewer only mean the reference model or also the selection methods themselves?
-Can we say something (vaguely) about the computational cost of the selection methods?
-Right now, I think this answer to the reviewer will not be percevied as fully satisfying.
+\fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
 \end{reply}
@@
 These results are confirmed also in the real word data example with the body fat dataset.
-The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 3).
+The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4).
 However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.

### 2022-01-18 paper/ref_approach.tex
computational time for bodyfat example

@@
 \citep{bair2006prediction,piironen2018} can produce useful reference
-models.
+models. \fede{As an example, Table \ref{tab:computational_time} reports
+the computational time for the body fat data example of Section \ref{bodyfat-1}. 
+For reference model approaches, i.e. projpred and ref+step.lm, the main
+time consuming operation is to fit the reference model. The burden of it depends clearly
+on the specific application and type of model used.}
+
+\begin{table}[tp]
+	\footnotesize
+	\centering
+	\begin{tabular}{l|cc|ccc}
+		Data & Reference model & Search path & projpred & step.lm & ref + step.lm \\
+		\hline
+		body fat & 37.661 & 15.289 & 52.95 &  &  \\
+		  &  & 0.078 &  & 0.078 &  \\
+		  & 37.661 & 0.078 &  &  & 37.739 \\
+		\hline 
+		+ noisy variables & 169.797 & 77.638 & 247.435 &  &  \\
+		  & & 12.019 & & 12.019 & \\
+		  & 169.797 & 12.019 & & & 181.816
+
+	\end{tabular}
+	\caption{Computational time (in seconds) of body fat example of Section \ref{bodyfat-1}.
+		The reported time is the sum of the time to fit the reference model (second column) and
+		to explore the search path (third column), according to the method.}
+	\label{tab:computational_time}
+\end{table}
 

### 2022-01-18 code/bodyfat_comp_time.R

@@ -1,0 +1,50 @@
+library(tidyverse)
+library(rstanarm)
+library(projpred)
+set.seed(453874)
+
+df <- read.table("bodyfat.txt", header = T, sep = ";")
+df[,4:19] <- scale(df[,4:19])
+df <- as.data.frame(df)
+n <- nrow(df)
+colnames(df[c("weight_kg", "height")]) <- c("weight", "height")
+pred <- c("age", "weight", "height", "neck", "chest", "abdomen", "hip",
+          "thigh", "knee", "ankle", "biceps", "forearm", "wrist")
+target <- "siri"
+formula <- paste("siri~", paste(pred, collapse = "+"))
+p <- length(pred)
+df <- df[,c(target,pred)]
+
+p0 <- 2 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+rhs_prior <- hs(global_scale=tau0)
+
+## Analysis with original covariates
+system.time({fit_ref <- stan_glm(formula, data = df,
+                                 prior=rhs_prior, QR=TRUE, seed=8786, refresh=0)})
+
+system.time({proj_path <- cv_varsel(fit_ref, method='forward', cv_method='LOO', nloo=n,
+                     verbose = FALSE) 
+proj_size <- suggest_size(proj_path, alpha=0.1)})
+  
+system.time({steplm <- step(lm(formula, data = df), direction = 'backward')})
+
+## Analysis with additional noisy covariates
+p <- 100
+noise <- array(rnorm((p-13)*n), c(n,p-13))
+dfr<-cbind(df,noise=noise)
+formula2<-paste(formula,"+",paste(colnames(dfr[,15:(p+1)]), collapse = "+"))
+noisy_names <- colnames(dfr[,15:(p+1)])
+
+p0 <- 5 # prior guess for the number of relevant variables
+tau0 <- p0/(p-p0) * 1/sqrt(n)
+hs_prior <- hs(global_scale=tau0)
+
+system.time({fit_ref2 <- stan_glm(formula2, data = dfr, prior = hs_prior, QR = TRUE,
+                                  seed=34523, refresh=0)})
+
+system.time({proj_path2 <- cv_varsel(fit_ref2, method = 'forward', cv_method = 'LOO',
+                                     nloo=n, verbose = FALSE)
+nv2 <- suggest_size(proj_path2, alpha=0.1)})
+
+system.time({steplm2 <- step(lm(formula2, data = dfr), direction = 'backward')})

### 2022-01-19 reviews/rebuttal.tex
edits

@@
 The paper is well written and organized an the topic analyzed is very relevant and practice.
-However, in my view, the goals of the paper, described in the introduction section, have already been reached in the excellent paper of Pironen et al.
+However, in my view, the goals of the paper, described in the introduction section, have already been reached in the excellent paper of Piironen et al.
 (2020) and, in this sense, the contributions of the current paper is very marginal.
-The framework of Pironen et al.
+The framework of Piironen et al.
 (2020) is more general (they consider exponential family models and generalized linear models) and provide some theoretical results that, as they said “...
@@
 	Thank you very much for your comments.
-We believe that in the first version of the paper, the purpouse of our work was not clear and subject to possible misunderstandings.
-Our contribution takes clear insipiration from the work of \citet{piironen2020projective}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm.
+We believe that in the first version of the paper, the purpose of our work was not clear and subject to possible misunderstandings.
+Our contribution takes clear inspiration from the work of \citet{paper:projpred}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm.
 	We now make our goals explicit already in Section 1, where we now write
 
-	\vspace{0.5cm}
-
-	\textit{``The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+\vspace{0.5\baselineskip}
+	\textit{The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
 In particular, we:
@@
 			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
-			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimial subset variable selection.''
+			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
 		\end{itemize}}
 
-		\vspace{0.5cm}
+		\vspace{0.5\baselineskip}
 
@@
 The method has been included solely for the sake of a more exhaustive comparison, since the good performances of the projective prediction method (projpred) for minimal variable selection.
-Indeed, we have highlighted how projpred has been designed specificly for the minimal selection case, making it non-trivial to extend for the complete selection.
+Indeed, we have highlighted how projpred has been designed specifically for the minimal selection case, making it non-trivial to extend for the complete selection.
 We cannot rule out that better projective prediction methods for complete selection can be designed in the future but this is not in the scope of this paper.
@@
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 \textit{
-``Clearly, the reference model approach requires a sensible reference model.
+Clearly, the reference model approach requires a sensible reference model.
 The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}.
@@
 The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
-[...] In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.''
+[...] In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
 }
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 
@@
 
-\vspace{0.5cm}
-
-\textit{``In general, there is no restriction on the type of model the reference models 
+\vspace{0.5\baselineskip}
+\textit{In general, there is no restriction on the type of model the reference models 
 	should be and a sensible reference model does not even need to be Bayesian.
@@
 However, more complex data can arise in practice, for example, including hierarchical structures.
-In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.''}
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 
@@
 \begin{reply}
-The projection predictive variable selection and its properties have been extensively discussed in \citet{piironen2017comparison} and \citet{piironen2020projective}, and we refer to them for the detailed discussion on the uncertainty related to search paths.
+The projection predictive variable selection and its properties have been extensively discussed in \citet{piironen2017comparison} and \citet{paper:projpred}, and we refer to them for the detailed discussion on the uncertainty related to search paths.
 \citet{paasiniemi2018} provides illustrations how this uncertainty can be communicated to the users.
@@
 
-\fede{We clarified this point in the paper in Section 3, writing:}
+We have clarified this point in the paper in Section 3, writing:
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 
-\textit{``Such nature of the minimal subset makes the solution
+\textit{Such nature of the minimal subset makes the solution
 	not unique, except in the particular case of completely orthogonal predictors. 
@@
 	However, it makes it difficult to define a proper
-	concept of stability of the selection.''}
+	concept of stability of the selection.}
 \end{reply}
@@
 The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}.
-Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved via an improved bias-variance tradeoff.
-TODO: clarify this in the paper 
+Even a misspecified model that would introduce some bias can reduce the variance so that the variable selection is improved via an improved bias-variance tradeoff.
+As the selection is to find a submodel that is not far from the reference model, the performance of the selected model is not far from the reference model.
+
+We have clarified this in the introduction:
 \end{reply}
+
+\vspace{0.5\baselineskip}
+\textit{
+We assume all models are wrong, but we assume we have constructed a
+model which reflects our beliefs about the future data in the best
+possible way and which has passed model checking and criticism
+\citep{gelman2020bayesian,gabry2019visualization}.  Using the usual
+best practices for constructing the reference model is important, as
+using a garbage reference model can only lead to selecting similarly
+garbage smaller model. If the reference model is considered to have
+useful predictions then the smaller models selected will also have
+similar useful predictions.
+}
 
@@
 \begin{reply}
-This situation was studied in \citet{piironen2020projective} and we now reference it in the paper by writing: 
-TODO: please add a clarifying sentence
+  Yes, it is possible. This situation has been studied by
+  \citet{piironen2017comparison},
+  \citet{Piironen:2015:Stan_projection}, and
+  \citet{paper:projpred}. We had added to the introduction:
 \end{reply}
+
+\vspace{0.5\baselineskip}
+\textit{
+Examples of useful reference models can be found for example for
+small-$n$-large-$p$ regression and logistic regression by
+\citet{piironen2017comparison} (with spike-and-slab prior),
+\citet{Piironen:2015:Stan_projection} (with horseshoe prior), and
+\citet{paper:projpred} (with iterative supervised principal
+components), for generalized linear and additive multilevel models by
+\citet{Catalina:2020:GAMM_projection}, for regression models with
+non-exponential family observation models by
+\citet{Catalina+etal:2021:latent_projection}, and for generic
+multivariate non-linear regression with higher order interactions by
+\citet{Piironen:2016:GPprojection}.
+}
 
@@
 There is no need of calibrating these $p$-values, since they are used only to pre-select predictors for potential exclusion.
-Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and of the not-reduced model including the predictor.
+Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and the not-reduced model including the predictor.
 In such a way, the posterior $p$-values matter only in terms of their ordering and not in terms of their magnitude.
@@
 \begin{reply}
-We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure.
+We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure and we wanted our results to be comparable to their results.
 The goal of our paper was not to compare all possible information criteria but to investigate whether using reference models helps variable selection methods.
@@
 \begin{reply}
-Thanks for pointing out the typo. We fixed it in the new version of the paper.
+Thanks for pointing out the typo. We have fixed it.
 \end{reply}
@@
 At each iteration, the best model is selected via the default stopping rule implemented in the \texttt{R}-package \texttt{projpred}.
-For details, see \citet{piironen2020projective}.
-Explained shortly, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
+For details, see \citet{paper:projpred}.
+The predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
 The obtained lpd samples form a distribution than can be used to estimate said probability.
-TODO: is it worth adding at least half of a sentence for this?
+We have added following sentence:
+TODO: is the sentence below enough?
 \end{reply}
+
+\textit{
+\ldots and the probability is computed from the normal approximation for the uncertainty in the cross-validation performance comparison \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
+}
 
@@
 \begin{reply}
-The above condition is derived from the original criteria to choose the model size in \citet{piironen2020projective} for the use of the projection predictive approach in the minimal subset scenario.
+The above condition is derived from the original criteria to choose the model size in \citet{paper:projpred} for the use of the projection predictive approach in the minimal subset scenario.
 In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model.
@@
 We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account.
-However, since this was not the main aim of this paper, we cannot reasonably address it here but will leave it for future research.
-TODO: is it worth adding a small sentence in the manuscropt about this?
+However, since the projection predictive approach was not the main point of this paper, we cannot reasonably address it here and leave it for future research.
+We have added a following sentence to the paper.
+TODO: would this be enough?
 \end{reply}
+
+\vspace{0.5\baselineskip}
+\textit{
+We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and worth a further research.
+}
 
@@
 \begin{reply}
-\fede{We clarified the choice of $\alpha$ by writing in Section 4.1:}
+We have clarified the choice of $\alpha$ by writing in Section 4.1:
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 
-\textit{``The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}.
-One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.''}
+\textit{The choice of $\alpha$ to determine the submodel size is discussed in \citet{paper:projpred}.
+One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.}
 
@@
 We have updated Section 1 following your suggestions.
-In particular, we clarified the motivation of our work and, thus, the purpouse of the reference model approach used in our experiments.
+In particular, we clarified the motivation of our work and, thus, the purpose of the reference model approach used in our experiments.
 In the revised version of the paper we write
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 
-\textit{``The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+\textit{The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
 In particular, we:
@@
 			\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
-			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimial subset variable selection.''
+			\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
 		\end{itemize}}
 
-	\vspace{0.5cm}
+	\vspace{0.5\baselineskip}
 
@@
 
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 \textit{
-``The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
+The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
 The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied.
@@
 Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
-Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.''
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
 }
-\vspace{0.5cm}
+\vspace{0.5\baselineskip}
 \end{reply}
@@
 \begin{reply}
-Thank you for the feedback, we mentioned the availability of the R codes under each section in the new version of the paper.
+Thank you for the feedback, we mentioned the availability of the R code in the end of the introduction.
 \end{reply}
@@
 \bibliographystyle{abbrvnat}
-\bibliography{rebuttal}
+\bibliography{../paper/ref_approach}
 

### 2022-01-19 paper/ref_approach.tex
edits

@@
 A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
-As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability leading to improved model selection performance.
-Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive variable selection approach.
+As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability, leading to improved model selection performance.
+Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model, leading to projection predictive variable selection approach.
 Alternatively, reference models may also be used in an ad-hoc manner in combination with common variable selection methods.
@@
 Our results indicate that the use of reference models generally translates into better and more stable variable selection.
-Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods independently of whether or not they use reference models.
+Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods, independently of whether or not they use reference models.
 \end{abstract}
@@
 observed empirical data distribution is utilised as a proxy of future
-data usually in combination with cross-validation or information
-criteria to provide estimates for out-of-sample predictive
+data, usually in combination with cross-validation or information
+criteria to provide estimates of out-of-sample predictive
 performance.  In contrast, reference model based methods approximate
@@
 of a reference model, which can be, for example, a full-encompassing
-model including all variables.  The main assumption under any
-reference model approach is that we operate in an
-$\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
-constructed a model which reflects our beliefs about
-the future data in the best possible way and which has passed model checking and criticism
-\citep[see, e.g.][]{gelman2013bayesian,gabry2019visualization}.  The reference model approach
-has been used in Bayesian statistics at least since the seminal
-work of \citet{paper:reference_lindley}. For more historical
-references, see \citet{vehtari2012survey} and
-\citet{paper:model_selection}, and for most recent methodological
-developments see \citet{paper:projpred}.
+model including all variables.
+%
+We assume all models are wrong, but we assume we have constructed a
+model which reflects our beliefs about the future data in the best
+possible way and which has passed model checking and criticism
+\citep{gelman2020bayesian,gabry2019visualization}.  Using the usual
+best practices for constructing the reference model is important, as
+using a bad reference model can only lead to selecting a similarly
+bad smaller model. If the reference model is considered to have
+useful predictions, then the smaller models selected will also have
+similar useful predictions.
+%
+The reference model approach has been used in Bayesian statistics in
+some form at least since the seminal work of
+\citet{paper:reference_lindley}. For more historical references, see
+\citet{vehtari2012survey} and \citet{paper:model_selection}, and for
+most recent methodological developments see \citet{paper:projpred}.
+%
+Examples of useful reference models can be found for example for
+small-$n$-large-$p$ regression and logistic regression by
+\citet{piironen2017comparison} (with spike-and-slab prior),
+\citet{Piironen:2015:Stan_projection} (with horseshoe prior), and
+\citet{paper:projpred} (with iterative supervised principal
+components), for generalized linear and additive multilevel models by
+\citet{Catalina:2020:GAMM_projection}, for regression models with
+non-exponential family observation models by
+\citet{Catalina+etal:2021:latent_projection}, and for generic
+multivariate non-linear regression with higher order interactions by
+\citet{Piironen:2016:GPprojection}.
 
@@
 Whatever the terminology or applied statistical framework, reference
-models offer a powerful approach to improving variable selection as we
+models offer a powerful approach to improving variable selection, as we
 will demonstrate in the present paper. \\
@@
 % The main contributions of our work are:
-
 \fede
@@
 variable selection, respectively, before we end with a conclusion in Section \ref{conclusion}.
+The code to run all
+the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 into the theoretical reasons why reference models help in variable selection.
-\\
-The code to run all
-the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 and circumference of different body parts). The
-variables are highly correlated which causes additional
+variables are highly correlated, which causes additional
 challenge in the variable selection. In total, we have 251
@@
 abdomen and height to be always included in the model. For better
-comparison we do not fix any of the variables.  The steplm approach is
+comparison, we do not fix any of the variables.  The steplm approach is
 carried out combining the \texttt{step} and \texttt{lm} functions in \texttt{R}.
@@
 when taking into account the uncertainty in estimating the predictive
-model performance. See Appendix A for brief review of projection
+model performance. See Appendix A for a brief review of projection
 predictive approach, and papers by \citet{paper:model_selection} and
@@
 or steplm.  There is no significant difference in predictive performance
-of the selected models by different approaches even if there is
+of the selected models by different approaches, even if there is
 clear difference in the number of selected variables. This can be explained by high
-correlation between the variables and different combinations can
+correlation between the variablesm and different combinations can
 provide similar predictive accuracy.
@@
 with respect to quality of the variable selection is indeed whether or 
-not a reference model is applied.
+not a reference model is applied, and the performance of steplm can
+also be improved by using a reference model.
 
@@
 \fede{When the goal is ranking the variables for importance to
-perform variable selection, it is known that variance is
-generally more harmful then bias \citep{piironen2017comparison}.}
+perform variable selection, it is known that large variance is
+generally more harmful than small bias \citep{piironen2017comparison}.}
 
@@
 reference model as it was estimated as part of the analysis anyway.
-Sometimes including all the available variables in an
+Sometimes, including all the available variables in an
 elaborate model can be computationally demanding.  In such a
@@
 as for example the supervised principal components
-\citep{bair2006prediction,piironen2018} can produce useful reference
-models. \fede{As an example, Table \ref{tab:computational_time} reports
+\citep{bair2006prediction,piironen2018}, can produce useful reference
+models \citep{paper:projpred}. \fede{As an example, Table \ref{tab:computational_time} reports
 the computational time for the body fat data example of Section \ref{bodyfat-1}. 
@@
 		\hline
-		body fat & 37.661 & 15.289 & 52.95 &  &  \\
-		  &  & 0.078 &  & 0.078 &  \\
-		  & 37.661 & 0.078 &  &  & 37.739 \\
+		body fat & 38 & 15 & 53 &  &  \\
+		  &  & 0.08 &  & 0.08 &  \\
+		  & 38 & 0.08 &  &  & 38 \\
 		\hline 
-		+ noisy variables & 169.797 & 77.638 & 247.435 &  &  \\
-		  & & 12.019 & & 12.019 & \\
-		  & 169.797 & 12.019 & & & 181.816
+		+ noisy variables & 170 & 78 & 247 &  &  \\
+		  & & 12 & & 12 & \\
+		  & 170 & 12 & & & 182
 
@@
 	\caption{Computational time (in seconds) of body fat example of Section \ref{bodyfat-1}.
-		The reported time is the sum of the time to fit the reference model (second column) and
-		to explore the search path (third column), according to the method.}
+		The reported times for each each method on the three last columns are sums of the time to fit the reference model (second column) and
+		to explore the search path (third column).}
 	\label{tab:computational_time}
@@
 variables with $Y$ against the corresponding correlations with the
-predictions of a reference model (in this case the posterior
+predictions of a reference model (in this case, the posterior
 predictive means of model \eqref{eq:ref_mod}; see Section
@@
   non-relevant in blue) with the target variable $y$ and the latent variable 
-  $f$ respectively on the x and y axis. Simulated data are generated according to 
+  $f$ respectively on the x- and y-axes. Simulated data are generated according to 
   \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
@@
 However, it makes it difficult to define a proper
-concept of stability of the selection.} \\
+concept of stability of the selection.} 
 We will return to a problem of finding all
 the variables with some predictive power in Section~\ref{complete-selection}.
-\\
-The code to run all
-the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
+%
+% The code to run all
+% the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 variables over the number of selected variables) of the selected submodel,
-averaged after 100 data simulations. We see that projpred has superior FDR and the
-smallest RMSE. Using a reference model improves steplm significantly,
-but the minimal subset variable selection stays unreliable. Stepwise
+averaged after 100 data simulations. Use of a reference model reduces RMSE of the selected model for all the methods. projpred has superior FDR and the
+smallest RMSE. Using a reference model improves also FDR of steplm significantly. Stepwise
 Bayesian linear regression is better than steplm when comparing both methods with
@@
 variables, and the largest entropy would be observed if the approach
-would always selected different sets of variables. Therefore, lower entropy 
+would always select different sets of variables. Therefore, lower entropy 
 corresponds to a more stable selection. Highly correlated predictive variables may happen to be
@@
 projpred approach turns out to be far more stable than all
-other methods. This is likely due to projpred being based on better
+other methods. This is likely due to projpred being based on a better
 decision theoretical formulation which 1) takes into account the full
-predictive distribution and not just point estimate and 2) projects
+predictive distribution and not just a point estimate and 2) projects
 the reference model posterior to the submodel instead of using a
@@
   \caption{Simulation study 1: Root mean square error (RMSE) against false discovery rate in the minimal subset variable selection with one standard deviation error bars.
+Use of a reference model reduces RMSE of the selected model for all the methods.
 The projpred approach has the smallest RMSE and false discovery ratio.}
@@
 
-Here we repeat the selection of Section \ref{bodyfat-1} via
+Here, we repeat the selection of Section \ref{bodyfat-1} via
 stepwise backward regression. In this case, the overall number of
@@
 reference model approach applied to the stepwise backward regression
-achieves outstanding improvements considering its simplicity, yet it
+achieves outstanding improvements considering its simplicity, although it
 does not reach the goodness of the much more sophisticated projective
@@
 \subsection{Reference model's effect and the projection predictive approach}
-\fede{The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case. \\
+\fede{The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
+  %
 The simulation study based on artificial data of Section \ref{minimal-simulated} shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied.
@@
 An alternative to minimal subset variable selection is \emph{complete
-  variable selection} in which the goal is to find all relevant
+  variable selection}, in which the goal is to find all relevant
 variables that have some predictive information about the target. In
@@
 The projection predictive approach was originally designed for the minimal subset
-variable selection but we will test a simple iterative variant for the complete
-variable selection case in this Section.
+variable selection, but we will test a simple iterative variant for the complete
+variable selection case in this section.
  In addition, we analyse the benefits of the reference
@@
 means a more stable selection. 
-\\
-The code to run all
-the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
+%
+% The code to run all
+% the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 
-We modify the projection predictive approach for complete variable
+Projection predictive approach has been originally designed for minimal subset selection. For the comparison purposes, 
+we modify the projection predictive approach for complete variable
 selection by using it iteratively.  Applying the straightforward
@@
 iterations from the search.
- At each iteration the selected submodel size corresponds to the
+ At each iteration, the selected submodel size corresponds to the
 one having a predictive performance close enough to the baseline
@@
 \end{equation}
-where $i$ indexes the submodel size and ``best'' stands for the best predictive explored submodel
-at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
+where $i$ indexes the submodel size, ``best'' stands for the best predictive explored submodel
+at the considered iteration, and the probability is computed from the normal approximation for the uncertainty in the cross-validation performance comparison \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
+The algorithm terminates when the empty model (only intercept) satisfies
 the stopping rule (see Algorithm \ref{alg:iterated_proj}).
@@
 number of observations or not very predictive variables.
-In our experiments we chose the default value used in the \texttt{projpred} 
+We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and worth a further research.
+In our experiments, we chose the default value used in the \texttt{projpred} 
 \texttt{R}-package, that is, $\alpha=0.16$. \fede{The choice of $\alpha$ to determine 
@@
 In the experiments shown in the next sections, we include an additional iterative
-method which we refer to as `iterative lasso'. It consists of the same iterative
+method, which we refer to as `iterative lasso'. It consists of the same iterative
 algorithm as iterative projpred except for not using any reference model, but
@@
 meaning no relevance) against the alternative hypothesis distribution
-$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
+$f_{1}$. In our case, $f_{0}$ corresponds to the standard normal
 distribution (see expression \eqref{eq:normal_means_problem2}). The
@@
 such that all the data under that threshold have posterior median
-equal to zero. Therefore the selection is done by selecting only those
+equal to zero. Therefore, the selection is done by selecting only those
 parameters whose posterior median is different from zero. The
@@
 
-All of these methods provide a complete selection approach and we
+All of these methods provide a complete selection approach, and we
 compare their performance with and without using a reference model.
@@
 normal means problem \eqref{eq:normal_means_problem}. For further
-details see the examples by \cite{paper:efron, efron2012large}.
+details, see the examples by \cite{paper:efron, efron2012large}.
 
@@
 use a reference model which a Bayesian linear regression using the first five
-supervised principal components (SPC) as variables and imposing an hierarchical prior on
+supervised principal components (SPC) as variables and imposing a hierarchical prior on
 their coefficients:
@@
 measure proposed by \cite{paper:stability} with 0.95 confidence
-intervals based on 100 simulations. Such a measure takes in account
+intervals based on 100 simulations. Such a measure takes to account
 the variability of the subset of the selected variables at each
@@
 We conclude our complete selection experiments using the body fat
-dataset one more time. As earlier we add noisy uncorrelated variables
+dataset one more time. As earlier, we add noisy uncorrelated variables
 to the original data to get a total of 100 variables.
-Since we do not have a ground truth available with regard the original
+Since we do not have a ground truth available with regard to the original
 variables of the data, we assume it is reasonable to consider all of
@@
 specifically designed for the complete variable selection perform better. 
-However we still observe a better selection with respect to iterative lasso
+However, we still observe a better selection with respect to iterative lasso
 in any of the examined scenarios, mainly in terms of false discovery rate.
@@
 \cite{paper:stability}. The benefits of the reference model are here
-marginal with only small improvements.
+marginal, with only small improvements.
 
@@
 predictive performance plus it is computationally efficient. We do not
-argue that this is always the best choice and more sophisticated
+argue that this is always the best choice, and more sophisticated
 models can lead to even better results. Here the purpose of the
@@
 specific selection method. These benefits apply to a large family of
-different methods all involving a reference model in one way or the
+different methods, all involving a reference model in one way or the
 other. Some of these approaches have been present in the literature for some time
@@
 developed using a robust Bayesian modelling workflow, for instance, as
-outlined by \citet{gelman2013bayesian} and \citet{gabry2019visualization}.
+outlined by \citet{gelman2020bayesian} and \citet{gabry2019visualization}.
 
@@
 approach shows superior performance in minimal subset variable
-selection compared to alternative methods whether or not these methods
+selection compared to alternative methods, whether or not these methods
 make use of a reference model. That is, while the reference model is
-certainly one important aspect the projective prediction approach, it
+certainly one important aspect of the projective prediction approach, it
 is not the only reason for its superior performance.  Rather, by
@@
 distribution into the variable selection procedure (instead of just
-using point estimates) and using principled cross-validation method,
+using point estimates) and using a principled cross-validation method,
 projective predictions combine several desirable variables into a
@@
 strongly recommend using projective predictions for minimal subset
- variable selection if possible and feasible. 
+ variable selection if possible and computationally feasible. 
  However, if this is not an option in a given
@@
 variable selection. We tested a simple iterative version of projpred,
-with mixed results and the methods specifically designed for complete
+with mixed results, and the methods specifically designed for complete
 variable selection (especially loc.fdr) performed better in our
@@
 and the \texttt{tidyverse} framework \citep{Rtidyverse}.
-The code to run all
-the experiments is available on GitHub
-(\url{https://github.com/fpavone/ref-approach-paper}).
+% The code to run all
+% the experiments is available on GitHub
+% (\url{https://github.com/fpavone/ref-approach-paper}).
 
@@
 variables for which we want to obtain a minimally relevant
-subset. Than, the main steps are the following:
+subset. Then, the main steps are the following:
 \begin{enumerate}
@@
   model size. This step is not strictly necessary but reduces the number
-  of submodels to considered in the following steps and thus reduces computation time.
+  of submodels considered in the following steps and thus reduces computation time.
 \item For each submodel $\pi$ selected in Step 2, project each of the reference model's posterior draws $\boldsymbol{\theta}_{*}^{s}$ as follows:
@@
 \item For each submodel (size), test the predictive performance for a chosen predictive utility score, for example, via cross-validation.
-Fast cross-validation can be performed using using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
+Fast cross-validation can be performed using approximate leave-one-out cross-validation via Pareto-smoothed importance-sampling
 \citep[PSIS-LOO-CV; ][]{paper:psis_loo}.
@@
 \citep{paper:original_proj}. For further details on the projective
-prediction workflow and implementation see the paper by \citet{paper:projpred}.
+prediction workflow and implementation, see the paper by \citet{paper:projpred}.
 

### 2022-01-19 paper/ref_approach.tex
more edits

@@
 Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model, leading to projection predictive variable selection approach.
-Alternatively, reference models may also be used in an ad-hoc manner in combination with common variable selection methods.
+We analyse how much the great performance of the projection predictive variable is due to the use of reference model and show that other variable selection methods can also be greatly improved by using the reference model as target instead of the original data.
 In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative variable selection methods with and without reference models.
 Our results indicate that the use of reference models generally translates into better and more stable variable selection.
-Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods, independently of whether or not they use reference models.
+  %Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods, independently of whether or not they use reference models.
 \end{abstract}
@@
 model including all variables.
-%
+
 We assume all models are wrong, but we assume we have constructed a
@@
 
-Reference models have been also used in non-Bayesian contexts, in which
+Reference models have been also used in non-Bayesian context.
 \cite{harrell2015regression} describes them as full models that can be
-thought of as a ``gold standard'' (for a given application).  For
-example, \cite{faraggi2001understanding} deal with the necessity of
+thought of as a ``gold standard'' (for a given application).
+\cite{faraggi2001understanding} deal with the necessity of
 identifying interpretable risk groups in the context of survival data
@@
 \fede{All these methods can be framed into the family of reference model approaches. 
-The common denominator is the use of the reference model posterior predictive information 
+The common denominator is the use of the reference model predictive information 
 instead of simply observed data to guide the selection.}
@@
 models offer a powerful approach to improving variable selection, as we
-will demonstrate in the present paper. \\
+will demonstrate in the present paper.
+
 \fede{The goal of our work is to study the impact of reference model approaches
@@
 variable selection example using body fat data by \citet{johnson1996fitting}.
+The same data was used illustrate the variable selection with classic stepwise backward regression by \citet{paper:bodyfat}.
 We compare the projective prediction approach (\emph{projpred},
@@
 uses Bayesian inference and steplm uses maximum likelihood estimation.
-However, as we show in the present paper, one of the primary difference 
-with respect to quality of the variable selection is indeed whether or 
-not a reference model is applied, and the performance of steplm can
-also be improved by using a reference model.
+%
+To separate the effect of using a reference model, we show that
+performance of other variable selection methods, including steplm, can
+also be improved by using reference models.
+% However, as we show in the present paper, one of the primary difference 
+% with respect to quality of the variable selection is indeed whether or 
+% not a reference model is applied, and the performance of steplm can
+% also be improved by using a reference model.
 
@@
 It is known that as the number of parameters in the model increases, the MLE
-estimator is dominated by shrunk estimators 
+estimator is dominated by shrinkage estimators 
 \citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
@@
 variables over the number of selected variables) of the selected submodel,
-averaged after 100 data simulations. Use of a reference model reduces RMSE of the selected model for all the methods. projpred has superior FDR and the
-smallest RMSE. Using a reference model improves also FDR of steplm significantly. Stepwise
-Bayesian linear regression is better than steplm when comparing both methods with
-and without a reference model, respectively. However, the minimal subset variable
-selection of the Bayesian linear regression is still less reliable than projpred.
+averaged after 100 data simulations.
+Use of a reference models greatly reduces the overfitting in the selection process, and thus produces much lower test set RMSE of the selected model for all the methods.
+projpred has the lowest FDR and RMSE.
+Using a reference model improves also FDR of steplm stepwise Bayesian liena rgegression significantly.
 
@@
 top-left corner of each plot, as it implies the lowest false discovery
-rate and the highest sensitivity. We see that regardless of the
-applied selection method, the use of a reference model improves the
+rate and the highest sensitivity. We see that for all tested
+selection methods, the use of a reference model improves the
 selection performance, as it reduces the false discovery rate (shifting
-to the left) or increases the sensitivity (shifting upwards). In
+to the left) and increases the sensitivity (shifting upwards). In
 accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
@@
 correlation level are small. It performs better than the iterative lasso 
-selection in any of the simulated scenarios. Tuning $\alpha$ might lead to improved
-selection, yet the main source of poor performance could well be the
-miscalibration of the uncertainty of the predictive utility score for
-misspecified models with cross-validation \citep{bengio2004no}.
+selection in all simulated scenarios.
+%
+For all these variable selection methods, tuning the corresponding
+method parameters could affect the balance between FDR and
+sensitivity, and thus the methods could made to produce more similar
+results. This was not done in this experiment, as the main point was
+to show that all methods can perform better with a reference model.
+% Tuning $\alpha$ might lead to improved selection, yet the main
+% source of poor performance could well be the miscalibration of the
+% uncertainty of the predictive utility score for misspecified models
+% with cross-validation \citep{Sivula+etal:2020:loo_uncertainty}.
 
@@
 selection of each variable as a Bernoulli process. Further details are
-available in \cite{paper:stability}. The reference model helps in
-improving the stability of the selection: again, the benefits are
-bigger when the problem is more difficult (small $n$ and $\rho$). In
+available in \cite{paper:stability}. Use of a reference model 
+improves the stability of all selection methods. The improvement is 
+larger when the problem is more difficult (small $n$ and $\rho$). In
 addition, we observe less uncertainty in the stability estimates for

### 2022-02-13 reviews/rebuttal.tex
fixed incoherences between rebuttal and paper

@@
 \vspace{0.5\baselineskip}
-\textit{In general, there is no restriction on the type of model the reference models 
-	should be and a sensible reference model does not even need to be Bayesian.
+\textit{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
 	However, Bayesian methods can help in some of those situations
@@
 best practices for constructing the reference model is important, as
-using a garbage reference model can only lead to selecting similarly
-garbage smaller model. If the reference model is considered to have
-useful predictions then the smaller models selected will also have
+using a bad reference model can only lead to selecting a similarly
+bad smaller model. If the reference model is considered to have
+useful predictions, then the smaller models selected will also have
 similar useful predictions.

### 2022-02-13 paper/ref_approach.tex
fixed incoherences between rebuttal and paper

@@
 
-\fede{The goal of our work is to study the impact of reference model approaches
-disentangling the benefit of the usage of a reference model from the specific selection algorithm.
-Specifically, we:}
-% The main contributions of our work are:
-\fede
-{\begin{itemize}
-\item disentangle the action of the reference model through a simple and intuitive way to combine any variable selection method with the reference model approach.
-This allows us to build up a comparison independent of the specific variable selection method;
-% We show a simple and intuitive way to combine any variable selection method with the reference model approach.
-\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection and assessing the quality of the selection;
-\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in variable selection.
-\end{itemize}
-}
+\fede{The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+In particular, we:
+\begin{itemize}
+	\item propose a simple and intuitive approach to combine any variable selection method with the reference model approach.
+This allows us to investigate the benefit of using reference models independent of the specific variable selection method;
+	\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
+	\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
+\end{itemize}}
 
@@
 
-\fede{In general, there is not restriction on the type of model the reference models 
-should be and a sensible reference model does not need to be Bayesian.
+\fede{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
 However, Bayesian methods can help in some of those situations
@@
 by linear regression models.
-However, more complex data can arise from applications, for example including hierarchical structures.
-In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the posterior distribution.}
+However, more complex data can arise in practice, for example, including hierarchical structures.
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}
 
@@
 \subsection{Reference model's effect and the projection predictive approach}
-\fede{The previous experiments allowed us to study and disantangle the effect of a reference model in variable selection, specifically in the minimal subset selection case.
-  %
-The simulation study based on artificial data of Section \ref{minimal-simulated} shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the method applied.
+\fede{The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
+The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied.
 These results are confirmed also in the real word data example with the body fat dataset.
-The stepwise selection achieves far better selection with the reference model approach (see Figure \ref{fig:bodyfat_step_refvsdata} and Table \ref{tab:step_refvsdata}).
+The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4).
 However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.

### 2022-02-14 reviews/rebuttal.tex
minor cleaning of the rebuttal

@@
 The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}.
-In this paper the point is not the Bayesian workflow, but to analyse given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model.
+As such, the aim of this paper is not to show how to build good reference models.
+Instead, we study the importance of reference models in submodel inference using either the decision theoretically justified version or other algorithms that we show can also be improved by replacing the data with filtered prediction from the reference model.
 
-The reference models used in the examples are using widely accepted weakly informative priors and there are no prior sensitivity issues for them.
+The reference models applied in the examples are using widely accepted weakly informative priors and there are no prior sensitivity issues for them.
 As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
@@
 For details, see \citet{paper:projpred}.
-The predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score.
-The obtained lpd samples form a distribution than can be used to estimate said probability.
+The predictive performance is evaluated via cross-validation both for the reference model and the submodels using the expected log-predictive density (elpd) score.
+The obtained elpd samples form a distribution than can be used to estimate said probability.
 We have added following sentence:
-TODO: is the sentence below enough?
+TODO: is the sentence below enough? Paul: Please note my change to the below sentence.
 \end{reply}
@@
 \textit{
-\ldots and the probability is computed from the normal approximation for the uncertainty in the cross-validation performance comparison \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
+\ldots and the probability is computed from a normal approximation of the uncertainty in the cross-validation performance comparison using the mean and standard error of the elpd difference between reference and submodel \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
 }
@@
 We have added a following sentence to the paper.
-TODO: would this be enough?
+TODO: would this be enough? Paul: please note that I changed the sentence below
 \end{reply}
@@
 \textit{
-We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and worth a further research.
+We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and may be worth further research.
 }
@@
 \fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
+Paul: why is this still in red?
 \end{reply}

### 2022-02-16 reviews/rebuttal.tex
minor edits

@@
  \newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent
-	{\begin{sf}\textbf{Reviewer~Point~\thepoint} } ---~#1\par \end{sf}}
+   \begin{sf}
+     {\textbf{Reviewer~Point~\thepoint} } ---~#1\par
+   \end{sf}}
 
@@
 Reviewer 3 gave precious comments on how to clarify the real intentions of our work, which is the study of the effect of reference models when used to guide the selection process, regardless of the selection method.
-We followed the suggestions and we believe that the current version reduces the possibility of misunderstandings.
+We followed the suggestions, and we believe that the current version reduces the possibility of misunderstandings.
 \end{reply}
@@
 The goodness of a reference model comes from its predictive ability which should be assessed via proper validation methods.
-[...] In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
+[...] In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
 }
@@
 
-The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}.
+The sensitivity of the Bayesian models to choice of priors is well studied, and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}.
 As such, the aim of this paper is not to show how to build good reference models.
@@
 
-The reference models applied in the examples are using widely accepted weakly informative priors and there are no prior sensitivity issues for them.
+The reference models applied in the examples are using widely accepted weakly informative priors, and there are no prior sensitivity issues for them.
 As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
@@
 This is an interesting question.
-The way we see it is that MLE tends to be more unstable than comparable Bayesian approaches, as the latter get improved stability both from integration over the parameter space (instead of using only a point estimate) and can further be improved by using even just weakly informative priors (rather than improper flat priors).
+The way we see it is that MLE tends to be more unstable than comparable Bayesian approaches, as the latter get improved stability both from integration over the parameter space (instead of using only a point estimate), and can further be improved by using even just weakly informative priors (rather than improper flat priors).
 We have added references that discuss the merits of Bayesian approaches compared to MLE.
@@
 We assume that all models are wrong.
-Analysing model misspecification is well studied in the Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}.
+Analysing model misspecification is well studied in the Bayesian literature, and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}.
 The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}.
@@
 Such a predictor is then excluded or not, by comparing the predictive performance of the reduced model without this predictor and the not-reduced model including the predictor.
-In such a way, the posterior $p$-values matter only in terms of their ordering and not in terms of their magnitude.
+In such a way, the posterior $p$-values matter only in terms of their ordering, and not in terms of their magnitude.
 \end{reply}
@@
 \begin{reply}
-We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure and we wanted our results to be comparable to their results.
+We used AIC because \citet{heinze2018variable} used AIC in the steplm procedure, and we wanted our results to be comparable to their results.
 The goal of our paper was not to compare all possible information criteria but to investigate whether using reference models helps variable selection methods.
@@
 We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account.
-However, since the projection predictive approach was not the main point of this paper, we cannot reasonably address it here and leave it for future research.
+However, since the projection predictive approach was not the main point of this paper, we cannot reasonably address it here, and leave it for future research.
 We have added a following sentence to the paper.
@@
 The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4).
-However, the projection predictive approach remains the best method in any of the experiment we run and on all the performance indexes we measured.
+However, the projection predictive approach remains the best method in any of the experiments we run and on all the performance indexes we measured.
 Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.

### 2022-02-16 paper/ref_approach.tex
minor edits

@@
 
-\fede{In general, there is no restriction on the type of model the reference models should be and a sensible reference model does not even need to be Bayesian necessarily.
+\fede{In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
 However, Bayesian methods can help in some of those situations

### 2022-02-21 reviews/rebuttal.tex
final version for revision

@@
 We believe that in the first version of the paper, the purpose of our work was not clear and subject to possible misunderstandings.
-Our contribution takes clear inspiration from the work of \citet{paper:projpred}, but aims at a different goal: We studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm.
-	We now make our goals explicit already in Section 1, where we now write
+Our contribution takes clear inspiration from the work of \citet{paper:projpred}, but aims at a different goal: we studied the impact of using a reference model in general, disentangled from the specific variable selection algorithm.
+	We now make our goals explicit already in Section 1, where we now write:
 
@@
 We have added following sentence:
-TODO: is the sentence below enough? Paul: Please note my change to the below sentence.
-\end{reply}
 
+\vspace{0.5\baselineskip}
 \textit{
@@
 }
+
+\end{reply}
 
@@
 We have added a following sentence to the paper.
-TODO: would this be enough? Paul: please note that I changed the sentence below
-\end{reply}
 
@@
 In any case we believe that the benefits of a more stable and efficient selection overcome the cost of fitting a reference model.
-\fede{We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.}
-Paul: why is this still in red?
+We added a new table (Table 3) reporting the computational time for the bodyf fat example, showing how the burden is divided between the fit of the reference model and the rest of the selection procedure.
 \end{reply}

### 2022-02-21 paper/ref_approach.tex
final version for revision

@@
 
-\newcommand{\fede}[1]{\textcolor{red}{#1}}
+% \newcommand{\fede}[1]{\textcolor{red}{#1}}
 
@@
 
-\fede{All these methods can be framed into the family of reference model approaches. 
+All these methods can be framed into the family of reference model approaches. 
 The common denominator is the use of the reference model predictive information 
-instead of simply observed data to guide the selection.}
+instead of simply observed data to guide the selection.
 Whatever the terminology or applied statistical framework, reference
@@
 
-\fede{The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
 In particular, we:
@@
 	\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
-\end{itemize}}
+\end{itemize}
 
@@
 clear difference in the number of selected variables. This can be explained by high
-correlation between the variablesm and different combinations can
+correlation between the variables and different combinations can
 provide similar predictive accuracy.
@@
 not perfectly resemble the true data generating process. 
-\fede{Clearly, the reference model approach requires a sensible model. 
+Clearly, the reference model approach requires a sensible model. 
 The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. 
 The goodness of a reference model comes from its predictive ability which should be 
-assessed via proper validation methods.} Our analyses indicate that the substantial 
+assessed via proper validation methods. Our analyses indicate that the substantial 
 reduction of variance attributable to noise is usually more important than small potential
 bias due to model misspecification.
-\fede{When the goal is ranking the variables for importance to
+When the goal is ranking the variables for importance to
 perform variable selection, it is known that large variance is
-generally more harmful than small bias \citep{piironen2017comparison}.}
-
-\fede{In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
+generally more harmful than small bias \citep{piironen2017comparison}.
+
+In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
 However, Bayesian methods can help in some of those situations
@@
 However, more complex data can arise in practice, for example, including hierarchical structures.
-In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.}
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.
 
@@
 \citep{bair2006prediction,piironen2018}, can produce useful reference
-models \citep{paper:projpred}. \fede{As an example, Table \ref{tab:computational_time} reports
+models \citep{paper:projpred}. As an example, Table \ref{tab:computational_time} reports
 the computational time for the body fat data example of Section \ref{bodyfat-1}. 
@@
 time consuming operation is to fit the reference model. The burden of it depends clearly
-on the specific application and type of model used.}
+on the specific application and type of model used.
 
@@
 which are not in the minimal subset are highly correlated with variables already in
-the minimal subset. \fede{Such nature of the minimal subset makes the solution
+the minimal subset. Such nature of the minimal subset makes the solution
 not unique, except in the particular case of completely orthogonal predictors. 
@@
 However, it makes it difficult to define a proper
-concept of stability of the selection.} 
+concept of stability of the selection.
 We will return to a problem of finding all
@@
 projpred has the lowest FDR and RMSE.
-Using a reference model improves also FDR of steplm stepwise Bayesian liena rgegression significantly.
+Using a reference model improves also FDR of steplm stepwise Bayesian linear regression significantly.
 
@@
 \subsection{Reference model's effect and the projection predictive approach}
-\fede{The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
+The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
 The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied.
@@
 Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
-Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.}
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
 
@@
 where $i$ indexes the submodel size, ``best'' stands for the best predictive explored submodel
-at the considered iteration, and the probability is computed from the normal approximation for the uncertainty in the cross-validation performance comparison \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
+at the considered iteration, and the probability is computed from a normal approximation of the uncertainty in the cross-validation performance comparison using the mean and standard error of the elpd difference between reference and submodel \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
 The algorithm terminates when the empty model (only intercept) satisfies
@@
 number of observations or not very predictive variables.
-We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and worth a further research.
+We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and may be worth further research.
 In our experiments, we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package, that is, $\alpha=0.16$. \fede{The choice of $\alpha$ to determine 
+\texttt{R}-package, that is, $\alpha=0.16$. The choice of $\alpha$ to determine 
 the submodel size is discussed in \cite{paper:projpred}. One possible way to proceed, 
@@
 that the submodel predictive score is at most at one standard deviation distance 
-from the best submodel predictive score.}
+from the best submodel predictive score.
 

### 2022-02-21 paper/ref_approach_blinded.tex
final version for revision

@@
             pdftitle={The reference model approach in variable selection},
-            %pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
+            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
             pdfkeywords={keywords},
@@
 
+% \newcommand{\fede}[1]{\textcolor{red}{#1}}
+
 \title{Using reference models in variable selection 
@@
 
-%    \author{
+    %\author{
    %   Federico Pavone\footnote{Department of Computer Science, Aalto University, Finland.}\, \footnote{Department of Decision Sciences, Bocconi University, Italy.}%$\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy.
@@
 A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism.
-As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability leading to improved model selection performance.
-Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model leading to projection predictive variable selection approach.
-Alternatively, reference models may also be used in an ad-hoc manner in combination with common variable selection methods.
+As a result, using the reference model predictions in the model selection procedure reduces the variability and improves stability, leading to improved model selection performance.
+Assuming that a Bayesian reference model describes the true distribution of future data well, the theoretically preferred usage of the reference model is to project its predictive distribution to a reduced model, leading to projection predictive variable selection approach.
+We analyse how much the great performance of the projection predictive variable is due to the use of reference model and show that other variable selection methods can also be greatly improved by using the reference model as target instead of the original data.
 In several numerical experiments, we investigate the performance of the projective prediction approach as well as alternative variable selection methods with and without reference models.
 Our results indicate that the use of reference models generally translates into better and more stable variable selection.
-Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods independently of whether or not they use reference models.
+  %Additionally, we demonstrate that the projection predictive approach shows superior performance as compared to alternative variable selection methods, independently of whether or not they use reference models.
 \end{abstract}
@@
 of a reference model, which can be, for example, a full-encompassing
-model including all variables.  The main assumption under any
-reference model approach is that we operate in an
-$\mathcal{M}$-\textit{complete} framework
-\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
-constructed a model which reflects our beliefs about
-the future data in the best possible way and which has passed model checking and criticism
-\citep[see, e.g.][]{gelman2013bayesian,gabry2019visualization}.  The reference model approach
-has been used in Bayesian statistics at least since the seminal
-work of \citet{paper:reference_lindley}. For more historical
-references, see \citet{vehtari2012survey} and
-\citet{paper:model_selection}, and for most recent methodological
-developments see \citet{paper:projpred}.
-
-Reference models have been also used in non-Bayesian contexts, in which
+model including all variables.
+
+We assume all models are wrong, but we assume we have constructed a
+model which reflects our beliefs about the future data in the best
+possible way and which has passed model checking and criticism
+\citep{gelman2020bayesian,gabry2019visualization}.  Using the usual
+best practices for constructing the reference model is important, as
+using a bad reference model can only lead to selecting a similarly
+bad smaller model. If the reference model is considered to have
+useful predictions, then the smaller models selected will also have
+similar useful predictions.
+%
+The reference model approach has been used in Bayesian statistics in
+some form at least since the seminal work of
+\citet{paper:reference_lindley}. For more historical references, see
+\citet{vehtari2012survey} and \citet{paper:model_selection}, and for
+most recent methodological developments see \citet{paper:projpred}.
+%
+Examples of useful reference models can be found for example for
+small-$n$-large-$p$ regression and logistic regression by
+\citet{piironen2017comparison} (with spike-and-slab prior),
+\citet{Piironen:2015:Stan_projection} (with horseshoe prior), and
+\citet{paper:projpred} (with iterative supervised principal
+components), for generalized linear and additive multilevel models by
+\citet{Catalina:2020:GAMM_projection}, for regression models with
+non-exponential family observation models by
+\citet{Catalina+etal:2021:latent_projection}, and for generic
+multivariate non-linear regression with higher order interactions by
+\citet{Piironen:2016:GPprojection}.
+
+Reference models have been also used in non-Bayesian context.
 \cite{harrell2015regression} describes them as full models that can be
-thought of as a ``gold standard'' (for a given application).  For
-example, \cite{faraggi2001understanding} deal with the necessity of
+thought of as a ``gold standard'' (for a given application).
+\cite{faraggi2001understanding} deal with the necessity of
 identifying interpretable risk groups in the context of survival data
@@
 reference model instead of the observed responses $y$.
+
+All these methods can be framed into the family of reference model approaches. 
+The common denominator is the use of the reference model predictive information 
+instead of simply observed data to guide the selection.
 Whatever the terminology or applied statistical framework, reference
-models offer a powerful approach to improving variable selection as we
+models offer a powerful approach to improving variable selection, as we
 will demonstrate in the present paper.
 
-The main contributions of our work are:
-
+The goal of the present paper is to study the impact of reference model approaches by disentangling the benefit of using reference models per se from the benefit of specific variable selection algorithms.
+In particular, we:
 \begin{itemize}
-\item We show a simple and intuitive way to combine any variable selection method with the reference model approach.
-\item We perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset feature selection.
-\item We provide evidence supporting the projection predictive approach as a principled way to use reference models.
+	\item propose a simple and intuitive approach to combine any variable selection method with the reference model approach.
+This allows us to investigate the benefit of using reference models independent of the specific variable selection method;
+	\item perform extensive numerical experiments to compare variable selection methods with or without using a reference model, both for complete and minimal subset variable selection and assessing the quality of the selection;
+	\item provide evidence supporting, in particular, the projection predictive approach as a principled way to use reference models in minimal subset variable selection.
 \end{itemize}
@@
 uses Bayesian inference and steplm uses maximum likelihood estimation.
-However, as we show in the present paper, one of the primary difference 
-with respect to quality of the variable selection is indeed whether or 
-not a reference model is applied.
+%
+To separate the effect of using a reference model, we show that
+performance of other variable selection methods, including steplm, can
+also be improved by using reference models.
+% However, as we show in the present paper, one of the primary difference 
+% with respect to quality of the variable selection is indeed whether or 
+% not a reference model is applied, and the performance of steplm can
+% also be improved by using a reference model.
 
@@
 stable selection process. This holds even if the reference model does
-not perfectly resemble the true data generating process. Moreover, our
-analyses indicate that the substantial reduction of variance
-attributable to noise is usually more important than small potential
-bias due to model misspecification.  We argue that, regardless of how
+not perfectly resemble the true data generating process. 
+Clearly, the reference model approach requires a sensible model. 
+The construction of such a model should follow proper modelling workflow \citep[see, e.g.][]{gelman2020bayesian}. Better predictive models imply better selection results. 
+The goodness of a reference model comes from its predictive ability which should be 
+assessed via proper validation methods. Our analyses indicate that the substantial 
+reduction of variance attributable to noise is usually more important than small potential
+bias due to model misspecification.
+When the goal is ranking the variables for importance to
+perform variable selection, it is known that large variance is
+generally more harmful than small bias \citep{piironen2017comparison}.
+
+In general, there is no restriction on the type of model the reference models should be, and a sensible reference model does not even need to be Bayesian necessarily.
+However, Bayesian methods can help in some of those situations
+where MLE procedures struggle. 
+It is known that as the number of parameters in the model increases, the MLE
+estimator is dominated by shrinkage estimators 
+\citep{stein1956inadmissibility, stein1961estimation, parmigiani2009decision, efron2011tweedie}.
+The use of a prior in Bayesian inference automatically incorporates 
+some kind of shrinkage in the Bayesian estimator under a given loss function \citep[see, e.g.][]{rockova2012hierarchical}. 
+For the sake of our study, we rely on simple data structure which can be well described 
+by linear regression models.
+However, more complex data can arise in practice, for example, including hierarchical structures.
+In these cases, MLE inference tends to become cumbersome, whereas the Bayesian framework provides a natural way to convey uncertainties and make inference through the joint posterior distribution of all parameters.
+
+We argue that, regardless of how
 the reference model is set up and used in the inference procedure, it
@@
 as for example the supervised principal components
-\citep{bair2006prediction,piironen2018} can produce useful reference
-models.
+\citep{bair2006prediction,piironen2018}, can produce useful reference
+models \citep{paper:projpred}. As an example, Table \ref{tab:computational_time} reports
+the computational time for the body fat data example of Section \ref{bodyfat-1}. 
+For reference model approaches, i.e. projpred and ref+step.lm, the main
+time consuming operation is to fit the reference model. The burden of it depends clearly
+on the specific application and type of model used.
+
+\begin{table}[tp]
+	\footnotesize
+	\centering
+	\begin{tabular}{l|cc|ccc}
+		Data & Reference model & Search path & projpred & step.lm & ref + step.lm \\
+		\hline
+		body fat & 38 & 15 & 53 &  &  \\
+		  &  & 0.08 &  & 0.08 &  \\
+		  & 38 & 0.08 &  &  & 38 \\
+		\hline 
+		+ noisy variables & 170 & 78 & 247 &  &  \\
+		  & & 12 & & 12 & \\
+		  & 170 & 12 & & & 182
+
+	\end{tabular}
+	\caption{Computational time (in seconds) of body fat example of Section \ref{bodyfat-1}.
+		The reported times for each each method on the three last columns are sums of the time to fit the reference model (second column) and
+		to explore the search path (third column).}
+	\label{tab:computational_time}
+\end{table}
 
@@
 which are not in the minimal subset are highly correlated with variables already in
-the minimal subset. We will return to a problem of finding all
+the minimal subset. Such nature of the minimal subset makes the solution
+not unique, except in the particular case of completely orthogonal predictors. 
+The non-uniqueness of the solution is not a problem per se, as different samples of the data
+are expected to give possible different minimal subsets but with same predictive power. 
+However, it makes it difficult to define a proper
+concept of stability of the selection.
+We will return to a problem of finding all
 the variables with some predictive power in Section~\ref{complete-selection}.
-
-\subsection{Simulation study 1}
+%
+% The code to run all
+% the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
+
+\subsection{Simulation study 1}\label{minimal-simulated}
 
@@
 variables over the number of selected variables) of the selected submodel,
-averaged after 100 data simulations. We see that projpred has superior FDR and the
-smallest RMSE. Using a reference model improves steplm significantly,
-but the minimal subset variable selection stays unreliable. Stepwise
-Bayesian linear regression is better than steplm when comparing both methods with
-and without a reference model, respectively. However, the minimal subset variable
-selection of the Bayesian linear regression is still less reliable than projpred.
+averaged after 100 data simulations.
+Use of a reference models greatly reduces the overfitting in the selection process, and thus produces much lower test set RMSE of the selected model for all the methods.
+projpred has the lowest FDR and RMSE.
+Using a reference model improves also FDR of steplm stepwise Bayesian liena rgegression significantly.
 
@@
 
+\subsection{Reference model's effect and the projection predictive approach}
+The previous experiments allowed us to study the impact of using reference models in variable selection and to disentangle their influence from that of the actual variable selection method, specifically in the minimal subset selection case.
+The simulation study based on artificial data of Section 3.1 shows clear improvements in terms of predictive performance of the selected model and false discovery rate when the selection is based on a reference model, regardless of the actual variable selection method applied.
+These results are confirmed also in the real word data example with the body fat dataset.
+The stepwise selection achieves far better selection when coupled with the reference model approach (see Figure 5 and Table 4).
+However, the projection predictive approach remains the best method in any of the experiments we run and on all the performance indexes we measured.
+Although we designed a reference model approach for general selection method, the projection predictive approach is a principled and validated way to do the selection.
+Indeed, the purpose of the former is only for fair comparisons in our study rather than a ready-to-use selection method.
+
 \section{Complete variable selection}\label{comparison-complete-subset}
@@
 means a more stable selection. 
+%
+% The code to run all
+% the experiments is available on GitHub\footnote{\url{https://github.com/fpavone/ref-approach-paper}}.
 
@@
 \end{equation}
-where $i$ indexes the submodel size and ``best'' stands for the best predictive explored submodel
-at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
+where $i$ indexes the submodel size, ``best'' stands for the best predictive explored submodel
+at the considered iteration, and the probability is computed from a normal approximation of the uncertainty in the cross-validation performance comparison using the mean and standard error of the elpd difference between reference and submodel \citep{Vehtari+etal:2017:practical,paper:projpred,Sivula+etal:2020:loo_uncertainty}.
+The algorithm terminates when the empty model (only intercept) satisfies
 the stopping rule (see Algorithm \ref{alg:iterated_proj}).
@@
 number of observations or not very predictive variables.
-In our experiments we chose the default value used in the \texttt{projpred} 
-\texttt{R}-package, that is, $\alpha=0.16$.
+We have used the stopping rule recommended by \citet{paper:projpred} for the minimal subset selection, but other stopping rules would be possible in the iterative case and may be worth further research.
+In our experiments, we chose the default value used in the \texttt{projpred} 
+\texttt{R}-package, that is, $\alpha=0.16$. The choice of $\alpha$ to determine 
+the submodel size is discussed in \cite{paper:projpred}. One possible way to proceed, 
+but just as rule of thumb, is to choose $\alpha = 0.16$, which correspond to requiring 
+that the submodel predictive score is at most at one standard deviation distance 
+from the best submodel predictive score.
 
@@
 In the experiments shown in the next sections, we include an additional iterative
-method which we refer to as `iterative lasso'. It consists of the same iterative
-algorithm as iterative projpred expect for not using any reference model, but
+method, which we refer to as `iterative lasso'. It consists of the same iterative
+algorithm as iterative projpred except for not using any reference model, but
 the lasso method for variable selection, instead.
